### 2015-10-04 state_abstraction.tex
adding outline doc from h2r talk

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\input{../p.tex}
\title{Approximating the Optimal State Abstraction}
\author{}
\date{}                                           % Activate to display a given date or no date

% --- Note Commands ---
\newcommand\davenote[1]{\textcolor{blue}{Dave: #1}}

\begin{document}
\maketitle

% --- ABSTRACT ---
\begin{abstract}

\end{abstract}

% --- SECTION: Outline of H2R Talk ---
\newpage
\section{Outline of H2R Talk}

\subsection{The Problem}
\begin{mdframed}
\vspace{1mm}
Goal: planning and learning in large\footnote{TOTALLY MASSIVE} state spaces. \\
Proposed Strategy: abstract the problem to simplify.
\end{mdframed}

\vspace{4mm}
\elem{For example:}
In this lab, we like OO-MDPs a lot. There are other possible representations one might consider to collapse our representation of the real world. Objects seem like a reasonable choice given how object-oriented the human experience seems to be.

%For vision, other compressions make sense.
%For other sensor channels, different compressions make sense.
%For different worlds, different compressions make sense.

The main point is that compression helps, but we don't totally know how effective these things could be, and we don't know exactly which compressions to choose. In some sense, we're just picking compressions based on what we think might work.

Some questions to consider:
\begin{itemize}
\item Q: Is there a unified definition of state abstraction?
\item Q: How do different abstractions relate to one another?
\item Q: How can we select among abstraction schemes?
\item Q: How does the solution to the abstracted MDP relate to the original MDP?
\item Q: How should we be compressing? Does it change from domain to domain, task to task?
\item Q: Can we learn these abstractions? How much data do they require?
\end{itemize}

Immediate question: How should we compress? Any ideas? Does it change depending on the domain? The task? Are there other things we can use compression for?

So it turns out there have been a huge number of attempts at this:
\begin{itemize}
\item Dynamic Programming Aggregation
\item Stochastic DP with factored representations
\item Model reduction techniques
\item Model minimization...
\item Abstraction Selection...
\item State Abstraction Selection from...
\item Proto-value functions
\item Selecting the state-representation in reinforcement learning
\item Optimal regret bounds for selecting the...
\item RL with selective perception
\item SMDP homomorphisms: an algebraic approach.
\item Selecting near optimal approximate state...
\end{itemize}

% - Subsection: Unified Theory Paper -
\midline
\subsection{Unified Theory Paper}
Michael, Tom Walsh, Lihong Li wrote a paper called ``Towards a Unified Theory of State Abstraction for MDPs''~\cite{li2006towards} that surveys these approaches, and puts them into a single framework.

The high level is that there are roughly 5 types of abstractions:
\begin{enumerate}
% Model Irrelevance
\item Model-irrelevance: $\phi_{\text{model}}$ :
\begin{multline*}
\forall_s \forall_a \phi_{\text{model}}(s_1) = \phi_{\text{model}}(s_2) \rightarrow \mathcal{R}(s_1,a) = \mathcal{R}(s_2,a)\ \wedge \\
\sum_{s' \in \phi_{\text{model}}^{-1}(s)} \Pr(s' \mid s_1, a) = \sum_{s' \in \phi_{\text{model}}^{-1}(s)} \Pr(s' \mid s_2, a)
\end{multline*}

% Q^\pi Irrelevance
\item $Q^\pi$-irrelevance: $\phi_{Q^\pi}$ :
\begin{equation*}
\forall_\pi \phi_{Q^\pi}(s_1) = \phi_{Q^\pi}(s_2) \rightarrow  \forall_a Q^\pi(s_1,a) = Q^\pi(s_2,a)
\end{equation*}

% Q^* Irrelevance
\item $Q^*$-irrelevance: $\phi_{Q^*}$ :
\begin{equation*}
\phi_Q^*(s_1) = \phi_Q^*(s_2) \rightarrow \forall_a  Q^*(s_1,a) = Q^*(s_2,a)
\end{equation*}

% a^* Irrelevance
\item $a^*$-irrelevance: $\phi_{a^*}$:
\begin{equation*}
\phi_{a^*}(s_1) = \phi_a^*(s_2) \rightarrow Q^*(s_1,a^*) = \max_a Q^*(s_1,a) = \max_a Q^*(s_2,a) = Q^*(s_2, a)
\end{equation*}

% \pi^* Irrelevance
\item $\pi^*$-irrelevance: $\phi_{\pi^*}$:
\begin{equation*}
\phi_{\pi^*}(s_1) = \phi_{\pi^*}(s_2) \rightarrow \left( Q^*(s_1, a^*) = \max_a Q^*(s_1,a) \wedge Q^*(s_2,a^*) = \max_a Q^*(s_2,a) \right)
\end{equation*}

\end{enumerate}

One note: I haven't thought about this too much, but I'm pretty sure that throwing in abstracted actions like Options fits into this framework neatly -- suppose we're in an SMDP and that an option is just an action. Then we can abstract the state space based on where subgoals are/aren't satisfied. Seems like the right sort of result.

Other results from the paper:

\thm{Theorem}{3}{With abstractions $\phi_{\text{model}}$, $\phi_{Q^\pi}$, $\phi_{Q^*}$, and $\phi_{a^*}$, the optimal abstract policy $\bar{\pi}^*$ is optimal in the ground MDP.}

\thm{Theorem}{4.1}{Q-Learning with abstractions $\phi_{\text{model}}$, $\phi_{Q^\pi}$, and $\phi_{Q^*}$, converges to the optimal state-action value function in the ground MDP}

\thm{Theorem}{4.2}{Q-Learning with abstraction $\phi_{a^*}$ does not necessarily converge.}

\thm{Theorem}{4.3}{Q-Learning with abstraction $\phi_{\pi^*}$ can converge to an action-value function whose greedy-policy is suboptimal in the ground MDP.}

In a follow up paper, they have a distribution on MDPs, sample some training MDPs to infer the optimal state abstraction, and use it to solve a test MDP from the same distribution.

\elem{Example time!}

First: Sample Complexity (e.g. PAC-MDP means $\epsilon-$optimalilty with polynomial Sample Complexity in the relevant parameters, w/ probability $1-\delta$).
Second: Grid example that goes from NxM to N.

Q: But what's the elephant in the room with all of this?
A: Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
A: Furthermore, we need to know something about the optimal behavior in advance!

\midline
\subsection{New Proposal}

An area I'm interested in investigating: lets relax this assumption of {\bf strict equality} and look at some notion of similarity/approximate equality, and then investigate what is preserved in the resulting policy.

This will let us back off and see what might be learned online in a lifelong reinforcement learning setting. That is, can investigate learning one of these $\phi$ functions online.

Tackles:
\begin{itemize}
\item Lifelong RL
\item Online learning
\item State abstraction
\item Macroaction/Option learning
\end{itemize}

% --- SECTION: Introduction ---
\newpage
\section{Introduction}

% --- SECTION: Conclusion ---
\newpage
\section{Conclusion}

% --- BIBLIOGRAPHY ---
\newpage
\bibliography{sca_bib}

\end{document}

### 2015-10-06 state_abstraction.tex
added notes from dave-ellis meeting from 10/6

@@
 
-% --- SECTION: Outline of H2R Talk ---
+% --- SECTION: Motivation ---
 \newpage
-\section{Outline of H2R Talk}
+\section{Background}
 
@@
 \elem{For example:}
-In this lab, we like OO-MDPs a lot.
+Historically, we'ved relied on OO-MDPs a lot.
 There are other possible representations one might consider to collapse our representation of the real world.
@@
 
-% - Subsection: Unified Theory Paper -
+% Subsection: Unified Theory Paper
 \midline
@@
 
-\elem{Example time!}
+% --- SECTION: Motivation ---
+\newpage
+\section{Motivation}
 
-First: Sample Complexity (e.g. PAC-MDP means $\epsilon-$optimalilty with polynomial Sample Complexity in the relevant parameters, w/ probability $1-\delta$).
-Second: Grid example that goes from NxM to N.
+% Subsection: Arbitrary reduction in Sample Complexity
+\subsection{Result 1: Arbitrary reduction in Sample Complexity}
+First: Grid example that goes from NxM to N, (always go up, no down action).
 
+\subsection{Result 2: With a perfect abstractor, consider the exploration problem}
+
+\subsection{Result 3: Collapsing on {\it just state variables} is insufficient to preserve any kind of optimality}
+
+\subsection{Elephant in the Room}
 Q: But what's the elephant in the room with all of this?
@@
 \midline
-\subsection{New Proposal}
 
-An area I'm interested in investigating: lets relax this assumption of {\bf strict equality} and look at some notion of similarity/approximate equality, and then investigate what is preserved in the resulting policy.
+% --- SECTION: New Proposal ---
+\newpage
+\section{New Proposal: Approximate Abstraction}
 
-This will let us back off and see what might be learned online in a lifelong reinforcement learning setting. That is, can investigate learning one of these $\phi$ functions online.
+For each of the following three cases:
+% Model Equivalence
+\begin{equation}
+ \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : T(s \mid s_i, a) = T(s \mid s_j, a)
+\end{equation}
 
-Tackles:
-\begin{itemize}
-\item Lifelong RL
-\item Online learning
-\item State abstraction
-\item Macroaction/Option learning
-\end{itemize}
+% Optimal Q Function Equivalence
+\begin{equation}
+ \phi(s_1) = \phi(s_2) \rightarrow \forall_a : Q^*(s_i, a) = Q^*(s_j, a)
+\end{equation}
 
-% --- SECTION: Introduction ---
+% Optimal action and value Equivalence
+\begin{equation}
+ \phi(s_1) = \phi(s_2) \rightarrow \argmax_a Q^*(s_i, a) = \argmax_a Q^*(s_j, a) \wedge \max_a Q^*(s_i, a) = \max_a Q^*(s_j, a)
+\end{equation}
+
+Relax the equality condition, instead consider the approximate case, e.g.:
+% Model Similarity
+\begin{equation}
+ \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : |T(s \mid s_i, a) - T(s \mid s_j, a)| \leq \epsilon
+\end{equation}
+
+\elem{The Question:} Can anything be said about the optimality of the policy $\pi_{\phi_{T,\epsilon}}$ in the ground MDP? Are we within some factor of $\epsilon$ away from being optimal?
+
+% --- SECTION: Temporal Abstraction ---
 \newpage
-\section{Introduction}
+\section{New Proposal: Temporal Abstraction}
+
+In light of Result 3, that state abstraction needs to be defined with respect to some sort of properties about actions, suppose a set of temporally extended actions are included in the action set.
+
+Now, abstractions become temporally extended.
+
+Should be some nice results there.
 
@@
 \section{Conclusion}
+
+Future Work:
+\begin{itemize}
+\item Learning $\phi$
+\item Connection to AMDPs (e.g. consider $\Omega : \langle S, A, R, T, \gamma \rangle \mapsto \langle S', A', R', T', \gamma' \rangle$
+\item Connection to teaching.
+\end{itemize}
 

### 2015-10-07 state_abstraction.tex
beep
updated section 2

@@
 \geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
-\input{../p.tex}
+\input{p.tex}
 \title{Approximating the Optimal State Abstraction}
@@
 
-% --- SECTION: Motivation ---
+% --- SECTION: Background ---
 \newpage
@@
 \elem{For example:}
-Historically, we'ved relied on OO-MDPs a lot.
+Historically, we've relied on OO-MDPs a lot.
 There are other possible representations one might consider to collapse our representation of the real world.
@@
 
-% Subsection: Arbitrary reduction in Sample Complexity
-\subsection{Result 1: Arbitrary reduction in Sample Complexity}
-First: Grid example that goes from NxM to N, (always go up, no down action).
+\elem{Basic Point:} State abstraction for planning, learning, possibly bandits could be EPIC.
 
-\subsection{Result 2: With a perfect abstractor, consider the exploration problem}
+% Subsection: Arbitrary reduction in Sample Complexity for a specific MDP.
+\subsection{Result 1: Arbitrary reduction in Sample Complexity for a particular MDP.}
 
-\subsection{Result 3: Collapsing on {\it just state variables} is insufficient to preserve any kind of optimality}
+% Subsection: More general SC reduction result.
+\subsection{Result 2: More general result about sample complexity reduction for MDPs of a certain type}
 
-\subsection{Elephant in the Room}
-Q: But what's the elephant in the room with all of this?
-A: Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
-A: Furthermore, we need to know something about the optimal behavior in advance!
+Q: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.
+
+% Maybe something about exploration.
+
+% Subsection: Things you should not compress on.
+\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it other?} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}
+
+% --- SECTION: Elephants In the Room ---
+\section{Elephants in the Room}
+
+\begin{itemize}
+\item Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
+\item Can't capture temporal abstraction.
+\end{itemize}
 
@@
 \item Connection to teaching.
+\begin{itemize}
+\item AMDPs seem well suited to hierarchical teaching Carl-style.
+\item Problem: once solved for optimal policy in AMDP already solved in low level state. Probably want to set up teaching to avoid this.
+\end{itemize}
 \end{itemize}

### 2015-10-07 state_abstraction.tex
updated post meeting

@@
 
-% Subsection: Things you should not compress on.
-\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it other?} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}
-
 % --- SECTION: Elephants In the Room ---
@@
 \newpage
-\section{New Proposal: Approximate Abstraction}
+\section{New Proposal 1: Approximate Abstraction}
 
-For each of the following three cases:
+For each of the following four cases:
+
 % Model Equivalence
+\begin{equation}
+ \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : T(s \mid s_1, a) = T(s \mid s_2, a) \wedge \forall_a : R(s_1,a) = R(s_2,a)
+\end{equation}
+
+% Transition Equivalence
 \begin{equation}
@@
 
-% Optimal action and value Equivalence
+% Optimal action and Q value Equivalence
 \begin{equation}
@@
 
-Relax the equality condition, instead consider the approximate case, e.g.:
+% Possible I-Learning?
+
+% Ordering of Q values?
+
+\elem{Our strategy:} relax the equality condition, instead consider the approximate case, e.g.:
 % Model Similarity
@@
 
-\elem{The Question:} Can anything be said about the optimality of the policy $\pi_{\phi_{T,\epsilon}}$ in the ground MDP? Are we within some factor of $\epsilon$ away from being optimal?
+\subsection{The Question:} Suppose we're given the optimal policy in the abstract MDP under one of the above approximate abstractions, e.g.
+$\pi^*_{\phi_{T,\epsilon}}$.
+What can be said about the potential optimality of this policy in the original ground MDP?
+(for each of the four approximate abstractions).
+
+Note: Similar to simulation lemma from $E^3$, lets take a look.
 
@@
 \newpage
-\section{New Proposal: Temporal Abstraction}
+\section{New Proposal 2: Temporal Abstraction}
 
@@
 Should be some nice results there.
+
+% --- SECTION: Other Fruits ---
+\newpage
+\section{Other Low Hanging Fruit Results}
+
+% Subsection: Things you should not compress on.
+\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it value} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}
 

### 2015-10-08 state_abstraction.tex
beep

@@
 
-% Subsection: Arbitrary reduction in Sample Complexity for a specific MDP.
-\subsection{Result 1: Arbitrary reduction in Sample Complexity for a particular MDP.}
+\elem{Result 1:} Arbitrary reduction in Sample Complexity for a particular MDP.
 
-% Subsection: More general SC reduction result.
-\subsection{Result 2: More general result about sample complexity reduction for MDPs of a certain type}
+\elem{Result 2:} More general result about sample complexity reduction for MDPs of a certain type
 
-Q: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.
+The Question: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.
 
-% Maybe something about exploration.
+Possible other Result: Exploration.
 
@@
 
-\begin{itemize}
-\item Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
+\begin{enumerate}
+\item Finding states with {\it exactly} the same Q values, or optimal action and action value, or same model, is rare!
 \item Can't capture temporal abstraction.
-\end{itemize}
+\end{enumerate}
+
+Proposal: Resolve (1) and (2), so that the nice results from Section 2 can be realized. The next two sections talk about how we might go about doing that.
 
@@
 
+Sort of like the Simulation Lemma from $E^3$.
+
 \subsection{The Question:} Suppose we're given the optimal policy in the abstract MDP under one of the above approximate abstractions, e.g.
@@
 
-Note: Similar to simulation lemma from $E^3$, lets take a look.
+\subsection{Followup Question:} Why {\it won't} this work for other types of abstractions?
+\begin{itemize}
+\item Just using state variables...
+\item Just Reward function at a state...
+\item Just Value of state...
+\item Any combination of these...
+\end{itemize}
+
+Results about which abstractions {\it don't} work. Note: Already have counter examples for the above 3, would be nice to get more general results.
+
+The result is that we identify which criteria are at the core of making state abstraction {\it useful}.
 
@@
 
-In light of Result 3, that state abstraction needs to be defined with respect to some sort of properties about actions, suppose a set of temporally extended actions are included in the action set.
+In light of the above negative results (regarding which abstractions are useful), that state abstraction needs to be defined with respect to some sort of properties about actions, suppose a set of temporally extended actions are included in the action set.
 
@@
 
-Should be some nice results there.
+What sort of thing do we want to prove here? Abstractions become temporal if actions are temporally extended? Without temporal extension, forces $T(s,a,s')$ and $R(s,a)$ to do weird things?
+
+Q: Can we treat temporally extended actions in a general enough way to prove things about all possible versions of TEAs, or do we need to do separate proofs for Options/Macroactions?
 
@@
 \subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it value} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}
+
+% --- SECTION: Game Plan ---
+\newpage{Game Plan}
+
+First, get results about the approximate state abstraction for each of the 4 under consideration.
+
+Second, investigate temporally extended actions w/ abstraction.
+
+Third, wrap up low hanging fruit results, investigate more general versions of these claims (beyond $\exists MDP s.t. \ldots$.).
 

### 2015-10-09 state_abstraction.tex
first results added

@@
 
+% --- SECTION: Results! ---
+\newpage
+\section{Results}
+
+\thm{Lemma}{1}{(Simulation Lemma)}
+
+\thm{Lemma}{2}{Under the model approximate abstraction scheme, an the Q values for the ground MDP will be within $\epsilon$ of the abstract MDP under an arbitrary policy.}
+
+\elem{Proof:} Recall our definition of model approximate abstraction:
+\begin{equation}
+\forall_{s_1,s_2} \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} | T(s,a,s_1) - T(s,a,s_2) | \leq 2\beta
+\label{eq:approx_model_abs}
+\end{equation}
+
+Sim Lemma says we need T and R to be within $2\beta = \alpha$.
+
+We have our ground MDP: $M_G$, abstract MDP, $M_A$, and noisy ground MDP, $M_{G'}$.
+
+Using a given state abstraction function $\phi$ subject to Equation~\ref{eq:approx_model_abs}, the difference between $T_G$ and $T_{G'}$.
+
+Sim lemma goes through (cause same for $R$).
+
+\thm{Lemma}{3}{Under the optimal Q function approximate abstraction, $\forall_s : |Q_A^*(s,.) - Q_G^*(s,.)| \leq \epsilon$ }
+
+Since for each state, the most you can screw up is by $\epsilon$, since if you don't take $\argmax_a Q^*(s,a)$, then one of the other actions Q functions must have jumped up by at most $\epsilon$, but it's fine because then you're doing no worse then $\epsilon$.
+It can't have jump mored, because otherwise you wouldn't have compressed on it.
+
 % --- SECTION: Temporal Abstraction ---

### 2015-10-11 state_abstraction.tex
Fleshed Out Results a Bit

@@
 
-\thm{Lemma}{1}{(Simulation Lemma)}
+\thm{Lemma}{1}{Given two MDPs, $M_1$ and $M_2$ which differ only by $T$ and $R$, if $\forall_{s,a} |T_1(s,a,\cdot)-T_2(s,a,\cdot)| \leq 2\beta$ and $\forall_{s,a} |R_1(s,a)-R_2(s,a)|\leq \alpha$ then for some fixed policy $\pi$ then $\forall_{s,a} |Q_1^\pi(s,a)-Q_2^\pi(s,a)| \leq \frac{\alpha v_{max}}{C(1-\gamma)} = \epsilon$ (Simulation Lemma)}
 
-\thm{Lemma}{2}{Under the model approximate abstraction scheme, an the Q values for the ground MDP will be within $\epsilon$ of the abstract MDP under an arbitrary policy.}
+Call the ground truth MDP $M_G$, the abstract MDP $M_A=\phi(M_G)$.\footnote{Sloppy notation -- really $\phi$ is only applied to $S$.} Suppose that the agent plans in $M_A$.
+We would like to bound how well it is \textit{really} performing in $M_G$ based on how it performs in $M_A$.
+Call the decompressed ground state of $M_A$, $M_{G'}$, the noisy ground MDP.
+
+\thm{Lemma}{2}{Under the model approximate abstraction scheme, $\phi_{model}$, the Q values under any policy in $M_A$ will be within $\epsilon$ of Q values under the same policy in $M_G$.}
 

### 2015-10-12 state_abstraction.tex
made a few cosmetic tweaks

@@
 \begin{equation*}
-\phi_{a^*}(s_1) = \phi_a^*(s_2) \rightarrow Q^*(s_1,a^*) = \max_a Q^*(s_1,a) = \max_a Q^*(s_2,a) = Q^*(s_2, a)
+\phi_{a^*}(s_1) = \phi_{a^*}(s_2) \rightarrow Q^*(s_1,a^*) = \max_a Q^*(s_1,a) = \max_a Q^*(s_2,a) = Q^*(s_2, a^*)
 \end{equation*}
@@
 
-\thm{Lemma}{1}{Given two MDPs, $M_1$ and $M_2$ which differ only by $T$ and $R$, if $\forall_{s,a} |T_1(s,a,\cdot)-T_2(s,a,\cdot)| \leq 2\beta$ and $\forall_{s,a} |R_1(s,a)-R_2(s,a)|\leq \alpha$ then for some fixed policy $\pi$ then $\forall_{s,a} |Q_1^\pi(s,a)-Q_2^\pi(s,a)| \leq \frac{\alpha v_{max}}{C(1-\gamma)} = \epsilon$ (Simulation Lemma)}
+\thm{Lemma}{1}{Given two MDPs, $M_1$ and $M_2$ which differ only by $T$ and $R$, if $\forall_{s,a} |T_1(s,a,\cdot)-T_2(s,a,\cdot)| \leq 2\beta$ and $\forall_{s,a} |R_1(s,a)-R_2(s,a)|\leq \alpha$ then for some fixed policy $\pi$ then:
+\begin{equation}
+\forall_{s,a} |Q_1^\pi(s,a)-Q_2^\pi(s,a)| \leq \frac{\alpha \textsc{Vmax}}{C(1-\gamma)} = \epsilon
+\end{equation} (Simulation Lemma)}
 
@@
 We would like to bound how well it is \textit{really} performing in $M_G$ based on how it performs in $M_A$.
-Call the decompressed ground state of $M_A$, $M_{G'}$, the noisy ground MDP.
+
+Consider the decompressed ground state space of $M_A$, $M_{G'} = \phi^{-1}(\phi(M_G))$.
 
@@
 \begin{equation}
-\forall_{s_1,s_2} \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} | T(s,a,s_1) - T(s,a,s_2) | \leq 2\beta
+\forall_{s_1,s_2} \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} | T(s,a,s_1) - T(s,a,s_2) | \leq 2\beta \wedge \forall_a |R(s_1,a) - R(s_2,a)| \leq \alpha
 \label{eq:approx_model_abs}
@@
 
-\thm{Lemma}{3}{Under the optimal Q function approximate abstraction, $\forall_s : |Q_A^*(s,.) - Q_G^*(s,.)| \leq \epsilon$ }
+\thm{Lemma}{3}{Under the optimal Q function approximate abstraction, $\forall_{s,a} : |Q_A^*(s,a) - Q_G^*(s,a)| \leq \epsilon$}
 
@@
 It can't have jump mored, because otherwise you wouldn't have compressed on it.
+
+% Note: this might be too tight.
+A looser bound is $\epsilon D$, where $D$ is the diameter of the MDP, since each state you can incur at most $\epsilon$ error?
+This seems wrong too, it's not $D$ necessarily?
+It's more the number of actions executed during planning/learning.
+Does that seem right?
+% Doesn't it depend on the policy? Like this assumes we're working under a greedy Q policy. Suppose we're using an {\it arbitrary} policy...
 

### 2015-11-17 Workspace and Code/stateAbstraction/State Abstraction/src/SARealGenerators/SARealGenerator.java
Added a means for reconstructing the the abstract policy in the ground MDP. See QValueAbstractionTest for an example as well as an example of evaluating the abstract policy in the ground MDP. Also added class comments for all classes and more comments in general..

@@ -1,0 +1,45 @@
+package SARealGenerators;
+
+import java.util.HashMap;
+import java.util.List;
+
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.RewardFunction;
+
+/**
+ * A class used to generate real values on state, action pairs to form
+ * the basis of some abstraction. Is fed to PhiSAReal to help it to determine
+ * if it should collapse two states.
+ * @author Dhershkowitz
+ *
+ */
+public abstract class SARealGenerator {
+	protected Domain d;
+	protected RewardFunction rf;
+	protected double gamma;
+	protected State initialState;
+	
+	/**
+	 * 
+	 * @param d
+	 * @param rf
+	 * @param gamma
+	 * @param initialState
+	 */
+	public SARealGenerator(Domain d, RewardFunction rf, double gamma, State initialState) {
+		this.d = d;
+		this.rf = rf;
+		this.gamma = gamma;
+		this.initialState = initialState;
+	}
+	
+	/**
+	 * 
+	 * @return The mapping from SAPairs to the real value function associated with
+	 * this SARealGenerator. E.g. qValueGenerator produces a map from state, action
+	 * pairs to Q values.
+	 */
+	public abstract HashMap<SAPair, Double> getRealsMap();
+}

### 2015-11-17 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/PhiModel.java

@@ -1,0 +1,17 @@
+package stateAbstractor;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.states.State;
+
+public class PhiModel extends StateAbstractor {
+
+	@Override
+	// TODO: implement. It is currently just an example of collapsing just the first two indexed graph defined states together.
+	protected boolean phi(State s1, State s2) {
+		return (GraphDefinedDomain.getNodeId(s1) == 0 && GraphDefinedDomain.getNodeId(s2) == 1)
+				||
+				(GraphDefinedDomain.getNodeId(s1) == 1 && GraphDefinedDomain.getNodeId(s2) == 0);
+	}
+
+}

### 2015-11-17 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/StateAbstractor.java

@@ -1,0 +1,214 @@
+package stateAbstractor;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.core.AbstractGroundedAction;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TransitionProbability;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.HashableState;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public abstract class StateAbstractor {
+
+	private RewardFunction rf;
+	private HashMap<Integer, Integer> groundToAbstractState;
+
+	/**
+	 * 
+	 * @param inpDG the ground MDP domain generator
+	 * @param rf the ground MDP reward function
+	 */
+	public GraphDefinedDomain abstractMDP(GraphDefinedDomain inpDG, RewardFunction rf) {
+		Domain inputD = inpDG.generateDomain();
+		HashableStateFactory hf = new SimpleHashableStateFactory();
+
+		HashMap<State, List<State>> stateToPhiedStates = new HashMap<State, List<State>>();
+		// Get all ground states.
+		for (int stateIndex = 0; stateIndex < inpDG.getNumNodes(); stateIndex++) {
+			State currGroundState = GraphDefinedDomain.getState(inputD, stateIndex);
+			boolean foundACluster = false;
+			for (State currGroundStateRep : stateToPhiedStates.keySet()) {
+				// Should add to this cluster.
+				if (this.phi(currGroundState, currGroundStateRep)) {
+					List<State> stateCluster = stateToPhiedStates.get(currGroundStateRep);
+					stateCluster.add(currGroundState);
+					foundACluster = true;
+				}
+			}
+			// No existing cluster for this state.
+			if (!foundACluster) {
+				List<State> newCluster = new ArrayList<State>();
[…]

### 2015-11-18 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java
adding .class to gitignore

@@ -1,75 +1,0 @@
-package graphStateAbstraction;
-
-import stateAbstractor.PhiModel;
-import stateAbstractor.PhiSAReal;
-import stateAbstractor.StateAbstractor;
-import SARealGenerators.qValueGenerator;
-import burlap.behavior.policy.GreedyQPolicy;
-import burlap.behavior.policy.Policy;
-import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
-import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
-import burlap.oomdp.core.states.State;
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.auxiliary.common.NullTermination;
-import burlap.oomdp.core.Domain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-import burlap.oomdp.singleagent.common.UniformCostRF;
-import burlap.oomdp.statehashing.HashableStateFactory;
-import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-
-/**
- * An example of Q* abstraction in an 5 state chain MDP.
- * @author Dhershkowitz
- *
- */
-public class QValueAbstractionTest {
-
-	public static void main(String[] args) {
-		//VI Params
-		int maxIterations = 10000;
-		double maxDelta = .0001;
-		double gamma = .9;
-		TerminalFunction tf = new NullTermination();
-
-		// Ground MDP
-		int n = 5;
-		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = Test.getNStateChain(n);
-		RewardFunction rf = new Test.nStateChainRF(n);
-		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
-		State gInitialState = GraphDefinedDomain.getState(d, 0);
-		Policy gPol = vi.planFromState(gInitialState);	
-		System.out.println("Ground initial state value: " + vi.value(gInitialState));
-
-		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 10;
-		qValueGenerator qGen = new qValueGenerator(d, rf, gamma, gInitialState);
[…]

### 2015-11-18 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java
adding qval test back in

@@ -1,0 +1,75 @@
+package graphStateAbstraction;
+
+import stateAbstractor.PhiModel;
+import stateAbstractor.PhiSAReal;
+import stateAbstractor.StateAbstractor;
+import SARealGenerators.qValueGenerator;
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.oomdp.core.states.State;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.common.UniformCostRF;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+/**
+ * An example of Q* abstraction in an 5 state chain MDP.
+ * @author Dhershkowitz
+ *
+ */
+public class QValueAbstractionTest {
+
+	public static void main(String[] args) {
+		//VI Params
+		int maxIterations = 10000;
+		double maxDelta = .0001;
+		double gamma = .9;
+		TerminalFunction tf = new NullTermination();
+
+		// Ground MDP
+		int n = 5;
+		HashableStateFactory hf = new SimpleHashableStateFactory();
+		GraphDefinedDomain dg = Test.getNStateChain(n);
+		RewardFunction rf = new Test.nStateChainRF(n);
+		Domain d = dg.generateDomain();
+		ValueIteration vi = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
+		State gInitialState = GraphDefinedDomain.getState(d, 0);
+		Policy gPol = vi.planFromState(gInitialState);	
+		System.out.println("Ground initial state value: " + vi.value(gInitialState));
+
+		// Abstract MDP VI with a PhiQ* for abstraction
+		double epsilon = 10;
+		qValueGenerator qGen = new qValueGenerator(d, rf, gamma, gInitialState);
[…]

### 2015-11-18 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java
adding test back

@@ -1,0 +1,115 @@
+package graphStateAbstraction;
+
+import stateAbstractor.PhiModel;
+import stateAbstractor.StateAbstractor;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.oomdp.core.states.State;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.common.UniformCostRF;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class Test {
+
+	/**
+	 * 
+	 * @param totalNumStates
+	 * @return an n state graph MDP.
+	 */
+	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
+		double slipProb = .8;
+		double gamma = .95;
+
+		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
+
+		// Set up transitions
+		for (int i = 0; i < totalNumStates-1; i++) {
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, i+1, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, 0, 1.0-slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, 0, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, i+1, 1.0-slipProb);
+		}
+
+		// Set up last state transition
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0, 1.0-slipProb);
+
+		return dg;
+	}	
+	
+	/**
[…]

### 2015-11-18 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java
Adde Graphvisualizer for MDPs in Burlap

@@ -1,0 +1,126 @@
+package graphStreamVisualizer;
+
+import java.math.RoundingMode;
+import java.text.DecimalFormat;
+import java.util.List;
+
+import graphStateAbstraction.Test;
+
+import org.graphstream.graph.Edge;
+import org.graphstream.graph.Graph;
+import org.graphstream.graph.Node;
+import org.graphstream.graph.implementations.*;
+import org.graphstream.ui.view.Viewer;
+
+import stateAbstractor.PhiSAReal;
+import stateAbstractor.StateAbstractor;
+import SARealGenerators.qValueGenerator;
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.TransitionProbability;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class GraphStreamVisualizer {
+	private GraphDefinedDomain d;
+	int numStates;
+	RewardFunction rf;
+
+	public GraphStreamVisualizer(GraphDefinedDomain d, int numStates, RewardFunction rf) {
+		this.d = d;
+		this.numStates = numStates;
+		this.rf = rf;
+	}
+
+	public void render() {	
+		Graph graph = new MultiGraph("Tutorial 1");	
+		Domain dom = d.generateDomain();
+
+		for (int stateIndex = 0; stateIndex < numStates; stateIndex++) {
+			//Add nodes for each state.
+			Node node = graph.addNode(Integer.toString(stateIndex));
+			node.addAttribute("ui.label", Integer.toString(stateIndex));
+		}
+
+
+		//Add transition probabilities/edges.
+		for (int stateIndex = 0; stateIndex < numStates; stateIndex++) {
+			//Add nodes for each state.
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java
Fixed visualizer. Also fixed bug with reward function and transition dynamics for state abstractor. Check out the sweet visualization.

@@ -22,7 +22,7 @@ public class Test {
 	 * @return an n state graph MDP.
 	 */
 	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
-		double slipProb = .8;
+		double slipProb = .2;
 		double gamma = .95;
 
 		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
@@ -37,9 +37,9 @@ public class Test {
 
 		// Set up last state transition
 		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0,1.0-slipProb);
 		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
 		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0, 1.0-slipProb);
 
 		return dg;
 	}	
@@ -63,7 +63,7 @@ public class Test {
 				return 2;
 			}
 			else {
-				if (GraphDefinedDomain.getNodeId(s) == n-1) {
+				if (GraphDefinedDomain.getNodeId(s) == n-1 && GraphDefinedDomain.getNodeId(sprime) == n-1) {
 					return 10;
 				}
 			}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -35,6 +35,29 @@ public class GraphStreamVisualizer {
 	int numStates;
 	RewardFunction rf;
 
+	public static String styleSheet = 
+			"node {fill-color: grey;size: 40px;}" +
+					"edge {shape: cubic-curve;size: 6px;}"		
+					;
+
+	public static String[] colorPalette = {
+		"rgb(198,255,179)",
+		"rgb(179,198,255)",
+		"rgb(236,179,255)",
+		"rgb(255,179,198)",
+		"rgb(198,179,255)",
+		"rgb(255,198,179)",
+		"rgb(255,236,179)",
+		"rgb(236,255,179)",
+		"rgb(179,255,236)",
+		"rgb(255,179,236)",
+		"rgb(179,255,198)",
+		"rgb(179,236,255)",
+		"rgb(117,152,255)",
+		"rgb(56,106,255)",
+		"rgb(255,221,117)",
+	"rgb(255,205,56)"};
+
 	public GraphStreamVisualizer(GraphDefinedDomain d, int numStates, RewardFunction rf) {
 		this.d = d;
 		this.numStates = numStates;
@@ -42,7 +65,11 @@ public class GraphStreamVisualizer {
 	}
 
 	public void render() {	
+		//Use advanced viewer
+		System.setProperty("org.graphstream.ui.renderer", "org.graphstream.ui.j2dviewer.J2DGraphRenderer");
+
 		Graph graph = new MultiGraph("Tutorial 1");	
+		graph.addAttribute("ui.stylesheet", styleSheet);
 		Domain dom = d.generateDomain();
 
 		for (int stateIndex = 0; stateIndex < numStates; stateIndex++) {
@@ -69,24 +96,31 @@ public class GraphStreamVisualizer {
 					int otherStateIndex = GraphDefinedDomain.getNodeId(sPrime);
 
 					//TODO DONT SKIP SELF LOOPS
-//					if (stateIndex != otherStateIndex) {
-						boolean directed = true;
-						DecimalFormat df = new DecimalFormat("#.#");
-						df.setRoundingMode(RoundingMode.DOWN);
-						String probString = df.format(prob);
-						Edge e = graph.addEdge(Integer.toString(stateIndex) + Integer.toString(otherStateIndex) + ga.actionName(), Integer.toString(stateIndex), Integer.toString(otherStateIndex), directed);
-						e.addAttribute("ui.label", probString + ", " + rf.reward(currState, ga, sPrime));
-//					}
+					//					if (stateIndex != otherStateIndex) {
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/StateAbstractor.java

@@ -4,6 +4,7 @@ import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
 
+import cern.colt.Arrays;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
@@ -83,6 +84,7 @@ public abstract class StateAbstractor {
 				for (int actionIndex = 0; actionIndex < inputD.getActions().size(); actionIndex++) {
 					GroundedAction currGA = inputD.getActions().get(actionIndex).getAssociatedGroundedAction();
 					double transitionProbability = 0.0;
+					//Loop over ground states.
 					for (State groundState : abstractStateIndexToGroundStates.get(abstractStateIndex)) {
 						double numStatesInCluster = abstractStateIndexToGroundStates.get(abstractStateIndex).size();
 						for (State otherGroundedState : abstractStateIndexToGroundStates.get(otherAbstractStateIndex)) {
@@ -91,18 +93,22 @@ public abstract class StateAbstractor {
 							//Add to transition prob based on weighting scheme.
 							double transitionProbInGroundState = 0;
 							List<TransitionProbability> gsgaTransitions = currGA.getTransitions(groundState);
+							boolean transitionBetweenGroundStates = false;
 							for (TransitionProbability tp : gsgaTransitions) {
 								if (tp.s.equals(otherGroundedState)) {
 									transitionProbInGroundState = tp.p;
+									transitionBetweenGroundStates = true;
 								}
 							}
+							if (!transitionBetweenGroundStates) continue;
+
 							transitionProbability += weightOfGroundState*transitionProbInGroundState;
 
 							//Add to rewards
-							double oldReward = rf.reward(groundState, currGA, otherGroundedState);
-							rewardMatrix.get(currGA)[abstractStateIndex][otherAbstractStateIndex] += weightOfGroundState*oldReward;
+							double groundReward = rf.reward(groundState, currGA, otherGroundedState);
+							rewardMatrix.get(currGA)[abstractStateIndex][otherAbstractStateIndex] += weightOfGroundState*groundReward;
 						}
-						toReturn.setTransition(abstractStateIndex, actionIndex, otherAbstractStateIndex, transitionProbability);
+						if (transitionProbability != 0) toReturn.setTransition(abstractStateIndex, actionIndex, otherAbstractStateIndex, transitionProbability);
 					}
 				}
 			}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/SARealGenerators/SARealGenerator.java
Added a namespace so all DP algorithms use the same gamma, maxDelta and maxIterations.

@@ -18,7 +18,6 @@ import burlap.oomdp.singleagent.RewardFunction;
 public abstract class SARealGenerator {
 	protected Domain d;
 	protected RewardFunction rf;
-	protected double gamma;
 	protected State initialState;
 	
 	/**
@@ -28,10 +27,9 @@ public abstract class SARealGenerator {
 	 * @param gamma
 	 * @param initialState
 	 */
-	public SARealGenerator(Domain d, RewardFunction rf, double gamma, State initialState) {
+	public SARealGenerator(Domain d, RewardFunction rf, State initialState) {
 		this.d = d;
 		this.rf = rf;
-		this.gamma = gamma;
 		this.initialState = initialState;
 	}
 	

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/SARealGenerators/qValueGenerator.java

@@ -1,5 +1,7 @@
 package SARealGenerators;
 
+import graphStateAbstraction.VIParams;
+
 import java.util.HashMap;
 import java.util.List;
 
@@ -21,30 +23,29 @@ import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 public class qValueGenerator extends SARealGenerator {
 
 	HashMap<SAPair, Double> realsMap;
+	public qValueGenerator(Domain d, RewardFunction rf, State initialState) {
+		super(d, rf, initialState);
+		
+		this.realsMap = this.getRealsMap();
+	}
+
 
 	/**
 	 * 
 	 * @param d
 	 * @param rf
-	 * @param gamma
 	 * @param initialState
 	 */
-	public qValueGenerator(Domain d, RewardFunction rf, double gamma,
-			State initialState) {
-		super(d, rf, gamma, initialState);
-		this.realsMap = getRealsMap();
-	}
+
 
 	@Override
 	public HashMap<SAPair, Double> getRealsMap() {
 		if (realsMap != null) return realsMap;
 		else {
 			HashMap<SAPair, Double> toReturn = new HashMap<SAPair, Double>();
-			double maxDelta = .001;
-			int maxIterations = 1000;
 			TerminalFunction tf = new NullTermination();
 			HashableStateFactory hf = new SimpleHashableStateFactory();
-			ValueIteration VI = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
+			ValueIteration VI = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 			VI.planFromState(initialState);
 			for (State s : VI.getAllStates()) {
 				for (Action a : VI.getActions()) {

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java

@@ -28,40 +28,35 @@ public class QValueAbstractionTest {
 
 	public static void main(String[] args) {
 		//VI Params
-		int maxIterations = 10000;
-		double maxDelta = .0001;
-		double gamma = .9;
 		TerminalFunction tf = new NullTermination();
 
 		// Ground MDP
-		int n = 5;
+		int n = 100;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
 		GraphDefinedDomain dg = Test.getNStateChain(n);
 		RewardFunction rf = new Test.nStateChainRF(n);
 		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
+		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
 		Policy gPol = vi.planFromState(gInitialState);	
 		System.out.println("Ground initial state value: " + vi.value(gInitialState));
 
 		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 10;
-		qValueGenerator qGen = new qValueGenerator(d, rf, gamma, gInitialState);
+		double epsilon = 1000;
+		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
 		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, d.getActions());
 		HashableStateFactory hfA = new SimpleHashableStateFactory();
 		GraphDefinedDomain absDG = qPhi.abstractMDP(dg, rf);
 		RewardFunction rfA = qPhi.getRewardFunction();
 		Domain absD= absDG.generateDomain();
-		ValueIteration aVi = new ValueIteration(absD, rfA, tf, gamma, hfA, maxDelta, maxIterations);
+		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
 		State aInitialState = GraphDefinedDomain.getState(absD, 0);
 		GreedyQPolicy abstractPolicy = aVi.planFromState(aInitialState);	
 		
-		Policy groundPolicyFromAbstractPolicy = qPhi.getPolicyForGroundMDP(abstractPolicy, absDG, dg);
 
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java

@@ -23,7 +23,6 @@ public class Test {
 	 */
 	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
 		double slipProb = .2;
-		double gamma = .95;
 
 		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
 
@@ -78,9 +77,7 @@ public class Test {
 	 */
 	public static void main(String[] args) {
 		//VI Params
-		int maxIterations = 10000;
-		double maxDelta = .0001;
-		double gamma = .95;
+
 		TerminalFunction tf = new NullTermination();
 		
 		// Ground MDP
@@ -89,7 +86,7 @@ public class Test {
 		GraphDefinedDomain dg = getNStateChain(n);
 		RewardFunction rf = new nStateChainRF(n);
 		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
+		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
 		vi.planFromState(gInitialState);	
 		System.out.println("Ground initial state value: " + vi.value(gInitialState));
@@ -100,7 +97,7 @@ public class Test {
 		GraphDefinedDomain absDG = phiMod.abstractMDP(dg, rf);
 		RewardFunction rfA = phiMod.getRewardFunction();
 		Domain absD= absDG.generateDomain();
-		ValueIteration aVi = new ValueIteration(absD, rfA, tf, gamma, hfA, maxDelta, maxIterations);
+		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
 		State aInitialState = GraphDefinedDomain.getState(absD, 0);
 		aVi.planFromState(aInitialState);	
 		System.out.println("Abstract initial state value: " + aVi.value(aInitialState));

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/VIParams.java

@@ -1,0 +1,7 @@
+package graphStateAbstraction;
+
+public class VIParams {
+	public static int maxIterations = 1000;
+	public static double maxDelta = .01;
+	public static double gamma = .7;
+}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -5,6 +5,7 @@ import java.text.DecimalFormat;
 import java.util.List;
 
 import graphStateAbstraction.Test;
+import graphStateAbstraction.VIParams;
 
 import org.graphstream.graph.Edge;
 import org.graphstream.graph.Graph;
@@ -17,6 +18,7 @@ import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.auxiliary.common.NullTermination;
@@ -122,38 +124,42 @@ public class GraphStreamVisualizer {
 	public static void main(String[] args) {
 
 		//VI Params
-		int maxIterations = 10000;
-		double maxDelta = .0001;
-		double gamma = .9;
 		TerminalFunction tf = new NullTermination();
 
 		// Ground MDP
-		int n = 100;
+		int n = 300;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
 		GraphDefinedDomain dg = Test.getNStateChain(n);
 		RewardFunction rf = new Test.nStateChainRF(n);
 		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, gamma, hf, maxDelta, maxIterations);
+		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
 		Policy gPol = vi.planFromState(gInitialState);	
 		System.out.println("Ground initial state value: " + vi.value(gInitialState));
 
 		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 1;
-		qValueGenerator qGen = new qValueGenerator(d, rf, gamma, gInitialState);
+		double epsilon = 0;
+		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
 		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, d.getActions());
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/VIParams.java
Fixed bug with color palette choosing for edges.

@@ -1,7 +1,7 @@
 package graphStateAbstraction;
 
 public class VIParams {
-	public static int maxIterations = 1000;
-	public static double maxDelta = .01;
-	public static double gamma = .7;
+	public static int maxIterations = 100;
+	public static double maxDelta = .1;
+	public static double gamma = .5;
 }

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -108,7 +108,7 @@ public class GraphStreamVisualizer {
 					int actionIndex = dom.getActions().indexOf(a);
 					e.addAttribute("ui.label", probString);
 					// Set color to match action
-					String colorString = "fill-color:" + colorPalette[actionIndex] + ";";
+					String colorString = "fill-color:" + colorPalette[actionIndex % colorPalette.length]  + ";";
 					// Set edge width to mag of reward
 					e.addAttribute("ui.style", "size:" + edgeReward + "px;" + colorString);
 				}
@@ -158,7 +158,7 @@ public class GraphStreamVisualizer {
 
 
 
-		//				GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
+//						GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
 		GraphStreamVisualizer test = new GraphStreamVisualizer(absDG, aVi.getAllStates().size(), rfA);
 		test.render();
 	}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/NStateChainGenerator.java
Added upworld and cleaned up the world generation.

@@ -1,0 +1,68 @@
+package graphStateAbstraction;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+
+/**
+ * A class with static methods to instantiate nstate problems and nstate chain reward functions.
+ * @author Dhershkowitz
+ *
+ */
+public class NStateChainGenerator {
+	/**
+	 * 
+	 * @param totalNumStates
+	 * @return an n state graph MDP.
+	 */
+	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
+		double slipProb = .2;
+
+		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
+
+		// Set up transitions
+		for (int i = 0; i < totalNumStates-1; i++) {
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, i+1, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, 0, 1.0-slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, 0, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, i+1, 1.0-slipProb);
+		}
+
+		// Set up last state transition
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0,1.0-slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
+
+		return dg;
+	}	
+	
+	/**
+	 * n State chain reward function -- returns 10 if action 1 is taken in the last state, 2 if
+	 * action 0 is taken ever and 0 otherwise.
+	 * @author Dhershkowitz
+	 *
+	 */
+	public static class nStateChainRF implements RewardFunction {
+		int n;
+		
+		public nStateChainRF(int n) {
+			this.n = n;
+		}
+
+		@Override
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java

@@ -33,8 +33,8 @@ public class QValueAbstractionTest {
 		// Ground MDP
 		int n = 100;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = Test.getNStateChain(n);
-		RewardFunction rf = new Test.nStateChainRF(n);
+		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
+		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
 		Domain d = dg.generateDomain();
 		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java

@@ -16,60 +16,6 @@ import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 public class Test {
 
-	/**
-	 * 
-	 * @param totalNumStates
-	 * @return an n state graph MDP.
-	 */
-	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
-		double slipProb = .2;
-
-		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
-
-		// Set up transitions
-		for (int i = 0; i < totalNumStates-1; i++) {
-			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, i+1, slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, 0, 1.0-slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, 0, slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, i+1, 1.0-slipProb);
-		}
-
-		// Set up last state transition
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0,1.0-slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
-
-		return dg;
-	}	
-	
-	/**
-	 * n State chain reward function -- returns 10 if action 1 is taken in the last state, 2 if
-	 * action 0 is taken ever and 0 otherwise.
-	 * @author Dhershkowitz
-	 *
-	 */
-	public static class nStateChainRF implements RewardFunction {
-		int n;
-		
-		public nStateChainRF(int n) {
-			this.n = n;
-		}
-
-		@Override
-		public double reward(State s, GroundedAction a, State sprime) {
-			if (a.actionName().equals("action0")) {
-				return 2;
-			}
-			else {
-				if (GraphDefinedDomain.getNodeId(s) == n-1 && GraphDefinedDomain.getNodeId(sprime) == n-1) {
-					return 10;
-				}
-			}
-			return 0;
-		}
-		
-	}
 
 	/**
[…]

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/UpWorldGenerator.java

@@ -1,0 +1,63 @@
+package graphStateAbstraction;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+
+public class UpWorldGenerator {
+	/**
+	 * 
+	 * @param totalNumStates
+	 * @return an n state graph MDP.
+	 */
+	public static GraphDefinedDomain getUPWorld(int width, int height) {
+		GraphDefinedDomain dg = new GraphDefinedDomain(height*width);
+
+		// Set up transitions for left/right.
+		for (int j = 0; j < height; j++){
+			for (int i = 0; i < width; i++) {
+				int currentStateIndex = i +j*width;
+
+				//Set up left action.
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, ((currentStateIndex-1)+width)%width, 1.0);
+
+				//Set up right action.
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*action*/, (currentStateIndex+1)%width, 1.0);
+			}
+		}
+
+		// Set up transition for up.
+		for (int j = 0; j < height-1; j++){
+			for (int i = 0; i < width; i++) {
+				int currentStateIndex = i +j*width;
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, currentStateIndex+width, 1.0);
+			}
+		}
+
+		// Set up self-loops at the end.
+		for (int i = 0; i < width; i++) {
+			int j = height-1;
+			int currentStateIndex = i +j*width;
+			((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, currentStateIndex, 1.0);
+		}
+
+		return dg;
+	}	
+
+	/**
+	 * n State chain reward function -- returns 10 if action 1 is taken in the last state, 2 if
+	 * action 0 is taken ever and 0 otherwise.
+	 * @author Dhershkowitz
+	 *
+	 */
+	public static class UpWorldRF implements RewardFunction {
+
+		@Override
+		public double reward(State s, GroundedAction a, State sprime) {
+			if (s.equals(sprime)) return 10;
+			else return 0;
+		}
+
+		}
+	}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/VIParams.java

@@ -3,5 +3,5 @@ package graphStateAbstraction;
 public class VIParams {
 	public static int maxIterations = 100;
 	public static double maxDelta = .1;
-	public static double gamma = .5;
+	public static double gamma = .99;
 }

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -4,6 +4,7 @@ import java.math.RoundingMode;
 import java.text.DecimalFormat;
 import java.util.List;
 
+import graphStateAbstraction.NStateChainGenerator;
 import graphStateAbstraction.Test;
 import graphStateAbstraction.VIParams;
 
@@ -117,7 +118,6 @@ public class GraphStreamVisualizer {
 
 		}
 
-		graph.display( false );
 		Viewer view = graph.display();
 	}
 
@@ -127,10 +127,10 @@ public class GraphStreamVisualizer {
 		TerminalFunction tf = new NullTermination();
 
 		// Ground MDP
-		int n = 300;
+		int n = 50;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = Test.getNStateChain(n);
-		RewardFunction rf = new Test.nStateChainRF(n);
+		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
+		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
 		Domain d = dg.generateDomain();
 		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
@@ -138,7 +138,7 @@ public class GraphStreamVisualizer {
 		System.out.println("Ground initial state value: " + vi.value(gInitialState));
 
 		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 0;
+		double epsilon = 3;
 		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
 		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, d.getActions());
 		HashableStateFactory hfA = new SimpleHashableStateFactory();
@@ -158,7 +158,7 @@ public class GraphStreamVisualizer {
 
 
 
-//						GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
+//		GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
 		GraphStreamVisualizer test = new GraphStreamVisualizer(absDG, aVi.getAllStates().size(), rfA);
 		test.render();
 	}

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/StateAbstractor.java

@@ -1,6 +1,7 @@
 package stateAbstractor;
 
 import java.util.ArrayList;
+import java.util.Collections;
 import java.util.HashMap;
 import java.util.List;
 
@@ -36,8 +37,14 @@ public abstract class StateAbstractor {
 		HashableStateFactory hf = new SimpleHashableStateFactory();
 
 		HashMap<State, List<State>> stateToPhiedStates = new HashMap<State, List<State>>();
-		// Get all ground states.
+		// Get all ground states in random shuffled order.
+		List<Integer> indexList = new ArrayList<Integer>();
 		for (int stateIndex = 0; stateIndex < inpDG.getNumNodes(); stateIndex++) {
+			indexList.add(stateIndex);
+		}
+		Collections.shuffle(indexList);
+		
+		for (int stateIndex : indexList) {
 			State currGroundState = GraphDefinedDomain.getState(inputD, stateIndex);
 			boolean foundACluster = false;
 			for (State currGroundStateRep : stateToPhiedStates.keySet()) {

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/UpWorldGenerator.java
Fixed upworld.

@@ -18,12 +18,20 @@ public class UpWorldGenerator {
 		for (int j = 0; j < height; j++){
 			for (int i = 0; i < width; i++) {
 				int currentStateIndex = i +j*width;
+				
+				int leftIndex = 0;
+				if (i==0) leftIndex =  currentStateIndex;
+				else leftIndex = currentStateIndex-1;
+						
+				int rightIndex = 0;
+				if (i == width-1) rightIndex = currentStateIndex;
+				else rightIndex = currentStateIndex+1;
 
 				//Set up left action.
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, ((currentStateIndex-1)+width)%width, 1.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, leftIndex, 1.0);
 
 				//Set up right action.
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*action*/, (currentStateIndex+1)%width, 1.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*action*/, rightIndex, 1.0);
 			}
 		}
 
@@ -31,7 +39,7 @@ public class UpWorldGenerator {
 		for (int j = 0; j < height-1; j++){
 			for (int i = 0; i < width; i++) {
 				int currentStateIndex = i +j*width;
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, currentStateIndex+width, 1.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*action*/, currentStateIndex+width, 1.0);
 			}
 		}
 
@@ -39,7 +47,7 @@ public class UpWorldGenerator {
 		for (int i = 0; i < width; i++) {
 			int j = height-1;
 			int currentStateIndex = i +j*width;
-			((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, currentStateIndex, 1.0);
+			((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*action*/, currentStateIndex, 1.0);
 		}
 
 		return dg;
@@ -55,7 +63,7 @@ public class UpWorldGenerator {
 
 		@Override
 		public double reward(State s, GroundedAction a, State sprime) {
-			if (s.equals(sprime)) return 10;
+			if (s.equals(sprime) && a.actionName().equals("action2")) return 10;
 			else return 0;
 		}
 

### 2015-11-19 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -6,6 +6,7 @@ import java.util.List;
 
 import graphStateAbstraction.NStateChainGenerator;
 import graphStateAbstraction.Test;
+import graphStateAbstraction.UpWorldGenerator;
 import graphStateAbstraction.VIParams;
 
 import org.graphstream.graph.Edge;
@@ -127,10 +128,12 @@ public class GraphStreamVisualizer {
 		TerminalFunction tf = new NullTermination();
 
 		// Ground MDP
-		int n = 50;
+		int height = 10;
+		int width = 5;
+		int n = height*width;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
-		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
+		GraphDefinedDomain dg = UpWorldGenerator.getUPWorld(width, height);
+		RewardFunction rf = new UpWorldGenerator.UpWorldRF();
 		Domain d = dg.generateDomain();
 		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
@@ -138,7 +141,7 @@ public class GraphStreamVisualizer {
 		System.out.println("Ground initial state value: " + vi.value(gInitialState));
 
 		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 3;
+		double epsilon = 0;
 		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
 		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, d.getActions());
 		HashableStateFactory hfA = new SimpleHashableStateFactory();
@@ -158,8 +161,8 @@ public class GraphStreamVisualizer {
 
 
 
-//		GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
-		GraphStreamVisualizer test = new GraphStreamVisualizer(absDG, aVi.getAllStates().size(), rfA);
+		GraphStreamVisualizer test = new GraphStreamVisualizer(dg, n, rf);
+//		GraphStreamVisualizer test = new GraphStreamVisualizer(absDG, aVi.getAllStates().size(), rfA);
 		test.render();
 	}
 

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java
Fixed a just awful bug in how the abstract policy was being converted into a policy for the ground state.

@@ -50,21 +50,21 @@ public class QValueAbstractionTest {
 		RewardFunction rfA = qPhi.getRewardFunction();
 		Domain absD= absDG.generateDomain();
 		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
-		State aInitialState = GraphDefinedDomain.getState(absD, 0);
+		State aInitialState =  qPhi.getAbstractInitialState(absD, gInitialState);
 		GreedyQPolicy abstractPolicy = aVi.planFromState(aInitialState);	
 		
 
 		//Evaluate abstract policy in ground MDP:
-		Policy groundPolicyFromAbstractPolicy = qPhi.getPolicyForGroundMDP(abstractPolicy, absDG, dg);
-		PolicyIteration PI = new PolicyIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations, 1);
-		PI.setPolicyToEvaluate(groundPolicyFromAbstractPolicy);
-		PI.planFromState(gInitialState);
-		System.out.println("Value of initial state using abstract MDP: " + PI.value(gInitialState) + " vs value actual value of " + vi.value(gInitialState));
+		Policy groundPolicyFromAbstractPolicy = qPhi.getPolicyForGroundMDP(abstractPolicy, absD, d);
+//		PolicyIteration PI = new PolicyIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations, 1);
+//		PI.setPolicyToEvaluate(groundPolicyFromAbstractPolicy);
+//		PI.planFromState(gInitialState);
+//		System.out.println("Value of initial state using abstract MDP: " + PI.value(gInitialState) + " vs value actual value of " + vi.value(gInitialState));
 
 		// Print actions for all states
-//		for (int i = 0; i < n; i++) {
-//			State s = GraphDefinedDomain.getState(d, i);
-//			System.out.println("Action for state " + i + " is " +  groundPolicyFromAbstractPolicy.getAction(s).actionName() + " vs " + gPol.getAction(s).actionName() + " from the ground MDP");
-//		}
+		for (int i = 0; i < n; i++) {
+			State s = GraphDefinedDomain.getState(d, i);
[…]

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java

@@ -44,7 +44,7 @@ public class Test {
 		RewardFunction rfA = phiMod.getRewardFunction();
 		Domain absD= absDG.generateDomain();
 		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
-		State aInitialState = GraphDefinedDomain.getState(absD, 0);
+		State aInitialState = phiMod.getAbstractInitialState(absD, gInitialState);
 		aVi.planFromState(aInitialState);	
 		System.out.println("Abstract initial state value: " + aVi.value(aInitialState));
 		

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/UpWorldGenerator.java

@@ -63,7 +63,9 @@ public class UpWorldGenerator {
 
 		@Override
 		public double reward(State s, GroundedAction a, State sprime) {
-			if (s.equals(sprime) && a.actionName().equals("action2")) return 10;
+			if (s.equals(sprime) && a.actionName().equals("action2")){ 
+				return 10;
+			}
 			else return 0;
 		}
 

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/VIParams.java

@@ -1,7 +1,7 @@
 package graphStateAbstraction;
 
 public class VIParams {
-	public static int maxIterations = 100;
-	public static double maxDelta = .1;
-	public static double gamma = .99;
+	public static int maxIterations = 1000;
+	public static double maxDelta = .01;
+	public static double gamma = .9;
 }

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -20,6 +20,7 @@ import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.learning.tdmethods.QLearning;
 import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
@@ -31,13 +32,15 @@ import burlap.oomdp.core.states.State;
 import burlap.oomdp.singleagent.Action;
 import burlap.oomdp.singleagent.GroundedAction;
 import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.environment.SimulatedEnvironment;
+import burlap.oomdp.singleagent.explorer.TerminalExplorer;
 import burlap.oomdp.statehashing.HashableStateFactory;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 public class GraphStreamVisualizer {
-	private GraphDefinedDomain d;
 	int numStates;
 	RewardFunction rf;
+	private Domain d;
 
 	public static String styleSheet = 
 			"node {fill-color: grey;size: 40px;}" +
@@ -62,10 +65,10 @@ public class GraphStreamVisualizer {
 		"rgb(255,221,117)",
 	"rgb(255,205,56)"};
 
-	public GraphStreamVisualizer(GraphDefinedDomain d, int numStates, RewardFunction rf) {
-		this.d = d;
+	public GraphStreamVisualizer(Domain d, int numStates, RewardFunction rf) {
 		this.numStates = numStates;
 		this.rf = rf;
+		this.d = d;
 	}
 
 	public void render() {	
@@ -74,7 +77,7 @@ public class GraphStreamVisualizer {
 
 		Graph graph = new MultiGraph("Tutorial 1");	
 		graph.addAttribute("ui.stylesheet", styleSheet);
-		Domain dom = d.generateDomain();
+		Domain dom = this.d;
 
 		for (int stateIndex = 0; stateIndex < numStates; stateIndex++) {
 			//Add nodes for each state.
@@ -95,12 +98,9 @@ public class GraphStreamVisualizer {
[…]

### 2015-11-20 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/StateAbstractor.java

@@ -42,7 +42,7 @@ public abstract class StateAbstractor {
 		for (int stateIndex = 0; stateIndex < inpDG.getNumNodes(); stateIndex++) {
 			indexList.add(stateIndex);
 		}
-		Collections.shuffle(indexList);
+//		Collections.shuffle(indexList);
 		
 		for (int stateIndex : indexList) {
 			State currGroundState = GraphDefinedDomain.getState(inputD, stateIndex);
@@ -115,8 +115,8 @@ public abstract class StateAbstractor {
 							double groundReward = rf.reward(groundState, currGA, otherGroundedState);
 							rewardMatrix.get(currGA)[abstractStateIndex][otherAbstractStateIndex] += weightOfGroundState*groundReward;
 						}
-						if (transitionProbability != 0) toReturn.setTransition(abstractStateIndex, actionIndex, otherAbstractStateIndex, transitionProbability);
 					}
+						if (transitionProbability != 0) toReturn.setTransition(abstractStateIndex, actionIndex, otherAbstractStateIndex, transitionProbability);
 				}
 			}
 		}
@@ -135,27 +135,33 @@ public abstract class StateAbstractor {
 		return toReturn;
 	}
 	
+	public State getAbstractInitialState(Domain abstractDomain, State groundInitialState) {
+		int groundIndex = GraphDefinedDomain.getNodeId(groundInitialState);
+		int abstractInitialStateIndex = this.groundToAbstractState.get(groundIndex);
+		return GraphDefinedDomain.getState(abstractDomain, abstractInitialStateIndex);
+	}
+	
 	/**
 	 * Uses VI to solve for optimal policy in abstract state, then
 	 * returns the policy for ground MDP as the abstract policy dictates.
 	 * @return policy for ground MDP
 	 */
-	public Policy getPolicyForGroundMDP(GreedyQPolicy abstractPolicy, DomainGenerator abstractDG, DomainGenerator groundDG) {
-		return new PolicyForGroundMDP(this.groundToAbstractState, abstractPolicy, abstractDG, groundDG);
+	public Policy getPolicyForGroundMDP(GreedyQPolicy abstractPolicy, Domain abstractDomain, Domain groundDomain) {
+		return new PolicyForGroundMDP(this.groundToAbstractState, abstractPolicy, groundDomain, abstractDomain);
 	}
 	
 	private class PolicyForGroundMDP extends Policy {
 		
[…]

### 2015-11-30 paper/approximate_state_abstraction.tex
adding paper folder

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{aaai}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\title{Approximate State Abstraction}
\author{David Abel, D. Ellis Hershkowitz, Michael Littman}
\date{}                                           % Activate to display a given date or no date

% --- Note Commands ---
\usepackage{color}
\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
\newcommand\ellisnote[1]{\textcolor{red}{Ellis: #1}}

\begin{document}
\maketitle

% --- ABSTRACT ---
\begin{abstract}
The combinatorial explosion that plagues planning and reinforcement learning algorithms can be reversed using abstraction. For instance, prohibitively difficult robotics task representations can be condensed so that solutions are tractably computable. In this work, we investigate a theoretical framework for approximate state abstraction that preserves near optimal behavior. Reinforcement learning agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences. We present preliminary results and directions for future work.

Abstraction lies at the heart of computation. In this work, we demonstrate that the combinatorial explosion central to many issues in artificial intelligence can be reversed using effective abstraction methods. We extend the framework of state abstraction proposed by (Lihong et. al. 2005) to allow for approximately optimal state abstraction, and demonstrate that, in ideal scenarios, this framework allows for arbitrary reduction in the sample complexity of learning in certain learning problem. We develop methods for creating abstract problem representations and prove that their solutions have bounded error on the original, un-abstracted problem. Furthermore, we provide visualizations of the abstracted problems.

\end{abstract}

% --- SECTION: Introduction ---
\section{Introduction}

% --- SECTION: Background ---
\section{Background}

% --- SECTION: Related Work ---
\section{Related Work}

% --- SECTION: State Abstraction ---
\section{State Abstraction}

% --- SECTION: Preserving Optimality ---
\section{Preserving Optimality}

% --- SECTION: Example Domains ---
\section{Example Domains}

% --- SECTION: Conclusion ---
\section{Conclusion}

% --- BIBLIOGRAPHY ---
\bibliographystyle{aaai}
\bibliography{state_abs}

\end{document}

### 2015-12-03 paper/approximate_state_abstraction.tex
Outline updated

@@
 \newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\ellisnote[1]{\textcolor{red}{Ellis: #1}}
+\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
 
@@
 
+\begin{itemize}
+\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
+\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
+\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce them to a simpler form.
+\item In this work we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
+\item Q: Why approximate?
+\item A: Approximate can compress strictly more than compression based on equality
+\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
+\end{itemize}
+
 % --- SECTION: Background ---
 \section{Background}
+
+% Quick MDP blurb
+
+% Previous state aggregation stuff?
 
@@
 
+% Lihong
+
+% Nan/Lihong
+
+% Approximate bisimulation
+
+% Other folks...
+
 % --- SECTION: State Abstraction ---
-\section{State Abstraction}
+\section{Approximate State Abstraction}
 
-% --- SECTION: Preserving Optimality ---
-\section{Preserving Optimality}
+% Explain each of the Phi's
+% Subsections for proofs for each phi
+\dnote{Insert lemma for each phi as their subsection}
+
+% Subsection: Phi_M
+\subsection{$\Phi_M$}
+
+% Subsection: Phi_Q
+\subsection{$\Phi_Q^*$}
+
+% Subsection: Phi_D
+\subsection{$\Phi_D$}
+
+% Subsection: Other Abstractions
+\subsection{Other Abstractions}
 
@@
 
+\subsection{UpWorld}
+
+\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity}
+
+% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
+
+\subsection{NChain}
+
+% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
+
+\subsection{Trench}
+
+% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
+
 % --- SECTION: Conclusion ---
 \section{Conclusion}
+
+% Summary
+
+% Future Work
+\begin{enumerate}
+\item Learning Phi
+\begin{itemize}
+\item Exploration vs. Exploitation problem is different while trying to learn Phi
+\end{itemize}
+\item Compressibility
+\begin{itemize}
+\item Relationship between approximate abstract and compressibility
+\end{itemize}
+\item 
+\end{enumerate}
 

### 2015-12-03 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/VIParams.java
Added start of presentation

@@ -2,6 +2,6 @@ package graphStateAbstraction;
 
 public class VIParams {
 	public static int maxIterations = 1000;
-	public static double maxDelta = .01;
-	public static double gamma = .9;
+	public static double maxDelta = .001;
+	public static double gamma = .99;
 }

### 2015-12-03 Workspace and Code/stateAbstraction/State Abstraction/src/graphStreamVisualizer/GraphStreamVisualizer.java

@@ -134,31 +134,28 @@ public class GraphStreamVisualizer {
 		TerminalFunction tf = new NullTermination();
 
 		// Ground MDP
-		int height = 4;
-		int width = 5;
-		int n = height*width;
+		int height = 10;
+		int width = 30;
+		int n = 10;// height*width;
 		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = UpWorldGenerator.getUPWorld(width, height);
-		RewardFunction rf = new UpWorldGenerator.UpWorldRF();
+		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);//UpWorldGenerator.getUPWorld(width, height);
+		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);//UpWorldGenerator.UpWorldRF();
 		Domain d = dg.generateDomain();
 		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
 		State gInitialState = GraphDefinedDomain.getState(d, 0);
 		Policy gPol = vi.planFromState(gInitialState);	
-		System.out.println("Ground initial state value: " + vi.value(gInitialState));
 
 		// Abstract MDP VI with a PhiQ* for abstraction
 		TerminalFunction tfa = new NullTermination();
-		double epsilon = 0;
+		double epsilon = .001;
 		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
 		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, d.getActions());
 		HashableStateFactory hfA = new SimpleHashableStateFactory();
 		GraphDefinedDomain absDG = qPhi.abstractMDP(dg, rf);
 		RewardFunction rfA = qPhi.getRewardFunction();
 		Domain absD= absDG.generateDomain();
-		System.out.println("RUNNING VI FOR ABSTRACT");
 		ValueIteration aVi = new ValueIteration(absD, rfA, tfa, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
 		State aInitialState =  qPhi.getAbstractInitialState(absD, gInitialState);
-		System.out.println("Abstract initial state is: " + aInitialState);
 		GreedyQPolicy abstractPolicy = aVi.planFromState(aInitialState);	
 
 		//Evaluate abstract policy in ground MDP:
[…]

### 2015-12-03 Workspace and Code/stateAbstraction/State Abstraction/src/stateAbstractor/StateAbstractor.java

@@ -42,7 +42,7 @@ public abstract class StateAbstractor {
 		for (int stateIndex = 0; stateIndex < inpDG.getNumNodes(); stateIndex++) {
 			indexList.add(stateIndex);
 		}
-//		Collections.shuffle(indexList);
+		Collections.shuffle(indexList);
 		
 		for (int stateIndex : indexList) {
 			State currGroundState = GraphDefinedDomain.getState(inputD, stateIndex);
@@ -166,11 +166,9 @@ public abstract class StateAbstractor {
 
 		@Override
 		public AbstractGroundedAction getAction(State s) {
-			//TODO Implement properly
 			Integer groundStateInteger = GraphDefinedDomain.getNodeId(s);
 			Integer abstractStateInteger = this.groundToAbstract.get(groundStateInteger);
 			State abstractState = GraphDefinedDomain.getState(this.aD, abstractStateInteger);
-			System.out.println("abs state " + abstractState);
 			AbstractGroundedAction toReturn = this.abstractPolicy.getAction(abstractState);
 			return toReturn;
 		}

### 2015-12-10 paper/approximate_state_abstraction.tex
adding icml author kit

@@
-\documentclass[11pt]{article}
-\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
-\usepackage{aaai}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\documentclass{article}
+\usepackage{times}
 \usepackage{graphicx}
-\title{Approximate State Abstraction}
-\author{David Abel, D. Ellis Hershkowitz, Michael Littman}
-\date{}                                           % Activate to display a given date or no date
+\usepackage{subfigure} 
+\usepackage{natbib}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{hyperref}
+\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
+\usepackage{icml2016/icml2016}
+
+\icmltitlerunning{Approximate State Abstraction}
 
@@
 
+% --- DOCUMENT ---
 \begin{document}
-\maketitle
+
+\twocolumn[
+\icmltitle{Approximate State Abstraction}
+
+% Paper Meta Info
+\icmlauthor{David Abel}{david_abel@brown.edu}
+\icmladdress{Brown University,
+            115 Waterman Street, Providence, RI 02906}
+\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
+\icmladdress{Brown University,
+            115 Waterman Street, Providence, RI 02906}
+\icmlauthor{Michael Littman}{michael_littman@brown.edu}
+\icmladdress{Brown University,
+            115 Waterman Street, Providence, RI 02906}
+
+\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
+
+\vskip 0.3in
+]
 
@@
 \end{abstract}
+
+% Set of actions within epsilon (Q*) is the same for two states? Better than boltzmann.
 

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/GraphTrenchRF.java
adding trench domain

@@ -1,0 +1,26 @@
+package domains.trench;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+
+public class GraphTrenchRF implements RewardFunction {
+
+	int terminalStateID;
+	
+	public GraphTrenchRF(int terminalStateID) {
+		this.terminalStateID = terminalStateID;
+	}
+	
+	@Override
+	public double reward(State s, GroundedAction a, State sprime) {
+		if(this.terminalStateID == GraphDefinedDomain.getNodeId(s)) {
+			return 100.0;
+		}
+		else {
+			return -1.0;
+		}
+	}
+
+}

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/GraphTrenchTF.java

@@ -1,0 +1,25 @@
+package domains.trench;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+
+public class GraphTrenchTF implements TerminalFunction {
+
+	int terminalStateID;
+	
+	public GraphTrenchTF(int terminalStateID) {
+		this.terminalStateID = terminalStateID;
+	}
+	
+	@Override
+	public boolean isTerminal(State s) {
+		if(this.terminalStateID == GraphDefinedDomain.getNodeId(s)) {
+			return true;
+		}
+		else {
+			return false;
+		}
+	}
+
+}

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/TrenchDomainToGraphDomain.java

@@ -1,0 +1,84 @@
+package domains.trench;
+
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class TrenchDomainToGraphDomain {
+
+	TrenchGenerator trenchGen;
+	Domain oldDomain;
+	public int goalStateID = -1;
+	public int initStateID = -1;
+	
+	public TrenchDomainToGraphDomain(TrenchGenerator tg) {
+		this.trenchGen = tg;
+		this.oldDomain = this.trenchGen.generateDomain();
+	}
+	
+	
+	public GraphDefinedDomain createGraphDomain() {
+		// Get all states and actions.
+		List<State> allStates = getAllStatesFromTrenchProb();
+		List<Action> allActions = this.oldDomain.getActions();
+		GraphDefinedDomain gd = new GraphDefinedDomain(allStates.size());
+		setTransitions(allStates, allActions, gd);
+		initStateID = allStates.indexOf(this.trenchGen.getInitialState(this.oldDomain));
+
+		return gd;
+	}
+	
+	private void setTransitions(List<State> allStates, List<Action> allActions, GraphDefinedDomain gd) {
+		
+		TerminalFunction tf = new TrenchGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
+		
+		
+		for (int stateIndex = 0; stateIndex < allStates.size(); stateIndex++) {
+			
+			if (goalStateID == -1 && tf.isTerminal(allStates.get(stateIndex))) {
+				// Found the terminal state.
+				goalStateID = stateIndex;
+			}
+			
+			for (int actionIndex = 0; actionIndex < allActions.size(); actionIndex++) {
+				
+				// Find S, A, S'.
+				GroundedAction ga = allActions.get(actionIndex).getAssociatedGroundedAction();
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/TrenchGenerator.java

@@ -1,0 +1,367 @@
+package domains.trench;
+
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.EpisodeAnalysis;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.core.Attribute;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.ObjectClass;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.TransitionProbability;
+import burlap.oomdp.core.objects.MutableObjectInstance;
+import burlap.oomdp.core.objects.ObjectInstance;
+import burlap.oomdp.core.states.MutableState;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.FullActionModel;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.SADomain;
+import burlap.oomdp.singleagent.common.SimpleAction;
+import burlap.oomdp.singleagent.common.SimpleAction.SimpleDeterministicAction;
+import burlap.oomdp.singleagent.environment.SimulatedEnvironment;
+import burlap.oomdp.singleagent.explorer.TerminalExplorer;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+
+
+public class TrenchGenerator implements DomainGenerator {
+	
+	public static final String ATTX = "x";
+	public static final String ATTY = "y";
+	public static final String ATTNUMBLOCKS = "numBlocks";
+
+	public static final String CLASSAGENT = "agent";
+	public static final String CLASSCELL = "cell";
+
+	public static final String ACTIONNORTH = "north";
+	public static final String ACTIONSOUTH = "south";
+	public static final String ACTIONEAST = "east";
+	public static final String ACTIONWEST = "west";
+	public static final String ACTIONPLACE = "place";
+
+	public static final String PFAT = "at";
+	
+	private int maxBlockStackHeight = 2;
+	
+	int width;
+	int height;
+	int trenchY;
+	
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QStarEpsilonTest.java

@@ -3,6 +3,10 @@ package graphStateAbstraction;
 import java.util.ArrayList;
 import java.util.List;
 
+import domains.trench.GraphTrenchRF;
+import domains.trench.GraphTrenchTF;
+import domains.trench.TrenchDomainToGraphDomain;
+import domains.trench.TrenchGenerator;
 import stateAbstractor.PhiSAReal;
 import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
@@ -10,6 +14,7 @@ import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
 import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.debugtools.DPrint;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.auxiliary.DomainGenerator;
 import burlap.oomdp.auxiliary.common.NullTermination;
@@ -37,7 +42,7 @@ public class QStarEpsilonTest {
 	}
 
 
-	public static List<EpsilonToNumStatesTuple> testQPhiStateReduction(GraphDefinedDomain dg, RewardFunction rf, double startEpsilon, double endEpsilon, double epsilonStep) {
+	public static List<EpsilonToNumStatesTuple> testQPhiStateReduction(GraphDefinedDomain dg, RewardFunction rf, int initStateID, double startEpsilon, double endEpsilon, double epsilonStep) {
 		List<EpsilonToNumStatesTuple> toReturn = new ArrayList<EpsilonToNumStatesTuple>();
 
 		for (double epsilon = startEpsilon; epsilon < endEpsilon; epsilon = epsilon*2) {
@@ -96,19 +101,44 @@ public class QStarEpsilonTest {
 		//		}
 
 		//--------UPWORLD--------
-		int upWorldWidth = 50;
-		int upWorldHeight = 20;
-		GraphDefinedDomain upWorldDG = UpWorldGenerator.getUPWorld(upWorldWidth, upWorldHeight);
-		RewardFunction upWorldRF = new UpWorldGenerator.UpWorldRF();
-		double UWStartEpsilon = 0.01;
-		double UWEndEpsilon = 1000;
-		double UWEpsStep = 1;
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/GraphTrenchRF.java
Fixed graph trench world.

@@ -1,26 +1,0 @@
-package domains.trench;
-
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.core.states.State;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-
-public class GraphTrenchRF implements RewardFunction {
-
-	int terminalStateID;
-	
-	public GraphTrenchRF(int terminalStateID) {
-		this.terminalStateID = terminalStateID;
-	}
-	
-	@Override
-	public double reward(State s, GroundedAction a, State sprime) {
-		if(this.terminalStateID == GraphDefinedDomain.getNodeId(s)) {
-			return 100.0;
-		}
-		else {
-			return -1.0;
-		}
-	}
-
-}

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/GraphTrenchTF.java

@@ -1,25 +1,0 @@
-package domains.trench;
-
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.core.states.State;
-
-public class GraphTrenchTF implements TerminalFunction {
-
-	int terminalStateID;
-	
-	public GraphTrenchTF(int terminalStateID) {
-		this.terminalStateID = terminalStateID;
-	}
-	
-	@Override
-	public boolean isTerminal(State s) {
-		if(this.terminalStateID == GraphDefinedDomain.getNodeId(s)) {
-			return true;
-		}
-		else {
-			return false;
-		}
-	}
-
-}

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/domains/trench/TrenchDomainToGraphDomain.java

@@ -1,84 +1,0 @@
-package domains.trench;
-
-import java.util.List;
-
-import burlap.behavior.policy.GreedyQPolicy;
-import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.core.Domain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.core.states.State;
-import burlap.oomdp.singleagent.Action;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-
-public class TrenchDomainToGraphDomain {
-
-	TrenchGenerator trenchGen;
-	Domain oldDomain;
-	public int goalStateID = -1;
-	public int initStateID = -1;
-	
-	public TrenchDomainToGraphDomain(TrenchGenerator tg) {
-		this.trenchGen = tg;
-		this.oldDomain = this.trenchGen.generateDomain();
-	}
-	
-	
-	public GraphDefinedDomain createGraphDomain() {
-		// Get all states and actions.
-		List<State> allStates = getAllStatesFromTrenchProb();
-		List<Action> allActions = this.oldDomain.getActions();
-		GraphDefinedDomain gd = new GraphDefinedDomain(allStates.size());
-		setTransitions(allStates, allActions, gd);
-		initStateID = allStates.indexOf(this.trenchGen.getInitialState(this.oldDomain));
-
-		return gd;
-	}
-	
-	private void setTransitions(List<State> allStates, List<Action> allActions, GraphDefinedDomain gd) {
-		
-		TerminalFunction tf = new TrenchGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
-		
-		
-		for (int stateIndex = 0; stateIndex < allStates.size(); stateIndex++) {
-			
-			if (goalStateID == -1 && tf.isTerminal(allStates.get(stateIndex))) {
-				// Found the terminal state.
-				goalStateID = stateIndex;
-			}
-			
-			for (int actionIndex = 0; actionIndex < allActions.size(); actionIndex++) {
-				
-				// Find S, A, S'.
-				GroundedAction ga = allActions.get(actionIndex).getAssociatedGroundedAction();
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/NStateChainGenerator.java

@@ -1,68 +1,0 @@
-package graphStateAbstraction;
-
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.core.states.State;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-
-/**
- * A class with static methods to instantiate nstate problems and nstate chain reward functions.
- * @author Dhershkowitz
- *
- */
-public class NStateChainGenerator {
-	/**
-	 * 
-	 * @param totalNumStates
-	 * @return an n state graph MDP.
-	 */
-	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
-		double slipProb = .2;
-
-		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
-
-		// Set up transitions
-		for (int i = 0; i < totalNumStates-1; i++) {
-			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, i+1, slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, 0, 1.0-slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, 0, slipProb);
-			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, i+1, 1.0-slipProb);
-		}
-
-		// Set up last state transition
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0,1.0-slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
-		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
-
-		return dg;
-	}	
-	
-	/**
-	 * n State chain reward function -- returns 10 if action 1 is taken in the last state, 2 if
-	 * action 0 is taken ever and 0 otherwise.
-	 * @author Dhershkowitz
-	 *
-	 */
-	public static class nStateChainRF implements RewardFunction {
-		int n;
-		
-		public nStateChainRF(int n) {
-			this.n = n;
-		}
-
-		@Override
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QStarEpsilonTest.java

@@ -1,158 +1,0 @@
-package graphStateAbstraction;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import domains.trench.GraphTrenchRF;
-import domains.trench.GraphTrenchTF;
-import domains.trench.TrenchDomainToGraphDomain;
-import domains.trench.TrenchGenerator;
-import stateAbstractor.PhiSAReal;
-import stateAbstractor.StateAbstractor;
-import SARealGenerators.qValueGenerator;
-import burlap.behavior.policy.GreedyQPolicy;
-import burlap.behavior.policy.Policy;
-import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
-import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
-import burlap.debugtools.DPrint;
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.auxiliary.DomainGenerator;
-import burlap.oomdp.auxiliary.common.NullTermination;
-import burlap.oomdp.core.Domain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.core.states.State;
-import burlap.oomdp.singleagent.RewardFunction;
-import burlap.oomdp.statehashing.HashableStateFactory;
-import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-
-public class QStarEpsilonTest {
-	public static class EpsilonToNumStatesTuple {
-		private double eps;
-		private int numStates;
-		private double valOfInitialState;
-		public EpsilonToNumStatesTuple(double epsilon, int numStates, double valOfInitialState) {
-			this.eps = epsilon;
-			this.numStates = numStates;
-			this.valOfInitialState = valOfInitialState;
-		}
-		@Override
-		public String toString() {
-			return eps + "\t" + numStates + "\t" + valOfInitialState;
-		}
-	}
-
-
-	public static List<EpsilonToNumStatesTuple> testQPhiStateReduction(GraphDefinedDomain dg, RewardFunction rf, int initStateID, double startEpsilon, double endEpsilon, double epsilonStep) {
-		List<EpsilonToNumStatesTuple> toReturn = new ArrayList<EpsilonToNumStatesTuple>();
-
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/QValueAbstractionTest.java

@@ -1,70 +1,0 @@
-package graphStateAbstraction;
-
-import stateAbstractor.PhiModel;
-import stateAbstractor.PhiSAReal;
-import stateAbstractor.StateAbstractor;
-import SARealGenerators.qValueGenerator;
-import burlap.behavior.policy.GreedyQPolicy;
-import burlap.behavior.policy.Policy;
-import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
-import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
-import burlap.oomdp.core.states.State;
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.auxiliary.common.NullTermination;
-import burlap.oomdp.core.Domain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-import burlap.oomdp.singleagent.common.UniformCostRF;
-import burlap.oomdp.statehashing.HashableStateFactory;
-import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-
-/**
- * An example of Q* abstraction in an 5 state chain MDP.
- * @author Dhershkowitz
- *
- */
-public class QValueAbstractionTest {
-
-	public static void main(String[] args) {
-		//VI Params
-		TerminalFunction tf = new NullTermination();
-
-		// Ground MDP
-		int n = 100;
-		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
-		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
-		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
-		State gInitialState = GraphDefinedDomain.getState(d, 0);
-		Policy gPol = vi.planFromState(gInitialState);	
-		System.out.println("Ground initial state value: " + vi.value(gInitialState));
-
-		// Abstract MDP VI with a PhiQ* for abstraction
-		double epsilon = 1000;
-		qValueGenerator qGen = new qValueGenerator(d, rf, gInitialState);
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/State Abstraction/src/graphStateAbstraction/Test.java

@@ -1,58 +1,0 @@
-package graphStateAbstraction;
-
-import stateAbstractor.PhiModel;
-import stateAbstractor.StateAbstractor;
-import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
-import burlap.oomdp.core.states.State;
-import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
-import burlap.oomdp.auxiliary.common.NullTermination;
-import burlap.oomdp.core.Domain;
-import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.singleagent.GroundedAction;
-import burlap.oomdp.singleagent.RewardFunction;
-import burlap.oomdp.singleagent.common.UniformCostRF;
-import burlap.oomdp.statehashing.HashableStateFactory;
-import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-
-public class Test {
-
-
-	/**
-	 * An example of phiModel (currently not actually implemented).
-	 * @param args
-	 */
-	public static void main(String[] args) {
-		//VI Params
-
-		TerminalFunction tf = new NullTermination();
-		
-		// Ground MDP
-		int n = 5;
-		HashableStateFactory hf = new SimpleHashableStateFactory();
-		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
-		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
-		Domain d = dg.generateDomain();
-		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
-		State gInitialState = GraphDefinedDomain.getState(d, 0);
-		vi.planFromState(gInitialState);	
-		System.out.println("Ground initial state value: " + vi.value(gInitialState));
-		
-		// Abstract MDP VI with a PhiModel for abstraction
-		HashableStateFactory hfA = new SimpleHashableStateFactory();
-		StateAbstractor phiMod = new PhiModel();
-		GraphDefinedDomain absDG = phiMod.abstractMDP(dg, rf);
-		RewardFunction rfA = phiMod.getRewardFunction();
-		Domain absD= absDG.generateDomain();
-		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/src/domains/NStateChainGenerator.java

@@ -1,0 +1,68 @@
+package domains;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+
+/**
+ * A class with static methods to instantiate nstate problems and nstate chain reward functions.
+ * @author Dhershkowitz
+ *
+ */
+public class NStateChainGenerator {
+	/**
+	 * 
+	 * @param totalNumStates
+	 * @return an n state graph MDP.
+	 */
+	public static GraphDefinedDomain getNStateChain(int totalNumStates) {
+		double slipProb = .2;
+
+		GraphDefinedDomain dg = new GraphDefinedDomain(totalNumStates);
+
+		// Set up transitions
+		for (int i = 0; i < totalNumStates-1; i++) {
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, i+1, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 0/*action*/, 0, 1.0-slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, 0, slipProb);
+			((GraphDefinedDomain) dg).setTransition(i, 1/*action*/, i+1, 1.0-slipProb);
+		}
+
+		// Set up last state transition
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, totalNumStates-1, slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 0/*action*/, 0,1.0-slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, totalNumStates-1, 1.0-slipProb);
+		((GraphDefinedDomain) dg).setTransition(totalNumStates-1, 1/*action*/, 0, slipProb);
+
+		return dg;
+	}	
+	
+	/**
+	 * n State chain reward function -- returns 10 if action 1 is taken in the last state, 2 if
+	 * action 0 is taken ever and 0 otherwise.
+	 * @author Dhershkowitz
+	 *
+	 */
+	public static class nStateChainRF implements RewardFunction {
+		int n;
+		
+		public nStateChainRF(int n) {
+			this.n = n;
+		}
+
+		@Override
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/src/domains/trench/TrenchDomainToGraphDomain.java

@@ -1,0 +1,86 @@
+package domains.trench;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class TrenchDomainToGraphDomain {
+
+	TrenchGenerator trenchGen;
+	Domain oldDomain;
+	public List<Integer> goalStateIDs;
+	public int initStateID;
+	
+	public TrenchDomainToGraphDomain(TrenchGenerator tg) {
+		this.trenchGen = tg;
+		this.goalStateIDs = new ArrayList<Integer>();
+		this.oldDomain = this.trenchGen.generateDomain();
+	}
+	
+	
+	public GraphDefinedDomain createGraphDomain() {
+		// Get all states and actions.
+		List<State> allStates = getAllStatesFromTrenchProb();
+		List<Action> allActions = this.oldDomain.getActions();
+		GraphDefinedDomain gd = new GraphDefinedDomain(allStates.size());
+		setTransitions(allStates, allActions, gd);
+		initStateID = allStates.indexOf(this.trenchGen.getInitialState(this.oldDomain));
+
+		return gd;
+	}
+	
+	private void setTransitions(List<State> allStates, List<Action> allActions, GraphDefinedDomain gd) {
+		
+		TerminalFunction tf = new TrenchGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
+		
+		
+		for (int stateIndex = 0; stateIndex < allStates.size(); stateIndex++) {
+			
+			if (tf.isTerminal(allStates.get(stateIndex))) {
+				// Found the terminal state.
+				goalStateIDs.add(stateIndex);
+			}
+			
+			for (int actionIndex = 0; actionIndex < allActions.size(); actionIndex++) {
+				
+				// Find S, A, S'.
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/src/domains/trench/TrenchGenerator.java

@@ -1,0 +1,381 @@
+package domains.trench;
+
+import graphStreamVisualizer.GraphStreamVisualizer;
+
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.EpisodeAnalysis;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.core.Attribute;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.ObjectClass;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.TransitionProbability;
+import burlap.oomdp.core.objects.MutableObjectInstance;
+import burlap.oomdp.core.objects.ObjectInstance;
+import burlap.oomdp.core.states.MutableState;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.FullActionModel;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.SADomain;
+import burlap.oomdp.singleagent.common.SimpleAction;
+import burlap.oomdp.singleagent.common.SimpleAction.SimpleDeterministicAction;
+import burlap.oomdp.singleagent.environment.SimulatedEnvironment;
+import burlap.oomdp.singleagent.explorer.TerminalExplorer;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+
+
+public class TrenchGenerator implements DomainGenerator {
+	
+	public static final String ATTX = "x";
+	public static final String ATTY = "y";
+	public static final String ATTNUMBLOCKS = "numBlocks";
+
+	public static final String CLASSAGENT = "agent";
+	public static final String CLASSCELL = "cell";
+
+	public static final String ACTIONNORTH = "north";
+	public static final String ACTIONSOUTH = "south";
+	public static final String ACTIONEAST = "east";
+	public static final String ACTIONWEST = "west";
+	public static final String ACTIONPLACE = "place";
+
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/src/graphStateAbstraction/QStarEpsilonTest.java

@@ -1,0 +1,159 @@
+package graphStateAbstraction;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import domains.trench.GraphTrenchRF;
+import domains.trench.GraphTrenchTF;
+import domains.trench.TrenchDomainToGraphDomain;
+import domains.trench.TrenchGenerator;
+import domains.trench.TrenchGenerator.TrenchRF;
+import domains.trench.TrenchGenerator.TrenchTF;
+import stateAbstractor.PhiSAReal;
+import stateAbstractor.StateAbstractor;
+import SARealGenerators.qValueGenerator;
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.EpisodeAnalysis;
+import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.debugtools.DPrint;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class QStarEpsilonTest {
+	public static class EpsilonToNumStatesTuple {
+		private double eps;
+		private int numStates;
+		private double valOfInitialState;
+		public EpsilonToNumStatesTuple(double epsilon, int numStates, double valOfInitialState) {
+			this.eps = epsilon;
+			this.numStates = numStates;
+			this.valOfInitialState = valOfInitialState;
+		}
+		@Override
+		public String toString() {
+			return eps + "\t" + numStates + "\t" + valOfInitialState;
+		}
+	}
+
+
[…]

### 2015-12-12 Workspace and Code/stateAbstraction/src/graphStateAbstraction/Test.java

@@ -1,0 +1,59 @@
+package graphStateAbstraction;
+
+import domains.NStateChainGenerator;
+import stateAbstractor.PhiModel;
+import stateAbstractor.StateAbstractor;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.oomdp.core.states.State;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.common.UniformCostRF;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class Test {
+
+
+	/**
+	 * An example of phiModel (currently not actually implemented).
+	 * @param args
+	 */
+	public static void main(String[] args) {
+		//VI Params
+
+		TerminalFunction tf = new NullTermination();
+		
+		// Ground MDP
+		int n = 5;
+		HashableStateFactory hf = new SimpleHashableStateFactory();
+		GraphDefinedDomain dg = NStateChainGenerator.getNStateChain(n);
+		RewardFunction rf = new NStateChainGenerator.nStateChainRF(n);
+		Domain d = dg.generateDomain();
+		ValueIteration vi = new ValueIteration(d, rf, tf, VIParams.gamma, hf, VIParams.maxDelta, VIParams.maxIterations);
+		State gInitialState = GraphDefinedDomain.getState(d, 0);
+		vi.planFromState(gInitialState);	
+		System.out.println("Ground initial state value: " + vi.value(gInitialState));
+		
+		// Abstract MDP VI with a PhiModel for abstraction
+		HashableStateFactory hfA = new SimpleHashableStateFactory();
+		StateAbstractor phiMod = new PhiModel();
+		GraphDefinedDomain absDG = phiMod.abstractMDP(dg, rf);
+		RewardFunction rfA = phiMod.getRewardFunction();
+		Domain absD= absDG.generateDomain();
+		ValueIteration aVi = new ValueIteration(absD, rfA, tf, VIParams.gamma, hfA, VIParams.maxDelta, VIParams.maxIterations);
[…]

### 2015-12-15 paper/approximate_state_abstraction.tex
adding writeup draft
adding outline and bib

@@
 \usepackage{algorithmic}
+\usepackage{subfigure}
 \usepackage{hyperref}
@@
 The combinatorial explosion that plagues planning and reinforcement learning algorithms can be reversed using abstraction.
-For instance, prohibitively difficult robotics task representations can be condensed so that solutions are tractably computable.
+For instance, prohibitively difficult task representations can be condensed so that solutions are tractably computable.
 In this work, we investigate a theoretical framework for approximate state abstraction that preserves near optimal behavior.
 Reinforcement learning agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present preliminary results and directions for future work.
-
-Abstraction lies at the heart of computation.
-In this work, we demonstrate that the combinatorial explosion central to many issues in artificial intelligence can be reversed using effective abstraction methods.
-We extend the framework of state abstraction proposed by (Lihong et.
-al.
-2005) to allow for approximately optimal state abstraction, and demonstrate that, in ideal scenarios, this framework allows for arbitrary reduction in the sample complexity of learning in certain learning problem.
-We develop methods for creating abstract problem representations and prove that their solutions have bounded error on the original, un-abstracted problem.
-Furthermore, we provide visualizations of the abstracted problems.
-
+We present theoretical guarantees of the quality of value functions derived from three classes of approximate state abstraction.
+Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved, as well as the tradeoff between approximation magnitude and optimality of behavior.
 \end{abstract}
@@
 \item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
-\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce them to a simpler form.
+\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
 \item In this work we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
@@
 
-% --- SECTION: Background ---
-\section{Background}
-
-% Quick MDP blurb
-
-% Previous state aggregation stuff?
-
 % --- SECTION: Related Work ---
@@
 
-% Lihong
+% Lihong/Walsh/Littman: Towards a unified theory...
+Citation test~\cite{li2006towards}
 
@@
 
-% Other folks...
+% David Silver: Options/State Abstraction?
+
+% Russell? PHAM/HAM/ALisp
+
+% Konidaris? Options induce symbolic representation on continuous state space
+
+% Littman: Relocatable Action Models
+
+% Stone: State Abstraction Discovery from Irrelevant State Vars
+
+% Others...
+
+% --- SECTION: Background ---
+\section{Background}
+
+% Quick MDP blurb?
+
+% Phi notation
+
+% Evluation of Abstract MDP
+
+% Abstract MDP, Ground MDP, Homogenizing Gun
+
+% Previous state aggregation stuff? Or should be in related work?
 
@@
 
-% Explain each of the Phi's
+% Explain each of the Phis
+
+% One theorem, each separate phi is its own lemma.
+
 % Subsections for proofs for each phi
 \dnote{Insert lemma for each phi as their subsection}
+
+% Subsection:
 
@@
 
+% Subsection: Phi_B
+\subsection{$\Phi_B$}
+\dnote{$\Phi_{Boltzmann}$}
+
 % Subsection: Other Abstractions
 \subsection{Other Abstractions}
+
+% Discussion of other abstractions we looked into
+
+% Some abstractions DON'T preserve a meaningful notion of optimality.
 
@@
 
+\dnote{For each section, we'll include a plot comparing $\epsilon$ to \# states, and $\epsilon$ to performance.
+For UpWorld and NChain, we can include visuals of uncompressed and compressed (not useful for trench).}
+
+% Subsection: UpWorld
 \subsection{UpWorld}
 
-\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity}
+\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity (small lemma or something?)}
 
@@
 
+% Subsection: NChain
 \subsection{NChain}
@@
 
+% Subsection: Trench
 \subsection{Trench}
@@
 % Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
+
+% Figure: The Trench Problem
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.42\columnwidth]{figures/placeholder.png}
+\caption{The Trench Problem}
+\label{fig:trench}
+\end{figure}
+
+% --- SECTION: Approximate Abstraction on Example Domains ---
+\section{Approximate Abstraction on Example Domains}
+
+% Figure: Epsilon vs. #States for all three sample domains.
+\begin{figure}
+\subfigure[UpWorld]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\subfigure[NChain]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\subfigure[Trench]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\label{fig:eps-states}
+\caption{$\epsilon$ vs. Num States}
+\end{figure}
+
+% Figure: Epsilon vs. Error in Abstract Value Function
+\begin{figure}
+\subfigure[UpWorld]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\subfigure[NChain]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\subfigure[Trench]{
+\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\label{fig:eps-states}
+\caption{$\epsilon$ vs. Error in Abstract Value Function}
+\end{figure}
+
+% Subsection: Abstract Domain Visualizations
+\subsection{Abstract Domain Visualizations}
+
+% Figure: UpWorld MDP visuals
+\begin{figure}[h]
+\centering
+\subfigure[UpWorld]{
+\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
+\hspace{3mm}
+\subfigure[Abstracted UpWorld]{
+\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
+\caption{Visualization of Original UpWorld vs. Abstracted UpWorld}
+\end{figure}
+
+% Figure: NChain MDP visuals
+\begin{figure}[h]
+\centering
+\subfigure[NChain]{
+\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
+\hspace{3mm}
+\subfigure[Abstracted NChain ]{
+\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
+\caption{Visualization of Original NChain vs. Abstracted NChain}
+\end{figure}
 
@@
 \end{itemize}
-\item 
+\item POMDP and abstraction
 \end{enumerate}
@@
 % --- BIBLIOGRAPHY ---
-\bibliographystyle{aaai}
+\bibliographystyle{icml2016/icml2016}
 \bibliography{state_abs}

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/NormalDomainToGraphDomain.java
added a class that takes as input an arbitrary domain generator and converts it into a graph domain

@@ -1,0 +1,99 @@
+package domains;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.Action;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+public class NormalDomainToGraphDomain {
+
+	DomainGenerator domainGen;
+	TerminalFunction oldDomainTF;
+	RewardFunction oldDomainRF;
+	State oldDomainInitialState;
+	Domain oldDomain;
+	public List<Integer> goalStateIDs;
+	public int initStateID;
+	
+	public NormalDomainToGraphDomain(DomainGenerator tg, TerminalFunction originalTF, RewardFunction originalRF, State initState) {
+		this.domainGen = tg;
+		this.oldDomainTF = originalTF;
+		this.oldDomainRF = originalRF;
+		this.oldDomainInitialState = initState;
+		this.goalStateIDs = new ArrayList<Integer>();
+		this.oldDomain = this.domainGen.generateDomain();
+	}
+	
+	
+	public GraphDefinedDomain createGraphDomain() {
+		// Get all states and actions.
+		List<State> allStates = getAllStates();
+		List<Action> allActions = this.oldDomain.getActions();
+		
+		// Create GraphDefinedDomain.
+		GraphDefinedDomain gd = new GraphDefinedDomain(allStates.size());
+		
+		// Set Transitions.
+		setTransitionsAndFindGoalStates(allStates, allActions, gd);
+		
+		// Set initial state.
+		initStateID = allStates.indexOf(this.oldDomainInitialState);
+
+		return gd;
+	}
+	
+	private void setTransitionsAndFindGoalStates(List<State> allStates, List<Action> allActions, GraphDefinedDomain gd) {
+		
+		// Loop over each state and set transitions in the graph.
+		for (int stateIndex = 0; stateIndex < allStates.size(); stateIndex++) {
+			
[…]

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/GraphRF.java
Streamlined experiments to single function

@@ -1,4 +1,4 @@
-package domains.trench;
+package domains;
 
 import java.util.List;
 
@@ -7,11 +7,11 @@ import burlap.oomdp.core.states.State;
 import burlap.oomdp.singleagent.GroundedAction;
 import burlap.oomdp.singleagent.RewardFunction;
 
-public class GraphTrenchRF implements RewardFunction {
+public class GraphRF implements RewardFunction {
 
 	List<Integer> terminalStateIDs;
 	
-	public GraphTrenchRF(List<Integer> terminalStateIDs) {
+	public GraphRF(List<Integer> terminalStateIDs) {
 		this.terminalStateIDs = terminalStateIDs;
 	}
 	

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/GraphTF.java

@@ -1,4 +1,4 @@
-package domains.trench;
+package domains;
 
 import java.util.List;
 
@@ -6,11 +6,11 @@ import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.core.TerminalFunction;
 import burlap.oomdp.core.states.State;
 
-public class GraphTrenchTF implements TerminalFunction {
+public class GraphTF implements TerminalFunction {
 
 	List<Integer> terminalStateIDs;
 	
-	public GraphTrenchTF(List<Integer> terminalStateIDs) {
+	public GraphTF(List<Integer> terminalStateIDs) {
 		this.terminalStateIDs = terminalStateIDs;
 	}
 	

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/nchain/NStateChainGenerator.java

@@ -1,4 +1,4 @@
-package domains;
+package domains.nchain;
 
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.core.states.State;

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/trench/TrenchDomainGenerator.java

@@ -1,9 +1,10 @@
 package domains.trench;
 
-import graphStreamVisualizer.GraphStreamVisualizer;
-
 import java.util.List;
 
+import domains.GraphRF;
+import domains.GraphTF;
+import domains.NormalDomainToGraphDomain;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.singleagent.EpisodeAnalysis;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
@@ -13,7 +14,6 @@ import burlap.oomdp.core.Attribute;
 import burlap.oomdp.core.Domain;
 import burlap.oomdp.core.ObjectClass;
 import burlap.oomdp.core.TerminalFunction;
-import burlap.oomdp.core.TransitionProbability;
 import burlap.oomdp.core.objects.MutableObjectInstance;
 import burlap.oomdp.core.objects.ObjectInstance;
 import burlap.oomdp.core.states.MutableState;
@@ -22,39 +22,39 @@ import burlap.oomdp.singleagent.FullActionModel;
 import burlap.oomdp.singleagent.GroundedAction;
 import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.singleagent.SADomain;
-import burlap.oomdp.singleagent.common.SimpleAction;
 import burlap.oomdp.singleagent.common.SimpleAction.SimpleDeterministicAction;
-import burlap.oomdp.singleagent.environment.SimulatedEnvironment;
-import burlap.oomdp.singleagent.explorer.TerminalExplorer;
-import burlap.oomdp.statehashing.HashableStateFactory;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 
 
-public class TrenchGenerator implements DomainGenerator {
+public class TrenchDomainGenerator implements DomainGenerator {
 	
+	// OO-MDP attributes.
 	public static final String ATTX = "x";
 	public static final String ATTY = "y";
 	public static final String ATTNUMBLOCKS = "numBlocks";
 
+	// OO-MDP object classes.
 	public static final String CLASSAGENT = "agent";
 	public static final String CLASSCELL = "cell";
 
+	// Action names.
 	public static final String ACTIONNORTH = "north";
 	public static final String ACTIONSOUTH = "south";
 	public static final String ACTIONEAST = "east";
 	public static final String ACTIONWEST = "west";
[…]

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/trench/TrenchDomainToGraphDomain.java

@@ -16,12 +16,12 @@ import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 public class TrenchDomainToGraphDomain {
 
-	TrenchGenerator trenchGen;
+	TrenchDomainGenerator trenchGen;
 	Domain oldDomain;
 	public List<Integer> goalStateIDs;
 	public int initStateID;
 	
-	public TrenchDomainToGraphDomain(TrenchGenerator tg) {
+	public TrenchDomainToGraphDomain(TrenchDomainGenerator tg) {
 		this.trenchGen = tg;
 		this.goalStateIDs = new ArrayList<Integer>();
 		this.oldDomain = this.trenchGen.generateDomain();
@@ -41,7 +41,7 @@ public class TrenchDomainToGraphDomain {
 	
 	private void setTransitions(List<State> allStates, List<Action> allActions, GraphDefinedDomain gd) {
 		
-		TerminalFunction tf = new TrenchGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
+		TerminalFunction tf = new TrenchDomainGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
 		
 		
 		for (int stateIndex = 0; stateIndex < allStates.size(); stateIndex++) {
@@ -70,8 +70,8 @@ public class TrenchDomainToGraphDomain {
 	private List<State> getAllStatesFromTrenchProb() {
 		
 		State initialState = this.trenchGen.getInitialState(this.oldDomain);
-		RewardFunction rf = new TrenchGenerator.TrenchRF(this.trenchGen.width - 1, this.trenchGen.height - 1);
-		TerminalFunction tf = new TrenchGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
+		RewardFunction rf = new TrenchDomainGenerator.TrenchRF(this.trenchGen.width - 1, this.trenchGen.height - 1);
+		TerminalFunction tf = new TrenchDomainGenerator.TrenchTF(this.trenchGen.width - 1, this.trenchGen.height - 1);
 		
 		double gamma = 0.99;
 		int numRollouts = 1;

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/upworld/UpWorldGenerator.java

@@ -1,4 +1,4 @@
-package domains;
+package domains.upworld;
 
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.core.states.State;

### 2015-12-15 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -1,0 +1,81 @@
+package experiments;
+
+import graphStateAbstractionTest.QStarEpsilonTest;
+import graphStateAbstractionTest.QStarEpsilonTest.EpsilonToNumStatesTuple;
+
+import java.util.List;
+
+import domains.GraphRF;
+import domains.GraphTF;
+import domains.NormalDomainToGraphDomain;
+import domains.nchain.NStateChainGenerator;
+import domains.trench.TrenchDomainGenerator;
+import domains.trench.TrenchDomainToGraphDomain;
+import stateAbstractor.PhiModel;
+import stateAbstractor.PhiSAReal;
+import stateAbstractor.StateAbstractor;
+import SARealGenerators.qValueGenerator;
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.oomdp.core.states.State;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.singleagent.common.UniformCostRF;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+
+/**
+ * An example of Q* abstraction in an 5 state chain MDP.
+ * @author Dhershkowitz
+ *
+ */
+public class EpsilonExperiments {
+
+	public static void createEpsilonVsPerformancePlot() {
+		
+	}
+	
+	public static void createEpsilonVsNumStatesPlot(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState) {
+		
+		// Convert to graph domain.
+		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
+		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain();
[…]

### 2015-12-15 Workspace and Code/stateAbstraction/src/domains/trench/TrenchDomainGenerator.java
Visuals automated

@@ -124,11 +124,11 @@ public class TrenchDomainGenerator implements DomainGenerator {
 	 */
 	public State getInitialState(Domain domain) {
 		
+		// Set the initial conditions for the agent.
 		State s = new MutableState();
 		ObjectInstance agent = new MutableObjectInstance(domain.getObjectClass(CLASSAGENT), "agent0");
 		agent.setValue(ATTX, 0);
 		agent.setValue(ATTY, 0);
-		
 		s.addObject(agent);
 
 		for(int x = 0; x < this.width; x++) {

### 2015-12-15 Workspace and Code/stateAbstraction/src/experiments/CreateVisuals.java

@@ -1,0 +1,110 @@
+package experiments;
+
+import graphStateAbstractionTest.VIParams;
+import graphStreamVisualizer.GraphStreamVisualizer;
+import stateAbstractor.PhiSAReal;
+import stateAbstractor.StateAbstractor;
+import SARealGenerators.qValueGenerator;
+import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
+import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.auxiliary.common.NullTermination;
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.TerminalFunction;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.RewardFunction;
+import burlap.oomdp.statehashing.HashableStateFactory;
+import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+import domains.GraphRF;
+import domains.GraphTF;
+import domains.NormalDomainToGraphDomain;
+import domains.nchain.NStateChainGenerator;
+import domains.trench.TrenchDomainGenerator;
+import domains.upworld.UpWorldGenerator;
+
+public class CreateVisuals {
+
+	public static void compressAndVisualizeMDP(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState, double epsilon) {
+		
+		// Convert to graph domain.
+		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
+		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain();
+		RewardFunction graphRF = new GraphRF(graphMaker.goalStateIDs);
+		TerminalFunction graphTF = new GraphTF(graphMaker.goalStateIDs);
+		Domain graphDomain = graphDefinedDomain.generateDomain();
+		State initGraphState = GraphDefinedDomain.getState(graphDomain, graphMaker.initStateID);
+		
+		// Run vi to compute Q*.
[…]

### 2015-12-15 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -3,6 +3,7 @@ package experiments;
 import graphStateAbstractionTest.QStarEpsilonTest;
 import graphStateAbstractionTest.QStarEpsilonTest.EpsilonToNumStatesTuple;
 
+import java.util.ArrayList;
 import java.util.List;
 
 import domains.GraphRF;
@@ -14,6 +15,7 @@ import domains.trench.TrenchDomainToGraphDomain;
 import stateAbstractor.PhiModel;
 import stateAbstractor.PhiSAReal;
 import stateAbstractor.StateAbstractor;
+import plotting.Plotter;
 import SARealGenerators.qValueGenerator;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
@@ -38,11 +40,25 @@ import burlap.oomdp.statehashing.SimpleHashableStateFactory;
  */
 public class EpsilonExperiments {
 
-	public static void createEpsilonVsPerformancePlot() {
+	public static void createEpsilonVsPerformancePlot(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState) {
+		// Convert to graph domain.
+		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
+		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain();
+		RewardFunction graphRF = new GraphRF(graphMaker.goalStateIDs);
+		TerminalFunction graphTF = new GraphTF(graphMaker.goalStateIDs);
 		
+		// Iterate over epsilon and compute the number of states.
+		double startEpsilon = 0.0;
+		double endEpsilon = 32.0; 
+		double epsilonIncrement = 0.5;
+		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = QStarEpsilonTest.testQPhiStateReduction(graphDefinedDomain, graphRF, graphTF, graphMaker.initStateID, startEpsilon, endEpsilon, epsilonIncrement);
+		System.out.println("results: ");
+		for (EpsilonToNumStatesTuple x : epsilonAndNumStatesPairs) {
+			System.out.println(x.getEpsilon() + "," + x.getValOfInitState());
+		}
 	}
 	
-	public static void createEpsilonVsNumStatesPlot(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState) {
[…]

### 2015-12-15 Workspace and Code/stateAbstraction/src/experiments/CreateVisuals.java
visualization automated and streamlined

@@ -27,15 +27,9 @@ import domains.upworld.UpWorldGenerator;
 
 public class CreateVisuals {
 
-	public static void compressAndVisualizeMDP(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState, double epsilon) {
-		
-		// Convert to graph domain.
-		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
-		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain();
-		RewardFunction graphRF = new GraphRF(graphMaker.goalStateIDs);
-		TerminalFunction graphTF = new GraphTF(graphMaker.goalStateIDs);
+	public static void compressAndVisualizeMDP(GraphDefinedDomain graphDefinedDomain, TerminalFunction graphTF, RewardFunction graphRF, State initGraphState, double epsilon) {
+		// Retrieve the graph domain.
 		Domain graphDomain = graphDefinedDomain.generateDomain();
-		State initGraphState = GraphDefinedDomain.getState(graphDomain, graphMaker.initStateID);
 		
 		// Run vi to compute Q*.
 		ValueIteration vi = new ValueIteration(graphDomain, graphRF, graphTF, VIParams.gamma, new SimpleHashableStateFactory(), VIParams.maxDelta, VIParams.maxIterations);
@@ -65,46 +59,59 @@ public class CreateVisuals {
 		abstractMDPVisualizer.render();
 	}
 	
+	public static void convertCompressAndVisualizeMDP(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState, double epsilon) {
+		
+		// Convert to graph domain.
+		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
+		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain();
+		RewardFunction graphRF = new GraphRF(graphMaker.goalStateIDs);
+		TerminalFunction graphTF = new GraphTF(graphMaker.goalStateIDs);
+		Domain graphDomain = graphDefinedDomain.generateDomain();
+		State initGraphState = GraphDefinedDomain.getState(graphDomain, graphMaker.initStateID);
+		
+		// Compress and visualize.
[…]

### 2016-01-14 paper/paper.tex
updated paper and added placeholder picture

--- 2015-12-15 paper/approximate_state_abstraction.tex
@@
             115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael Littman}{michael_littman@brown.edu}
+\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
 \icmladdress{Brown University,
@@
 \begin{abstract}
-The combinatorial explosion that plagues planning and reinforcement learning algorithms can be reversed using abstraction.
+The combinatorial explosion that plagues planning and reinforcement-learning algorithms can be reversed using abstraction.
 For instance, prohibitively difficult task representations can be condensed so that solutions are tractably computable.
@@
 \item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
-\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
-\item In this work we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
+\item To make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
+\item In this work, we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
 \item Q: Why approximate?
@@
 
-\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity (small lemma or something?)}
+\dnote{As part of UpWorld we can include the result about the unbounded improvement in sample complexity (small lemma or something?)}
 

### 2016-01-15 paper/paper.tex
Added all the related work we will talk about

@@
 Reinforcement learning agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from three classes of approximate state abstraction.
+We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
 Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved, as well as the tradeoff between approximation magnitude and optimality of behavior.
@@
 Citation test~\cite{li2006towards}
+
+\begin{itemize}
+\item ALisp~\cite{andre2002state}
+
+Programming language for enabling abstraction.
+
+\item Aggregation in DP~\cite{Bean2011}
+
+Assumes the MDP is a DAG. Only does shortest path.
+
+\item New Operators for RL~\cite{Bellemare2015}
+
+Comes up with an approximate Bellman Operator. Not sure how it's related yet.
+
+\item DP with Factored Representations~\cite{Boutilier2000}
+
+Uses decision trees and DBNs to represent MDPs. Does state aggregation. Theorem 4.4 should be looked at in more detail.
+
+\item {\bf Model reduction techniques for nearly optimal MDP solutions}~\cite{dean1997model}
+
+$\epsilon$-homogeneity: groups together states that behave approximately the same under all or some subset of policies.
+
+Bounded Parameter MDP: family of MDP with upper and lower bounds on T. Find policies approximately optimal w.r.t. original MDP.
+% Also covers model minimization..
+
+\item Abstraction selection~\cite{jiang2015abstraction}
+
+\item State abstraction discovery from irrelevant state variables~\cite{jong2005state}
+
+\item Selecting the state rep in RL~\cite{maillard2011selecting}
+
+\item Near optimal state reps~\cite{ortner2014selecting}
+
+\item SMDP homomorphisms~\cite{ravindran2003smdp}
+
+\end{itemize}
 

### 2016-01-15 Workspace and Code/stateAbstraction/src/domains/taxi/GetPassengerOption.java
adding an option

@@ -1,0 +1,54 @@
+package domains.taxi;
+
+import java.util.List;
+
+import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.options.DeterministicTerminationOption;
+import burlap.oomdp.auxiliary.stateconditiontest.StateConditionTest;
+import burlap.oomdp.core.objects.ObjectInstance;
+import burlap.oomdp.core.states.State;
+
+
+public class GetPassengerOption extends DeterministicTerminationOption {
+
+	public GetPassengerOption( Policy p, StateConditionTest init) {
+		super("getPassengerOption", p, init, new IsPassengerInCarSCT());
+		// TODO Auto-generated constructor stub
+	}
+
+	public static boolean isTaxiEmpty(State s) {
+		List<ObjectInstance> allPassengers = s.getObjectsOfClass(TaxiDomainGenerator.TAXICLASS);
+	
+		for(ObjectInstance passenger : allPassengers) {
+			boolean inTaxi = passenger.getBooleanValForAttribute(TaxiDomainGenerator.BEENPICKEDUPATT);
+			
+			if (inTaxi) {
+				// There's a passenger in a car.
+				return false;
+			}
+		}
+		return true;
+	}
+
+
+}
+
+
+
+// Initiation condition.
+class IsTaxiEmptySCT implements StateConditionTest {
+	@Override
+	public boolean satisfies(State s) {
+		return !GetPassengerOption.isTaxiEmpty(s);
+	}
+}
+
+// Terminal condition.
+class IsPassengerInCarSCT implements StateConditionTest {
+
+	@Override
+	public boolean satisfies(State s) {
+		return GetPassengerOption.isTaxiEmpty(s);
+	}
+	
+}

### 2016-01-16 Workspace and Code/stateAbstraction/src/domains/NormalDomainToGraphDomain.java
Added phi a star to code and results. Also added a pickup passenger option for taxi (but not working with abstraction stuff yet)

@@ -6,7 +6,9 @@ import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
 
+import domains.taxi.GetPassengerOptionMaker;
 import burlap.behavior.policy.GreedyQPolicy;
+import burlap.behavior.singleagent.options.Option;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.auxiliary.DomainGenerator;
@@ -61,6 +63,7 @@ public class NormalDomainToGraphDomain {
 
 	private void setTransitionsAndFindGoalStates(List<State> allNonGraphStates, List<Action> allActions, GraphDefinedDomain gd) {
 		
+
 		// Loop over each state and set transitions in the graph.
 		for (int stateIndex = 0; stateIndex < allNonGraphStates.size(); stateIndex++) {
 			this.graphIndexToNonGraphState.put(stateIndex, allNonGraphStates.get(stateIndex));

### 2016-01-16 Workspace and Code/stateAbstraction/src/domains/taxi/TaxiDomainGenerator.java

@@ -7,9 +7,14 @@ import java.util.ArrayList;
 import java.util.List;
 import java.util.Random;
 
+import burlap.behavior.policy.Policy;
+import burlap.behavior.policy.Policy.ActionProb;
+import burlap.behavior.singleagent.options.DeterministicTerminationOption;
+import burlap.behavior.singleagent.options.Option;
 import burlap.oomdp.core.objects.MutableObjectInstance;
 import burlap.oomdp.core.objects.ObjectInstance;
 import burlap.oomdp.auxiliary.DomainGenerator;
+import burlap.oomdp.auxiliary.stateconditiontest.StateConditionTest;
 import burlap.oomdp.core.*;
 import burlap.oomdp.core.Attribute.AttributeType;
 import burlap.oomdp.core.states.MutableState;
@@ -84,9 +89,9 @@ public class TaxiDomainGenerator implements DomainGenerator {
 	@Override
 	public Domain generateDomain() {
 				
-				
 		Domain domain = new SADomain();
 
+		// Attributes.
 		Attribute xAtt = new Attribute(domain, XATT, AttributeType.DISC);
 		xAtt.setDiscValuesForRange(0, maxX, 1);
 
@@ -110,8 +115,6 @@ public class TaxiDomainGenerator implements DomainGenerator {
 		Attribute wallOffsetAtt = new Attribute(domain, WALLOFFSETATT, AttributeType.DISC);
 		wallOffsetAtt.setDiscValuesForRange(0, Math.max(this.maxX, this.maxY)+1, 1);
 
-
-
 		Attribute locationAtt = new Attribute(domain, LOCATIONATT, AttributeType.DISC);
 		List<String> locationTypes = new ArrayList<String>();
 		locationTypes.add("fuel");
@@ -130,6 +133,8 @@ public class TaxiDomainGenerator implements DomainGenerator {
 			beenPickedupAtt = new Attribute(domain, BEENPICKEDUPATT, AttributeType.BOOLEAN);
 		}
 
+		
+		// Objects.
 		ObjectClass taxi = new ObjectClass(domain, TAXICLASS);
 		taxi.addAttribute(xAtt);
 		taxi.addAttribute(yAtt);
@@ -162,7 +167,7 @@ public class TaxiDomainGenerator implements DomainGenerator {
 		verticalWall.addAttribute(wallOffsetAtt);
 
 
-
+		// Actions.
[…]

### 2016-01-16 Workspace and Code/stateAbstraction/src/domains/trench/TrenchDomainGenerator.java

@@ -1,12 +1,11 @@
 package domains.trench;
 
+import java.util.ArrayList;
 import java.util.List;
 
-import domains.GraphRF;
-import domains.GraphTF;
-import domains.NormalDomainToGraphDomain;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.singleagent.EpisodeAnalysis;
+import burlap.behavior.singleagent.options.Option;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
 import burlap.oomdp.auxiliary.DomainGenerator;
@@ -25,6 +24,8 @@ import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.singleagent.SADomain;
 import burlap.oomdp.singleagent.common.SimpleAction.SimpleDeterministicAction;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
+import domains.GraphRF;
+import domains.NormalDomainToGraphDomain;
 
 
 public class TrenchDomainGenerator implements DomainGenerator {

### 2016-01-16 Workspace and Code/stateAbstraction/src/experiments/CreateVisuals.java

@@ -1,5 +1,8 @@
 package experiments;
 
+import java.util.ArrayList;
+import java.util.List;
+
 import graphStateAbstractionTest.VIParams;
 import graphStreamVisualizer.GraphStreamVisualizer;
 import stateAbstractor.PhiSAReal;
@@ -7,6 +10,7 @@ import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
+import burlap.behavior.singleagent.options.Option;
 import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
@@ -20,6 +24,7 @@ import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 import domains.GraphRF;
 import domains.NormalDomainToGraphDomain;
 import domains.nchain.NChainGenerator;
+import domains.taxi.GetPassengerOptionMaker;
 import domains.taxi.TaxiDomainGenerator;
 import domains.trench.TrenchDomainGenerator;
 import domains.upworld.UpWorldGenerator;
@@ -99,8 +104,8 @@ public class CreateVisuals {
 	public static void main(String[] args) {
 		
 		// Change the text here to switch between visuals.
-		String domainToVisualize = "TAXI"; // One of "TRENCH", "UPWORLD", "NCHAIN", "TAXI" or add your own.
-		double epsilon = .05;
+		String domainToVisualize = "UPWORLD"; // One of "TRENCH", "UPWORLD", "NCHAIN", "TAXI" or add your own.
+		double epsilon = .01;
 		
 		if (domainToVisualize == "TRENCH") {
 			// Create trench domain.

### 2016-01-16 Workspace and Code/stateAbstraction/src/graphStateAbstractionTest/AStarEpsilonTest.java

@@ -3,12 +3,14 @@ package graphStateAbstractionTest;
 import java.util.ArrayList;
 import java.util.List;
 
-import stateAbstractor.PhiSAReal;
+import domains.taxi.GetPassengerOptionMaker;
+import stateAbstractor.PhiAStar;
 import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
 import burlap.behavior.policy.GreedyQPolicy;
 import burlap.behavior.policy.Policy;
 import burlap.behavior.singleagent.EpisodeAnalysis;
+import burlap.behavior.singleagent.options.Option;
 import burlap.behavior.singleagent.planning.stochastic.policyiteration.PolicyIteration;
 import burlap.behavior.singleagent.planning.stochastic.valueiteration.ValueIteration;
 import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
@@ -19,45 +21,9 @@ import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.statehashing.HashableStateFactory;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
-public class QStarEpsilonTest {
-	public static class EpsilonToNumStatesTuple {
-		private double eps;
-		private int numStates;
-		private double valOfInitGroundState; // NOW STORES THE DELTA BETWEEN THE VALUE OF GROUND AND ABSTRACT
-		private double valOfInitAbstractState;
-		
-		
-		public EpsilonToNumStatesTuple(double epsilon, int numStates, double valOfInitGroundState, double valOfInitAbstractState) {
-			this.eps = epsilon;
-			this.numStates = numStates;
-			this.valOfInitGroundState = valOfInitGroundState;
-			this.valOfInitAbstractState = valOfInitAbstractState;
-		}
-		@Override
-		public String toString() {
-			return eps + "\t" + numStates + "\t" + valOfInitGroundState + "\t" + valOfInitAbstractState;
-		}
-		
-		public double getEpsilon() {
-			return this.eps;
-		}
-		
-		public int getNumStates() {
-			return this.numStates;
-		}
-		
-		public double getValOfGroundInitState() {
-			return this.valOfInitGroundState;
-		}
-		
-		public double getValOfInitAbstractState() {
-			return this.valOfInitAbstractState;
-		}
-	}
[…]

### 2016-01-17 paper/paper.tex
Did a tiny bit of paper editing -- e.g. switched sections
added a bit more to related work

@@
 
+% --- SECTION: Background ---
+\section{Background}
+
+\subsection{MDP/RL}
+
+\subsection{Lihong Li}
+
+% Quick MDP blurb?
+
+% Phi notation
+
+% Evluation of Abstract MDP
+
+% Abstract MDP, Ground MDP, Homogenizing Gun
+
+% Previous state aggregation stuff? Or should be in related work?
+
 % --- SECTION: Related Work ---
@@
 % Lihong/Walsh/Littman: Towards a unified theory...
-Citation test~\cite{li2006towards}
 
@@
 
-Programming language for enabling abstraction.
+\citep{andre2002state} investigate the notion of {\it safe} state abstraction through a programming language called ALISP that can be used to specify hierarchical abstractions to reinforcement learning agents, enabling agents to ignore irrelevant parts of the state.
+The primary contribution of this work is the development of ALISP, and the decomposition of the Bellman equation into a form that enables safe planning algorithms using the abstractions from ALISP.
+Critically, our work differs in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while ALISP investigates one particular means of abstraction for use in planning, using partial programs.
 
@@
 
-Assumes the MDP is a DAG. Only does shortest path.
+~\citep{Bean2011} develop an an algorithm (SADA) that performs aggregation on planning tasks that can be structured as a DAG, and conducts analysis on this process, achieving bounded error on the problem resulting from the aggregation.
+Our work differs in that the scope of aggregation and analysis is novel, and we make no assumptions about the structure of the underlying task.
+Lastly, we consider the reinforcement learning setting, as opposed to planning.
+
+\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
+
+Does epsilon equivalence of MDPs and proves bounds of value of the optimal policy in the ground versus the abstract.
+
+\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
+
+Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
+Wowza.
+Only uses the whole model similarity business though.
+Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
 
@@
 
-% --- SECTION: Background ---
-\section{Background}
-
-% Quick MDP blurb?
-
-% Phi notation
-
-% Evluation of Abstract MDP
-
-% Abstract MDP, Ground MDP, Homogenizing Gun
-
-% Previous state aggregation stuff? Or should be in related work?
-
 % --- SECTION: State Abstraction ---
@@
 
+% Subsection: Phi_Q
+\subsection{$\phi_{Q^*}$}
+
 % Subsection: Phi_M
-\subsection{$\Phi_M$}
+\subsection{$\phi_{model}$}
 
-% Subsection: Phi_Q
-\subsection{$\Phi_Q^*$}
-
-% Subsection: Phi_D
-\subsection{$\Phi_D$}
+% Subsection: Phi_{Mult}
+\subsection{$\phi_{mult}$}
 
 % Subsection: Phi_B
-\subsection{$\Phi_B$}
-\dnote{$\Phi_{Boltzmann}$}
+\subsection{$\phi_{bolt}$}
 

### 2016-01-18 paper/paper.tex
RW updated

@@
 
-Does epsilon equivalence of MDPs and proves bounds of value of the optimal policy in the ground versus the abstract.
+A number of works consider abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning~\cite{even2003approximate,ortner2013adaptive,dean1997model,Boutilier2000}.
+This work is closely in line with our own in that we seek abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
+However, we extend these results by considering broader classes of abstraction beyond the model similarity, or $\epsilon-homogeneity$, first introduced by ~\cite{dean1997model}.
 
@@
 
-\item DP with Factored Representations~\cite{Boutilier2000}
+\item Abstraction selection~\cite{jiang2015abstraction}
 
-Uses decision trees and DBNs to represent MDPs. Does state aggregation. Theorem 4.4 should be looked at in more detail.
-
-\item {\bf Model reduction techniques for nearly optimal MDP solutions}~\cite{dean1997model}
-
-$\epsilon$-homogeneity: groups together states that behave approximately the same under all or some subset of policies.
-
-Bounded Parameter MDP: family of MDP with upper and lower bounds on T. Find policies approximately optimal w.r.t. original MDP.
-% Also covers model minimization..
-
-\item Abstraction selection~\cite{jiang2015abstraction}
+~\cite{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
 

### 2016-01-18 paper/paper.tex
filled in rel worl

--- 2016-01-15 paper/paper.tex
@@
 
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-Citation test~\cite{li2006towards}
-
-\begin{itemize}
-\item ALisp~\cite{andre2002state}
-
-Programming language for enabling abstraction.
-
-\item Aggregation in DP~\cite{Bean2011}
-
-Assumes the MDP is a DAG. Only does shortest path.
-
-\item New Operators for RL~\cite{Bellemare2015}
-
-Comes up with an approximate Bellman Operator. Not sure how it's related yet.
-
-\item DP with Factored Representations~\cite{Boutilier2000}
-
-Uses decision trees and DBNs to represent MDPs. Does state aggregation. Theorem 4.4 should be looked at in more detail.
-
-\item {\bf Model reduction techniques for nearly optimal MDP solutions}~\cite{dean1997model}
-
-$\epsilon$-homogeneity: groups together states that behave approximately the same under all or some subset of policies.
-
-Bounded Parameter MDP: family of MDP with upper and lower bounds on T. Find policies approximately optimal w.r.t. original MDP.
-% Also covers model minimization..
-
-\item Abstraction selection~\cite{jiang2015abstraction}
-
-\item State abstraction discovery from irrelevant state variables~\cite{jong2005state}
-
-\item Selecting the state rep in RL~\cite{maillard2011selecting}
-
-\item Near optimal state reps~\cite{ortner2014selecting}
-
-\item SMDP homomorphisms~\cite{ravindran2003smdp}
-
-\end{itemize}
-
-% Nan/Lihong
-
-% Approximate bisimulation
-
-% David Silver: Options/State Abstraction?
-
-% Russell? PHAM/HAM/ALisp
-
-% Konidaris? Options induce symbolic representation on continuous state space
-
-% Littman: Relocatable Action Models
-
-% Stone: State Abstraction Discovery from Irrelevant State Vars
-
-% Others...
-
 % --- SECTION: Background ---
 \section{Background}
+
+\subsection{MDP/RL}
+
+\subsection{Lihong Li}
 
@@
 
+% --- SECTION: Related Work ---
+\section{Related Work}
+
+% Other approximate abstraction work.
+Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,dean1997model,Boutilier2000,Bean2011}.
+All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
+However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
+Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
+
+% Hierarchical Reinforcement learning
+ALISP investigates a method for state abstraction in hierarchical reinforcement learning~\citep{andre2002state}.
+ALISP promotes the notion of {\it safe} state abstraction through a programming language that can be used to specify hierarchical abstractions to reinforcement learning agents.
+Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstraction that maintains optimality.
+
+\citep{jong2005state} introduce a method called {\it policy-irrelevance}, in which agents identify (online) which state variables may be safely ignored in a factored MDP, and consequently achieve state abstraction.
+The agent will learn to ignore state variables that don't impact optimal behavior, and is consequently contained within the approximate $\phi_{a^*}$ work.
+
+\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
+
+% Defining
+
+% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
+
+% Lihong/Walsh/Littman: Towards a unified theory...
+
+%\begin{itemize}
+%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
+%\item ALisp~\cite{andre2002state}
+%\item Aggregation in DP~\cite{Bean2011}
+%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
+%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
+Wowza.
+Only uses the whole model similarity business though.
+Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
+%
+%\item New Operators for RL~\cite{Bellemare2015
+%Comes up with an approximate Bellman Operator. Not sure how it's related yet.
+%
+%\item Selecting the state rep in RL~\cite{maillard2011selecting}
+%\item Near optimal state reps~\cite{ortner2014selecting}
+%\item SMDP homomorphisms~\cite{ravindran2003smdp}
+%\end{itemize}
+
 % --- SECTION: State Abstraction ---
@@
 
+% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
+
 % Subsections for proofs for each phi
@@
 
-% Discussion of other abstractions we looked into
+We note that the approximate version of $\phi_{a^*}$, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
+A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
+Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
+
+We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
+
+Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
+Furthermore, an MDP for which this is true is an awfully weird MDP...
+
+Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
 

### 2016-01-18 paper/paper.tex
related work written oop

@@
 
-% Other approximate abstraction work.
-Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,dean1997model,Boutilier2000,Bean2011}.
+% Approximate abstraction work.
+%Dean: 
+%\begin{itemize}
+%\item \citep{dean1997model} Does abstraction with model equality.
+%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
+%\end{itemize}
+%
+%Boutilier:
+%\begin{itemize}
+%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
+%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
+%\end{itemize}
+%
+%Even~\cite{even2003approximate}: COLT paper on different metrics
+%
+%Ortner:
+%\begin{itemize}
+%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
+%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
+%\end{itemize}
+
+\subsection{Approximate State Abstraction}
+\citep{dean1997modelmin} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
+This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
+Several approaches build on the notion of $\epsilon$-homogeneity.
+~\citep{even2003approximate} analyze different distant metrics used in the process of identifying $\epsilon$-homogenous partitions.
+~\cite{ortner2013adaptive} develops an algorithm for learning partitions in an on line setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
+
+%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
 All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
@@
 
-% Hierarchical Reinforcement learning
-ALISP investigates a method for state abstraction in hierarchical reinforcement learning~\citep{andre2002state}.
-ALISP promotes the notion of {\it safe} state abstraction through a programming language that can be used to specify hierarchical abstractions to reinforcement learning agents.
+\subsection{Specific Abstraction Algorithms}
+Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
+\citep{andre2002state} investigates a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstraction that maintains optimality.
-
+~\cite{dietterich2000hierarchical} develops the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy.
 \citep{jong2005state} introduce a method called {\it policy-irrelevance}, in which agents identify (online) which state variables may be safely ignored in a factored MDP, and consequently achieve state abstraction.
 The agent will learn to ignore state variables that don't impact optimal behavior, and is consequently contained within the approximate $\phi_{a^*}$ work.
+For a full survey of algorithms that leverage state abstraction in recent reinforcement learning literature, see~\cite{li2006towards}.
 
-\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
+% Other? Selecting abstractions
+%\subsection{Selecting Abstractions}
+%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
 
@@
 %
-%\item New Operators for RL~\cite{Bellemare2015
-%Comes up with an approximate Bellman Operator. Not sure how it's related yet.
-%
 %\item Selecting the state rep in RL~\cite{maillard2011selecting}
@@
 
+% Proof of Q^*
+
 % Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
@@
 % Subsections for proofs for each phi
-\dnote{Insert lemma for each phi as their subsection}
+\dnote{Insert lemma for each phi as their subsection, maybe with proof sketch but likely just dump in appendix.}
 
@@
 
-We note that the approximate version of $\phi_{a^*}$, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
+We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
 A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.

### 2016-01-20 paper/paper.tex
Added intro and background to related work.

--- 2016-01-18 paper/paper.tex
@@
 \usepackage{icml2016/icml2016} 
+\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
 
 \icmltitlerunning{Approximate State Abstraction}
+
+% --- Notation Commands ---
+\newcommand{\ep}{\widetilde \phi}
 
@@
 
+%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
+\begin{acronym}
+\acro{MDP}{Markov Decision Process}
+\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
+
+\acro{RL}{reinforcement learning}
+\acrodefplural{RL}{RL}{Reinforcement learning}
+\end{acronym}
+
 % --- ABSTRACT ---
 \begin{abstract}
-The combinatorial explosion that plagues planning and reinforcement-learning algorithms can be reversed using abstraction.
+The combinatorial explosion that plagues planning and \ac{RL} algorithms can be reversed using abstraction.
 For instance, prohibitively difficult task representations can be condensed so that solutions are tractably computable.
 In this work, we investigate a theoretical framework for approximate state abstraction that preserves near optimal behavior.
-Reinforcement learning agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
+\acp{RL} agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
 We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
@@
 \section{Introduction}
+Abstraction is a fundamental tool of intelligent agent seeking to compute over only the salient features of its environment.
+However, the knowledge available to an agent at any given moment is typically approximate and so agents are faced with the challenge of deciding when their knowledge is sufficiently accurate to form the basis of abstraction.
+This work focuses on characterizing what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
 
-\begin{itemize}
-\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
-\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
-\item To make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
-\item In this work, we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
-\item Q: Why approximate?
-\item A: Approximate can compress strictly more than compression based on equality
-\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
-\end{itemize}
+Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space CITE MICHAEL COMPLEXITY PAPER.
+Similarly, many \ac{RL} algorithms for solving MDPs are known to require a number of samples polynomial in the size of the state space CITE SOME SAMPLE COMPLEXITY PAPER.
+Although polynomial runtime or sample complexity is often what one hopes, due to Bellman's so-called curse of dimensionality the state space of an MDP often grows super-polynomially with the number of variables that characterize the domain.
+Thus, polynomial behavior in state space size is not necessarily the \enote{bee's knees}.
+For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
+
+Thus, a key research interest of planning and RL has been leveraging abstraction as means of grappling with large state spaces (CITE VARIOUS ABSTRACTION JOANT).
+These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states with similar values of interest.
+Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality CITE LIHONG.
+However, exactly solving for these quantities is itself computationally taxing and sometimes as difficult as solving for optimal behavior in the ground MDP, thereby defeating the purpose of abstraction.
+
+In this work we demonstrate that aggregation of states on the basis of various approximately equal criteria incur bounded error.
+Relaxing the aggregation criteria from equality of quantities to epsilon-closeness offers two benefits.
+First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we might reasonably a planning or learning algorithm to approximate without fully solving the MDP.
+Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incuring bounded error.
+
+\enote{QUICK SUMMARY OF PAPER PARAGRAPH}
+
+%\begin{itemize}
+%\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
+%\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
+%\item To make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
+%\item In this work, we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
+%\item Q: Why approximate?
+%\item A: Approximate can compress strictly more than compression based on equality
+%\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
+%\end{itemize}
 
@@
 
-\subsection{MDP/RL}
+%MDP/SDM Background and Notation
+\subsection{\acp{MDP} and Sequential Decision Making}
+A \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers immediate rewards over future rewards.
 
-\subsection{Lihong Li}
+The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
+In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
+This goal policy is denoted $\pi^*$.
+We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V(s)^\pi$.
+We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$ respectively.
+
+%Lihong Section
+\subsection{Abstraction Notation}
+We build upon the notation used by \cite{li2006towards} \enote{This should probably say more}.
+We understand an abstraction as a mapping from a ground MDP $M_G$ to an abstract MDP $M_A$ using a state aggregation scheme.
+$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
+
+The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP. $\mathcal{S}_A$
 
@@
 % Lihong/Walsh/Littman: Towards a unified theory...
+Citation test~\cite{li2006towards}
 
@@
 
-\citep{andre2002state} investigate the notion of {\it safe} state abstraction through a programming language called ALISP that can be used to specify hierarchical abstractions to reinforcement learning agents, enabling agents to ignore irrelevant parts of the state.
-The primary contribution of this work is the development of ALISP, and the decomposition of the Bellman equation into a form that enables safe planning algorithms using the abstractions from ALISP.
-Critically, our work differs in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while ALISP investigates one particular means of abstraction for use in planning, using partial programs.
+Programming language for enabling abstraction.
 
@@
 
-~\citep{Bean2011} develop an an algorithm (SADA) that performs aggregation on planning tasks that can be structured as a DAG, and conducts analysis on this process, achieving bounded error on the problem resulting from the aggregation.
-Our work differs in that the scope of aggregation and analysis is novel, and we make no assumptions about the structure of the underlying task.
-Lastly, we consider the reinforcement learning setting, as opposed to planning.
-
-\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-
-A number of works consider abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning~\cite{even2003approximate,ortner2013adaptive,dean1997model,Boutilier2000}.
-This work is closely in line with our own in that we seek abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, we extend these results by considering broader classes of abstraction beyond the model similarity, or $\epsilon-homogeneity$, first introduced by ~\cite{dean1997model}.
-
-\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-
-Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
+Assumes the MDP is a DAG. Only does shortest path.
 
@@
 
+\item DP with Factored Representations~\cite{Boutilier2000}
+
+Uses decision trees and DBNs to represent MDPs. Does state aggregation. Theorem 4.4 should be looked at in more detail.
+
+\item {\bf Model reduction techniques for nearly optimal MDP solutions}~\cite{dean1997model}
+
+$\epsilon$-homogeneity: groups together states that behave approximately the same under all or some subset of policies.
+
+Bounded Parameter MDP: family of MDP with upper and lower bounds on T. Find policies approximately optimal w.r.t. original MDP.
+% Also covers model minimization..
+
 \item Abstraction selection~\cite{jiang2015abstraction}
-
-~\cite{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
 

### 2016-01-21 paper/paper.tex
added citations, a bit more to intro and background

@@
 \section{Introduction}
-Abstraction is a fundamental tool of intelligent agent seeking to compute over only the salient features of its environment.
+Abstraction is a fundamental tool of intelligent agents seeking to reason about only the salient features of its environment.
 However, the knowledge available to an agent at any given moment is typically approximate and so agents are faced with the challenge of deciding when their knowledge is sufficiently accurate to form the basis of abstraction.
@@
 
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space CITE MICHAEL COMPLEXITY PAPER.
-Similarly, many \ac{RL} algorithms for solving MDPs are known to require a number of samples polynomial in the size of the state space CITE SOME SAMPLE COMPLEXITY PAPER.
+Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{littman1995complexity,papadimitriou1987complexity}.
+Similarly, many \ac{RL} algorithms for solving MDPs are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
 Although polynomial runtime or sample complexity is often what one hopes, due to Bellman's so-called curse of dimensionality the state space of an MDP often grows super-polynomially with the number of variables that characterize the domain.
@@
 
-Thus, a key research interest of planning and RL has been leveraging abstraction as means of grappling with large state spaces (CITE VARIOUS ABSTRACTION JOANT).
+Thus, a key research interest of planning and RL has been leveraging abstraction as means of grappling with large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
 These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states with similar values of interest.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality CITE LIHONG.
+Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
 However, exactly solving for these quantities is itself computationally taxing and sometimes as difficult as solving for optimal behavior in the ground MDP, thereby defeating the purpose of abstraction.
@@
 We build upon the notation used by \cite{li2006towards} \enote{This should probably say more}.
+
 We understand an abstraction as a mapping from a ground MDP $M_G$ to an abstract MDP $M_A$ using a state aggregation scheme.
@@
 
-The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP. $\mathcal{S}_A$
+% States
+The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP, $\mathcal{S}_A$.
+More specifically, $\phi$ maps a state in the ground MDP to a state in the abstract MDP.
+\begin{equation}
+\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}
+\end{equation}
+
+Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
+We make now assumptions about the weighting scheme, except that the weighting is a convex combination across all states in partition.
+
+% Reward
+The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the abstract state:
+\begin{equation}
+\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) 
+\end{equation}
+
+% Transition
+The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the abstract state:
+\begin{equation}
+\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g) 
+\end{equation}
+For:
+\begin{equation}
+s, s' \in \mathcal{S}_A
+\end{equation}
 
@@
 \subsection{Approximate State Abstraction}
-\citep{dean1997modelmin} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citep{dean1997model} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
 They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.

### 2016-01-21 paper/paper.tex
intro thingy

@@
 \usepackage{algorithm}
+\usepackage{amsmath}
 \usepackage{algorithmic}
@@
 \newcommand{\ep}{\widetilde \phi}
+\newcommand\defn[1]{{\bf Definition:} #1}
 
@@
 
-% Quick MDP blurb?
+% Abstract policy using in ground.
+In general we are interested in how policies defined over the abstract MDP perform in the ground MDP.
+To leverage a policy defined in the abstract in the ground, we map a ground state into the abstract state space, and query the abstract policy for behavior.
+Specifically:
+\begin{equation}
+\pi_A(s) = \pi_A(\phi(s)),\ s \in \mathcal{S}_G
+\end{equation}
 
-% Phi notation
+We evaluate the value of the abstract policy in the ground MDP by following the abstract policy:
+\begin{equation}
+V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(a)) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(a),s')V^{\pi_A}(s')
+\end{equation}
 
-% Evluation of Abstract MDP
+\subsection{Exact Abstraction Framework}
 
-% Abstract MDP, Ground MDP, Homogenizing Gun
+\citep{li2006towards} develop a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
+Here we survey their main results that we extend to the framework of approximate abstraction.
 
-% Previous state aggregation stuff? Or should be in related work?
+In particular, they define the following five classes of state abstractors, inspired by existing methods for state abstraction in \acp{MDP}.
+For brevity, we include those which we build upon directly (see their paper for full details).
+
+\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is such that:
+\begin{equation}
+\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \longrightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right)
+\end{equation}
+}
+
+\defn{A model-irrelevance abstraction, $\phi_{model}$, is such that:
+\begin{multline}
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a) \\
+\end{multline}
+And:
+\begin{multline}
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s') \\
+\end{multline}
+}
 

### 2016-01-21 paper/paper.tex
Some minor tweaks
quick skim of intro

@@
 \begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be reversed using abstraction.
+The combinatorial explosion that plagues planning and \ac{RL} algorithms can be overcome using abstraction.
 For instance, prohibitively difficult task representations can be condensed so that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that preserves near optimal behavior.
+In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compressing while preserving near optimal behavior.
 \acp{RL} agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
 We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved, as well as the tradeoff between approximation magnitude and optimality of behavior.
+Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of tasks, as well as the tradeoff between approximation magnitude and optimality of behavior.
 \end{abstract}
@@
 \section{Introduction}
-Abstraction is a fundamental tool of intelligent agents seeking to reason about only the salient features of its environment.
-However, the knowledge available to an agent at any given moment is typically approximate and so agents are faced with the challenge of deciding when their knowledge is sufficiently accurate to form the basis of abstraction.
-This work focuses on characterizing what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
+Abstraction plays a fundamental role in learning; it encourages intelligent agents to reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
+However, the knowledge available to a learning agent at any given moment is approximate.
+Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
+This work characterizes what is ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
 
@@
 Similarly, many \ac{RL} algorithms for solving MDPs are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity is often what one hopes, due to Bellman's so-called curse of dimensionality the state space of an MDP often grows super-polynomially with the number of variables that characterize the domain.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's so-called curse of dimensionality the size of the state space of an MDP grows super-polynomially with the number of variables that characterize the domain.
 Thus, polynomial behavior in state space size is not necessarily the \enote{bee's knees}.
@@
 
-Thus, a key research interest of planning and RL has been leveraging abstraction as means of grappling with large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states with similar values of interest.
+Thus, a key research agenda for planning and RL has been leveraging abstraction as means of reducing large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
 Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
@@
 
-In this work we demonstrate that aggregation of states on the basis of various approximately equal criteria incur bounded error.
-Relaxing the aggregation criteria from equality of quantities to epsilon-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we might reasonably a planning or learning algorithm to approximate without fully solving the MDP.
-Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incuring bounded error.
+In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur bounded error.
+Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
+First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the MDP.
+Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
 

### 2016-01-24 paper/paper.tex
a few small edits and comments

@@
 \acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-
 \acro{RL}{reinforcement learning}
@@
 The combinatorial explosion that plagues planning and \ac{RL} algorithms can be overcome using abstraction.
-For instance, prohibitively difficult task representations can be condensed so that solutions are tractably computable.
+For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
 In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compressing while preserving near optimal behavior.
-\acp{RL} agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
+\acp{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
 We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
@@
 
-% Set of actions within epsilon (Q*) is the same for two states? Better than boltzmann.
-
 % --- SECTION: Introduction ---
 \section{Introduction}
-Abstraction plays a fundamental role in learning; it encourages intelligent agents to reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, the knowledge available to a learning agent at any given moment is approximate.
+Abstraction plays a fundamental role in learning.
+Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
+However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}.
 Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
@@
 
+% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
 Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{littman1995complexity,papadimitriou1987complexity}.
-Similarly, many \ac{RL} algorithms for solving MDPs are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's so-called curse of dimensionality the size of the state space of an MDP grows super-polynomially with the number of variables that characterize the domain.
-Thus, polynomial behavior in state space size is not necessarily the \enote{bee's knees}.
-For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
+Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
+Thus, polynomial behavior in state space size often translates to intractability for sufficiently complicated tasks.
+\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
 
-Thus, a key research agenda for planning and RL has been leveraging abstraction as means of reducing large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+% Existing work on state abstraction.
+Thus, a key research agenda for planning and RL is leveraging abstraction in order to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
 These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
 Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and sometimes as difficult as solving for optimal behavior in the ground MDP, thereby defeating the purpose of abstraction.
+However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
 
-In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur bounded error.
+% Approximate abstraction
+In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
 Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the MDP.
+First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
 Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
 
-\enote{QUICK SUMMARY OF PAPER PARAGRAPH}
-
-%\begin{itemize}
-%\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
-%\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
-%\item To make MDPs with large $|\mathcal{S}|$ tractable, we can reduce the MDPs to a simpler form.
-%\item In this work, we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
-%\item Q: Why approximate?
-%\item A: Approximate can compress strictly more than compression based on equality
-%\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
-%\end{itemize}
+% Summary	
+This paper is organized as follows.
+We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
+We then survey existing approaches in state abstraction as applied to sequential decision making.
+The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
+We then discuss our experimentation, in which we apply one class of approximate abstraction to a variety of different tasks, visualizing their abstraction and showing the relationship between degrees of compression and error incurred.
 
@@
 
+We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).
+
 % Some abstractions DON'T preserve a meaningful notion of optimality.
@@
 
-% Subsection: UpWorld
+% Subsection: UpWorld.
 \subsection{UpWorld}
@@
 
-% Subsection: NChain
+% Subsection: NChain.
 \subsection{NChain}
@@
 
-% Subsection: Trench
+% Subsection: Trench.
 \subsection{Trench}
@@
 \end{figure}
+
+% Subsection: Minefield.
+\subsection{Minefield}
 

### 2016-01-26 paper/paper.tex
davellis started fully outlining section 4, including theorem 1, and the structure of the remaining lemmas

@@
 \acro{RL}{reinforcement learning}
-\acrodefplural{RL}{RL}{Reinforcement learning}
+\acrodefplural{RL}{Reinforcement learning}
 \end{acronym}
@@
 
+% Subsection: Exact Abstraction Framework
 \subsection{Exact Abstraction Framework}
@@
 
+% INTRO PARAGRAPH, setup + structure
+
+\dnote{Explain the notation so like the $\phi_f$}
+
+\dnote{Tee up other stuff/ideas}
+
+% Main theorem:
+
+\dnote{I wish this theorem used the term approximate somewhere (i.e. was using the same terminology as the intro/abstract)}
+{\bf Theorem 1:} There exist at least four classes of functions on state spaces that induce abstract MDPs such that:
+\begin{equation}
+\forall_{s_1, s_2 \in S_G} \phi_f(s_1) = \phi_f(s_2) \rightarrow \forall_a  |f(s_1,a) - f(s_2,a)| \leq \epsilon
+\end{equation}
+
+Where, the MDP induced by the abstraction function, when solved, provides the policy $\pi^*_A$, such that:
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon)
+\end{equation}
+
+\dnote{Possible note about what all 4 functions are}
+
+% Subsection: Optimal Q Function
+\subsection{Optimal Q Function: $\phi_{Q^*}$}
+
+\dnote{Plan to put full Q proof}
+
+% Subsection: Model Similarity
+\subsection{Model Similarity: $\phi_{model}$}
+
+\dnote{Proof sketch}
+
+% Subsection: Multinomial over Optimal Q
+\subsection{Multinomial over Optimal Q: $\phi_{mult}$}
+
+\dnote{Proof sketch}
+
+% Subsection: Boltzmann over Optimal Q
+\subsection{Boltzmann over Optimal Q: $\phi_{bolt}$}
+
+\dnote{Comment about similarity to Multinomial.}
+
+\dnote{(Probably put full proofs in appendix if we have room?}
+
+% There are at least four classes of functions:
+% 1 \phi_q^*
+% 2 \phi_model
+% 3 \phi_mult
+% 4 \phi_bolt
+
 % Explain each of the Phis
@@
 % Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsections for proofs for each phi
-\dnote{Insert lemma for each phi as their subsection, maybe with proof sketch but likely just dump in appendix.}
-
-% Subsection:
-
-% Subsection: Phi_Q
-\subsection{$\phi_{Q^*}$}
-
-% Subsection: Phi_M
-\subsection{$\phi_{model}$}
-
-% Subsection: Phi_{Mult}
-\subsection{$\phi_{mult}$}
-
-% Subsection: Phi_B
-\subsection{$\phi_{bolt}$}
 

### 2016-01-28 paper/paper.tex
Added proof for Q* to paper

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{algorithmic}
@@
 Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$ respectively.
+\enote{Add citation -- either Littman review paper or Sutton/Barto}
+
+\enote{Define value of state under a policy}
 
@@
 
-\dnote{Explain the notation so like the $\phi_f$}
-
 \dnote{Tee up other stuff/ideas}
@@
 % Main theorem:
+\enote{Add intro-y stuff}
 
 \dnote{I wish this theorem used the term approximate somewhere (i.e. was using the same terminology as the intro/abstract)}
-{\bf Theorem 1:} There exist at least four classes of functions on state spaces that induce abstract MDPs such that:
+
+\enote{For clarity define phi TILDE}
+
+{\bf $\ep_f$ definition:} Given a function $f : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state abstraction function which satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}
-\forall_{s_1, s_2 \in S_G} \phi_f(s_1) = \phi_f(s_2) \rightarrow \forall_a  |f(s_1,a) - f(s_2,a)| \leq \epsilon
+\label{eq:phi_f}
+\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
 \end{equation}
 
-Where, the MDP induced by the abstraction function, when solved, provides the policy $\pi^*_A$, such that:
+That is, when $\phi_f$ aggregates states, all aggregated states the aggregated states have values of $f$ within $\epsilon$ of one another for all actions.
+
+Note that for any $f$, there are many such functions that satisfy this criteria.
+
+% Theorem 1
+{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP applied to the ground MDP has error bounded polynomially in $\epsilon$:
 \begin{equation}
@@
 
+\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
+
 \dnote{Possible note about what all 4 functions are}
 
+% Subsection:  Similarity of Value = Similar Behavior
+\subsection{Similarity of Value Yields Similar Behaviour}
+\enote{Proof that if values in the abstract and ground are similar then behavior is similar. State that for remainder of lemmas that we prove antecedent of this statement.}
+
 % Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\phi_{Q^*}$}
+\subsection{Optimal Q Function: $\ep_{Q^*}$}
 
-\dnote{Plan to put full Q proof}
+% Q* Lemma
+Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
+Consequently,  as per Equation $\ref{eq:phi_f}$, $\ep_{Q^*}$ is a type of abstraction that for a fixed $\epsilon$ satisfies:
+\begin{equation}
+\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon
+\end{equation}
+
+{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
+
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon}{1-\gamma}
+\end{equation}
+
+\textbf{Proof:}
+Consider a temporally heterogeneous \ac{MDP}, $M^T$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
+Note that $M^0 = M_G$ and $M^\infty = M_A$.
+
+The value of a state in $M^T$ is defined by:
+\begin{equation}
+V_T(s) = \max_a \left| \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') V_{T-1}(s') \right|
+\end{equation}
+
+Where:
+\begin{equation}
+\mathcal{R}_T = \begin{cases}
+\mathcal{R}_A& T > 0 \\
+\mathcal{R}_G& \text{otherwise} \\
+\end{cases}
+\end{equation}
+
+And similarly:
+\begin{equation}
+\mathcal{T}_T = \begin{cases}
+\mathcal{T}_A& T > 0 \\
+\mathcal{T}_G& \text{otherwise} \\
+\end{cases}
+\end{equation}
+
+We proceed by induction on $T$ to show that:
+\begin{equation}
+\forall_T |V^{\pi_G^*}(s) - V_T(s)| \leq \sum_{t=0}^{T+1} \epsilon \gamma^t
+\end{equation}
+
+% Base Case
+\textit{Base Case:}
+
+When T = 0, $V^{\pi_G^*}(s) = V_0(s)$, so it trivially follows that:
+\begin{equation}
+|V^{\pi_G^*}(s) - V_0(s)| \leq \epsilon = \sum_{t=0}^{0} \epsilon \gamma^t
+\end{equation}
+
+% Inductive Case
+\textit{Inductive Case:}
+
+We assume as our inductive hypothesis that:
+\begin{equation}
+\forall_s\ V_{T-1}(s) \leq \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s)
+\end{equation}
+\begin{align*}
+&\text{By definition of $V_{T}(s)$:}\\
+&V_{T}(s) = \max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')V_{T-1}(s')\right] \\
+&\leq \max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')\left(V_0(s) + \sum_{t=0}^{T-1}\epsilon\gamma^t \right) \right] \\
+&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^{t}\right) + \\ &\max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')V_0(s') \right] \\
+\end{align*}
+\begin{align*}
+&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \\ &\max_a \left[\sum_{g \in s} R_{G}(g,a)\omega(g) + \gamma \sum_{s'} \sum_{g \in s}T_G(g,a,s')\omega(g)V_0(s') \right] \\
+&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \epsilon + \left(\max_a Q_G(s,a)\right) \\
+&= \sum_{t=0}^{T} \epsilon \gamma^{t} + \max_a Q^{\pi_G^*}(s,a) \\
+&= \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
+\end{align*}
+
+Therefore, for all $T$:
+\begin{align*}
+V_{T}(s) &\leq \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
+|V^{\pi_G^*}(s) - V_{T}(s)| &\leq \frac{\epsilon}{1-\gamma}
+\end{align*}
+
+Note that as $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:
+
+\begin{equation}
+|V^{\pi_G^*}(s) - V^{\pi_A^*}(s)| \leq \frac{\epsilon}{1-\gamma}
+\end{equation}
 
 % Subsection: Model Similarity
-\subsection{Model Similarity: $\phi_{model}$}
+\subsection{Model Similarity: $\ep_{model}$}
 
@@
 % Subsection: Multinomial over Optimal Q
-\subsection{Multinomial over Optimal Q: $\phi_{mult}$}
+\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
 
@@
 % Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\phi_{bolt}$}
+\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
 

### 2016-01-28 paper/paper.tex
More edits

@@
 
+\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
+
 % Subsection: Exact Abstraction Framework
@@
 
-% INTRO PARAGRAPH, setup + structure
-
-\dnote{Tee up other stuff/ideas}
-
-% Main theorem:
-\enote{Add intro-y stuff}
-
-\dnote{I wish this theorem used the term approximate somewhere (i.e. was using the same terminology as the intro/abstract)}
-
-\enote{For clarity define phi TILDE}
+% Intro to approx state abstraction results.
+Here we introduce our formal method for approximate state abstraction, and the related results bounding the error associated with these abstraction methods.
+In particular, we demonstrate that abstractions based on $Q^*$ similarity, Model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann disibtruions, induce abstract MDPs for which the optimal policy has bounded error in the ground MDP.
+We now introduce some additional notation to formally discuss these results.
 
@@
 
-That is, when $\phi_f$ aggregates states, all aggregated states the aggregated states have values of $f$ within $\epsilon$ of one another for all actions.
-
+That is, when $\phi_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
 Note that for any $f$, there are many such functions that satisfy this criteria.
 
+We now introduce the main result of the paper.
+
 % Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP applied to the ground MDP has error bounded polynomially in $\epsilon$:
+{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP, applied to the ground MDP, has error bounded polynomially in $\epsilon$:
 \begin{equation}
@@
 
-\dnote{Possible note about what all 4 functions are}
+% Subsection:  Similarity of Value = Similar Behavior
+\subsection{Similarity of Value Yields Similar Behavior}
 
-% Subsection:  Similarity of Value = Similar Behavior
-\subsection{Similarity of Value Yields Similar Behaviour}
-\enote{Proof that if values in the abstract and ground are similar then behavior is similar. State that for remainder of lemmas that we prove antecedent of this statement.}
+{\bf Lemma 1:}
+If the value of a state in the ground \ac{MDP} is within $\kappa \in \mathbb{R}$ of the value of the corresponding abstract state, then the value of the ground state under the optimal policy in the abstract \ac{MDP} is within $\kappa$ of the value of the ground state:
+\begin{multline*}
+| V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow
+\left| V_G(s) - V_G^{\pi_A^*} \right| \leq \kappa
+\end{multline*}
+
+\textbf{Proof:}
 
@@
 Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-Consequently,  as per Equation $\ref{eq:phi_f}$, $\ep_{Q^*}$ is a type of abstraction that for a fixed $\epsilon$ satisfies:
+Consequently, by Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
 \begin{equation}
@@
 
-{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
-
+{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
 \begin{equation}

### 2016-01-28 paper/paper.tex
added lemma statements for each section

@@
 
-\dnote{Proof sketch}
+We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon_\mathcal{R}$ and $\epsilon_\mathcal{T}$, satisfies:
+\begin{multline}
+\ep_{model}(s_1) = \ep_{model}(s_2) \rightarrow \\
+\forall_a \left|\mathcal{R}(s_1, a) - \mathcal{R}(s_2, a)\right| \leq \epsilon_\mathcal{R}\ \wedge\ \\
+\forall_{a,s'} \left|\mathcal{T}(s_1, a,s') - \mathcal{T}(s_2, a,s')\right| \leq \epsilon_\mathcal{T}
+\end{multline}
+
+{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{model}$ type:
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
+\end{equation}
+
+{\bf Proof:}
+
+Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B_s$.
+
+\begin{align*}
+B_{s} &= \max_{s,a}|Q'(s,a)-Q(s,a)|\\
+%B_{s} &= \max_{s,a}|R'(s,a) - R(s,a) + \gamma \sum_{s'}\left[T'(s,a,s')\max_{a'}Q'(s',a')-T(s,a,s')\max_{a'}Q(s', a')\right]|\\
+&\forall s' \text{ WLOG } T'(s,a,s')\max_{a'}Q'(s',a') \geq T(s,a,s')\max_{a'}Q(s',a')\\
+\end{align*}
+Applying max is a non-expansion:
+\begin{multline}
+=\max_{s,a}(|R'(s,a)-R(s,a)| + \gamma \sum_{s'} \\
+\max_{a'} [(T(s,a,s')+T'(s,a,s')- \\ T(s,a,s'))Q'(s', a')-T(s,a,s')Q(s',a')])
+\end{multline}
+%&\leq \max_{s,a}|R'_s-R_s|+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')+\epsilon_{\mathcal{T}})Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
+%&\leq \epsilon_{\mathcal{R}}+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')Q'(s',a')+\epsilon_{\mathcal{T}}Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
+%&\leq \epsilon_{\mathcal{R}} + \max_{s,a} \gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')(Q'(s',a')-Q(s',a'))+\epsilon_{\mathcal{T}}Q'(s',a') \right]\\
+\begin{align*}
+&\leq \epsilon_{\mathcal{R}}+\gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{\text{max}} + \gamma \sum_{s'}\left[ T(s,a,s') B_s\right]\\
+&\leq \epsilon_{\mathcal{R}} + \gamma B_{s} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{max}
+\end{align*}
+
+Applying $Q'_{max}=V'_{max} \leq V_{max}=\frac{1}{1-\gamma}$:
+\begin{align*}
+B_{s} &\leq 
+\frac
+{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}
+{(1-\gamma)^2}
+\end{align*}
+
+Therefore:
+\begin{align*}
+\forall_{s,a} : |Q'(s,a) - Q(s,a)| &\leq \max_{s,a}|Q'(s,a)-Q(s,a)| \\
+&\leq  \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}} }{(1-\gamma)^2}
+\end{align*}
+
+Consequently, from the below $\phi_Q^*$ results, we conclude that:
+\begin{equation}
+\forall_s : |V^{\pi^*_M}(s) - V^{\pi^*_{M'}}(s)| \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
+\end{equation}
 
@@
 \subsection{Multinomial over Optimal Q: $\ep_{mult}$}
+
+We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
+\begin{multline}
+\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
+\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
+\end{multline}
+
+\dnote{We also need to add the point about the denominator bound...}
+
+{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
+\end{equation}
+
+{\bf Proof Sketch:}
 
@@
 
-\dnote{Comment about similarity to Multinomial.}
+Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
+\begin{multline}
+\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
+\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
+\end{multline}
+
+{\bf Lemma 5:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
+\end{equation}
+
+{\bf Proof Sketch:}
+
+\dnote{Proof sketch}
 

### 2016-01-28 paper/paper.tex
a few fixes

@@
 A \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers immediate rewards over future rewards.
+We assume without loss of generality that all reward functions are normalized to $[0,1]$.
 
@@
 Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make now assumptions about the weighting scheme, except that the weighting is a convex combination across all states in partition.
+We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
 
@@
 In particular, we demonstrate that abstractions based on $Q^*$ similarity, Model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann disibtruions, induce abstract MDPs for which the optimal policy has bounded error in the ground MDP.
+
+In general, our proof strategy for each of the included results is as follows:
+\begin{itemize}
+\item First, we relate the values of states in the ground MDP to value of the states in the Abstract MDP
+\item Then, we relate the value of states in the ground MDP to value of the states in the Abstract MDP under the optimal abstract policy.
+\end{itemize}
+
 We now introduce some additional notation to formally discuss these results.
@@
 Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-Consequently, by Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
+Inspired by the $Q^*$ irrelevance abstraction, we consider the approximate case.
+By Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
 \begin{equation}
@@
 
+Inspired by the model-irrelevance abstraction, we consider the approximate case.
 We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon_\mathcal{R}$ and $\epsilon_\mathcal{T}$, satisfies:
@@
 
+To empirically evaluate our approximate abstractions, we test out the $\ep{Q^*}$ abstraction on a variety of domains.
+We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
+
+The domains we evaluate in are UpWorld, a contrived version of Grid World, NChain, the classic exploration task form the Bayesian Reinforcement Learning literature, the Trench task, introduced by CITE DABE, and the Taxi Problem, a classic problem discussed in hierarchical Reinforcement tLearning literature.
+
 \dnote{For each section, we'll include a plot comparing $\epsilon$ to \# states, and $\epsilon$ to performance.

### 2016-01-28 paper/paper.tex
Crappy proof that doesn't work for Lemma 1

@@
 {\bf Lemma 1:}
-If the value of a state in the ground \ac{MDP} is within $\kappa \in \mathbb{R}$ of the value of the corresponding abstract state, then the value of the ground state under the optimal policy in the abstract \ac{MDP} is within $\kappa$ of the value of the ground state:
+If the value of all states in the ground \ac{MDP} are within $\kappa \in \mathbb{R}$ of the value of their corresponding abstract state, then the value of all ground states under the optimal policy in the abstract \ac{MDP} are within $3 \kappa$ of the value of their corresponding ground states:
 \begin{multline*}
-| V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow
-\left| V_G(s) - V_G^{\pi_A^*} \right| \leq \kappa
+\forall_{s\in \mathcal{S}_G} | V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow\\
+\forall_{s\in \mathcal{S}_G}\left| V_G(s) - V_G^{\pi_A^*}(s) \right| \leq 3\kappa
 \end{multline*}
@@
 \textbf{Proof:}
+Given a state, $s \in \mathcal{S}_G$ by definition:
+
+Assume
+\begin{equation}
+\label{eq:similarValAssum}
+|V_G(s) - V_A(\phi (s)) | \leq \kappa
+\end{equation}
+
+Let $s_A$ stand for $\phi(s)$
+
+\begin{align*}
+&V_A(s_A) = \max_a \left| R_A(s_A, a) + \gamma \sum_{s_A' \in \mathcal{S}_A} T_A(s_A, a, s_A') V_A(s'a)   \right| \\
+&\leq \max_a \left| \sum_{g \in s_A} \left[ R_G(g,a) + \gamma  \sum_{g'}T_G(g, a, g')(V_g(g') + \kappa) \right] \right|\\
+\end{align*}
+
+\begin{equation}
+\label{eq:similarValIntResult}
+\leq \gamma \kappa + \sum_{g \in s_A} w(g)V_G(g)
+\end{equation}
+
+Given two ground states, $s_1$ and $s_2$ for which $\phi(s_1) = \phi(s_2)$ we know by Equation \ref{eq:similarValAssum} that 
+\begin{align*}
+V_A(\phi(s_1))-\kappa \leq V_G(s_1) \leq V_A(\phi(s_1))+\kappa
+\end{align*}
+
+and symmetrically that
+\begin{align*}
+V_A(\phi(s_1))-\kappa \leq V_G(s_2) \leq V_A(\phi(s_1))+\kappa
+\end{align*}
+
+By subtraction,
+\begin{align*}
+-2 \kappa \leq V_G(s_1) - V_G(s_2) \leq 2 \kappa \\
+\end{align*}
+
+\begin{equation}
+\label{eq:similarValIntResult2}
+\left|  V_G(s_1) - V_G(s_2) \right| \leq 2\kappa
+\end{equation}
+
+Let $g_{min}$ stand for $\underset{g}{argmin} V_{G}(g)$.
+
+We know by equations \ref{eq:similarValIntResult} and \ref{eq:similarValIntResult2} that
+\begin{align*}
+V_A(s_A) &\leq \gamma \kappa +\sum_{g \in s_A} w(g)(V_G(g_{min})+2\kappa) \\
+&\leq 3\kappa + V_G(g_{min})\\
+V_A(s_A)  -  V_G(g_{min}) &\leq 3 \kappa
+\end{align*}
 
@@
 
-Note that as $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:
+As $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:
 

### 2016-01-29 paper/paper.tex
Mostly fixed Q* proof

--- 2016-01-28 paper/paper.tex
@@
 \newcommand{\ep}{\widetilde \phi}
+\newcommand{\epQ}{\ep_{Q^*}}
 \newcommand\defn[1]{{\bf Definition:} #1}
@@
 
-% Subsection:  Similarity of Value = Similar Behavior
-\subsection{Similarity of Value Yields Similar Behavior}
-
-{\bf Lemma 1:}
-If the value of a state in the ground \ac{MDP} is within $\kappa \in \mathbb{R}$ of the value of the corresponding abstract state, then the value of the ground state under the optimal policy in the abstract \ac{MDP} is within $\kappa$ of the value of the ground state:
-\begin{multline*}
-| V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow
-\left| V_G(s) - V_G^{\pi_A^*} \right| \leq \kappa
-\end{multline*}
-
-\textbf{Proof:}
-
 % Subsection: Optimal Q Function
@@
 By Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
+
 \begin{equation}
@@
 
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
+{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon}{1-\gamma}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon}{(1-\gamma)^2}
 \end{equation}
@@
 \textbf{Proof:}
+We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
+
 Consider a temporally heterogeneous \ac{MDP}, $M^T$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
@@
 V_T(s) = \max_a \left| \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') V_{T-1}(s') \right|
+\end{equation}
+
+Similarly, the Q-value of state $s$ in $M^T$ for action $a$ is defined by:
+\begin{equation}
+Q(s, a) = \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') \max_{a'} Q(s',a')
 \end{equation}
@@
 
-And similarly:
+And:
 \begin{equation}
@@
 
+\enote{Add something about weirdness of state spaces changing at $T=1$}
+
 We proceed by induction on $T$ to show that:
 \begin{equation}
-\forall_T |V^{\pi_G^*}(s) - V_T(s)| \leq \sum_{t=0}^{T+1} \epsilon \gamma^t
+\forall_{T, g \in \mathcal{S}_G, a} |Q_G(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T+1} \epsilon \gamma^t
 \end{equation}
@@
 
-When T = 0, $V^{\pi_G^*}(s) = V_0(s)$, so it trivially follows that:
+\enote{Fix this -- state spaces are the same for this case}
+
+When T = 0, $Q^{\pi_G^*} = Q_0$, so it trivially follows that:
 \begin{equation}
-|V^{\pi_G^*}(s) - V_0(s)| \leq \epsilon = \sum_{t=0}^{0} \epsilon \gamma^t
+\forall_{g\in \mathcal{S_G}, a} |Q^{\pi_G^*}(g, a) - Q_T(\ep_{Q^*}(g), a)| \leq \sum_{t=0}^{0} \epsilon \gamma^t
 \end{equation}
 
+\enote{Add base case for $T=1$ since our value function is not well defined unless $T > 1$.}
+
 % Inductive Case
-\textit{Inductive Case:}
+\textit{Inductive Case:} \enote {For $T>1$}
 
@@
 \begin{equation}
-\forall_s\ V_{T-1}(s) \leq \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s)
+\forall_{g \in \mathcal{S}_G, a} |Q^{\pi_G^*}(g, a) - Q_{T-1}(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t\\
 \end{equation}
+
+Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
+
+We denote $\epQ(s_G)$ as $s_A$.
 \begin{align*}
-&\text{By definition of $V_{T}(s)$:}\\
-&V_{T}(s) = \max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')V_{T-1}(s')\right] \\
-&\leq \max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')\left(V_0(s) + \sum_{t=0}^{T-1}\epsilon\gamma^t \right) \right] \\
-&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^{t}\right) + \\ &\max_a \left[R_{T}(s,a) + \gamma \sum_s' T_{T}(s,a,s')V_0(s') \right] \\
-\end{align*}
-\begin{align*}
-&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \\ &\max_a \left[\sum_{g \in s} R_{G}(g,a)\omega(g) + \gamma \sum_{s'} \sum_{g \in s}T_G(g,a,s')\omega(g)V_0(s') \right] \\
-&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \epsilon + \left(\max_a Q_G(s,a)\right) \\
-&= \sum_{t=0}^{T} \epsilon \gamma^{t} + \max_a Q^{\pi_G^*}(s,a) \\
-&= \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
+&\text{By definition of $Q_{T}(s_A, a)$:}\\
+&Q_T(s_A, a) = \mathcal{R}_T(s_A,a) + \gamma \sum_{{s_A}' \in M_T} \mathcal{T}_T(s_A,a,{s_A}') \max_{a'} Q_{T-1}({s_A}',a')\\
+&=\sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
+&\text{Where $g$ ranges over states such that $\epQ(g) = S_A$ and $g' \in \mathcal{S}_G$}\\
+&\text{Applying our inductive hypothesis yields}\\
+&\leq \sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-1} \epsilon \gamma^t)      \right]\\
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'}Q_0      \right]\\
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \sum_{g}\left[ w(g)\ Q_0(g,a)\right]\\
+&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
+&\leq \gamma\sum_{t=0}^{T} \epsilon \gamma^t + Q_0(s_G, a)\\
+&\text{Thus,}\\
+&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
 \end{align*}
 
-Therefore, for all $T$:
+Since $s_G$ and $s_A$ are arbitrary, we conclude
+\begin{equation}
+\forall_{T, g \in \mathcal{S}_G, a} |Q^{\pi_G^*}(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T} \epsilon \gamma^t
+\end{equation}
+
+%\begin{align*}
+%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \\ &\max_a \left[\sum_{g \in s} R_{G}(g,a)\omega(g) + \gamma \sum_{s'} \sum_{g \in s}T_G(g,a,s')\omega(g)V_0(s') \right] \\
+%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \epsilon + \left(\max_a Q_G(s,a)\right) \\
+%&= \sum_{t=0}^{T} \epsilon \gamma^{t} + \max_a Q^{\pi_G^*}(s,a) \\
+%&= \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
+%\end{align*}
+
+As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore:
+
+\begin{equation}
+\label{eq:Q*HalfResult}
+\forall_{g \in \mathcal{S}_G, a} |Q_G(g, a) - Q_A(\epQ(g), a)| \leq \frac{\epsilon}{1-\gamma}
+\end{equation}
+
+max
+
+Having proved that the Q values in the abstract MDP formed by abstractions of the $\epQ$ type closely resemble those in the ground \ac{MDP}, we now use this result to demonstrate that optimal behavior in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}.
+
+Consider the following policy on states in $\mathcal{S}_G$:
+\begin{equation}
+\pi_{A,t}(s)=
+\begin{cases}
+\pi_G^*(s), \text{if $t<=0$}\\
+\pi_A^*(\ep(s)), \text{if $t > 0$}\\
+\end{cases}
+\end{equation}
+
 \begin{align*}
-V_{T}(s) &\leq \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
-|V^{\pi_G^*}(s) - V_{T}(s)| &\leq \frac{\epsilon}{1-\gamma}
+\text{Let }Q^{\pi_{A,t}}(g) &= \\
+&R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')
 \end{align*}
 
-Note that as $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:
+where $g, g' \in \mathcal{S}_G$.
 
+We now show by induction on $t$ that
 \begin{equation}
-|V^{\pi_G^*}(s) - V^{\pi_A^*}(s)| \leq \frac{\epsilon}{1-\gamma}
+\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t}\gamma^i \frac{\epsilon}{1-\gamma}
 \end{equation}
 
+\textit{Base case: $t=0$}
+
+By definition when $t=0$, $Q^{\pi_{A,t}} = Q^{\pi^*}$ so it trivially follows that
+\begin{equation}
+\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,0}}(g, a) \leq Q^{\pi^*}(g,a) + \frac{\epsilon}{1-\gamma}
+\end{equation}
+
+\textit{Inductive case: $t > 0$}
+
+We assume for our inductive hypothesis that
+\begin{equation}
+\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t-1}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma}
+\end{equation}
+
+By definition 
+\begin{align*}
+&Q^{\pi_{A,t}}(g, a) = R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')\\
+&\text{Applying our inductive hypothesis yields}\\
+&Q^{\pi_{A,t}}(g, a) \leq\\
+&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}\left(Q^{\pi^*}(g',a') + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} \right)\\
+&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi^*}(g',a')\\
+&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
+&\text{Applying Equation \ref{} yields}\\
+&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, a)\\
+\end{align*}
 % Subsection: Model Similarity
@@
 \end{align*}
-Applying max is a non-expansion:
+Applying max is a non-expansion \enote{Probably want a citation and or explanation for this}:
 \begin{multline}
@@
 % Subsection: Multinomial over Optimal Q
+\enote{If not here, we should have some motivation for multinomial (and boltz)}
 \subsection{Multinomial over Optimal Q: $\ep_{mult}$}

### 2016-01-29 paper/paper.tex
Q* proof done first pass -- still need to do t=1 case for heterogeneous MDP.

@@
 \newcommand\defn[1]{{\bf Definition:} #1}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 
-%\begin{align*}
-%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \\ &\max_a \left[\sum_{g \in s} R_{G}(g,a)\omega(g) + \gamma \sum_{s'} \sum_{g \in s}T_G(g,a,s')\omega(g)V_0(s') \right] \\
-%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \epsilon + \left(\max_a Q_G(s,a)\right) \\
-%&= \sum_{t=0}^{T} \epsilon \gamma^{t} + \max_a Q^{\pi_G^*}(s,a) \\
-%&= \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
-%\end{align*}
-
 As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore:
@@
 
-max
+Having proved that the Q values in the abstract MDP formed by abstractions of the $\epQ$ type closely resemble those in the ground \ac{MDP}, we now use this result to demonstrate that optimal behavior in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}.
 
-Having proved that the Q values in the abstract MDP formed by abstractions of the $\epQ$ type closely resemble those in the ground \ac{MDP}, we now use this result to demonstrate that optimal behavior in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}.
+Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
+
+Let $a^*_G$ stand for the optimal action for $s_G$: \\
+$a^*_G = \argmin Q_G(s_G, a)$
+
+Let $a^*_A$ stand for the optimal action for $s_A$:\\
+ $a^*_A = \argmin Q_A(s_A, a)$
+
+By Equation \ref{eq:Q*HalfResult} and the definition of $a^*_G$ and $a^*_A$ we know that 
+\begin{align}
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \nonumber \\
+\label{eq:Q*OptActionResult}
+&\leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
+\end{align}
 
@@
 
+Again, consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$
+
 \begin{align*}
-\text{Let }Q^{\pi_{A,t}}(g) &= \\
-&R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')
+\text{Let }V^{\pi_{A,t}}(s_G) &= \\
+&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
 \end{align*}
@@
 
+%Start induction on following the optimal abstract policy
 We now show by induction on $t$ that
 \begin{equation}
-\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t}\gamma^i \frac{\epsilon}{1-\gamma}
+\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 
-By definition when $t=0$, $Q^{\pi_{A,t}} = Q^{\pi^*}$ so it trivially follows that
+By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so it trivially follows that
 \begin{equation}
-\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,0}}(g, a) \leq Q^{\pi^*}(g,a) + \frac{\epsilon}{1-\gamma}
+V^{\pi^*}(s_G) \leq V^{\pi_{A,0}}(s_G) + \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 \begin{equation}
-\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t-1}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma}
+V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 \begin{align*}
-&Q^{\pi_{A,t}}(g, a) = R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')\\
+&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
 &\text{Applying our inductive hypothesis yields}\\
-&Q^{\pi_{A,t}}(g, a) \leq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}\left(Q^{\pi^*}(g',a') + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} \right)\\
-&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi^*}(g',a')\\
-&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{} yields}\\
-&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, a)\\
+&V^{\pi_{A,t}}(g, a) \geq\\
+&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
+&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
+&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
+&\text{Applying Equation \ref{eq:Q*OptActionResult} yields}\\
+&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
+&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
+& \text{Thus,}\\
+&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{align*}
+
+From our base case and induction we conclude that
+\begin{equation}
+\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\end{equation}
+
+Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of a geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
+
+Thus we conclude,
+\begin{equation*}
+\forall_{g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A}^*}(g) + \frac{2\epsilon}{(1-\gamma)^2}
+\end{equation*}
+
+\begin{equation*}
+\forall_{g \in \mathcal{S}_g} \left | V^{\pi^*}(g) - V^{\pi_{A}^*}(g) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
+\end{equation*}
+
 % Subsection: Model Similarity

### 2016-01-29 paper/paper.tex
prepping for merge

--- 2016-01-29 paper/paper.tex
@@
 
-To empirically evaluate our approximate abstractions, we test out the $\ep{Q^*}$ abstraction on a variety of domains.
+To demonstrate the efficacy of these approximate abstraction functions, we test out functions in the $\ep{Q^*}$ abstraction on a variety of domains.
 We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
 
-The domains we evaluate in are UpWorld, a contrived version of Grid World, NChain, the classic exploration task form the Bayesian Reinforcement Learning literature, the Trench task, introduced by CITE DABE, and the Taxi Problem, a classic problem discussed in hierarchical Reinforcement tLearning literature.
+The domains we evaluate in are UpWorld, a contrived version of Grid World in which the agent can only move left, right, and up (where up is always optimal, thus the name), 5Chain, the classic exploration task form the Bayesian Reinforcement Learning literature, the goal-based Trench task introduced by CITE DABE, and the Minefield domain.
+Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
 
@@
 
-\dnote{As part of UpWorld we can include the result about the unbounded improvement in sample complexity (small lemma or something?)}
+The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
+The agent may move left, right, and up.
+The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
+the agent receives 0 reward for all other transitions.
+Consequently, moving up is always the optimal thing to do, since moving left and right does not change the agent's manhattan distance to positive reward.
+During experimentation, we set $N=10$, $M=4$.
+
+% PUT INTO RESULTS One interesting fact about UpWorld is that, if $M$ the width of the grid, is defined to be an arbitrary function of $N$, say $k^N$ for some $k \in \mathbb{Z}$, then optimality preserving abstractions can arbitrarily reduce the sample complexity of the problem.
+
+\begin{figure}
+\subfigure[Ground UpWorld]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
+\subfigure[Abstract UpWorld]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
+\label{fig:eps-states}
+\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
+\end{figure}
 
@@
 
-% Subsection: NChain.
+% Subsection: 5Chain.
 \subsection{NChain}
@@
 
+\begin{figure}
+\subfigure[Ground NChain]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
+\subfigure[Abstract NChain]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
+\label{fig:eps-states}
+\caption{Comparison of Original NChain MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
+\end{figure}
+
+% Subsection: Minefield.
+\subsection{Minefield}
+
+There is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
+
+\begin{figure}
+\subfigure[Ground Minefield]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
+\subfigure[Abstract Minefield]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
+\label{fig:eps-states}
+\caption{Comparison of Original Minefield MDP and Abstract MDP, under $\epQ$, with $\epsilon=1.1$}
+\end{figure}
+
 % Subsection: Trench.
 \subsection{Trench}
+
+To demonstrate the effects of approximate abstraction on goal-based tasks, we investigate the Trench problem, introduced by \dnote{Cite dabe}.
 

### 2016-01-29 paper/paper.tex
Trying to pull

--- 2016-01-29 paper/paper.tex
@@
 
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of a geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
+Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
 

### 2016-01-29 Workspace and Code/stateAbstraction/src/plotting/plotter.py
added support for displaying random policy, added legends, multiple ydata

@@ -7,10 +7,13 @@
 import matplotlib.pyplot as plt
 import matplotlib
 import numpy as np
+import pylab
 import sys
 import os
 from os import listdir
 from os.path import isdir, join
+
+_markers = ['v','^','s']
 
 def loadFile(taskName):
 
@@ -27,40 +30,61 @@ def parseResultsFile(resultsFile):
 	numStates = []
 	groundStateVals = []
 	abstractStateVals = []
+	rand = []
+	numGroundStates = []
 
 	for line in file(resultsFile,"r").readlines():
 		results = line.split("\t") # Tab separated result file.
+
+		if "RAND" in results:
+			# Add rand if it's in there.
+			rand.append(float(results[1]))
+			continue
+		if "NUMGROUNDSTATES" in results:
+			numGroundStates.append(int(results[1]))
+			continue
+
 		epsilons.append(float(results[0]))
 		numStates.append(int(results[1]))
 		groundStateVals.append(float(results[2]))
 		abstractStateVals.append(float(results[3]))
 
-	return epsilons, numStates, groundStateVals, abstractStateVals
+	return numGroundStates, rand, epsilons, numStates, groundStateVals, abstractStateVals
 
-def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon", epsilons=[]):
+def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon", epsilons=[], yDataNames=[]):
 	
 	if scatter:
 		# Scatter plot.
-		
-
 		for i in xrange(len(xData)):
-			plt.scatter(xData[i], yData[i], s=(epsilons[i]**4+1)*20, alpha=0.5)
+			plt.scatter(xData[i], yData[i], s=(epsilons[i]*200)/max(epsilons), alpha=0.5)
+	elif type(yData[0]) == list:
 
-		
+		for i, yDatum in enumerate(yData):
+			if len(yDataNames) >= i:
+				legendInfo = yDataNames[i]
+			else:
+				legendInfo = ""
+			plt.plot(xData, yDatum, "-", marker=_markers[i], markersize=10, label=legendInfo)
+
+		plt.xlim([min(0,min(xData)), max(xData)])
+		plt.ylim([0, max([max(y) for y in yData]) *1.2])
+
 	else: 
 		# Line plot.
-		plt.plot(xData, yData, marker="o", color="black")
[…]

### 2016-01-29 paper/paper.tex
added expeirment writeup

--- 2016-01-29 paper/paper.tex
@@
 
+% -----------------------------------------------
 % --- SECTION: Example Domains ---
+% -----------------------------------------------
 \section{Example Domains}
 
-To demonstrate the efficacy of these approximate abstraction functions, we test out functions in the $\ep{Q^*}$ abstraction on a variety of domains.
+To demonstrate the efficacy of these approximate abstraction functions, we test out functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
 We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
+More specifically, we relate $\epsilon$ to
+\begin{equation}
+|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
+\end{equation}
 
-The domains we evaluate in are UpWorld, a contrived version of Grid World in which the agent can only move left, right, and up (where up is always optimal, thus the name), 5Chain, the classic exploration task form the Bayesian Reinforcement Learning literature, the goal-based Trench task introduced by CITE DABE, and the Minefield domain.
+For different values of $\epsilon$.
+
+The domains we evaluate in are UpWorld, Nchain, Trench, and Minefield.
+UpWorld is a contrived version of Grid World in which the agent can only move left, right, and up (where up is always optimal, thus the name).
+NChain is a classic exploration task from the Bayesian Reinforcement Learning literature.
+Trench is a highly challenging goal-based task introduced by CITE DABE.
+Lastly, the Minefield domain is similar to UpWorld, but introduces stochastic transition dynamics, .
 Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-
-\dnote{For each section, we'll include a plot comparing $\epsilon$ to \# states, and $\epsilon$ to performance.
-For UpWorld and NChain, we can include visuals of uncompressed and compressed (not useful for trench).}
 
@@
 the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal thing to do, since moving left and right does not change the agent's manhattan distance to positive reward.
+Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
 During experimentation, we set $N=10$, $M=4$.
-
-% PUT INTO RESULTS One interesting fact about UpWorld is that, if $M$ the width of the grid, is defined to be an arbitrary function of $N$, say $k^N$ for some $k \in \mathbb{Z}$, then optimality preserving abstractions can arbitrarily reduce the sample complexity of the problem.
 
@@
 
-% Subsection: 5Chain.
+% Subsection: NChain.
 \subsection{NChain}
@@
 
-There is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
+Minefield is identical to UpWorld, except the transitions and rewards are perturbed slightly.
+In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
+The reward function is nearly identical to UpWorld: transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states that receive $0$ reward (these are the mine states, that receive $\textsc{RMin}$).
+During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
 
@@
 \subfigure[UpWorld]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\includegraphics[width=0.28\columnwidth]{figures/upworld_epsilon_vs_num_abstract_states.png}}
 \subfigure[NChain]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\includegraphics[width=0.28\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
+\subfigure[Minefield]{
+\includegraphics[width=0.28\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
 \subfigure[Trench]{
@@
 \subfigure[UpWorld]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\includegraphics[width=0.28\columnwidth]{figures/upworld_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
 \subfigure[NChain]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
-\subfigure[Trench]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\includegraphics[width=0.28\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
+\subfigure[Minefield]{
+\includegraphics[width=0.28\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
 \label{fig:eps-states}
-\caption{$\epsilon$ vs. Error in Abstract Value Function}
+\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
 \end{figure}

### 2016-01-30 paper/paper.tex
Claim1 for Q* now super clear.

--- 2016-01-29 paper/paper.tex
@@
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon}{(1-\gamma)^2}
+\forall_{s \in S_M} : | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}
 \end{equation}
@@
 
-Consider a temporally heterogeneous \ac{MDP}, $M^T$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-Note that $M^0 = M_G$ and $M^\infty = M_A$.
+Let $Q_G : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G : \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
 
-The value of a state in $M^T$ is defined by:
+Let $Q_A  : \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A : \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
+
+Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$.
+
+%Claim 1
+\textbf{Claim 1 -- Q-Values in the abstract MDP, closely resemble those in the ground MDP:}
 \begin{equation}
-V_T(s) = \max_a \left| \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') V_{T-1}(s') \right|
+\label{eq:Q*Claim1}
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}
 \end{equation}
 
-Similarly, the Q-value of state $s$ in $M^T$ for action $a$ is defined by:
-\begin{equation}
-Q(s, a) = \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') \max_{a'} Q(s',a')
-\end{equation}
+Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
 
@@
 \begin{equation}
-\mathcal{R}_T = \begin{cases}
-\mathcal{R}_A& T > 0 \\
-\mathcal{R}_G& \text{otherwise} \\
+\mathcal{S}_T = \begin{cases}
+\mathcal{S}_G& T \leq 0 \\
+\mathcal{S}_A& \text{o/w} \\
 \end{cases}
@@
 \begin{equation}
-\mathcal{T}_T = \begin{cases}
-\mathcal{T}_A& T > 0 \\
-\mathcal{T}_G& \text{otherwise} \\
+\mathcal{R}_T(s,a) = \begin{cases}
+\mathcal{R}_G(s,a)& T \leq 0 \\
+\mathcal{R}_A(s, a)& \text{o/w} \\
 \end{cases}
@@
 
-\enote{Add something about weirdness of state spaces changing at $T=1$}
+And:
+\begin{equation}
+\mathcal{T}_T(s,a,s') = \begin{cases}
+\mathcal{T}_G(s,a,s')& T \leq 0 \\
+\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
+\mathcal{T}_A(s,a,s')& \text{o/w} \\
+\end{cases}
+\end{equation}
+
+It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
+\begin{equation}
+Q_T(s, a) = 
+\begin{cases}
+	   Q_G(s, a) &  T=0\\
+	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
+%	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
+\end{cases}
+\end{equation}
 
@@
 \begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_G(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T+1} \epsilon \gamma^t
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t}
 \end{equation}
 
-% Base Case
-\textit{Base Case:}
+% Base Case t=0
+\textit{Base Case: $T = 0$}
 
-\enote{Fix this -- state spaces are the same for this case}
+When T = 0, $Q_T = Q_0$, so the result trivially follows.
 
-When T = 0, $Q^{\pi_G^*} = Q_0$, so it trivially follows that:
-\begin{equation}
-\forall_{g\in \mathcal{S_G}, a} |Q^{\pi_G^*}(g, a) - Q_T(\ep_{Q^*}(g), a)| \leq \sum_{t=0}^{0} \epsilon \gamma^t
-\end{equation}
-
-\enote{Add base case for $T=1$ since our value function is not well defined unless $T > 1$.}
+% Base Case t=1
+\textit{Base Case: $T = 1$}
+\begin{align*}
+&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right]\\
+\end{align*}
+Since all aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination.
+\begin{align*}
+&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
+&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a)\\
+&\text{Thus,}\\
+&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
+\end{align*}
 
 % Inductive Case
-\textit{Inductive Case:} \enote {For $T>1$}
+\textit{Inductive Case: $T > 1$}
 
@@
 \begin{equation}
-\forall_{g \in \mathcal{S}_G, a} |Q^{\pi_G^*}(g, a) - Q_{T-1}(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t\\
+\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t\\
 \end{equation}
@@
 \begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$:}\\
-&Q_T(s_A, a) = \mathcal{R}_T(s_A,a) + \gamma \sum_{{s_A}' \in M_T} \mathcal{T}_T(s_A,a,{s_A}') \max_{a'} Q_{T-1}({s_A}',a')\\
-&=\sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Where $g$ ranges over states such that $\epQ(g) = S_A$ and $g' \in \mathcal{S}_G$}\\
+&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
+&Q_T(s_A, a) =\sum_{g \in X}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-2}(g', a')      \right]\\
 &\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-1} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \sum_{g}w(g)\left[ R_0(g,a) + \gamma \sum_{g'} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \sum_{g}\left[ w(g)\ Q_0(g,a)\right]\\
+&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
+&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
+&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
 &\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T} \epsilon \gamma^t + Q_0(s_G, a)\\
+&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
 &\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
+&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
 \end{align*}
 
-Since $s_G$ and $s_A$ are arbitrary, we conclude
+Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
 \begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q^{\pi_G^*}(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T} \epsilon \gamma^t
+\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
 \end{equation}
 
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore:
+As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
+
+\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
 
 \begin{equation}
-\label{eq:Q*HalfResult}
-\forall_{g \in \mathcal{S}_G, a} |Q_G(g, a) - Q_A(\epQ(g), a)| \leq \frac{\epsilon}{1-\gamma}
+\label{eq:Q*Claim2}
+V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
 \end{equation}
-
-Having proved that the Q values in the abstract MDP formed by abstractions of the $\epQ$ type closely resemble those in the ground \ac{MDP}, we now use this result to demonstrate that optimal behavior in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}.
 
@@
 
-By Equation \ref{eq:Q*HalfResult} and the definition of $a^*_G$ and $a^*_A$ we know that 
+By Equation \ref{eq:Q*Claim1} and the definition of $a^*_G$ and $a^*_A$ we know that 
 \begin{align}
@@
 \end{align}
+
+Therefore, we conclude Equation \ref{eq:Q*Claim2}.
 

### 2016-01-30 paper/paper.tex
Fixed comment out Q
prepping for merge

--- 2016-01-29 paper/paper.tex
@@
 We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to
+More specifically, we relate $\epsilon$ to:
 \begin{equation}
@@
 \end{equation}
-
 For different values of $\epsilon$.
 
-The domains we evaluate in are UpWorld, Nchain, Trench, and Minefield.
-UpWorld is a contrived version of Grid World in which the agent can only move left, right, and up (where up is always optimal, thus the name).
-NChain is a classic exploration task from the Bayesian Reinforcement Learning literature.
-Trench is a highly challenging goal-based task introduced by CITE DABE.
-Lastly, the Minefield domain is similar to UpWorld, but introduces stochastic transition dynamics, .
+% Description of visuals.
 Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
+The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
+We use the graph visualization library GraphStream~\cite{graphstream}.
+In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
+The thickness of the arrow indicates how much reward is associated with that transition.
+In the ground MDPs, states are labeled with a number.
+In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
 
-% Subsection: UpWorld.
-\subsection{UpWorld}
+% Subsection: NChain.
+\subsection{NChain}
 
-The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
+NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
+
+% NChain Compression Visuals.
+\begin{figure}[h]
+\subfigure[Ground NChain]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
+\subfigure[Abstract NChain]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
+\label{fig:nchain-visual}
+\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under $\epQ$, with $\epsilon=0.5$}
+\end{figure}
+
+%% Subsection: UpWorld.
+%\subsection{UpWorld}
+%
+%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
 The agent may move left, right, and up.
@@
 During experimentation, we set $N=10$, $M=4$.
+%
+%\begin{figure}
+%\subfigure[Ground UpWorld]{
+%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
+%\subfigure[Abstract UpWorld]{
+%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
+%\label{fig:upworld-visual}
+%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
+%\end{figure}
 
-\begin{figure}
-\subfigure[Ground UpWorld]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-\subfigure[Abstract UpWorld]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-\label{fig:eps-states}
-\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
+% Subsection: Taxi
+\subsection{Taxi}
+
+Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
+The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
+The agent must seek out passengers and take them to their destination.
+We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
+As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
+
+% Taxi Compression Visuals
+\begin{figure}[h]
+\subfigure[Ground Taxi]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
+\subfigure[Abstract Taxi]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
+\label{fig:taxi-visual}
+\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under $\epQ$, with $\epsilon=0.03$}
 \end{figure}
@@
 
-% Subsection: NChain.
-\subsection{NChain}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-\begin{figure}
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:eps-states}
-\caption{Comparison of Original NChain MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-\end{figure}
-
 % Subsection: Minefield.
@@
 
-Minefield is identical to UpWorld, except the transitions and rewards are perturbed slightly.
+Minefield is a slight variant of Grid World.
+The transitions and rewards are perturbed slightly, and there is no down action.
 In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is nearly identical to UpWorld: transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states that receive $0$ reward (these are the mine states, that receive $\textsc{RMin}$).
+The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
 During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
 
+% Minefield Compression Visuals
 \begin{figure}
@@
 \includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:eps-states}
+\label{fig:minefield-visual}
 \caption{Comparison of Original Minefield MDP and Abstract MDP, under $\epQ$, with $\epsilon=1.1$}
@@
 
-% Subsection: Trench.
-\subsection{Trench}
+% Subsection: Random.
+\subsection{Random}
 
-To demonstrate the effects of approximate abstraction on goal-based tasks, we investigate the Trench problem, introduced by \dnote{Cite dabe}.
+The Random MDP domain we consider is as follows.
+There are $N$ states, and $K$ actions.
+For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
 
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Figure: The Trench Problem
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.42\columnwidth]{figures/placeholder.png}
-\caption{The Trench Problem}
-\label{fig:trench}
+% Random Compression Visuals
+\begin{figure}
+\subfigure[Ground Random]{
+\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
+\subfigure[Abstract Random]{
+\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
+\label{fig:minefield-visual}
+\caption{Comparison of Original Random MDP and Abstract Random MDP, under $\epQ$, with $\epsilon=0.2$}
 \end{figure}
-
-% Subsection: Minefield.
-\subsection{Minefield}
 
@@
 \begin{figure}
-\subfigure[UpWorld]{
-\includegraphics[width=0.28\columnwidth]{figures/upworld_epsilon_vs_num_abstract_states.png}}
+\centering
 \subfigure[NChain]{
-\includegraphics[width=0.28\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
+\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
+\subfigure[Taxi]{
+\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
 \subfigure[Minefield]{
-\includegraphics[width=0.28\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Trench]{
-\includegraphics[width=0.28\columnwidth]{figures/placeholder.png}}
+\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
+\subfigure[Random]{
+\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
 \label{fig:eps-states}
@@
 \begin{figure}
-\subfigure[UpWorld]{
-\includegraphics[width=0.28\columnwidth]{figures/upworld_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
 \subfigure[NChain]{
-\includegraphics[width=0.28\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
+\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
+\subfigure[Taxi]{
+\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
 \subfigure[Minefield]{
-\includegraphics[width=0.28\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
+\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
+\subfigure[Random]{
+\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
 \label{fig:eps-states}
 \caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% Subsection: Abstract Domain Visualizations
-\subsection{Abstract Domain Visualizations}
-
-% Figure: UpWorld MDP visuals
-\begin{figure}[h]
-\centering
-\subfigure[UpWorld]{
-\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
-\hspace{3mm}
-\subfigure[Abstracted UpWorld]{
-\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
-\caption{Visualization of Original UpWorld vs. Abstracted UpWorld}
-\end{figure}
-
-% Figure: NChain MDP visuals
-\begin{figure}[h]
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
-\hspace{3mm}
-\subfigure[Abstracted NChain ]{
-\includegraphics[width=0.46\columnwidth]{figures/placeholder.png}}
-\caption{Visualization of Original NChain vs. Abstracted NChain}
 \end{figure}

### 2016-01-30 paper/paper.tex

@@
 
-\enote{Add something about weirdness of state spaces changing at $T=1$}
+And:
+\begin{equation}
+\mathcal{T}_T(s,a,s') = \begin{cases}
+\mathcal{T}_G(s,a,s')& T \leq 0 \\
+\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
+\mathcal{T}_A(s,a,s')& \text{o/w} \\
+\end{cases}
+\end{equation}
+
+It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
+\begin{equation}
+Q_T(s, a) = 
+\begin{cases}
+	   Q_G(s, a) &  T=0\\
+	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
+	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
+\end{cases}
+\end{equation}
 

### 2016-01-30 paper/paper.tex
Fixed claim 2

@@
 &\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
+&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{0}\epsilon \gamma^t
 \end{align*}
@@
 &\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-2}(g', a')      \right]\\
+&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
 &\text{Applying our inductive hypothesis yields}\\
@@
 
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
 Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
@@
 
-By Equation \ref{eq:Q*Claim1} and the definition of $a^*_G$ and $a^*_A$ we know that 
+%Claim 2
+\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
+
+\begin{equation}
+\label{eq:Q*Claim2}
+V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
+\end{equation}
+
+By Equation \ref{eq:Q*Claim1}
 \begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \nonumber \\
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
 \label{eq:Q*OptActionResult}
-&\leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
+\end{align}
+
+ By the definition of $a^*_A$ we know that 
+ \begin{align}
+Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
+\end{align}
+
+Lastly again by Equation \ref{eq:Q*Claim1} we know
+\begin{align}
+Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
 \end{align}
@@
 Therefore, we conclude Equation \ref{eq:Q*Claim2}.
+
+%Claim 3
+\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
 

### 2016-01-30 paper/paper.tex
Lemma 1 proof all done -- needs a good formatting though

@@
 
-Consider the following policy on states in $\mathcal{S}_G$:
+Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
+
 \begin{equation}
@@
 
-Again, consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$
-
+For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
 \begin{align*}
-\text{Let }V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
+V^{\pi_{A,t}}(s_G) &= \\
+&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
 \end{align*}
-
-where $g, g' \in \mathcal{S}_G$.
 
@@
 \begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so it trivially follows that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,0}}(s_G) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
+By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
 
 \textit{Inductive case: $t > 0$}
+
+Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
 
@@
 &\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*OptActionResult} yields}\\
+&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
 &\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
@@
 
-From our base case and induction we conclude that
+Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
+
+Thus, our base case and induction we conclude that
 \begin{equation}
@@
 
-Thus we conclude,
+Thus, we conclude
 \begin{equation*}
-\forall_{g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A}^*}(g) + \frac{2\epsilon}{(1-\gamma)^2}
+\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
 \end{equation*}
@@
 \begin{equation*}
-\forall_{g \in \mathcal{S}_g} \left | V^{\pi^*}(g) - V^{\pi_{A}^*}(g) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
+\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
 \end{equation*}

### 2016-01-30 Workspace and Code/stateAbstraction/src/domains/NormalDomainToGraphDomain.java
adding minefield, experiments update

@@ -99,8 +99,18 @@ public class NormalDomainToGraphDomain {
 				Action nextAction = allActions.get(actionIndex);
 				this.graphActionIndexToNonGraphAction.put(actionIndex, nextAction);
 
+
 				
 				GroundedAction ga = nextAction.getAssociatedGroundedAction();
+				
+				
+				if (nextAction instanceof Option){
+					if (((Option) nextAction).probabilityOfTermination(allNonGraphStates.get(stateIndex), ga) == 1.0) {
+						// If this is a terminating state for the option, assume it self loops.
+						gd.setTransition(stateIndex, actionIndex, stateIndex, 1.0);
+						continue;
+					}
+				}
 				
 				if (this.oldDomainTF.isTerminal(allNonGraphStates.get(stateIndex))) {
 					terminalStates.add(stateIndex);
@@ -109,7 +119,6 @@ public class NormalDomainToGraphDomain {
 					gd.setTransition(stateIndex, actionIndex, stateIndex, 1.0);
 				}
 				else {
-					
 					List<TransitionProbability> tps = ga.getTransitions(allNonGraphStates.get(stateIndex));
 					for (TransitionProbability tp : tps) {
 						// Set non-terminal transitions.

### 2016-01-30 Workspace and Code/stateAbstraction/src/domains/minefield/MinefieldGenerator.java

@@ -1,0 +1,102 @@
+package domains.minefield;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Random;
+
+import burlap.domain.singleagent.graphdefined.GraphDefinedDomain;
+import burlap.oomdp.core.states.State;
+import burlap.oomdp.singleagent.GroundedAction;
+import burlap.oomdp.singleagent.RewardFunction;
+
+public class MinefieldGenerator {
+	
+	private static double slipProbability = 0.01;
+	
+	/**
+	 * 
+	 * @param totalNumStates
+	 * @return an n state graph MDP.
+	 */
+	public static GraphDefinedDomain getMinefield(int width, int height) {
+		GraphDefinedDomain dg = new GraphDefinedDomain(height*width);
+		
+		// Set up transitions for left/right.
+		for (int j = 0; j < height; j++){
+			for (int i = 0; i < width; i++) {
+				int currentStateIndex = i +j*width;
+
+				int leftIndex = 0;
+				if (i==0) leftIndex =  currentStateIndex;
+				else leftIndex = currentStateIndex-1;
+
+				int rightIndex = 0;
+				if (i == width-1) rightIndex = currentStateIndex;
+				else rightIndex = currentStateIndex+1;
+
+				//Set up left action.
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, leftIndex, 1.0 - slipProbability);
+				
+				//Set up right action.
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*action*/, rightIndex, 1.0 - slipProbability);
+				
+				// Set slip probs for Up:
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, leftIndex, slipProbability/2.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, rightIndex, slipProbability/2.0);
+			}
+		}
+
+		// Set up transition for up.
+		for (int j = 0; j < height-1; j++){
+			for (int i = 0; i < width; i++) {
+				int currentStateIndex = i +j*width;
+				// Set normal transition for up.
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, currentStateIndex+width, 1.0 - slipProbability);
+				
+				// Set slip for Left and Right
[…]

### 2016-01-30 Workspace and Code/stateAbstraction/src/domains/taxi/DropPassengerOffOptionMaker.java

@@ -15,29 +15,49 @@ import burlap.oomdp.core.states.State;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 
-public class GetPassengerOptionMaker {
+public class DropPassengerOffOptionMaker {
 
-	public static boolean isTaxiEmpty(State s) {
+	public static boolean isTaxiEmptyAndPassAtDest(State s) {
 		List<ObjectInstance> allPassengers = s.getObjectsOfClass(TaxiDomainGenerator.PASSENGERCLASS);
-	
+		List<ObjectInstance> allLocations = s.getObjectsOfClass(TaxiDomainGenerator.LOCATIONCLASS);
+		
 		for(ObjectInstance passenger : allPassengers) {
 			boolean inTaxi = passenger.getBooleanValForAttribute(TaxiDomainGenerator.INTAXIATT);
-			
+
 			if (inTaxi) {
 				// There's a passenger in a car.
 				return false;
 			}
+			else {
+				for (ObjectInstance dest : allLocations) {
+					Integer passengerLoc = passenger.getIntValForAttribute(TaxiDomainGenerator.LOCATIONATT);
+					Integer destLoc = dest.getIntValForAttribute(TaxiDomainGenerator.LOCATIONATT);
+					
+					if (passengerLoc == destLoc) {
+						Integer passengerX = passenger.getIntValForAttribute(TaxiDomainGenerator.XATT);
+						Integer passengerY = passenger.getIntValForAttribute(TaxiDomainGenerator.YATT);
+						
+						Integer destX = dest.getIntValForAttribute(TaxiDomainGenerator.XATT);
+						Integer destY = dest.getIntValForAttribute(TaxiDomainGenerator.YATT);
+						
+						if (passengerX == destX && passengerY == passengerX) {
+							return true;
+						}
+					}
+					
+				}
+			}
 		}
-		return true;
+		return false;
 	}
 	
-	public static Option makeGetPassengerOption(Domain domain) {
+	public static Option makeDropOffPassengerOption(Domain domain) {
 		BFS bfs = new BFS(domain, new IsTaxiFullSCT(), new SimpleHashableStateFactory());
 		bfs.toggleDebugPrinting(false);
 		Policy optionPolicy = new DDPlannerPolicy(bfs);
 		
 		//now that we have the parts of our option, instantiate it
[…]

### 2016-01-30 Workspace and Code/stateAbstraction/src/domains/taxi/TaxiDomainGenerator.java

@@ -754,10 +754,12 @@ public class TaxiDomainGenerator implements DomainGenerator {
 
 	public List<Option> getOptions(Domain domain) {
 		Option getPassengerOpt = GetPassengerOptionMaker.makeGetPassengerOption(domain);
+		Option dropOffPassengerOpt = DropPassengerOffOptionMaker.makeDropOffPassengerOption(domain);
 
 		List<Option> allOptions = new ArrayList<Option>();
 		
 		allOptions.add(getPassengerOpt);
+		allOptions.add(dropOffPassengerOpt);
 		
 		return allOptions;
 	}

### 2016-01-30 Workspace and Code/stateAbstraction/src/experiments/CreateVisuals.java

@@ -5,6 +5,7 @@ import java.util.List;
 
 import graphStateAbstractionTest.VIParams;
 import graphStreamVisualizer.GraphStreamVisualizer;
+import stateAbstractor.PhiAStar;
 import stateAbstractor.PhiSAReal;
 import stateAbstractor.StateAbstractor;
 import SARealGenerators.qValueGenerator;
@@ -23,7 +24,9 @@ import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 import domains.GraphRF;
 import domains.NormalDomainToGraphDomain;
+import domains.minefield.MinefieldGenerator;
 import domains.nchain.NChainGenerator;
+import domains.randommdp.RandomMDPGenerator;
 import domains.taxi.GetPassengerOptionMaker;
 import domains.taxi.TaxiDomainGenerator;
 import domains.trench.TrenchDomainGenerator;
@@ -56,7 +59,8 @@ public class CreateVisuals {
 		
 		// Abstract the MDP.
 		qValueGenerator qGen = new qValueGenerator(graphDomain, graphRF, initGraphState, graphTF);
-		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, graphDomain.getActions());
+//		StateAbstractor qPhi = new PhiSAReal(qGen, epsilon, graphDomain.getActions());
+		StateAbstractor qPhi = new PhiAStar(qGen, epsilon, graphDomain.getActions());
 		GraphDefinedDomain abstractDG = qPhi.abstractMDP(graphDefinedDomain, graphRF, graphTF, initGraphState);
 		RewardFunction abstractRF = qPhi.getRewardFunction();
 		Domain abstractDomain = abstractDG.generateDomain();
@@ -101,11 +105,25 @@ public class CreateVisuals {
 		compressAndVisualizeMDP(graphDefinedDomain, graphTF, graphRF, initGraphState, epsilon);
 	}
 	
+	public static void convertCompressAndVisualizeMDPOptions(DomainGenerator gen, TerminalFunction tf, RewardFunction rf, State initialState, double epsilon, List<Option> options) {
+		
+		// Convert to graph domain.
+		NormalDomainToGraphDomain graphMaker = new NormalDomainToGraphDomain(gen, tf, rf, initialState);
+		GraphDefinedDomain graphDefinedDomain = graphMaker.createGraphDomain(options);
[…]

### 2016-01-30 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -1,6 +1,7 @@
 package experiments;
 
 import graphStateAbstractionTest.AStarEpsilonTest;
+import graphStateAbstractionTest.QStarEpsilonTest;
 import graphStateAbstractionTest.VIParams;
 import graphStateAbstractionTest.EpsilonToNumStatesTuple;
 
@@ -27,6 +28,7 @@ import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 import domains.GraphRF;
 import domains.NormalDomainToGraphDomain;
+import domains.minefield.MinefieldGenerator;
 import domains.nchain.NChainGenerator;
 import domains.randommdp.RandomMDPGenerator;
 import domains.taxi.GetPassengerOptionMaker;
@@ -46,7 +48,7 @@ public class EpsilonExperiments {
 	
 	// Iterate over epsilon and compute the number of states.
 	final static double startEpsilon = 0.0;
-	final static double endEpsilon = 0.1;
+	final static double endEpsilon = 0.50;
 	final static double epsilonIncrement = 0.01;
 	
 	/**
@@ -59,8 +61,8 @@ public class EpsilonExperiments {
 	 */
 	public static void generateEpsilonResults(GraphDefinedDomain graphDefinedDomain, RewardFunction graphRF, State initGraphState, String taskName) {
 		
-//		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = QStarEpsilonTest.testQPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);
-		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = AStarEpsilonTest.testAStarPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);
+		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = QStarEpsilonTest.testQPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);
[…]

### 2016-01-30 Workspace and Code/stateAbstraction/src/graphStateAbstractionTest/QStarEpsilonTest.java

@@ -20,41 +20,6 @@ import burlap.oomdp.statehashing.HashableStateFactory;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
 
 public class QStarEpsilonTest {
-	public static class EpsilonToNumStatesTuple {
-		private double eps;
-		private int numStates;
-		private double valOfInitGroundState; // NOW STORES THE DELTA BETWEEN THE VALUE OF GROUND AND ABSTRACT
-		private double valOfInitAbstractState;
-		
-		
-		public EpsilonToNumStatesTuple(double epsilon, int numStates, double valOfInitGroundState, double valOfInitAbstractState) {
-			this.eps = epsilon;
-			this.numStates = numStates;
-			this.valOfInitGroundState = valOfInitGroundState;
-			this.valOfInitAbstractState = valOfInitAbstractState;
-		}
-		@Override
-		public String toString() {
-			return eps + "\t" + numStates + "\t" + valOfInitGroundState + "\t" + valOfInitAbstractState;
-		}
-		
-		public double getEpsilon() {
-			return this.eps;
-		}
-		
-		public int getNumStates() {
-			return this.numStates;
-		}
-		
-		public double getValOfGroundInitState() {
-			return this.valOfInitGroundState;
-		}
-		
-		public double getValOfInitAbstractState() {
-			return this.valOfInitAbstractState;
-		}
-	}
-
 
 
 	public static List<EpsilonToNumStatesTuple> testQPhiStateReduction(GraphDefinedDomain dg, RewardFunction rf, TerminalFunction tf, State initGraphState, double startEpsilon, double endEpsilon, double epsilonIncrement) {
@@ -89,7 +54,6 @@ public class QStarEpsilonTest {
 			GreedyQPolicy abstractPolicy = aVi.planFromState(aInitialState);	
 			
 			
-			
 			//Gather up values for this test iteration
 			int numAbstractStates = aVi.getAllStates().size();
 			System.out.println("Num abstract states (eps): " + numAbstractStates + " (" + epsilon + ")");
@@ -99,16 +63,13 @@ public class QStarEpsilonTest {
 			abstractPI.setPolicyToEvaluate(groundPolicyFromAbstractPolicy);
 			GreedyQPolicy pol = abstractPI.planFromState(initGraphState);
 			
-			
[…]

### 2016-01-30 Workspace and Code/stateAbstraction/src/plotting/plotter.py

@@ -110,11 +110,8 @@ def makePlot(taskName):
 	randYData = randVal*len(abstractStateVals)
 	numGroundStatesYData = numGroundStates*len(numStates)
 
-
-	print "len:", len(numStates), len(numGroundStatesYData)
-
 	# Plot.
-	plot(epsilons, [numStates, numGroundStatesYData], "Num Abstract States", taskName, yDataNames=["Num. Abstract States", "Num. GroundS tates"])
+	plot(epsilons, [numStates, numGroundStatesYData], "Num Abstract States", taskName, yDataNames=["Num. Abstract States", "Num. Ground States"])
 	plot(epsilons, [abstractStateVals, groundStateVals, randYData], "Value of Abstract Policy Init Ground State", taskName, yDataNames=["Val. Abstract Policy", "Val. Optimal Policy", "Val. Random Policy"])
 	plot(abstractStateVals, numStates, "Num States", taskName, scatter=True, xAxisLabel="Abstract Policy Value", epsilons=epsilons)
 

### 2016-01-30 paper/paper.tex
Fixed typo
Started on formalizing Phi_model but didn't get that far :/

@@
 \newcommand{\epQ}{\ep_{Q^*}}
+\newcommand{\epM}{\ep_{\text{model}}}
 \newcommand\defn[1]{{\bf Definition:} #1}
@@
 \enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
+\enote{Say more about the weighting (that is sums to 1 but that's all we assume)}
 
@@
 
-Thus, our base case and induction we conclude that
+Thus, from our base case and induction we conclude that
 \begin{equation}
@@
 
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{model}$ type:
+{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
 \begin{equation}
@@
 {\bf Proof:}
+Given the ground \ac{MDP}, $M_G$, consider the \ac{MDP}, $M_G'$ which is identical to $M_G$ except in its transition and rewards.
 
-Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B_s$.
+\begin{equation}
+M_G' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
+\end{equation}
+
+Where
+\begin{align}
+\mathcal{R}_G'(s,a) = R_A(\epM(s), a)\\
+\mathcal{T}_G'(s,a, s') = R_A(\epM(s), a, \epM(s'))
+\end{align}
+
+We know by \cite{li2006towards} that .
+
+Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B$.
 
@@
 
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
+{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
 \begin{equation}
@@
 
-{\bf Lemma 5:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
+{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
 \begin{equation}

### 2016-01-30 paper/paper.tex
First pass at setting up the homogenized MDP description for lemma 2

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
+\newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\mcS}{\mathcal{S}}
+\newcommand{\mcT}{\mathcal{T}}
+\newcommand{\mcR}{\mathcal{R}}
+\newcommand{\pM}{\phi_{\text{model}}}
 
@@
 \textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
 
@@
 \begin{equation}
+\label{eq:lemma2}
 \forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
@@
 
-{\bf Proof:}
-Given the ground \ac{MDP}, $M_G$, consider the \ac{MDP}, $M_G'$ which is identical to $M_G$ except in its transition and rewards.
+{\bf Proof:} Our proof proceeds as follows: converting a ground \ac{MDP}, $M_G$, to an abstract \ac{MDP}, $M_A$, using a fixed but arbitrary aggregation function, $\ep_m$, that satisfies the $\epM$ criteria is shown to be equivalent to creating an intermediate \ac{MDP}, ${M_G}'$ and then applying an aggregation of the $\pM$ type.
+${M_G}'$ is shown to have Q values identical to $M_A$ and Q values boundedly close to $M_G$ -- applying Lemma 1 we are able to conclude Lemma 2.
+
+\enote{Maybe introduce language of ``homogenization"}
 
 \begin{equation}
-M_G' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
+{M_G}' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
 \end{equation}
@@
 \begin{align}
-\mathcal{R}_G'(s,a) = R_A(\epM(s), a)\\
-\mathcal{T}_G'(s,a, s') = R_A(\epM(s), a, \epM(s'))
+{\mcR_G}'(s,a) = \mcR_A(\ep_m(s), a)\\
+{\mcT_G}'(s,a, s') = \frac{\mcT_A(\ep_m(s), a, \ep_m(s'))}{|X(s')|}
 \end{align}
 
-We know by \cite{li2006towards} that .
+where $X(s') = \{g \in \mathcal{S}_G | \ep_m(g) = \ep_m(s')\}$.
+
+It is easily verifiable that ${\mcT_G}'$ induces a valid probability distribution.
+
+Next note that the rewards of states in ${M_G}'$ that are aggregated in $M_A$ are identical:
+\begin{align*}
+&\forall{s1_G, s2_G \in \mc{S}_G, a} \\
+&\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcR_G}'(s1_G, a) = {\mcR_G}'(s2_G, a) \right]
+\end{align*}
+
+Similarly, the transitions of states in ${M_G}'$ that are aggregated in $M_A$ are identical:
+\begin{align*}
+\forall{s1_G, s2_G, {s_G}' \in \mcS_G, a}\\
+\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') \right]
+\end{align*}
+
+Now consider applying to $M_G$' the state aggregation scheme, $\phi_m$, which satisfies the following:
+\begin{align*}
+\forall{a, s_G \in \mcS_G}  [&{\mcR_G}'(s1_G, a) = {\mcR_G}'(s2_G, a) \wedge \\
+&{\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') ]  \rightarrow \\
+\phi_m(s1_G) = \phi_m(s2_G)
+\end{align*}
+
+$\phi_m$ is of the $\pM$ type and when applied to ${M_G}'$ results in $M_A$.
+
+ \cite{li2006towards} demonstrate that abstraction schemes of the $\pM$ type maintain Q values so we know that $\forall{s_G \in \mcS} Q_{G'}(s_G) = Q_{A}(s_G)$.
+
+Knowing that the Q values in $M_A$ are identical to those in ${M_G}'$, we now demonstrate that those of $M_G$ are boundedly close to those of ${M_G}'$ and then conclude by applying Lemma 1 (which states similar Q values in the abstract and ground MDP results in near optimal behavior of the optimal abstract policy applied to the ground MDP).
 

### 2016-01-30 paper/paper.tex
Added proof for lemma 2 but it just seems like simulation lemma

@@
 
-Inspired by the model-irrelevance abstraction, we consider the approximate case.
-We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon_\mathcal{R}$ and $\epsilon_\mathcal{T}$, satisfies:
+Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
 \begin{multline}
 \ep_{model}(s_1) = \ep_{model}(s_2) \rightarrow \\
-\forall_a \left|\mathcal{R}(s_1, a) - \mathcal{R}(s_2, a)\right| \leq \epsilon_\mathcal{R}\ \wedge\ \\
-\forall_{a,s'} \left|\mathcal{T}(s_1, a,s') - \mathcal{T}(s_2, a,s')\right| \leq \epsilon_\mathcal{T}
+\forall_a \left|\mathcal{R}(s_1, a) - \mathcal{R}(s_2, a)\right| \leq \epsilon \wedge\ \\
+\forall_{a,s'} \left|\mathcal{T}(s_1, a,s') - \mathcal{T}(s_2, a,s')\right| \leq \epsilon
 \end{multline}
@@
 \begin{equation}
-{M_G}' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
+{M_G}' =  \langle \mcS_G, \mathcal{A}, {\mcR_G}', {\mcT_G}', \gamma \rangle
 \end{equation}
@@
 \begin{align}
-{\mcR_G}'(s,a) = \mcR_A(\ep_m(s), a)\\
-{\mcT_G}'(s,a, s') = \frac{\mcT_A(\ep_m(s), a, \ep_m(s'))}{|X(s')|}
+&{\mcR_G}'(s,a) = \mcR_A(\ep_m(s), a)\\
+&{\mcT_G}'(s,a, s') = \frac{\mcT_A(\ep_m(s), a, \ep_m(s'))}{|X(s')|}
 \end{align}
@@
 where $X(s') = \{g \in \mathcal{S}_G | \ep_m(g) = \ep_m(s')\}$.
+\enote{Disambiguate this X from earlier X}
 
-It is easily verifiable that ${\mcT_G}'$ induces a valid probability distribution.
+It is easily verifiable that ${\mcT_G}'$ is a probability distribution.
 
@@
 
-Similarly, the transitions of states in ${M_G}'$ that are aggregated in $M_A$ are identical:
+The transitions of states in ${M_G}'$ that are aggregated in $M_A$ are identical :
+\begin{align}
+\forall{s1_G, s2_G, {s_G}' \in \mcS_G, a} \nonumber\\
+\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') \right] \wedge\label{eq:sameTrans}
+\end{align}
+
+Additionally, it is easily verified \enote{or not -- consider adding proof} that transitions and rewards in $M_G'$ are within $\epsilon$ of those in $M_G$:
 \begin{align*}
-\forall{s1_G, s2_G, {s_G}' \in \mcS_G, a}\\
-\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') \right]
+\forall{s,s' \in \mcS_G, a} : |\mcT_G'(s,a,s') - \mcT_G(s,a,s')| \leq \epsilon\\
+\forall{s \in \mcS_G, a} : |\mcR_G'(s,a) - \mcR_G(s,a)| \leq \epsilon
 \end{align*}
 
+\enote{If this is the case, why can't we just leverage the simulation lemma?...}
+
 Now consider applying to $M_G$' the state aggregation scheme, $\phi_m$, which satisfies the following:
-\begin{align*}
-\forall{a, s_G \in \mcS_G}  [&{\mcR_G}'(s1_G, a) = {\mcR_G}'(s2_G, a) \wedge \\
-&{\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') ]  \rightarrow \\
-\phi_m(s1_G) = \phi_m(s2_G)
-\end{align*}
+\begin{align}
+\forall{a, s_G \in \mcS_G} \left[\epM(s1_G) =\epM(s2_G) \leftrightarrow \phi_m(s1_G) = \phi_m(s2_G) \right] \label{eq:sameR}
+\end{align}
 
@@
 
- \cite{li2006towards} demonstrate that abstraction schemes of the $\pM$ type maintain Q values so we know that $\forall{s_G \in \mcS} Q_{G'}(s_G) = Q_{A}(s_G)$.
+ \cite{li2006towards} demonstrate that abstraction schemes of the $\pM$ type maintain Q values so we know that $\forall{s_G \in \mcS_G}  \left[ Q_{G'}(s_G) = Q_{A}(\epM(s_G)) \right]$ where $Q_{G'}$ is the Q function in ${M_G}'$ and $Q_G$
 
-Knowing that the Q values in $M_A$ are identical to those in ${M_G}'$, we now demonstrate that those of $M_G$ are boundedly close to those of ${M_G}'$ and then conclude by applying Lemma 1 (which states similar Q values in the abstract and ground MDP results in near optimal behavior of the optimal abstract policy applied to the ground MDP).
+Knowing that the Q values in $M_A$ are identical to those in ${M_G}'$, we now demonstrate that those of $M_G$ are boundedly close to those of ${M_G}'$.
 
-Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B$.
+For the remainder of the proof, $s, s' \in \mcS_G$.
 
+Let the maximum Q difference in ${M_G}'$ and $M_G$ be $B$:
 \begin{align*}
-B_{s} &= \max_{s,a}|Q'(s,a)-Q(s,a)|\\
+B = &\max_{s,a}|Q_{G'}(s,a)-Q_{G}(s,a)|\\
 %B_{s} &= \max_{s,a}|R'(s,a) - R(s,a) + \gamma \sum_{s'}\left[T'(s,a,s')\max_{a'}Q'(s',a')-T(s,a,s')\max_{a'}Q(s', a')\right]|\\
-&\forall s' \text{ WLOG } T'(s,a,s')\max_{a'}Q'(s',a') \geq T(s,a,s')\max_{a'}Q(s',a')\\
-\end{align*}
-Applying max is a non-expansion \enote{Probably want a citation and or explanation for this}:
-\begin{multline}
-=\max_{s,a}(|R'(s,a)-R(s,a)| + \gamma \sum_{s'} \\
-\max_{a'} [(T(s,a,s')+T'(s,a,s')- \\ T(s,a,s'))Q'(s', a')-T(s,a,s')Q(s',a')])
-\end{multline}
-%&\leq \max_{s,a}|R'_s-R_s|+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')+\epsilon_{\mathcal{T}})Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
-%&\leq \epsilon_{\mathcal{R}}+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')Q'(s',a')+\epsilon_{\mathcal{T}}Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
-%&\leq \epsilon_{\mathcal{R}} + \max_{s,a} \gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')(Q'(s',a')-Q(s',a'))+\epsilon_{\mathcal{T}}Q'(s',a') \right]\\
-\begin{align*}
-&\leq \epsilon_{\mathcal{R}}+\gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{\text{max}} + \gamma \sum_{s'}\left[ T(s,a,s') B_s\right]\\
-&\leq \epsilon_{\mathcal{R}} + \gamma B_{s} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{max}
+&\text{Applying the definition of Q values:}\\
+%---Write out using Q definitions
+B \leq &\max_{s,a} |\mcR_G'(s,a)-\mcR(s,a) +  \gamma \sum_{s'} \\
+&\left[ \mcT_G'(s, a, s')\max_{a'}Q_G'(s', a') - \mcT_G(s, a, s')\max_{a'}Q_G(s', a')\right] |\\
+%---Apply WLOG
+& \text{ WLOG }T'(s,a,s')\max_{a'}Q'(s',a') \geq T(s,a,s')\max_{a'}Q(s',a')\\
+\leq &\max_{s,a}(|\mcR_G'(s,a)-\mcR(s,a)| + \gamma \sum_{s'} \\
+&\max_{a'} [(\mcT_G'(s,a,s'))Q_G'(s', a')-\mcT_G(s,a,s')Q_G(s',a')])\\
+%---Apply epsilon to reward and transitions
+\leq & \epsilon +\\
+& \gamma \sum_{s'}  \max_{a'} [(\epsilon+ \mcT_G(s,a,s'))Q_G'(s', a')-\mcT_G(s,a,s')Q_G(s',a')])\\
+%---Do algebra
+= & \epsilon +\\
+&\gamma \sum_{s'}  \max_{a'} [\epsilon Q_G'(s', a')+ \mcT_G(s,a,s')(Q_G'(s', a') - Q_G(s', a'))])
+%---Pull terms out of some
+&\leq \epsilon+\gamma |\mcS|\epsilon Q'_{\text{max}} + \gamma \sum_{s'}\left[ \mcT(s,a,s') B\right]\\
+&\leq \epsilon + \gamma B + \gamma |\mcS|\epsilon Q'_{max}
 \end{align*}
@@
 \begin{align*}
-B_{s} &\leq 
+B &\leq 
 \frac
-{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}
+{ \gamma |\mathcal{S} + 1 |\epsilon}
 {(1-\gamma)^2}
@@
 \begin{align*}
-\forall_{s,a} : |Q'(s,a) - Q(s,a)| &\leq \max_{s,a}|Q'(s,a)-Q(s,a)| \\
-&\leq  \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}} }{(1-\gamma)^2}
+\forall_{s,a} : &|Q_A(s,a) - Q_G(s,a)| = |Q_G'(s,a) - Q_G(s,a)| \\
+&\leq \max_{s,a}|Q_G'(s,a)-Q_G(s,a)| \\
+&\leq  \frac{\gamma |\mathcal{S} + 1|\epsilon}{(1-\gamma)^2}
 \end{align*}
 
-Consequently, from the below $\phi_Q^*$ results, we conclude that:
+Consequently, by the logic of the proof for Lemma 1, we conclude that:
 \begin{equation}
-\forall_s : |V^{\pi^*_M}(s) - V^{\pi^*_{M'}}(s)| \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
+\forall_s : |V^{\pi^*_M}(s) - V^{\pi^*_{A}}(s)| \leq
+\frac{2\gamma|\mcS + 1|\epsilon}{(1-\gamma)^3}
 \end{equation}

### 2016-01-31 paper/paper.tex
Lemma 2 presentation and proof now fully written up -- fixed it to actually match Lihong

--- 2016-01-30 paper/paper.tex
@@
 
-Inspired by the model-irrelevance abstraction, we consider the approximate case.
-We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon_\mathcal{R}$ and $\epsilon_\mathcal{T}$, satisfies:
+Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
 \begin{multline}
-\ep_{model}(s_1) = \ep_{model}(s_2) \rightarrow \\
-\forall_a \left|\mathcal{R}(s_1, a) - \mathcal{R}(s_2, a)\right| \leq \epsilon_\mathcal{R}\ \wedge\ \\
-\forall_{a,s'} \left|\mathcal{T}(s_1, a,s') - \mathcal{T}(s_2, a,s')\right| \leq \epsilon_\mathcal{T}
+\epM(s_1) = \epM(s_2) \rightarrow \\
+\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
+\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
 \end{multline}
+where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
+
+\enote{Do we want to make it clear that this is ground transitions and rewards?}
+
+\enote{Note that it is possible }
 
@@
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
+\label{eq:lemma2}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma(|\mcS-1|\epsilon)}{(1-\gamma)^3}
 \end{equation}
 
-{\bf Proof:}
-Given the ground \ac{MDP}, $M_G$, consider the \ac{MDP}, $M_G'$ which is identical to $M_G$ except in its transition and rewards.
+{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
+Consequently $\epM$ abstractions are interpretable as an instantiation of of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
 
-\begin{equation}
-M_G' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
-\end{equation}
-
-Where
-\begin{align}
-\mathcal{R}_G'(s,a) = R_A(\epM(s), a)\\
-\mathcal{T}_G'(s,a, s') = R_A(\epM(s), a, \epM(s'))
-\end{align}
-
-We know by \cite{li2006towards} that .
-
-Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B$.
+Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
 
 \begin{align*}
-B_{s} &= \max_{s,a}|Q'(s,a)-Q(s,a)|\\
-%B_{s} &= \max_{s,a}|R'(s,a) - R(s,a) + \gamma \sum_{s'}\left[T'(s,a,s')\max_{a'}Q'(s',a')-T(s,a,s')\max_{a'}Q(s', a')\right]|\\
-&\forall s' \text{ WLOG } T'(s,a,s')\max_{a'}Q'(s',a') \geq T(s,a,s')\max_{a'}Q(s',a')\\
-\end{align*}
-Applying max is a non-expansion \enote{Probably want a citation and or explanation for this}:
-\begin{multline}
-=\max_{s,a}(|R'(s,a)-R(s,a)| + \gamma \sum_{s'} \\
-\max_{a'} [(T(s,a,s')+T'(s,a,s')- \\ T(s,a,s'))Q'(s', a')-T(s,a,s')Q(s',a')])
-\end{multline}
-%&\leq \max_{s,a}|R'_s-R_s|+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')+\epsilon_{\mathcal{T}})Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
-%&\leq \epsilon_{\mathcal{R}}+\max_{s,a}\gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')Q'(s',a')+\epsilon_{\mathcal{T}}Q'(s',a') - T(s,a,s')Q(s',a')\right]\\
-%&\leq \epsilon_{\mathcal{R}} + \max_{s,a} \gamma \sum_{s'} \max_{a'} \left[(T(s,a,s')(Q'(s',a')-Q(s',a'))+\epsilon_{\mathcal{T}}Q'(s',a') \right]\\
-\begin{align*}
-&\leq \epsilon_{\mathcal{R}}+\gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{\text{max}} + \gamma \sum_{s'}\left[ T(s,a,s') B_s\right]\\
-&\leq \epsilon_{\mathcal{R}} + \gamma B_{s} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}Q'_{max}
+B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
+=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
+& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
+&\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in \mcS_G}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
+&\text{By the similarity of transitions of grouped states under $\epM$:}\\
+& \leq \epsilon + \gamma \sum_{s_A \in \mcS_A} \epsilon Q_{max} \\
+&\leq \epsilon + \gamma|\mcS|\epsilon Q_{max}\\
+&\text{Applying 0-1 reward normalization and algebra:}\\
+& \leq \frac{\epsilon + \gamma(|\mcS| - 1) \epsilon}{1-\gamma}
 \end{align*}
 
-Applying $Q'_{max}=V'_{max} \leq V_{max}=\frac{1}{1-\gamma}$:
-\begin{align*}
-B_{s} &\leq 
-\frac
-{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}
-{(1-\gamma)^2}
-\end{align*}
-
-Therefore:
-\begin{align*}
-\forall_{s,a} : |Q'(s,a) - Q(s,a)| &\leq \max_{s,a}|Q'(s,a)-Q(s,a)| \\
-&\leq  \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}} }{(1-\gamma)^2}
-\end{align*}
-
-Consequently, from the below $\phi_Q^*$ results, we conclude that:
-\begin{equation}
-\forall_s : |V^{\pi^*_M}(s) - V^{\pi^*_{M'}}(s)| \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
-\end{equation}
+Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+Applying Lemma 1, this yields Equation \ref{eq:lemma2}.
 
@@
 
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).
+We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
 
@@
 
-To demonstrate the efficacy of these approximate abstraction functions, we test out functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
+To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
 We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.

### 2016-01-31 paper/paper.tex
Cleaned up phi model proof

@@
 Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
-This work characterizes what is ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
+This work characterizes what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
 
@@
 \label{eq:lemma2}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma(|\mcS-1|\epsilon)}{(1-\gamma)^3}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
 \end{equation}
@@
 {\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
+Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
 
@@
 & \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-&\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in \mcS_G}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
+\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
 &\text{By the similarity of transitions of grouped states under $\epM$:}\\
-& \leq \epsilon + \gamma \sum_{s_A \in \mcS_A} \epsilon Q_{max} \\
-&\leq \epsilon + \gamma|\mcS|\epsilon Q_{max}\\
+ \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
+\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
 &\text{Applying 0-1 reward normalization and algebra:}\\
-& \leq \frac{\epsilon + \gamma(|\mcS| - 1) \epsilon}{1-\gamma}
+ \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
 \end{align*}
 
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
-Applying Lemma 1, this yields Equation \ref{eq:lemma2}.
+Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
 
@@
 \label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under $\epQ$, with $\epsilon=0.5$}
+\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
 \end{figure}
@@
 \label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under $\epQ$, with $\epsilon=0.03$}
+\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
 \end{figure}
@@
 \label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under $\epQ$, with $\epsilon=1.1$}
+\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
 \end{figure}
@@
 \label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under $\epQ$, with $\epsilon=0.2$}
+\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
 \end{figure}

### 2016-01-31 paper/paper.tex
Random push
results outline, taxi plots with different epsilon range

@@
 
+\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
+
 To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
@@
 In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
+
+\dnote{One thing we want to add is a description of how diverse these domains are!}
+\dnote{Also put in a note that we're using a uniform weighting scheme}
 
@@
 
+Here we discuss the results shown in states blah blah \dnote{Description of this section}.
+
+\begin{itemize}
+\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
+Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
+This hits the learnable point.
+\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
+\item Possibly talk about stochasticity (low priority)
+\item Explain Random behavior, smooth interpolation, mention randomness, etc.
+\item Describe plots a bit (what is the y-axis?)
+\end{itemize}
+
 % Figure: Epsilon vs. #States for all three sample domains.

### 2016-02-01 Workspace and Code/stateAbstraction/bin/plotting/plotter.py
Added support for plotting with confidence intervals

@@ -7,10 +7,13 @@
 import matplotlib.pyplot as plt
 import matplotlib
 import numpy as np
+import pylab
 import sys
 import os
 from os import listdir
 from os.path import isdir, join
+
+_markers = ['v','^','s']
 
 def loadFile(taskName):
 
@@ -27,40 +30,61 @@ def parseResultsFile(resultsFile):
 	numStates = []
 	groundStateVals = []
 	abstractStateVals = []
+	rand = []
+	numGroundStates = []
 
 	for line in file(resultsFile,"r").readlines():
 		results = line.split("\t") # Tab separated result file.
+
+		if "RAND" in results:
+			# Add rand if it's in there.
+			rand.append(float(results[1]))
+			continue
+		if "NUMGROUNDSTATES" in results:
+			numGroundStates.append(int(results[1]))
+			continue
+
 		epsilons.append(float(results[0]))
 		numStates.append(int(results[1]))
 		groundStateVals.append(float(results[2]))
 		abstractStateVals.append(float(results[3]))
 
-	return epsilons, numStates, groundStateVals, abstractStateVals
+	return numGroundStates, rand, epsilons, numStates, groundStateVals, abstractStateVals
 
-def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon", epsilons=[]):
+def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon", epsilons=[], yDataNames=[]):
 	
 	if scatter:
 		# Scatter plot.
-		
-
 		for i in xrange(len(xData)):
-			plt.scatter(xData[i], yData[i], s=(epsilons[i]**2+1)*20, alpha=0.5)
+			plt.scatter(xData[i], yData[i], s=(epsilons[i]*200)/max(epsilons), alpha=0.5)
+	elif type(yData[0]) == list:
 
-		
+		for i, yDatum in enumerate(yData):
+			if len(yDataNames) >= i:
+				legendInfo = yDataNames[i]
+			else:
+				legendInfo = ""
+			plt.plot(xData, yDatum, "-", marker=_markers[i], markersize=10, label=legendInfo)
+
+		plt.xlim([min(0,min(xData)), max(xData)])
+		plt.ylim([0, max([max(y) for y in yData]) *1.2])
+
 	else: 
 		# Line plot.
-		plt.plot(xData, yData, marker="o", color="black")
[…]

### 2016-02-01 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -42,15 +42,17 @@ import domains.upworld.UpWorldGenerator;
  *
  */
 public class EpsilonExperiments {
-	
+
 	static String filePath = new File("").getAbsolutePath();
 	static String resultsDir = filePath + "/src/plotting/";
-	
+
 	// Iterate over epsilon and compute the number of states.
 	final static double startEpsilon = 0.0;
 	final static double endEpsilon = 0.50;
-	final static double epsilonIncrement = 0.01;
-	
+	final static double epsilonIncrement = 0.05;
+	final static int numTrials = 10;
+	final static String task = "RANDOM"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.
 	 * @param domainName
@@ -60,47 +62,54 @@ public class EpsilonExperiments {
 	 * @param initialState
 	 */
 	public static void generateEpsilonResults(GraphDefinedDomain graphDefinedDomain, RewardFunction graphRF, State initGraphState, String taskName) {
-		
-		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = QStarEpsilonTest.testQPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);
-//		List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = AStarEpsilonTest.testAStarPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);
-		
-		List<Double> epsilons = new ArrayList<Double>();
-		List<Integer> numStates = new ArrayList<Integer>();
-		
 		clearOldResultsFile(taskName);
-		
-		Double randomPolValue = computeValueOfRandomPolicy(graphDefinedDomain, graphRF, initGraphState);
-		
-		int numOriginalStates = graphDefinedDomain.getNumNodes();
-		
-		System.out.println("NUMGROUNDSTATES\t" + numOriginalStates);
-		System.out.println("RAND\t" + randomPolValue);
-		
-		writeDataPointToFile("NUMGROUNDSTATES\t" + numOriginalStates, taskName);
[…]

### 2016-02-01 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java
Slight tweaks for epsilon experiments -- can now specify if you want to clear the old data

@@ -47,11 +47,12 @@ public class EpsilonExperiments {
 	static String resultsDir = filePath + "/src/plotting/";
 
 	// Iterate over epsilon and compute the number of states.
-	final static double startEpsilon = 0.0;
-	final static double endEpsilon = 0.50;
-	final static double epsilonIncrement = 0.05;
-	final static int numTrials = 10;
-	final static String task = "RANDOM"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+	final static double startEpsilon = 0.027;
+	final static double endEpsilon = 0.033;
+	final static double epsilonIncrement = 0.001;
+	final static int numTrials = 15;
+	final static String task = "TAXI"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+	final static boolean clearOldResults = false;
 
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.
@@ -62,8 +63,10 @@ public class EpsilonExperiments {
 	 * @param initialState
 	 */
 	public static void generateEpsilonResults(GraphDefinedDomain graphDefinedDomain, RewardFunction graphRF, State initGraphState, String taskName) {
-		clearOldResultsFile(taskName);
-		for (int trialIndex = 0; trialIndex < numTrials; trialIndex++) {
+		if (clearOldResults) {
+			clearOldResultsFile(taskName);
+		}
+		for (int trialIndex = 1; trialIndex <= numTrials; trialIndex++) {
 			System.out.println("---Trial: " + trialIndex + "---");
 
 			List<EpsilonToNumStatesTuple> epsilonAndNumStatesPairs = QStarEpsilonTest.testQPhiStateReduction(graphDefinedDomain, graphRF, new NullTermination(), initGraphState, startEpsilon, endEpsilon, epsilonIncrement);

### 2016-02-01 Workspace and Code/stateAbstraction/bin/plotting/plotter.py
prepping for merge

@@ -1,106 +1,0 @@
-# ===================================================================
-# =========== Authors: David Abel and D Ellis Hershkowits ===========
-# == Summary: Plotting tool for Approximate State Abstraction work ==
-# ===================================================================
-
-# Python imports.
-import matplotlib.pyplot as plt
-import matplotlib
-import numpy as np
-import sys
-import os
-from os import listdir
-from os.path import isdir, join
-
-def loadFile(taskName):
-
-	resultsFile = taskName + "/" + taskName + ".results"
-	
-	if not os.path.isfile(resultsFile):
-		print "Error: file '" + resultsFile + "' not found."
-		quit()
-
-	return resultsFile
-
-def parseResultsFile(resultsFile):
-	epsilons = []
-	numStates = []
-	groundStateVals = []
-	abstractStateVals = []
-
-	for line in file(resultsFile,"r").readlines():
-		results = line.split("\t") # Tab separated result file.
-		epsilons.append(float(results[0]))
-		numStates.append(int(results[1]))
-		groundStateVals.append(float(results[2]))
-		abstractStateVals.append(float(results[3]))
-
-	return epsilons, numStates, groundStateVals, abstractStateVals
-
-def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon", epsilons=[]):
-	
-	if scatter:
-		# Scatter plot.
-		
-
-		for i in xrange(len(xData)):
-			plt.scatter(xData[i], yData[i], s=(epsilons[i]**2+1)*20, alpha=0.5)
-
-		
-	else: 
-		# Line plot.
-		plt.plot(xData, yData, marker="o", color="black")
-
-	font = {'family' : 'normal',
-	        'size'   : 15}
-
-	matplotlib.rc('font', **font)
-	plt.xlim([min(0,min(xData)), max(xData)])
-	plt.ylim([0, max(yData) + 5.0])
-	plt.xlabel(xAxisLabel)
-	plt.ylabel(yAxisLabel)
-	plt.title(taskName[0].upper() + taskName[1:] + ': ' + xAxisLabel + ' vs. ' + yAxisLabel)
-	plt.grid(True)
-	plt.savefig(taskName.lower() + '/' + xAxisLabel.lower() + '_vs_' + yAxisLabel.lower().replace(" ", "_") + '.png')
-	plt.clf()
-	# plt.show()
-	
-
-def makeAllPlots():
[…]

### 2016-02-01 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -48,8 +48,8 @@ public class EpsilonExperiments {
 	
 	// Iterate over epsilon and compute the number of states.
 	final static double startEpsilon = 0.0;
-	final static double endEpsilon = 0.50;
-	final static double epsilonIncrement = 0.01;
+	final static double endEpsilon = 0.05;
+	final static double epsilonIncrement = 0.001;
 	
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.
@@ -201,7 +201,7 @@ public class EpsilonExperiments {
 		State initialMinefieldState = GraphDefinedDomain.getState(minefieldDomain, 0);
 		RewardFunction minefieldRF = new MinefieldGenerator.MinefieldRF(numMineStates, minefieldHeight * minefieldWidth);
 		
-		String task = "RANDOM"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+		String task = "TAXI"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
 		
 		if (task == "ALL") {
 			generateEpsilonResults(nChainGen, nChainRF, initialNChainState, "nchain");

### 2016-02-01 Workspace and Code/stateAbstraction/src/plotting/plotter.py

@@ -85,7 +85,7 @@ def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon"
 	plt.title(taskName[0].upper() + taskName[1:] + ': ' + xAxisLabel + ' vs. ' + yAxisLabel)
 	plt.grid(True)
 	plt.legend()
-	plt.savefig(taskName.lower() + '/' + xAxisLabel.lower() + '_vs_' + yAxisLabel.lower().replace(" ", "_") + '.png')
+	plt.savefig(taskName.lower() + '/' + xAxisLabel.lower() + '_vs_' + yAxisLabel.lower().replace(" ", "_") + '.pdf', format="pdf")
 	plt.clf()
 	# plt.show()
 	

### 2016-02-01 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java
Plotter will now allow you to plot trials with different epsilons. Will also label each data point for which there were multiple trials with the number of trials it ran for.

@@ -47,12 +47,12 @@ public class EpsilonExperiments {
 	static String resultsDir = filePath + "/src/plotting/";
 
 	// Iterate over epsilon and compute the number of states.
-	final static double startEpsilon = 0.027;
-	final static double endEpsilon = 0.033;
+	final static double startEpsilon = 0.028;
+	final static double endEpsilon = 0.03;
 	final static double epsilonIncrement = 0.001;
-	final static int numTrials = 15;
-	final static String task = "TAXI"; // NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
-	final static boolean clearOldResults = false;
+	final static int numTrials = 5;
+	final static String task = "TAXI"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+	final static boolean clearOldResults = false; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
 
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.

### 2016-02-01 Workspace and Code/stateAbstraction/src/plotting/plotter.py

@@ -12,10 +12,12 @@ import sys
 import os
 from os import listdir
 from os.path import isdir, join
+from collections import defaultdict
 import numpy as np
 import scipy as sp
 import scipy.stats as stats
 import math
+from math import log10, floor
 
 _markers = ['v','^','s']
 
@@ -99,33 +101,46 @@ def plot(xData, yData, yAxisLabel, taskName, scatter=False, xAxisLabel="Epsilon"
 	plt.clf()
 	# plt.show()
 	
+
 def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidence=.95, xAxisLabel="Epsilon", yDataNames=[]):
 	
 	maxY = -99999
 
+
 	for yDataIndex, yData in enumerate(allYData):
-		means = []
-		errors = []
-		#Setup legend names
+
+		#Grab legend name
 		legendInfo = ""
 		if len(yDataNames) > yDataIndex:
 			legendInfo = yDataNames[yDataIndex]
 
-		#Plot CIs if there is data for multiple trials
-		if (type(yData[0]) == list):
+		#If Y data is a constant, convert it to a list
+		if (not type(yData) == list):
+			maxY = max(maxY, yData)
+			plt.plot(xData, [yData]*len(xData), label=legendInfo, marker="o", markersize=10)
+		#If a list of constants plot as a line
+		elif(not type(yData[0]) == list):
+			maxY = max(maxY, max(yData))
+			plt.plot(xData, yData, label=legendInfo, marker="o", markersize=10)
+		#If a list of lists, plot CIs if there is data for multiple trials
+		elif (type(yData[0]) == list):
+			means = []
+			errors = []
+			numTrials = []
 			for yDataAcrossTrials in yData:
-				mean, plusminus = mean_confidence_interval(yDataAcrossTrials, confidence)
+				mean, plusminus, numTrial = mean_confidence_interval(yDataAcrossTrials, confidence)
 				if math.isnan(plusminus):
 					errors.append(0)
 				else:
 					errors.append(plusminus)
 				means.append(mean)
+				numTrials.append(numTrial)
 			maxY = max(maxY, max(means))
 			plt.errorbar(xData, means, yerr=errors, label=legendInfo)
-		#Otherwise just plot it without
-		else:
-			maxY = max(maxY, max(yData))
[…]

### 2016-02-01 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java
Cleaned up plotting code

@@ -47,10 +47,10 @@ public class EpsilonExperiments {
 	static String resultsDir = filePath + "/src/plotting/";
 
 	// Iterate over epsilon and compute the number of states.
-	final static double startEpsilon = 0.028;
+	final static double startEpsilon = 0.029;
 	final static double endEpsilon = 0.03;
-	final static double epsilonIncrement = 0.001;
-	final static int numTrials = 5;
+	final static double epsilonIncrement = 0.0005;
+	final static int numTrials = 10;
 	final static String task = "TAXI"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
 	final static boolean clearOldResults = false; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
 

### 2016-02-01 Workspace and Code/stateAbstraction/src/plotting/plotter.py

@@ -160,8 +160,8 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 	plt.grid(True)
 	plt.legend()
 	plt.savefig(taskName.lower() + '/' + xAxisLabel.lower() + '_vs_' + yAxisLabel.lower().replace(" ", "_") + '.png')
-	# plt.clf()
-	plt.show()
+	plt.clf()
+	# plt.show()
 
 
 def mean_confidence_interval(data, confidence):
@@ -176,12 +176,11 @@ def makeAllPlots():
 	for taskName in allLocalDirs:
 		makePlot(taskName)
 
-def round_sig(x, sig=4):
+def round_sig(x, sig=5):
 	return round(x, sig-int(floor(log10(x)))-1)
 
 
 def combineTrialData(trialToDataHM, yDataIndex, xDataIndex):
-	# print "trialToDataHM:", trialToDataHM
 	xToListOfYData = defaultdict(list)
 	#Create HM from x values to list of y values across trials
 	for trialIndex, trialData in trialToDataHM.iteritems():
@@ -214,8 +213,6 @@ def makePlot(taskName):
 
 	numAbstractStatesEpsilons, numAbstractStates = combineTrialData(trialIndexToData, 3, 2)
 	abstratStateValEpsilons, abstractStateVals = combineTrialData(trialIndexToData, 5, 2)
-
-	print "numAbstractStatesEpsilons:", numAbstractStatesEpsilons
 
 	# Plot with CIs.
 	plotWithConfidenceIntervals(numAbstractStatesEpsilons, [numAbstractStates, numGroundStates],"Num Abstract States", taskName, yDataNames=["Num. Abstract States", "Num. Ground States"])

### 2016-02-01 Workspace and Code/stateAbstraction/src/plotting/plotter.py
Fixed plotter runtime warnings

@@ -129,10 +129,7 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 			numTrials = []
 			for yDataAcrossTrials in yData:
 				mean, plusminus, numTrial = mean_confidence_interval(yDataAcrossTrials, confidence)
-				if math.isnan(plusminus):
-					errors.append(0)
-				else:
-					errors.append(plusminus)
+				errors.append(plusminus)
 				means.append(mean)
 				numTrials.append(numTrial)
 			maxY = max(maxY, max(means))
@@ -166,6 +163,11 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 
 def mean_confidence_interval(data, confidence):
 	mean, sigma = np.mean(data), np.std(data)
+	#If all same element return 0 for interval
+	if len(set(data)) <= 1:
+		return mean, 0, len(data)
+
+	#Otherwise calculate bounds
 	lowerMean, upperMean = stats.norm.interval(confidence, loc=mean, scale=sigma/math.sqrt(len(data)))
 
 	return mean, mean-lowerMean, len(data)

### 2016-02-01 Workspace and Code/stateAbstraction/src/plotting/plotter.py
Pushed out x axis so CIs visibile for last datapoint

@@ -140,7 +140,7 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 				plt.annotate(numTrials[i], xy=(x, y))
 
 	#Set x axis limits	
-	plt.xlim([min(0,min(xData)), max(xData)])
+	plt.xlim([min(0,min(xData)), max(xData)*1.01])
 
 	#Set y axis limits
 	plt.ylim([0,maxY *1.2])

### 2016-02-01 paper/paper.tex
Added Michael's edits of first half of paper -- zzz comments still need to be addressed.

@@
 
-\icmltitlerunning{Approximate State Abstraction}
+\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
 
@@
 \twocolumn[
-\icmltitle{Approximate State Abstraction}
+\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
 
@@
 \begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be overcome using abstraction.
+The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
 For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compressing while preserving near optimal behavior.
-\acp{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
+In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
+\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
 We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of tasks, as well as the tradeoff between approximation magnitude and optimality of behavior.
+Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
 \end{abstract}
@@
 Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}.
-Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
-This work characterizes what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
+However, in natural environments, no two states are identical.
+This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
 
 % Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{littman1995complexity,papadimitriou1987complexity}.
+Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
 Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, polynomial behavior in state space size often translates to intractability for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
+Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
+\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
 
 % Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction in order to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
 These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
+Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
 However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
@@
 % Approximate abstraction
-In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
+In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
 Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
+First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
+Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
 
@@
 We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing approaches in state abstraction as applied to sequential decision making.
+We then survey existing types in state abstraction as applied to sequential decision making.
 The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss our experimentation, in which we apply one class of approximate abstraction to a variety of different tasks, visualizing their abstraction and showing the relationship between degrees of compression and error incurred.
+We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
 
@@
 
+First, some background.
+
 %MDP/SDM Background and Notation
 \subsection{\acp{MDP} and Sequential Decision Making}
-A \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers immediate rewards over future rewards.
+An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
 We assume without loss of generality that all reward functions are normalized to $[0,1]$.
@@
 This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V(s)^\pi$.
+We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
 We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$ respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto}
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
+\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
 
@@
 \subsection{Abstraction Notation}
-We build upon the notation used by \cite{li2006towards} \enote{This should probably say more}.
+We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
 
-We understand an abstraction as a mapping from a ground MDP $M_G$ to an abstract MDP $M_A$ using a state aggregation scheme.
+We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
 $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
@@
 % States
-The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground MDP to a state in the abstract MDP.
+The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
+More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
 \begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}
+\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
 \end{equation}
@@
 % Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the abstract state:
+The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
 \begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) 
+\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
 \end{equation}
+% zzz g in phi(s) seems like a type error, no?
 
 % Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the abstract state:
+The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
 \begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g) 
+\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
 \end{equation}
-For:
-\begin{equation}
+\noindent where $
 s, s' \in \mathcal{S}_A
-\end{equation}
+$.
 
-% Abstract policy using in ground.
-In general we are interested in how policies defined over the abstract MDP perform in the ground MDP.
-To leverage a policy defined in the abstract in the ground, we map a ground state into the abstract state space, and query the abstract policy for behavior.
+% Abstract policy in ground.
+In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
+To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
 Specifically:
 \begin{equation}
-\pi_A(s) = \pi_A(\phi(s)),\ s \in \mathcal{S}_G
-\end{equation}
-
-We evaluate the value of the abstract policy in the ground MDP by following the abstract policy:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(a)) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(a),s')V^{\pi_A}(s')
+V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
 \end{equation}
@@
 \enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that is sums to 1 but that's all we assume)}
+\enote{Say more about the weighting (that it sums to 1 but that's all we assume)}
 
@@
 
-\citep{li2006towards} develop a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here we survey their main results that we extend to the framework of approximate abstraction.
+\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
+Here, we survey their main results, which we then extend to the framework of approximate abstraction.
 
-In particular, they define the following five classes of state abstractors, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those which we build upon directly (see their paper for full details).
+In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
+For brevity, we include those that we build upon directly.
+(See their paper for full details.)
 
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is such that:
+\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
 \begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \longrightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right)
+\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
 \end{equation}
@@
 
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is such that:
+\defn{A model-irrelevance abstraction, $\phi_{model}$, is one such that:
 \begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a) \\
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
 \end{multline}
-And:
+and
 \begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s') \\
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
 \end{multline}
@@
 
+In words, zzz.
+
 % --- SECTION: Related Work ---
 \section{Related Work}
+
+Several other projects have addressed similar topics.
 
@@
 \subsection{Approximate State Abstraction}
-\citep{dean1997model} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
 They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
@@
 Several approaches build on the notion of $\epsilon$-homogeneity.
-~\citep{even2003approximate} analyze different distant metrics used in the process of identifying $\epsilon$-homogenous partitions.
-~\cite{ortner2013adaptive} develops an algorithm for learning partitions in an on line setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
+\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
+\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
 
@@
 Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citep{andre2002state} investigates a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstraction that maintains optimality.
-~\cite{dietterich2000hierarchical} develops the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy.
-\citep{jong2005state} introduce a method called {\it policy-irrelevance}, in which agents identify (online) which state variables may be safely ignored in a factored MDP, and consequently achieve state abstraction.
-The agent will learn to ignore state variables that don't impact optimal behavior, and is consequently contained within the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in recent reinforcement learning literature, see~\cite{li2006towards}.
+\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
+Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
+\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
+\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
+The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
+For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
 
@@
 % Intro to approx state abstraction results.
-Here we introduce our formal method for approximate state abstraction, and the related results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, Model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann disibtruions, induce abstract MDPs for which the optimal policy has bounded error in the ground MDP.
+Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
+In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
 
@@
 \begin{itemize}
-\item First, we relate the values of states in the ground MDP to value of the states in the Abstract MDP
-\item Then, we relate the value of states in the ground MDP to value of the states in the Abstract MDP under the optimal abstract policy.
+\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
+\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
 \end{itemize}
+
+% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
 
@@
 
-{\bf $\ep_f$ definition:} Given a function $f : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state abstraction function which satisfies the following for any two ground states $s_1$ and $s_2$:
+{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}
@@
 
-That is, when $\phi_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that for any $f$, there are many such functions that satisfy this criteria.
+That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
+Note that, for any $f$, there are many functions that satisfy this criterion.
 
@@
 % Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP, applied to the ground MDP, has error bounded polynomially in $\epsilon$:
+{\bf Theorem 1:} There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon)
+\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
 \end{equation}
@@
 \enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
+% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
 
@@
 Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-Inspired by the $Q^*$ irrelevance abstraction, we consider the approximate case.
-By Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
-
+We consider an approximate version of the $Q^*$-irrelevance abstraction.
+An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
 \begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon
+\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
 \end{equation}
 
-{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
+% zzz wy not \begin{lemma} ? you know, to get the number right automatically?
+{\bf Lemma 1:} When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
 \begin{equation}
-\forall_{s \in S_M} : | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}
+\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
 \end{equation}
@@
 \textbf{Proof:}
+We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
 
-Let $Q_G : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G : \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
+Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
 
-Let $Q_A  : \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A : \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
+Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
 
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$.
+% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
 
-%Claim 1
-\textbf{Claim 1 -- Q-Values in the abstract MDP, closely resemble those in the ground MDP:}
+Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
+
+%Claim 1 zzz \begin{claim} ?
+\textbf{Claim 1 -- Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:}
 \begin{equation}
 \label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
 \end{equation}
@@
 Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-
-Where:
+Thus,
 \begin{equation}
 \mathcal{S}_T = \begin{cases}
-\mathcal{S}_G& T \leq 0 \\
-\mathcal{S}_A& \text{o/w} \\
+\mathcal{S}_G,& T \leq 0, \\
+\mathcal{S}_A,& \text{o/w}, \\
 \end{cases}
 \end{equation}
-
-And:
 \begin{equation}
 \mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a)& T \leq 0 \\
-\mathcal{R}_A(s, a)& \text{o/w} \\
+\mathcal{R}_G(s,a),& T \leq 0, \\
+\mathcal{R}_A(s, a),& \text{o/w}, \\
 \end{cases}
 \end{equation}
-
-And:
+and
 \begin{equation}
 \mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s')& T \leq 0 \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
-\mathcal{T}_A(s,a,s')& \text{o/w} \\
+\mathcal{T}_G(s,a,s'),& T \leq 0, \\
+\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
+\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
 \end{cases}
@@
 It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
+% zzz too long... needs to be broken up.
+% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
+% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
 \begin{equation}
@@
 \begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t}
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
 \end{equation}
+that is, the Q function remains relatively unchanged over time.
 
@@
 
-When T = 0, $Q_T = Q_0$, so the result trivially follows.
+When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
 
@@
 \begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right]\\
+&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
 \end{align*}
-Since all aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination.
+Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
 \begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a)\\
+&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
+&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
 &\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{0}\epsilon \gamma^t
+&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
 \end{align*}
@@
 \begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t\\
+\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
 \end{equation}

### 2016-02-01 paper/paper.tex
Some minor changes -- defns now are automatically counted

@@
 \usepackage{amsmath}
+\usepackage{amsthm}%For stating numbered theorems
 \usepackage{amsfonts}
@@
 
+%THeorem declarations
+\newtheorem{thm}{Theorem}
+\newtheorem{lma}{Lemma}
+\newtheorem{clm}{Claim}
+\newtheorem{defn}{Definition}
+
 \icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
@@
 \newcommand{\epM}{\ep_{\text{model}}}
-\newcommand\defn[1]{{\bf Definition:} #1}
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
+\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.
 
@@
 \enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that it sums to 1 but that's all we assume)}
+\enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}
 
@@
 
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
+\begin{defn}
+A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
 \begin{equation}
@@
 \end{equation}
-}
+\end{defn}
 
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is one such that:
+\begin{defn}
+A model-irrelevance abstraction, $\phi_{model}$, is one such that:
 \begin{multline}
@@
 \end{multline}
-}
+\end{defn}
 
@@
 % Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
+\begin{thm}
+There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
 \begin{equation}
@@
 \end{equation}
+
+\end{thm}
 
@@
 
-% zzz wy not \begin{lemma} ? you know, to get the number right automatically?
-{\bf Lemma 1:} When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
+\begin{lma}
+\label{lma:Q*}
+When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
 \begin{equation}
@@
 \end{equation}
+\end{lma}
 
@@
 
-%Claim 1 zzz \begin{claim} ?
-\textbf{Claim 1 -- Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:}
+\begin{clm}
+Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:
 \begin{equation}
@@
 \end{equation}
+\end{clm}
 
@@
 %Claim 2
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
+\begin{clm}
+\label{clm:optAbsActionNearOptGround}
+The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal.
+\end{clm}
 
@@
 %Claim 3
-\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
+\begin{clm}
+We conclude Lemma \ref{lma:Q*} by Claim \ref{clm:optAbsActionNearOptGround}.
+\end{clm}
 
@@
 
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
+%Model Lemma
+\begin{lma}
+\label{lma:model}
+When $S_A$ is created using a function of the $\ep_{model}$ type:
 \begin{equation}
-\label{eq:lemma2}
 \forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
 \end{equation}
+\end{lma}
 
 {\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
+Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
 
@@
 
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
+Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
 

### 2016-02-02 paper/abstract.tex
Reorganize tex so less conflicts

--- 2016-02-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\newcommand\defn[1]{{\bf Definition:} #1}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
 The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
@@
 \ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
+We present theoretical guarantees of the quality of policies derived from four classes of approximate state abstraction.
 Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
-This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
-
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
-
-% Approximate abstraction
-In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing types in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-First, some background.
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-% zzz g in phi(s) seems like a type error, no?
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
-\end{equation}
-\noindent where $
-s, s' \in \mathcal{S}_A
-$.
-
-% Abstract policy in ground.
-In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that it sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here, we survey their main results, which we then extend to the framework of approximate abstraction.
-
-In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those that we build upon directly.
-(See their paper for full details.)
-
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
-\end{equation}
-}
-
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is one such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
-\end{multline}
-and
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
-\end{multline}
-}
-
-In words, zzz.
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-Several other projects have addressed similar topics.
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-\end{itemize}
-
-% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy this criterion.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
-\end{equation}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
-\end{equation}
-
-% zzz wy not \begin{lemma} ? you know, to get the number right automatically?
-{\bf Lemma 1:} When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
-\end{equation}
-
-\textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
-
-%Claim 1 zzz \begin{claim} ?
-\textbf{Claim 1 -- Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:}
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
-\end{equation}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-Thus,
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w}, \\
-\end{cases}
-\end{equation}
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}, \\
-\end{cases}
-\end{equation}
-and
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-% zzz too long... needs to be broken up.
-% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
-% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
-\end{equation}
-that is, the Q function remains relatively unchanged over time.
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
-\end{align*}
-Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\label{eq:lemma2}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-02 paper/background.tex
Reorganize tex so less conflicts

--- 2016-02-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsthm}%For stating numbered theorems
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-%THeorem declarations
-\newtheorem{thm}{Theorem}
-\newtheorem{lma}{Lemma}
-\newtheorem{clm}{Claim}
-\newtheorem{defn}{Definition}
-
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
-\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
-This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.
-
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
-
-% Approximate abstraction
-In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing types in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
-
-% --- SECTION: Background ---
 \section{Background}
 
-First, some background.
+First, some background.\dnote{Mmm. Hmmm? mmmm.}
 
@@
 \enote{Define value of state under a policy}
+\dnote{Q function, since we use it a lot}
 
@@
 $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
+
+\dnote{Might be worth noting that $\phi$ induces a full abstract MDP in the ``intuitively" section}
 
@@
 \end{equation}
+\dnote{Need to change the subscript here.}
 % zzz g in phi(s) seems like a type error, no?
@@
 \enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
+\dnote{This should be done in the background section, right? Just defining a value fund under a policy}
 \enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}
@@
 
-In words, zzz.
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-Several other projects have addressed similar topics.
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-\end{itemize}
-
-% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy this criterion.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-\begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
-\end{equation}
-
-\end{thm}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
-\end{equation}
-
-\begin{lma}
-\label{lma:Q*}
-When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
-\end{equation}
-\end{lma}
-
-\textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
-
-\begin{clm}
-Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
-\end{equation}
-\end{clm}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-Thus,
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w}, \\
-\end{cases}
-\end{equation}
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}, \\
-\end{cases}
-\end{equation}
-and
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-% zzz too long... needs to be broken up.
-% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
-% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
-\end{equation}
-that is, the Q function remains relatively unchanged over time.
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
-\end{align*}
-Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\begin{clm}
-\label{clm:optAbsActionNearOptGround}
-The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal.
-\end{clm}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\begin{clm}
-We conclude Lemma \ref{lma:Q*} by Claim \ref{clm:optAbsActionNearOptGround}.
-\end{clm}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-%Model Lemma
-\begin{lma}
-\label{lma:model}
-When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-\end{lma}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
-Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}
+In words, zzz.\dnote{Insert details about each $\phi$ above}

### 2016-02-02 paper/related_work.tex
Reorganize tex so less conflicts

--- 2016-02-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\newcommand\defn[1]{{\bf Definition:} #1}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
-\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
-This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
-
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
-
-% Approximate abstraction
-In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing types in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-First, some background.
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-% zzz g in phi(s) seems like a type error, no?
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
-\end{equation}
-\noindent where $
-s, s' \in \mathcal{S}_A
-$.
-
-% Abstract policy in ground.
-In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that it sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here, we survey their main results, which we then extend to the framework of approximate abstraction.
-
-In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those that we build upon directly.
-(See their paper for full details.)
-
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
-\end{equation}
-}
-
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is one such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
-\end{multline}
-and
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
-\end{multline}
-}
-
-In words, zzz.
-
-% --- SECTION: Related Work ---
 \section{Related Work}
@@
 %\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-\end{itemize}
-
-% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy this criterion.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
-\end{equation}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
-\end{equation}
-
-% zzz wy not \begin{lemma} ? you know, to get the number right automatically?
-{\bf Lemma 1:} When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
-\end{equation}
-
-\textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
-
-%Claim 1 zzz \begin{claim} ?
-\textbf{Claim 1 -- Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:}
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
-\end{equation}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-Thus,
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w}, \\
-\end{cases}
-\end{equation}
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}, \\
-\end{cases}
-\end{equation}
-and
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-% zzz too long... needs to be broken up.
-% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
-% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
-\end{equation}
-that is, the Q function remains relatively unchanged over time.
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
-\end{align*}
-Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\label{eq:lemma2}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-02 paper/results_discussion.tex
Reorganize tex so less conflicts

--- 2016-01-31 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-\icmltitlerunning{Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\newcommand\defn[1]{{\bf Definition:} #1}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be overcome using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compressing while preserving near optimal behavior.
-\acp{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of tasks, as well as the tradeoff between approximation magnitude and optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}.
-Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
-This work characterizes what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
-
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{littman1995complexity,papadimitriou1987complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, polynomial behavior in state space size often translates to intractability for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
-
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction in order to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
-
-% Approximate abstraction
-In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing approaches in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss our experimentation, in which we apply one class of approximate abstraction to a variety of different tasks, visualizing their abstraction and showing the relationship between degrees of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-A \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers immediate rewards over future rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V(s)^\pi$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$ respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \cite{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from a ground MDP $M_G$ to an abstract MDP $M_A$ using a state aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground MDP to a state in the abstract MDP.
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) 
-\end{equation}
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g) 
-\end{equation}
-For:
-\begin{equation}
-s, s' \in \mathcal{S}_A
-\end{equation}
-
-% Abstract policy using in ground.
-In general we are interested in how policies defined over the abstract MDP perform in the ground MDP.
-To leverage a policy defined in the abstract in the ground, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-\pi_A(s) = \pi_A(\phi(s)),\ s \in \mathcal{S}_G
-\end{equation}
-
-We evaluate the value of the abstract policy in the ground MDP by following the abstract policy:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(a)) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(a),s')V^{\pi_A}(s')
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that is sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citep{li2006towards} develop a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here we survey their main results that we extend to the framework of approximate abstraction.
-
-In particular, they define the following five classes of state abstractors, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those which we build upon directly (see their paper for full details).
-
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \longrightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right)
-\end{equation}
-}
-
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a) \\
-\end{multline}
-And:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s') \\
-\end{multline}
-}
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citep{dean1997model} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-~\citep{even2003approximate} analyze different distant metrics used in the process of identifying $\epsilon$-homogenous partitions.
-~\cite{ortner2013adaptive} develops an algorithm for learning partitions in an on line setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citep{andre2002state} investigates a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstraction that maintains optimality.
-~\cite{dietterich2000hierarchical} develops the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy.
-\citep{jong2005state} introduce a method called {\it policy-irrelevance}, in which agents identify (online) which state variables may be safely ignored in a factored MDP, and consequently achieve state abstraction.
-The agent will learn to ignore state variables that don't impact optimal behavior, and is consequently contained within the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in recent reinforcement learning literature, see~\cite{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here we introduce our formal method for approximate state abstraction, and the related results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, Model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann disibtruions, induce abstract MDPs for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to value of the states in the Abstract MDP
-\item Then, we relate the value of states in the ground MDP to value of the states in the Abstract MDP under the optimal abstract policy.
-\end{itemize}
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state abstraction function which satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\phi_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that for any $f$, there are many such functions that satisfy this criteria.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP, applied to the ground MDP, has error bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon)
-\end{equation}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-Inspired by the $Q^*$ irrelevance abstraction, we consider the approximate case.
-By Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
-
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation}
-
-\textbf{Proof:}
-
-Let $Q_G : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G : \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A  : \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A : \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$.
-
-%Claim 1
-\textbf{Claim 1 -- Q-Values in the abstract MDP, closely resemble those in the ground MDP:}
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}
-\end{equation}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-
-Where:
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G& T \leq 0 \\
-\mathcal{S}_A& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-And:
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a)& T \leq 0 \\
-\mathcal{R}_A(s, a)& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-And:
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s')& T \leq 0 \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
-\mathcal{T}_A(s,a,s')& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t}
-\end{equation}
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When T = 0, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right]\\
-\end{align*}
-Since all aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination.
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{0}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\label{eq:lemma2}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
 \section{Approximate Abstraction on Example Domains}
@@
 \end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-02 paper/theory_results.tex
Reorganize tex so less conflicts

--- 2016-02-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsthm}%For stating numbered theorems
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-%THeorem declarations
-\newtheorem{thm}{Theorem}
-\newtheorem{lma}{Lemma}
-\newtheorem{clm}{Claim}
-\newtheorem{defn}{Definition}
-
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
-\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
-This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.
-
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
-
-% Approximate abstraction
-In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing types in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-First, some background.
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-% zzz g in phi(s) seems like a type error, no?
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
-\end{equation}
-\noindent where $
-s, s' \in \mathcal{S}_A
-$.
-
-% Abstract policy in ground.
-In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here, we survey their main results, which we then extend to the framework of approximate abstraction.
-
-In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those that we build upon directly.
-(See their paper for full details.)
-
-\begin{defn}
-A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
-\end{equation}
-\end{defn}
-
-\begin{defn}
-A model-irrelevance abstraction, $\phi_{model}$, is one such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
-\end{multline}
-and
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
-\end{multline}
-\end{defn}
-
-In words, zzz.
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-Several other projects have addressed similar topics.
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
 % --- SECTION: State Abstraction ---
@@
 % zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
+% In response^^^ Could add a sentence pointing out how these differ.
 
@@
 % zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
+\dnote{Let's put a reminder of the weighting scheme here}
 \begin{equation}
@@
 % Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-02 paper/introduction.tex

--- 2016-02-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{times}
-\usepackage{graphicx}
-\usepackage{subfigure} 
-\usepackage{natbib}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amsthm}%For stating numbered theorems
-\usepackage{amsfonts}
-\usepackage{algorithmic}
-\usepackage{subfigure}
-\usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
-\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
-
-%THeorem declarations
-\newtheorem{thm}{Theorem}
-\newtheorem{lma}{Lemma}
-\newtheorem{clm}{Claim}
-\newtheorem{defn}{Definition}
-
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
-
-% --- Notation Commands ---
-\newcommand{\ep}{\widetilde \phi}
-\newcommand{\epQ}{\ep_{Q^*}}
-\newcommand{\epM}{\ep_{\text{model}}}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mcS}{\mathcal{S}}
-\newcommand{\mcT}{\mathcal{T}}
-\newcommand{\mcR}{\mathcal{R}}
-\newcommand{\pM}{\phi_{\text{model}}}
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-% --- DOCUMENT ---
-\begin{document}
-
-\twocolumn[
-\icmltitle{Suboptimality Bounds for Approximate State Abstraction}
-
-% Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
-\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
-]
-
-%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
-\begin{acronym}
-\acro{MDP}{Markov Decision Process}
-\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
-\acro{RL}{reinforcement learning}
-\acrodefplural{RL}{Reinforcement learning}
-\end{acronym}
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
-\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
-\end{abstract}
-
-% --- SECTION: Introduction ---
 \section{Introduction}
@@
 We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-First, some background.
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-% zzz g in phi(s) seems like a type error, no?
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
-\end{equation}
-\noindent where $
-s, s' \in \mathcal{S}_A
-$.
-
-% Abstract policy in ground.
-In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here, we survey their main results, which we then extend to the framework of approximate abstraction.
-
-In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those that we build upon directly.
-(See their paper for full details.)
-
-\begin{defn}
-A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
-\end{equation}
-\end{defn}
-
-\begin{defn}
-A model-irrelevance abstraction, $\phi_{model}$, is one such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
-\end{multline}
-and
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
-\end{multline}
-\end{defn}
-
-In words, zzz.
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-Several other projects have addressed similar topics.
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-\end{itemize}
-
-% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy this criterion.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-\begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
-\end{equation}
-
-\end{thm}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
-\end{equation}
-
-\begin{lma}
-\label{lma:Q*}
-When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
-\begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
-\end{equation}
-\end{lma}
-
-\textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
-
-\begin{clm}
-Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
-\end{equation}
-\end{clm}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-Thus,
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w}, \\
-\end{cases}
-\end{equation}
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}, \\
-\end{cases}
-\end{equation}
-and
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-% zzz too long... needs to be broken up.
-% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
-% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
-\end{equation}
-that is, the Q function remains relatively unchanged over time.
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
-\end{align*}
-Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\begin{clm}
-\label{clm:optAbsActionNearOptGround}
-The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal.
-\end{clm}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\begin{clm}
-We conclude Lemma \ref{lma:Q*} by Claim \ref{clm:optAbsActionNearOptGround}.
-\end{clm}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-%Model Lemma
-\begin{lma}
-\label{lma:model}
-When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-\end{lma}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
-Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
-
-% -----------------------------------------------
-% --- SECTION: Example Domains ---
-% -----------------------------------------------
-\section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
-% --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
-
-% --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{icml2016/icml2016}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-02 paper/paper.tex

--- 2016-01-31 paper/paper.tex
@@
 
-\icmltitlerunning{Approximate State Abstraction}
+%THeorem declarations
+\newtheorem{thm}{Theorem}
+\newtheorem{lma}{Lemma}
+\newtheorem{clm}{Claim}
+\newtheorem{defn}{Definition}
+
+\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
 
@@
 \twocolumn[
-\icmltitle{Approximate State Abstraction}
+\icmltitle{Optimality Bounds for Approximate State Abstraction}
 
@@
 
+% ------------------------
 % --- ABSTRACT ---
+% ------------------------
 \begin{abstract}
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be overcome using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compressing while preserving near optimal behavior.
-\acp{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of tasks, as well as the tradeoff between approximation magnitude and optimality of behavior.
+\input{abstract.tex}
 \end{abstract}
 
+% ---------------------------------------
 % --- SECTION: Introduction ---
-\section{Introduction}
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}.
-Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction.
-This work characterizes what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.
+% ---------------------------------------
+\input{introduction.tex}
 
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{littman1995complexity,papadimitriou1987complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, polynomial behavior in state space size often translates to intractability for sufficiently complicated tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over CITE DABE ICAPS.
+% ---------------------------------------
+% --- SECTION: Background ---
+% ---------------------------------------
+\input{background.tex}
 
-% Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction in order to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
+% -----------------------------------------
+% --- SECTION: Related Work ---
+% -----------------------------------------
+\input{related_work.tex}
 
-% Approximate abstraction
-In this work we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge which we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state aggregation criteria are relaxed to approximate equality, methods which employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-
-% Summary	
-This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing approaches in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss our experimentation, in which we apply one class of approximate abstraction to a variety of different tasks, visualizing their abstraction and showing the relationship between degrees of compression and error incurred.
-
-% --- SECTION: Background ---
-\section{Background}
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-A \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers immediate rewards over future rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
-
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V(s)^\pi$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$ respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto}
-
-\enote{Define value of state under a policy}
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \cite{li2006towards} \enote{This should probably say more}.
-
-We understand an abstraction as a mapping from a ground MDP $M_G$ to an abstract MDP $M_A$ using a state aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-% States
-The states in the abstract MDP are constructed by applying a state aggregation scheme, $\phi$, to the states in the ground MDP, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground MDP to a state in the abstract MDP.
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}
-\end{equation}
-
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
-
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) 
-\end{equation}
-
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g) 
-\end{equation}
-For:
-\begin{equation}
-s, s' \in \mathcal{S}_A
-\end{equation}
-
-% Abstract policy using in ground.
-In general we are interested in how policies defined over the abstract MDP perform in the ground MDP.
-To leverage a policy defined in the abstract in the ground, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-\pi_A(s) = \pi_A(\phi(s)),\ s \in \mathcal{S}_G
-\end{equation}
-
-We evaluate the value of the abstract policy in the ground MDP by following the abstract policy:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(a)) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(a),s')V^{\pi_A}(s')
-\end{equation}
-
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\enote{Say more about the weighting (that is sums to 1 but that's all we assume)}
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citep{li2006towards} develop a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here we survey their main results that we extend to the framework of approximate abstraction.
-
-In particular, they define the following five classes of state abstractors, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those which we build upon directly (see their paper for full details).
-
-\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \longrightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right)
-\end{equation}
-}
-
-\defn{A model-irrelevance abstraction, $\phi_{model}$, is such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a) \\
-\end{multline}
-And:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s') \\
-\end{multline}
-}
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
-
-\subsection{Approximate State Abstraction}
-\citep{dean1997model} investigates partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-~\citep{even2003approximate} analyze different distant metrics used in the process of identifying $\epsilon$-homogenous partitions.
-~\cite{ortner2013adaptive} develops an algorithm for learning partitions in an on line setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
-
-\subsection{Specific Abstraction Algorithms}
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citep{andre2002state} investigates a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstraction that maintains optimality.
-~\cite{dietterich2000hierarchical} develops the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy.
-\citep{jong2005state} introduce a method called {\it policy-irrelevance}, in which agents identify (online) which state variables may be safely ignored in a factored MDP, and consequently achieve state abstraction.
-The agent will learn to ignore state variables that don't impact optimal behavior, and is consequently contained within the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in recent reinforcement learning literature, see~\cite{li2006towards}.
-
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
-
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Intro to approx state abstraction results.
-Here we introduce our formal method for approximate state abstraction, and the related results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, Model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann disibtruions, induce abstract MDPs for which the optimal policy has bounded error in the ground MDP.
-
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to value of the states in the Abstract MDP
-\item Then, we relate the value of states in the ground MDP to value of the states in the Abstract MDP under the optimal abstract policy.
-\end{itemize}
-
-We now introduce some additional notation to formally discuss these results.
-
-{\bf $\ep_f$ definition:} Given a function $f : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state abstraction function which satisfies the following for any two ground states $s_1$ and $s_2$:
-\begin{equation}
-\label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-That is, when $\phi_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that for any $f$, there are many such functions that satisfy this criteria.
-
-We now introduce the main result of the paper.
-
-% Theorem 1
-{\bf Theorem 1:} There exist at least four classes of approximate state aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract MDP, applied to the ground MDP, has error bounded polynomially in $\epsilon$:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon)
-\end{equation}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-
-% Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
-
-% Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-Inspired by the $Q^*$ irrelevance abstraction, we consider the approximate case.
-By Equation~\ref{eq:phi_f}, $\ep_{Q^*}$ is a type of abstraction that, for a fixed $\epsilon$, satisfies:
-
-\begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon
-\end{equation}
-
-{\bf Lemma 1:} When $S_A$ is created using a function of the $\ep_{Q^*}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation}
-
-\textbf{Proof:}
-
-Let $Q_G : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G : \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A  : \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A : \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$.
-
-%Claim 1
-\textbf{Claim 1 -- Q-Values in the abstract MDP, closely resemble those in the ground MDP:}
-\begin{equation}
-\label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}
-\end{equation}
-
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
-
-Where:
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
-\mathcal{S}_G& T \leq 0 \\
-\mathcal{S}_A& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-And:
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
-\mathcal{R}_G(s,a)& T \leq 0 \\
-\mathcal{R}_A(s, a)& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-And:
-\begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s')& T \leq 0 \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
-\mathcal{T}_A(s,a,s')& \text{o/w} \\
-\end{cases}
-\end{equation}
-
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
-\begin{equation}
-Q_T(s, a) = 
-\begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
-\end{cases}
-\end{equation}
-
-We proceed by induction on $T$ to show that:
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t}
-\end{equation}
-
-% Base Case t=0
-\textit{Base Case: $T = 0$}
-
-When T = 0, $Q_T = Q_0$, so the result trivially follows.
-
-% Base Case t=1
-\textit{Base Case: $T = 1$}
-\begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right]\\
-\end{align*}
-Since all aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination.
-\begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{0}\epsilon \gamma^t
-\end{align*}
-
-% Inductive Case
-\textit{Inductive Case: $T > 1$}
-
-We assume as our inductive hypothesis that:
-\begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t\\
-\end{equation}
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
-We denote $\epQ(s_G)$ as $s_A$.
-\begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{align*}
-
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
-\begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
-\end{equation}
-
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
-
-Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
-
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
-
-%Claim 2
-\textbf{Claim 2: the optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:}
-
-\begin{equation}
-\label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By Equation \ref{eq:Q*Claim1}
-\begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
-\label{eq:Q*OptActionResult}
-\end{align}
-
- By the definition of $a^*_A$ we know that 
- \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
-\end{align}
-
-Lastly again by Equation \ref{eq:Q*Claim1} we know
-\begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
-\end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
-
-%Claim 3
-\textbf{Claim 3: we conclude Lemma 1 by Claim 2}
-
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
-\begin{equation}
-\pi_{A,t}(s)=
-\begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
-\end{cases}
-\end{equation}
-
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
-%Start induction on following the optimal abstract policy
-We now show by induction on $t$ that
-\begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-\textit{Base case: $t=0$}
-
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
-
-\textit{Inductive case: $t > 0$}
-
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
-We assume for our inductive hypothesis that
-\begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-By definition 
-\begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{align*}
-
-Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
-\begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation}
-
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
-
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-% Subsection: Model Similarity
-\subsection{Model Similarity: $\ep_{model}$}
-
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
-\begin{multline}
-\epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
-\end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
-
-{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
-\begin{equation}
-\label{eq:lemma2}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
-\end{equation}
-
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.
-
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
-\end{align*}
-
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.
-
-% Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
-
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
-\end{multline}
-
-\dnote{We also need to add the point about the denominator bound...}
-
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
-
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
-A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
-Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
-Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
-
-% Some abstractions DON'T preserve a meaningful notion of optimality.
+% ----------------------------------------------------------------
+% --- SECTION: Approximate State Abstraction  ---
+% ----------------------------------------------------------------
+\input{theory_results.tex}
 
@@
 % -----------------------------------------------
-\section{Example Domains}
+\input{example_domains.tex}
 
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-% Description of visuals.
-Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
-The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-
-% Subsection: NChain.
-\subsection{NChain}
-
-NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}
-
-% NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
-\end{figure}
-
-%% Subsection: UpWorld.
-%\subsection{UpWorld}
-%
-%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner.
-The agent may move left, right, and up.
-The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions.
-the agent receives 0 reward for all other transitions.
-Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward.
-During experimentation, we set $N=10$, $M=4$.
-%
-%\begin{figure}
-%\subfigure[Ground UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
-%\subfigure[Abstract UpWorld]{
-%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
-%\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
-%\end{figure}
-
-% Subsection: Taxi
-\subsection{Taxi}
-
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals.
-The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
-As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.
-
-% Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% Subsection: Minefield.
-\subsection{Minefield}
-
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed slightly, and there is no down action.
-In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-
-% Minefield Compression Visuals
-\begin{figure}
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
-\end{figure}
-
-% Subsection: Random.
-\subsection{Random}
-
-The Random MDP domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-
-% Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
-
+% ------------------------------------------------------------------------------------
 % --- SECTION: Approximate Abstraction on Example Domains ---
-\section{Approximate Abstraction on Example Domains}
-
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
-
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
-
-% Figure: Epsilon vs. #States for all three sample domains.
-\begin{figure}
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
-\end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}
+% ------------------------------------------------------------------------------------
+\input{results_discussion.tex}
 

### 2016-02-02 paper/background.tex
pass partially complete

@@
 
-First, some background.\dnote{Mmm. Hmmm? mmmm.}
+%First, some background.
 
@@
 \subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
+An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
 We assume without loss of generality that all reward functions are normalized to $[0,1]$.
@@
 We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$.
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively.
-\enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}
+We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$, defined by the Bellman Equation as:
+\begin{equation}
+Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s))
+\end{equation}
+Similarly, the value function defined under a given policy, denoted $V^\pi(s)$, is defined as:
+\begin{equation}
+V^\pi(s) = \max_a Q^\pi(s,a)
+\end{equation}
 
-\enote{Define value of state under a policy}
-\dnote{Q function, since we use it a lot}
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively~\cite{kaelbling1996reinforcement}.
 
@@
 \subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.
+We build upon the notation used by \citeauthor{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
+We build heavily on their notation, and discuss other similarities in our work in the next section.
 
 We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-
-\dnote{Might be worth noting that $\phi$ induces a full abstract MDP in the ``intuitively" section}
+Consequently, this mapping induces an abstract MDP.
+Let:$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
 
@@
 
+We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$.
+The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
+\begin{equation}
+\left(\sum_{s \in \mathcal{S}_G} \omega(s)\right) = 1,\hspace{6mm} \forall_{s \in \mathcal{S}_G} \omega(s) \in [0,1]
+\end{equation}
+
 % Abstract policy in ground.
@@
 \end{equation}
+\dnote{I don't think this is right. Should be the max action? Or am I confused? My reading of the Q function from above is then possibly confused...}
 
-\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-\dnote{This should be done in the background section, right? Just defining a value fund under a policy}
-\enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}
+%\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
+%\dnote{This should be done in the background section, right? Just defining a value fund under a policy}
 
@@
 \begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a).
 \end{multline}
@@
 \begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
+\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') = \sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s').
 \end{multline}
@@
 
-In words, zzz.\dnote{Insert details about each $\phi$ above}
+Intuitively, a $Q^*$-irrelevance is one that is guaranteed to compress states that share optimal Q functions.
+Critically, the direction of the implication is such that the abstraction is not guaranteed to abstract all states for which this condition is true, only that, if the abstraction function collapses two (or more) states to an abstract state, that those states have the same $Q^*$.
+Computing such a function is as difficult as solving the MDP, as it requires knowledge of the $Q*$, which is a sufficient condition for knowing the optimal policy.
+This is one of the motivations for investigating approximate abstractions, as we anticipate that an approximation of $Q^*$ is the sort of knowledge a learner can infer online.
+
+A model-irrelevance abstraction is one that is guaranteed to compress states that transition to the same compressed states, and have identical rewards.
+Critically, this need not require that the ground transition functions of any two compressed states are identical; only that their corresponding abstract state transitions {\it in the abstract} MDP are identical.
+Unlike the $Q^*$ irrelevance, in the planning setting we anticipate knowing the full transition function and reward function up front, so it is feasible that an abstraction function of this kind may be used.
+In a model based learning setting, we expect an approximate abstraction akin to model-irrelevance to be more realistic, as we anticipate reinforcement learners to be able to approximate the information content of the transition function and reward function during learning.

### 2016-02-02 paper/paper.tex
pass partially complete

@@
 
-%THeorem declarations
+%Theorem declarations
 \newtheorem{thm}{Theorem}
@@
 
-\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}
+\icmltitlerunning{Near Optimal Behavior with Approximate State Abstraction}
 
@@
 \twocolumn[
-\icmltitle{Optimality Bounds for Approximate State Abstraction}
+% Suboptimality Bounds for Approximate State Abstraction
+\icmltitle{Near Optimal Behavior with Approximate State Abstraction}
 
@@
 
+% --------------------------------------
 % --- SECTION: Conclusion ---
-\section{Conclusion}
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}
+% --------------------------------------
+\input{conclusion.tex}
 

### 2016-02-02 paper/related_work.tex
pass partially complete

@@
 \subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
-They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP.
+\citeauthor*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
 This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.

### 2016-02-02 paper/theory_results.tex
pass partially complete

@@
 \end{itemize}
+
+% Explanation of the above.
+The first statement is relating Q values defined over the ground MDP with Q values defined over the abstract MDP, while the second statement is comparing the optimal Q values in the ground MDP, with the Q values in the ground MDP under the abstract policy.
+This is because our learners will solve for the optimal policy in the abstract, and use it in the ground MDP by mapping each ground state to its abstract state and querying the abstract policy for behavior.
+That is:
+\begin{equation}
+\pi_G(s) = \pi_A(\phi(s))
+\end{equation}
 
@@
 
+% Q^* Lemma
 \begin{lma}
@@
 
+% Proof
 \textbf{Proof:}
@@
 
+% Claim 1:
 \begin{clm}
@@
 \mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w}, \\
+\mathcal{S}_A,& \text{o/w},
 \end{cases}
@@
 \mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}, \\
+\mathcal{R}_A(s, a),& \text{o/w},
 \end{cases}
@@
 \underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}. \\
+\mathcal{T}_A(s,a,s'),& \text{o/w}.
 \end{cases}

### 2016-02-02 paper/theory_results.tex
Reformatted all the math

@@
 	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
+	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a) &\text{o/w}
+
 \end{cases}
+\end{equation}
+
+Where:
+\begin{equation}
+\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a')
 \end{equation}
@@
 \textit{Base Case: $T = 0$}
-
 When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
-
 % Base Case t=1
@@
 \begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].\\
+&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
 \end{align*}
@@
 &Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).\\
-&\text{Thus,}\\
-&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
+&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).
 \end{align*}
-
+Thus,
+\begin{equation}
+Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
+\end{equation}
 % Inductive Case
@@
 
-We denote $\epQ(s_G)$ as $s_A$.
+We denote $\epQ(s_G)$ as $s_A$. By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
+\begin{multline*}
+Q_T(s_A, a) = \sum_{g \in X(s_A)}w(g)* \\ 
+ \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
+\end{multline*}
+Applying our inductive hypothesis yields,
+\begin{multline*}
+\leq \sum_{g \in X(s_A)}w(g) * \\ \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
+\end{multline*}
+%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
+Then:
+\begin{equation*}
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]
+\end{equation*}
+Since all aggregated states have Q-values within $\epsilon$ of one another:
 \begin{align*}
-&\text{By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:}\\
-&Q_T(s_A, a) =\sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]\\
-&\text{Applying our inductive hypothesis yields}\\
-&\leq \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]\\
-&\text{Since all aggregated states have Q-values within $\epsilon$ of one another:}\\
 &\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)\\
-&\text{Thus,}\\
-&\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)
 \end{align*}
+Thus,
+\begin{equation*}
+\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
+\end{equation*}
 
@@
 \begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \\
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}
 \label{eq:Q*OptActionResult}
@@
 Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
-
 \begin{equation}
@@
 \pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}\\
+\pi_A^*(\ep(s)), \text{if $t > 0$}
 \end{cases}
@@
 For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
-\begin{align*}
-V^{\pi_{A,t}}(s_G) &= \\
-&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
-\end{align*}
-
+\begin{multline*}
+V^{\pi_{A,t}}(s_G) = \\
+R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
+\end{multline*}
 %Start induction on following the optimal abstract policy
@@
 \end{equation}
-
 \textit{Base case: $t=0$}
@@
 \end{equation}
-
 By definition 
+\begin{multline*}
+V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
+\end{multline*}
+Applying our inductive hypothesis yields:
+\begin{multline*}
+V^{\pi_{A,t}}(g, a) \geq R_G(s, \pi_{A,t}(g, a))\ + \\ \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
+\end{multline*}
+Therefore:
 \begin{align*}
-&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
-&\text{Applying our inductive hypothesis yields}\\
-&V^{\pi_{A,t}}(g, a) \geq\\
-&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
-&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
+%&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
+&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))
+\end{align*}
+Applying Equation \ref{eq:Q*Claim2} yields:
+\begin{align*}
 &\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
-& \text{Thus,}\\
-&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)
 \end{align*}
 
+Thus,
+\begin{equation*}
+V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\end{equation*}
 Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
@@
 =&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
-\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
-&\text{By the similarity of transitions of grouped states under $\epM$:}\\
+& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|
+\end{align*}
+\begin{multline*}
+\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)} \\ \left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]
+\end{multline*}
+By the similarity of transitions of grouped states under $\epM$:
+\begin{align*}
  \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\

### 2016-02-02 paper/theory_results.tex
a few small cleanups in the proofs

@@
  \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
-&\text{Applying 0-1 reward normalization and algebra:}\\
- \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
+\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}
 \end{align*}
+Applying 0-1 reward normalization and algebra:
+\begin{equation*}
+ \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
+\end{equation*}
 
@@
 
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
+{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some constant positive $k \in \mathbb{R}$:
 \begin{equation}
@@
 
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
+{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some constant positive $k \in \mathbb{R}$::
 \begin{equation}

### 2016-02-02 Workspace and Code/stateAbstraction/src/domains/minefield/MinefieldGenerator.java
Changed minefield to have down action -- currently slips wierdly on the edges of map

@@ -15,8 +15,9 @@ public class MinefieldGenerator {
 	
 	/**
 	 * 
-	 * @param totalNumStates
-	 * @return an n state graph MDP.
+	 * @param width
+	 * @param height
+	 * @return
 	 */
 	public static GraphDefinedDomain getMinefield(int width, int height) {
 		GraphDefinedDomain dg = new GraphDefinedDomain(height*width);
@@ -43,6 +44,10 @@ public class MinefieldGenerator {
 				// Set slip probs for Up:
 				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, leftIndex, slipProbability/2.0);
 				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, rightIndex, slipProbability/2.0);
+				
+				// Set slip probs for down:
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 3/*down action*/, leftIndex, slipProbability/2.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 3/*down action*/, rightIndex, slipProbability/2.0);
 			}
 		}
 
@@ -54,8 +59,24 @@ public class MinefieldGenerator {
 				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, currentStateIndex+width, 1.0 - slipProbability);
 				
 				// Set slip for Left and Right
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*left action*/, currentStateIndex+width, slipProbability);
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*right action*/, currentStateIndex+width, slipProbability);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*left action*/, currentStateIndex+width, slipProbability/2.0);
+				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*right action*/, currentStateIndex+width, slipProbability/2.0);
+			}
+		}
+		// Set up transition for down.
+		for (int j = 0; j < height-1; j++){
+			for (int i = 0; i < width; i++) {
+				int currentStateIndex = i +j*width;
+				int stateBelowIndex = currentStateIndex-width;
+				if (stateBelowIndex < 0) stateBelowIndex = currentStateIndex; // Self loop at bottom
+				System.out.println("sbelow: " + stateBelowIndex);
+				
[…]

### 2016-02-02 Workspace and Code/stateAbstraction/src/domains/minefield/MinefieldGenerator.java
Minefield now working and with down action

@@ -1,6 +1,7 @@
 package domains.minefield;
 
 import java.util.ArrayList;
+import java.util.HashMap;
 import java.util.List;
 import java.util.Random;
 
@@ -10,9 +11,9 @@ import burlap.oomdp.singleagent.GroundedAction;
 import burlap.oomdp.singleagent.RewardFunction;
 
 public class MinefieldGenerator {
-	
+
 	private static double slipProbability = 0.01;
-	
+
 	/**
 	 * 
 	 * @param width
@@ -21,7 +22,7 @@ public class MinefieldGenerator {
 	 */
 	public static GraphDefinedDomain getMinefield(int width, int height) {
 		GraphDefinedDomain dg = new GraphDefinedDomain(height*width);
-		
+
 		// Set up transitions for left/right.
 		for (int j = 0; j < height; j++){
 			for (int i = 0; i < width; i++) {
@@ -35,89 +36,95 @@ public class MinefieldGenerator {
 				if (i == width-1) rightIndex = currentStateIndex;
 				else rightIndex = currentStateIndex+1;
 
-				//Set up left action.
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 0/*action*/, leftIndex, 1.0 - slipProbability);
-				
-				//Set up right action.
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 1/*action*/, rightIndex, 1.0 - slipProbability);
-				
-				// Set slip probs for Up:
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, leftIndex, slipProbability/2.0);
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 2/*up action*/, rightIndex, slipProbability/2.0);
-				
-				// Set slip probs for down:
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 3/*down action*/, leftIndex, slipProbability/2.0);
-				((GraphDefinedDomain) dg).setTransition(currentStateIndex, 3/*down action*/, rightIndex, slipProbability/2.0);
+				int aboveIndex = currentStateIndex+width;
+				if (aboveIndex >= height*width) aboveIndex = currentStateIndex;
+
+				int belowIndex = currentStateIndex-width;
+				if (belowIndex < 0) belowIndex = currentStateIndex; // Self loop at bottom
+
+
+
+				//Left
+				HashMap<Integer, Double> leftHM = new HashMap<Integer, Double>();
[…]

### 2016-02-02 Workspace and Code/stateAbstraction/src/domains/minefield/MinefieldGenerator.java
Fixed minefield RF to match new down action and slip prob

@@ -106,20 +106,36 @@ public class MinefieldGenerator {
 		public static class MinefieldRF implements RewardFunction {
 
 			private List<Integer> mineStates = new ArrayList<Integer>();
+			private List<Integer> topNodeIndices = new ArrayList<Integer>();
 			private Random prf = new Random();
 
-			public MinefieldRF(int numMineStates, int numTotalStates) {
+			/**
+			 * 
+			 * @param numMineStates
+			 * @param numTotalStates
+			 * @param height
+			 * @param width
+			 */
+			public MinefieldRF(int numMineStates, int numTotalStates, int height, int width) {
+				//Randomize mines
 				for (int i = 0; i < numMineStates; i++) {
 					mineStates.add(prf.nextInt(numTotalStates));
+				}
+				//Add to topNodes
+				for (int i = 0; i < width; i++) {
+					int indexToAdd = numTotalStates-1-i;
+					topNodeIndices.add(indexToAdd);
 				}
 			}
 
 			@Override
 			public double reward(State s, GroundedAction a, State sprime) {
-				if (s.equals(sprime) && a.actionName().equals("action2")){ 
+				int sIndex = GraphDefinedDomain.getNodeId(s);
+				int sPrimeIndex = GraphDefinedDomain.getNodeId(sprime);
+				if (topNodeIndices.contains(sIndex) && sIndex == sPrimeIndex && a.actionName().equals("action3")){ 
 					return 1;
 				}
-				else if (mineStates.contains(sprime)) {
+				else if (mineStates.contains(sPrimeIndex)) {
 					return 0;
 				} else{
 					return 0.1;

### 2016-02-02 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -48,11 +48,11 @@ public class EpsilonExperiments {
 
 	// Iterate over epsilon and compute the number of states.
 	final static double startEpsilon = 0.00;
-	final static double endEpsilon = 0.5;
+	final static double endEpsilon = 0.1;
 	final static double epsilonIncrement = 0.01;
-	final static int numTrials = 20;
-	final static String task = "RANDOM"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
-	final static boolean clearOldResults = false; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
+	final static int numTrials = 5;
+	final static String task = "MINEFIELD"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+	final static boolean clearOldResults = true; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
 
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.
@@ -211,7 +211,7 @@ public class EpsilonExperiments {
 		GraphDefinedDomain minefieldGen = MinefieldGenerator.getMinefield(minefieldHeight, minefieldWidth);
 		Domain minefieldDomain = minefieldGen.generateDomain();
 		State initialMinefieldState = GraphDefinedDomain.getState(minefieldDomain, 0);
-		RewardFunction minefieldRF = new MinefieldGenerator.MinefieldRF(numMineStates, minefieldHeight * minefieldWidth);
+		RewardFunction minefieldRF = new MinefieldGenerator.MinefieldRF(numMineStates, minefieldHeight * minefieldWidth, minefieldHeight, minefieldWidth);
 
 		if (task.equals("ALL")) {
 			generateEpsilonResults(nChainGen, nChainRF, initialNChainState, "nchain");

### 2016-02-02 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java
Tweaked experiments

@@ -47,12 +47,12 @@ public class EpsilonExperiments {
 	static String resultsDir = filePath + "/src/plotting/";
 
 	// Iterate over epsilon and compute the number of states.
-	final static double startEpsilon = 0.00;
-	final static double endEpsilon = 0.1;
+	final static double startEpsilon = 0.15;
+	final static double endEpsilon = 0.25;
 	final static double epsilonIncrement = 0.01;
-	final static int numTrials = 5;
+	final static int numTrials = 3;
 	final static String task = "MINEFIELD"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
-	final static boolean clearOldResults = true; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
+	final static boolean clearOldResults = false; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
 
 	/**
 	 * Given a DomainGenerator + RF + TF + initState, this method generates abstract MDPs subject to different epsilons, and prints the results.

### 2016-02-03 paper/example_domains.tex
PUSHPUSHPUSH

\section{Example Domains}

\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}

To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains. We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP. More specifically, we relate $\epsilon$ to:
\begin{equation}
|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
\end{equation}
For different values of $\epsilon$.

% Description of visuals.
Our code base provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction. The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted. We use the graph visualization library GraphStream~\cite{graphstream}. In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground MDPs, states are labeled with a number. In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).

\dnote{One thing we want to add is a description of how diverse these domains are!}
\dnote{Also put in a note that we're using a uniform weighting scheme}

% Subsection: NChain.
\subsection{NChain}

NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain. This transition provides a large positive reward, $r_{large}$. Thus, the agent must explore down the chain and avoid the intermediate smaller rewards in order to find the large reward at the end. In many implementations, there is also a small slip probability that the applied action has the unintended effect of the opposing action (so advancing down the chain with probability $\rho$ will take the agent back to state 0, and vice versa). In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
\end{figure}

%% Subsection: UpWorld.
%\subsection{UpWorld}
%
%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner. The agent may move left, right, and up. The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions. the agent receives 0 reward for all other transitions. Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward. During experimentation, we set $N=10$, $M=4$.
%
%\begin{figure}
%\subfigure[Ground UpWorld]{
%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
%\subfigure[Abstract UpWorld]{
%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
%\label{fig:upworld-visual}
%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
%\end{figure}

% Subsection: Taxi
\subsection{Taxi}

Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into hierarchical subgoals. The agent, operating in a grid world style domain, may move left, right, up, and down, as well as pickup a passenger and drop off a passenger. The agent must seek out passengers and take them to their destination. We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}. As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and abstract MDP in the same format.

% Taxi Compression Visuals
\begin{figure}[h]
\subfigure[Ground Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
\subfigure[Abstract Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
\label{fig:taxi-visual}
\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
\end{figure}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

% Subsection: Minefield.
\subsection{Minefield}

Minefield is a slight variant of Grid World. The transitions and rewards are perturbed, and there is no down action available to the agent. There is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right. The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$. We visualize the original Minefield, represented as a graph, and the abstract Minefield in ~\ref{ref:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
\end{figure}

% Subsection: Random.
\subsection{Random}

The Random MDP domain we consider is as follows. There are $N$ states, and $K$ actions. For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$. The Random MDP and its compression are visualized in Figure~\ref{fig:minefield-visual}.

% Random Compression Visuals
\begin{figure}
\subfigure[Ground Random]{
\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
\subfigure[Abstract Random]{
\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
\end{figure}

### 2016-02-03 paper/conclusion.tex
PUSHPUSHPUSH

--- 2015-12-03 paper/approximate_state_abstraction.tex
@@
-\documentclass[11pt]{article}
-\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
-\usepackage{aaai}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\title{Approximate State Abstraction}
-\author{David Abel, D. Ellis Hershkowitz, Michael Littman}
-\date{}                                           % Activate to display a given date or no date
-
-% --- Note Commands ---
-\usepackage{color}
-\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
-\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}
-
-\begin{document}
-\maketitle
-
-% --- ABSTRACT ---
-\begin{abstract}
-The combinatorial explosion that plagues planning and reinforcement learning algorithms can be reversed using abstraction.
-For instance, prohibitively difficult robotics task representations can be condensed so that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that preserves near optimal behavior.
-Reinforcement learning agents using these abstractions may treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present preliminary results and directions for future work.
-
-Abstraction lies at the heart of computation.
-In this work, we demonstrate that the combinatorial explosion central to many issues in artificial intelligence can be reversed using effective abstraction methods.
-We extend the framework of state abstraction proposed by (Lihong et.
-al.
-2005) to allow for approximately optimal state abstraction, and demonstrate that, in ideal scenarios, this framework allows for arbitrary reduction in the sample complexity of learning in certain learning problem.
-We develop methods for creating abstract problem representations and prove that their solutions have bounded error on the original, un-abstracted problem.
-Furthermore, we provide visualizations of the abstracted problems.
-
-\end{abstract}
-
-% --- SECTION: Introduction ---
-\section{Introduction}
-
-\begin{itemize}
-\item Solving MDPs is P-Complete, where the dominant factor is $|\mathcal{S}|$.
-\item Sample complexity is {\it also} dominated by $|\mathcal{S}|$.
-\item So, in order to make MDPs with large $|\mathcal{S}|$ tractable, we can reduce them to a simpler form.
-\item In this work we show that compressing MDPs in a particular way allows for the transfer of bounded-error solutions between the compressed MDP and ground MDP.
-\item Q: Why approximate?
-\item A: Approximate can compress strictly more than compression based on equality
-\item A: Approximate compression requires the type of knowledge that we could imagine learning (i.e.. approximate knowledge)
-\end{itemize}
-
-% --- SECTION: Background ---
-\section{Background}
-
-% Quick MDP blurb
-
-% Previous state aggregation stuff?
-
-% --- SECTION: Related Work ---
-\section{Related Work}
-
-% Lihong
-
-% Nan/Lihong
-
-% Approximate bisimulation
-
-% Other folks...
-
-% --- SECTION: State Abstraction ---
-\section{Approximate State Abstraction}
-
-% Explain each of the Phi's
-% Subsections for proofs for each phi
-\dnote{Insert lemma for each phi as their subsection}
-
-% Subsection: Phi_M
-\subsection{$\Phi_M$}
-
-% Subsection: Phi_Q
-\subsection{$\Phi_Q^*$}
-
-% Subsection: Phi_D
-\subsection{$\Phi_D$}
-
-% Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-% --- SECTION: Example Domains ---
-\section{Example Domains}
-
-\subsection{UpWorld}
-
-\dnote{As part of upworld we can include the result about the unbounded improvement in sample complexity}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-\subsection{NChain}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-\subsection{Trench}
-
-% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP
-
-% --- SECTION: Conclusion ---
 \section{Conclusion}
@@
 \end{itemize}
-\item 
+\item POMDP and abstraction
 \end{enumerate}
-
-% --- BIBLIOGRAPHY ---
-\bibliographystyle{aaai}
-\bibliography{state_abs}
-
-\end{document}

### 2016-02-03 paper/results_discussion.tex
Updated visuals for Minefield and combined figures into single SUPER figure.

@@
 \centering
+
 \subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
+\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}
+}
+\subfigure[NChain]{
+\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
+}
+
 \subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}
+}
+\subfigure[Taxi]{
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
+}
+
 \subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. Num States}
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Minefield]{
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+}
+
+\subfigure[RandomStates]{
+\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[RandomVal]{
+\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+}
+
+\label{fig:main results}
+\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
 \end{figure}
-
-% Figure: Epsilon vs. Error in Abstract Value Function
-\begin{figure}
-\subfigure[NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
-\subfigure[Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\subfigure[Random]{
-\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
-\label{fig:eps-states}
-\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
-\end{figure}

### 2016-02-03 Workspace and Code/stateAbstraction/src/experiments/EpsilonExperiments.java

@@ -47,11 +47,11 @@ public class EpsilonExperiments {
 	static String resultsDir = filePath + "/src/plotting/";
 
 	// Iterate over epsilon and compute the number of states.
-	final static double startEpsilon = 0.15;
-	final static double endEpsilon = 0.25;
-	final static double epsilonIncrement = 0.01;
-	final static int numTrials = 3;
-	final static String task = "MINEFIELD"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
+	final static double startEpsilon = 0;
+	final static double endEpsilon = 0.04;
+	final static double epsilonIncrement = 0.001;
+	final static int numTrials = 50;
+	final static String task = "TAXI"; // ALL, NCHAIN, TRENCH, TAXI, UPWORLD, RANDOM, MINEFIELD
 	final static boolean clearOldResults = false; //IF THIS IS TRUE, WILL DELETE ALL OLD ACCUMULATED RESULTS
 
 	/**

### 2016-02-03 paper/example_domains.tex
Updated visuals for Minefield and combined figures into single SUPER figure.
Discussion of results now written. Still need to explain plots.

@@
 \section{Example Domains}
-
-\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}
-
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains.
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
+To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on four domains -- NChain, Taxi, Minefield and Random MDP, which we dub ``Random".
+These domains were selected for the variety they offer -- Nchain is relatively simple domain, Taxi is goal-based and hierarchical in nature, Minefield is stochastic and Random MDP has a high number of near-optimal behavior.
 
@@
 In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).
-
-\dnote{One thing we want to add is a description of how diverse these domains are!}
-\dnote{Also put in a note that we're using a uniform weighting scheme}
+In some abstract MDPs, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were ignored).
 
@@
 \label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
+\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=.8$}
 \end{figure}

### 2016-02-03 paper/introduction.tex
Discussion of results now written. Still need to explain plots.

@@
 % Approximate abstraction
-In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
+The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
 Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.

### 2016-02-03 paper/results_discussion.tex
Discussion of results now written. Still need to explain plots.

@@
 
+%Explanation of what abstraction is used
+We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
+More specifically, we relate $\epsilon$ to:
+\begin{equation}
+|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
+\end{equation}
+For different values of $\epsilon$.
+
+\dnote{Also put in a note that we're using a uniform weighting scheme}
+\enote{Also put in a note how we're randomly choosing a Q*}
+%Explain plots
 Here we discuss the results shown in states blah blah \dnote{Description of this section}.
 
-\begin{itemize}
-\item For $\epsilon > 0$, there are extremely useful abstractions to be made.
-Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP).
-This hits the learnable point.
-\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
-\item Possibly talk about stochasticity (low priority)
-\item Explain Random behavior, smooth interpolation, mention randomness, etc.
-\item Describe plots a bit (what is the y-axis?)
-\end{itemize}
+%Discuss results
+Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis of learnable and useful state aggregation criteria.
+In both NChain and Minefield, we observe that despite increasing $\epsilon$ to reduce the number of states which must be planned over, optimal behavior is either fully maintained (NChain) or optimal behavior is very nearly maintained (Minefield).
+Similarly for Taxi and $\epsilon$ between $.02$ and $.025$ we observe a reduction in the number of states that must be planned over while value is fully maintained.
+After $.025$, increased reduction in state space size comes at a cost of value.
+Lastly, as $\epsilon$ is increased Random smoothly reduces the number of abstract states which must be planned over with a corresponding cost in the value of the derived policy.
 
-% Figure: Epsilon vs. #States for all three sample domains.
+Our experimental results also demonstrate a noteworthy contrast between approximate state abstraction on goal-based \acp{MDP} and random \acp{MDP}.
+Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both precipitously fall off.
+We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once certain information critical for optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is rendered entirely unattainable.
+Conversely, in Random a great deal of near-optimal policies are available to the agent.
+Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost in the state aggregation.
+
+% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. Value for all four sample domains.
 \begin{figure}
@@
 
+\subfigure[Minefield]{
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Minefield]{
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+}
+
 \subfigure[Taxi]{
@@
 
-\subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
-}
-\subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
-}
-
-\subfigure[RandomStates]{
+\subfigure[Random]{
 \includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
 }
-\subfigure[RandomVal]{
+\subfigure[Random]{
 \includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
@@
 
-\label{fig:main results}
+\label{fig:main_empirical_results}
 \caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}

### 2016-02-03 paper/theory_results.tex
Discussion of results now written. Still need to explain plots.
prepping for merge

@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
+There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{mult}}$ and $\ep_{\text{bolt}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
 \begin{equation}
@@
 \end{equation}
-
 \end{thm}
@@
 % zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
+% "The" q function is the optimal one.
 

### 2016-02-03 paper/results_discussion.tex

@@
 \section{Approximate Abstraction on Example Domains}
+%Explanation of what abstraction is used
+We run experiments on aggregation functions the $\ep{Q^*}$ abstraction.
+For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\ep{Q^*}$ criteria.
+The order in which ground states are selected and then greedily added is randomized so there is randomization across trials.
+Every ground state is equally weighted in its abstract state.
 
-%Explanation of what abstraction is used
-We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP.
-More specifically, we relate $\epsilon$ to:
-\begin{equation}
-|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
-\end{equation}
-For different values of $\epsilon$.
-
-\dnote{Also put in a note that we're using a uniform weighting scheme}
-\enote{Also put in a note how we're randomly choosing a Q*}
-%Explain plots
-Here we discuss the results shown in states blah blah \dnote{Description of this section}.
+%Explanation of what plots done
+For each domain we report two quantities as a function of epsilon in Figures \ref{fig:main_empirical_results1} and \ref{fig:main_empirical_results2}.
+First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$.
+The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
+Second, we report the value under the abstract policy of the initial ground state.
+50 Trials are gathered for each data point \enote{except ones where it doesn't matter (nChain and Minefield) -- is this worth noting?}
 
@@
 
-% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. Value for all four sample domains.
+\enote{Should we regenerate plots for nChain so it has CIs to match other plots?}
+% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
 \begin{figure}
+\label{fig:main_empirical_results1}
 \centering
@@
 
+\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
+\end{figure}
+
+% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
+\begin{figure}
+\label{fig:main_empirical_results2}
+\centering
 \subfigure[Taxi]{
@@
 
-\label{fig:main_empirical_results}
 \caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}

### 2016-02-03 paper/results_discussion.tex
merging results updates

@@
 %Explanation of what plots done
-For each domain we report two quantities as a function of epsilon in Figures \ref{fig:main_empirical_results1} and \ref{fig:main_empirical_results2}.
-First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$.
+For each domain we report two quantities as a function of epsilon.
+First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
 The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
-Second, we report the value under the abstract policy of the initial ground state.
-50 Trials are gathered for each data point \enote{except ones where it doesn't matter (nChain and Minefield) -- is this worth noting?}
+Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}.
+200 Trials are run for each data point.
 
@@
 Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis of learnable and useful state aggregation criteria.
-In both NChain and Minefield, we observe that despite increasing $\epsilon$ to reduce the number of states which must be planned over, optimal behavior is either fully maintained (NChain) or optimal behavior is very nearly maintained (Minefield).
-Similarly for Taxi and $\epsilon$ between $.02$ and $.025$ we observe a reduction in the number of states that must be planned over while value is fully maintained.
+In both NChain and Minefield, we observe that despite increasing $\epsilon$ to reduce the number of states which must be planned over, optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
+Similarly for Taxi and $\epsilon$ between $.02$ and $.025$ we observe a reduction in the number of states in the Abstract MDP while value is fully maintained.
 After $.025$, increased reduction in state space size comes at a cost of value.
-Lastly, as $\epsilon$ is increased Random smoothly reduces the number of abstract states which must be planned over with a corresponding cost in the value of the derived policy.
+Lastly, as $\epsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states which must be planned over with a corresponding cost in the value of the derived policy.
 
-Our experimental results also demonstrate a noteworthy contrast between approximate state abstraction on goal-based \acp{MDP} and random \acp{MDP}.
-Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both precipitously fall off.
-We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once certain information critical for optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is rendered entirely unattainable.
-Conversely, in Random a great deal of near-optimal policies are available to the agent.
+Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}.
+Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically.
+We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
+Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
 Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost in the state aggregation.

### 2016-02-03 paper/background.tex
Starting to unify notation

@@
 
-% Abstract policy in ground.
-In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
-\begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
-\end{equation}
-\dnote{I don't think this is right. Should be the max action? Or am I confused? My reading of the Q function from above is then possibly confused...}
-
 %\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}

### 2016-02-03 paper/theory_results.tex
Starting to unify notation

--- 2016-02-02 paper/theory_results.tex
@@
 Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity, model similarity (that is, $\mathcal{T}$ and $\mathcal{R}$), and similarity between distributions over $Q^*$, for both multinomial and Boltzmann distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
+In particular, we demonstrate that abstractions based on $Q^*$ similarity (\ref{sec:Q*}), model similarity (\ref{sec:model}), and similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
 
-In general, our proof strategy for each of the included results is as follows:
-\begin{itemize}
-\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-\end{itemize}
+%In general, our proof strategy for each of the included results is as follows:
+%\begin{itemize}
+%\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
+%\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
+%\end{itemize}
 
 % Explanation of the above.
-The first statement is relating Q values defined over the ground MDP with Q values defined over the abstract MDP, while the second statement is comparing the optimal Q values in the ground MDP, with the Q values in the ground MDP under the abstract policy.
+%The first statement is relating Q values defined over the ground MDP with Q values defined over the abstract MDP, while the second statement is comparing the optimal Q values in the ground MDP, with the Q values in the ground MDP under the abstract policy.
 This is because our learners will solve for the optimal policy in the abstract, and use it in the ground MDP by mapping each ground state to its abstract state and querying the abstract policy for behavior.
 That is:
-\begin{equation}
-\pi_G(s) = \pi_A(\phi(s))
-\end{equation}
+%\begin{equation}
+%\pi_G(s) = \pi_A(\phi(s))
+%\end{equation}
 
@@
 
-We now introduce some additional notation to formally discuss these results.
+We now introduce some additional notation to formally discuss these results:
 
-{\bf $\ep_f$ definition:} Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
+% Abstract policy in ground.
+We are interested in how the optimal policy in the abstract \ac{MDP} performs in the ground \ac{MDP}.
+To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
+Specifically:
+\begin{equation}
+V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
+\end{equation}
+\dnote{I don't think this is right. Should be the max action? Or am I confused? My reading of the Q function from above is then possibly confused...}
+
+\begin{defn}
+Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}
@@
 \end{equation}
+\end{defn}
 
 That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy this criterion.
+Note that, for any $f$, there are many functions that satisfy the $\ep_f$ criterion.
 
@@
 \subsection{Optimal Q Function: $\ep_{Q^*}$}
+\label{sec:Q*}
 
@@
 \label{clm:optAbsActionNearOptGround}
-The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal.
+The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:
 \end{clm}
@@
 \subsection{Model Similarity: $\ep_{model}$}
+\label{sec:model}
 
@@
 
+% Subsection: Boltzmann over Optimal Q
+\enote{Motivate Boltzmann + multinomial}
+
+\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
+\label{sec:boltz}
+
+Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
+\begin{multline}
+\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
+\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
+\end{multline}
+
+{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some constant positive $k \in \mathbb{R}$::
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq 
+\epsilon:
+\end{equation}
+
+{\bf Proof Sketch:}
+
+\dnote{Proof sketch}
+
+\dnote{(Probably put full proofs in appendix if we have room?}
+
 % Subsection: Multinomial over Optimal Q
-\enote{If not here, we should have some motivation for multinomial (and boltz)}
 \subsection{Multinomial over Optimal Q: $\ep_{mult}$}
+\label{sec:mult}
 
@@
 {\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-% Subsection: Boltzmann over Optimal Q
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
-
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
-\begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
-\end{multline}
-
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some constant positive $k \in \mathbb{R}$::
-\begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
-\end{equation}
-
-{\bf Proof Sketch:}
-
-\dnote{Proof sketch}
-
-\dnote{(Probably put full proofs in appendix if we have room?}
-
-% There are at least four classes of functions:
-% 1 \phi_q^*
-% 2 \phi_model
-% 3 \phi_mult
-% 4 \phi_bolt
-
-% Explain each of the Phis
-
-% One theorem, each separate phi is its own lemma.
-
-% Proof of Q^*
 

### 2016-02-03 paper/background.tex
Added new definition command and starting to unify notation more

@@
 \end{equation}
+\enote{This ins't right -- should be a prob distribution over ground states of a \textit{single} abstract state -- not all ground states.}
 
@@
 
-\begin{defn}
+\bdefn{$\phi_{Q^*}$}
 A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
@@
 \end{equation}
-\end{defn}
+\edefn
 
-\begin{defn}
+\bdefn{$\phi_{model}$}
 A model-irrelevance abstraction, $\phi_{model}$, is one such that:
@@
 \end{multline}
-\end{defn}
+\edefn
 

### 2016-02-03 paper/conclusion.tex

@@
 \section{Conclusion}
+
+In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy in the abstract \ac{MDP}.
+This approach is appealing for two reasons.
+First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
+Second, since the state-aggregation criteria are relaxed to approximate equality, methods that employ these techniques are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
+We evaluate our approaches empirically on four different \acs{MDP}, providing visuals of the compression, as well as displaying the relationship between $\epsilon$ and the degree of compress, as well as the value of the abstract policy.
+We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.
+
+There are many directions for future work.
+First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting.
+\citeauthor{ortner2013adaptive} previously proposed this strategy by combining the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}, and are curious how this strategy will fair under the proposed approximate abstraction families introduced in this paper.
+Learning these abstraction functions also poses interesting implications for the exploration problem.
+If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,
+
+We are also interested in approximate relaxations of additional classes of abstraction functions, and in characterizing the necessary conditions for an abstraction that will preserve any notion of optimality.
+In particular, the abstraction class $\phi_{a^*}$ discussed by~\cite{li2006towards}, which is guaranteed to collapse states that share the optimal action and the optimal actions $Q^*$ value.
+To do this properly, one must apply confidence intervals to the event of each action's optimality, in addition to relaxing $Q^*$ equivalence to similarity.
+This abstraction class may also introduce compelling connections to temporal abstractions, including Options, discussed at length in reinforcement learning and planning \dnote{Options citations}.
+We investigated the use of options in the Taxi domain under $\phi_{a^*}$, and found a negligible difference in the degree and quality of compression compared to the compression without Options.
+In future work, we are interested in characterizing the relationship between temporal abstractions and approximate abstraction.
+Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
 

### 2016-02-03 paper/theory_results.tex

@@
 We are interested in how the optimal policy in the abstract \ac{MDP} performs in the ground \ac{MDP}.
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior.
-Specifically:
+
+\begin{defn}
+To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
 \begin{equation}
@@
 \end{equation}
-\dnote{I don't think this is right. Should be the max action? Or am I confused? My reading of the Q function from above is then possibly confused...}
+\end{defn}
 
@@
 
+\begin{defn}
+Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
+\end{defn}
+
+\begin{defn}
+Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
+\end{defn}
+
 We now introduce the main result of the paper.
@@
 \begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
+\forall_{s \in \mathcal{S}_G}: | V_G^{\pi^*_G}(s) - V_G^{\pi^*_{A}}(s) | \leq poly(\epsilon).
 \end{equation}
@@
 We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.
-
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.
 

### 2016-02-03 paper/background.tex
beep
Abstraction notation in background now all nicely partitioned into definitions

@@
 
+\bdefn{$M_G$, $M_A$}
 We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
 Consequently, this mapping induces an abstract MDP.
-Let:$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
+Let $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
+\edefn
 
 % States
+\bdefn{$\mcS_A$, $\phi$}
 The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
@@
 \end{equation}
+\edefn
 
-Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.
+\bdefn{$G$}
+Given a $\phi$, each ground state has associated with it the ground states with which it is aggregated.
+Similarly, each abstract state has its constituent ground states.
+We let $G$ be the function that retrieves these states:
+\begin{equation}
+G(s)=
+\begin{cases}
+\{g \in \mcS_G \mid \phi(g) = \phi(s) \}& s \in \mcS_G\\
+\{g \in \mcS_G \mid \phi(g)=s \}& s \in \mcS_A
+\end{cases}
+\end{equation}
+\edefn
 
-% Reward
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-\dnote{Need to change the subscript here.}
-% zzz g in phi(s) seems like a type error, no?
+The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
+We make no assumptions about the weighting scheme, except that for each abstract state, the weighting is a convex combination across all ground states.
 
-% Transition
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
-\end{equation}
-\noindent where $
-s, s' \in \mathcal{S}_A
-$.
-
+\bdefn{$\omega(s)$}
 We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$.
@@
 \begin{equation}
-\left(\sum_{s \in \mathcal{S}_G} \omega(s)\right) = 1,\hspace{6mm} \forall_{s \in \mathcal{S}_G} \omega(s) \in [0,1]
+\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \texttt{ and }\hspace{6mm}  \omega(s) \in [0,1]
 \end{equation}
-\enote{This ins't right -- should be a prob distribution over ground states of a \textit{single} abstract state -- not all ground states.}
+\edefn
+
+% Reward
+\bdefn{$\mcR_A$}
+The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
+\begin{equation}
+\mathcal{R}_A(s,a) = \sum_{g \in G(s)} \mathcal{R}_G(g,a) \omega(g) .
+\end{equation}
+\edefn
+
+% Transition
+\bdefn{$\mcT_A$}
+The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
+\begin{equation}
+\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g),
+\end{equation}
+\edefn
 

### 2016-02-03 paper/theory_results.tex
Abstraction notation in background now all nicely partitioned into definitions

@@
 Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on $Q^*$ similarity (\ref{sec:Q*}), model similarity (\ref{sec:model}), and similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
+In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
 
@@
 
-\begin{defn}
-To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
+\bdefn{$\pi_A^*$}
+To evaluate a the optimal abstractpolicy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
 \begin{equation}
@@
 \end{equation}
-\end{defn}
+\edefn
 
@@
 
-\begin{defn}
+\bdefn{$Q_G$, $V_G$}
 Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
-\end{defn}
+\edefn
 
-\begin{defn}
+\bdefn{$Q_A$, $V_A$}
 Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
-\end{defn}
+\edefn
 

### 2016-02-03 paper/conclusion.tex

@@
 
+% Summary of contributions.
 In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy in the abstract \ac{MDP}.
@@
 
+% Future work.
 There are many directions for future work.
-First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting.
-\citeauthor{ortner2013adaptive} previously proposed this strategy by combining the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}, and are curious how this strategy will fair under the proposed approximate abstraction families introduced in this paper.
-Learning these abstraction functions also poses interesting implications for the exploration problem.
+First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}.
+Learning abstraction functions online also has interesting implications for the exploration problem.
 If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,
@@
 Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
-
-% Summary
-
-% Future Work
-\begin{enumerate}
-\item Learning Phi
-\begin{itemize}
-\item Exploration vs. Exploitation problem is different while trying to learn Phi
-\end{itemize}
-\item Compressibility
-\begin{itemize}
-\item Relationship between approximate abstract and compressibility
-\end{itemize}
-\item POMDP and abstraction
-\end{enumerate}

### 2016-02-03 paper/background.tex
Updated taxi figure for 200 trials

@@
 \subsection{\acp{MDP} and Sequential Decision Making}
+\enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
 An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.

### 2016-02-03 paper/results_discussion.tex
Updated taxi figure for 200 trials

@@
 %Explanation of what plots done
-For each domain we report two quantities as a function of epsilon.
+For each domain we report two quantities as a function of epsilon with \%95 confidence bars.
 First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
@@
 \subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
 }
 \subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
 }

### 2016-02-03 paper/theory_results.tex
Lemma 3 and 4 proofs added

@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{mult}}$ and $\ep_{\text{bolt}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
+There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
 \begin{equation}
@@
 
-% Subsection: Boltzmann over Optimal Q
-\enote{Motivate Boltzmann + multinomial}
-
 \subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
@@
 
-Similarly to the multinomial abstraction, we let $\phi_{bolt}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
+Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal Q values as equivalent.
+This family of abstractions is appealing as the Boltzmman distribution over Q-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
+
+We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$ satisfies:
 \begin{multline}
 \ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}}\right| \leq \epsilon
+\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_2,a)}}{\sum_b e^{Q^*(s_2,b)}}\right| \leq \epsilon
+\label{eq:phi_bolt}
 \end{multline}
 
-{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some constant positive $k \in \mathbb{R}$::
+We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq 
-\epsilon:
+\sum_b e^{Q^*(s_1,b)} - \sum_b e^{Q^*(s_2,b)} \leq k*\epsilon
+\label{eq:bolt_denom}
 \end{equation}
+
+\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$::
+\begin{equation}
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
+\end{equation}
+\label{lma:bolt_lemma}
+\end{lma}
+
+We prove Lemma~\ref{lma:bolt_lemma} by using the approximation for $e^x$:
+\begin{equation}
+1 + x + \delta = e^x
+\label{eq:e_to_x_approx}
+\end{equation}
+Where $\delta$ is the error associated with the approximation.
 
@@
 
-\dnote{Proof sketch}
+By the approximation in Equation~\ref{eq:e_to_x_approx} and the assumption in Equation~\ref{eq:bolt_denom}:
+\begin{align*}
+|\frac{1 + Q(s_1,a) + \delta_1}{\sum_j e^{Q(s_1,a_j)}} - \frac{1 + Q(s_2,a) + \delta_2}{\sum_j e^{Q(s_1,a_j)} \pm k\epsilon}| \leq \epsilon
+\end{align*}
 
-\dnote{(Probably put full proofs in appendix if we have room?}
+It follows that:
+\begin{equation}
+|Q(s_1,a) - Q(s_2,a)| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
+\label{eq:bolt_qs}
+\end{equation}
+
+Consequently, we can consider $\widetilde{\phi}_{bolt}$ as a type of $\epQ$, where the difference in Q values is bounded by: $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
+The Lemma follows directly from Lemma~\ref{lma:Q*}.
 
@@
 
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies:
+We consider a multinomial distribution over $Q^*$ for similar reasons as the Boltzmann. We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
 \begin{multline}
@@
 
-\dnote{We also need to add the point about the denominator bound...}
+We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
+\begin{equation}
+|\sum_i Q(s_1,a_i) - \sum_j Q(s_2,a_j) | \leq k\epsilon
+\end{equation}
 
-{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some constant positive $k \in \mathbb{R}$:
+\begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
+\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
 \end{equation}
+\end{lma}
 
@@
 
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
+The proof follows a near identical strategy to that of Lemma~\ref{lma:bolt_lemma}.
+
+\dnote{Bounds for multi and bolt suspisiously similar. Double check math}
 

### 2016-02-03 paper/theory_results.tex
Unified notation up to Theorem 1

--- 2016-02-03 paper/theory_results.tex
@@
 
-We now introduce some additional notation to formally discuss these results:
+We now introduce some additional notation to formally discuss these results.
 
@@
 We are interested in how the optimal policy in the abstract \ac{MDP} performs in the ground \ac{MDP}.
+As such we formally define the policy in the ground \ac{MDP} derived from optimal behavior in the abstract \ac{MDP}:
 
-\bdefn{$\pi_A^*$}
-To evaluate a the optimal abstractpolicy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
+\bdefn{$\pi_{GA}$}
+Given a $s \in \mcS_G$ and a state aggregation function, $\phi$, 
 \begin{equation}
-V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
+\pi_{GA}(s)=\pi_A^*(\phi(s))
 \end{equation}
+where $\pi_A^*$ is the optimal policy in the abstract \ac{MDP}.
 \edefn
 
-\begin{defn}
+We now define classes of abstraction based on functions state, action pairs.
+\bdefn{$\ep_f$}
 Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
@@
 \end{equation}
-\end{defn}
+\edefn
 
 That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
-Note that, for any $f$, there are many functions that satisfy the $\ep_f$ criterion.
 
@@
 \begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V_G^{\pi^*_G}(s) - V_G^{\pi^*_{A}}(s) | \leq poly(\epsilon).
+\forall_{s \in \mathcal{S}_G}: | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(\epsilon).
 \end{equation}
+Where $\pi_G^*$ is the optimal policy in the ground \ac{MDP}.
 \end{thm}
-
-\enote{Consider moving definition of $V^{\pi^*_{A}}(s)$ so it's fresh for reader.}
-% zzz Also, I think it might be worth spelling out the poly(eps) part. Seems incomplete this way.
 
@@
 % Q* Lemma
-Recall that $Q^*$ is a function on $\mathcal{S}_G \times \mathcal{A}$ that satisfies \enote{$Q^*$ definition}.
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
+We consider an approximate version of the $Q^*$-irrelevance abstraction. An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
 \begin{equation}

### 2016-02-03 paper/theory_results.tex
updating conc

--- 2016-02-03 paper/theory_results.tex
@@
 
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
+We note that one natural way of approximating $\phi_{a^*}$ from , in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
 A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.

### 2016-02-03 paper/theory_results.tex
Notation for Lemma 1 fixed

--- 2016-02-03 paper/theory_results.tex
@@
 
+\bdefn{$\pi_A^*$, $\pi_G^*$}
+We let $\pi_A^* : \mcS_A \rightarrow \mcA$ and $\pi_G^* : \mcS_G \rightarrow \mcA$ stand for the optimal policies in the abstract and ground \acp{MDP} respectively.
+\edefn
+
 % Abstract policy in ground.
@@
 \end{equation}
-where $\pi_A^*$ is the optimal policy in the abstract \ac{MDP}.
 \edefn
@@
 \bdefn{$Q_G$, $V_G$}
-Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
+Let $Q_G = Q^{\pi_G^*} : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R} $ and $V_G = V^{\pi_G^*}: \mathcal{S}_G \rightarrow \mathbb{R} $ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
 \edefn
@@
 \bdefn{$Q_A$, $V_A$}
-Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
+Let $Q_A  = Q^{\pi_A^*}: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A  = V^{\pi_A^*}: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
 \edefn
@@
 \end{equation}
-Where $\pi_G^*$ is the optimal policy in the ground \ac{MDP}.
 \end{thm}
@@
 \begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q^*(s_1, a) - Q^*(s_2, a)\right| \leq \epsilon.
+\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \epsilon.
 \end{equation}
@@
 \label{lma:Q*}
-When $\ep_{Q^*}$ is used to create the abstract state space $\mathcal{S}_A$:
+When $\ep_{Q^*}$ is used to create the abstract state space $\mcS_A$:
 \begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G}: | V^{\pi_G^*}(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
 \end{equation}
@@
 \textbf{Proof:}
-We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.
-
-% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
-% "The" q function is the optimal one.
-
-Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$, the set of ground states that correspond to abstract state $s$.
-
+\enote{I would like a quick overview of the proof here if nobody objects.}
 % Claim 1:
 \begin{clm}
-Q-Values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}:
+\label{clm:closeQs}
+Optimal $Q$ values in the abstract \ac{MDP} closely resemble optimal $Q$ values in the ground \ac{MDP}:
 \begin{equation}
@@
 \end{equation}
-and
 \begin{equation}
-\mathcal{T}_T(s,a,s') = \begin{cases}
-\mathcal{T}_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right],& T = 1, \\
-\mathcal{T}_A(s,a,s'),& \text{o/w}.
+\mcT_T(s,a,s') = \begin{cases}
+\mcT_G(s,a,s'),& T \leq 0, \\
+\underset{{g \in G(s)}}{\sum}\left[w(g)\mcT_G(g, a, s')\right],& T = 1, \\
+\mcT_A(s,a,s'),& \text{o/w}.
 \end{cases}
@@
 
-It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
+It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
 % zzz too long... needs to be broken up.
-% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
-% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
-\dnote{Let's put a reminder of the weighting scheme here}
+
 \begin{equation}
@@
 	   Q_G(s, a) &  T=0\\
-	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
+	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
 	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a) &\text{o/w}
@@
 \begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
 \end{equation}
-that is, the Q function remains relatively unchanged over time.
 
 % Base Case t=0
-\textit{Base Case: $T = 0$}
-When $T = 0$, $Q_T = Q_0$, so the result trivially follows.
+\textit{Base Case: $T = 0$}\\
+When $T = 0$, $Q_T = Q_G$, so the result trivially follows.
 % Base Case t=1
-\textit{Base Case: $T = 1$}
+\textit{Base Case: $T = 1$}\\
 \begin{align*}
-&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
+&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
 \end{align*}
@@
 \begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a).
+&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),\\
+&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_G(s_G, a).
 \end{align*}
@@
 \begin{equation}
-Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T}\epsilon \gamma^t
+\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
 \end{equation}
@@
 \begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
 \end{equation}
@@
 
-We denote $\epQ(s_G)$ as $s_A$. By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
+We denote $\epQ(s_G)$ as $s_A$.
+
+By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
+
 \begin{multline*}
-Q_T(s_A, a) = \sum_{g \in X(s_A)}w(g)* \\ 
+Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)* \\ 
  \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
@@
 \begin{multline*}
-\leq \sum_{g \in X(s_A)}w(g) * \\ \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}(Q_0(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
+\leq \sum_{g \in G(s_A)}w(g) * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
 \end{multline*}
@@
 \begin{equation*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_0(g,a)\right]
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_G(g,a)\right]
 \end{equation*}
@@
 \begin{align*}
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_0(s_G, a)
+&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a)\\
+&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_G(s_G, a)
 \end{align*}
@@
 \begin{equation*}
-\left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
+\left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
 \end{equation*}
 
-Since $s_G$ and $s_A$ are arbitrary and $Q_0=Q_G$ we conclude
+Since $s_G$ and $s_A$ are arbitrary we conclude
 \begin{equation}
-\forall_{T, g \in \mathcal{S}_G, a} |Q_0(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
 \end{equation}
@@
 As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
+
+%Claim 2
+\begin{clm}
+\label{clm:optAbsActionNearOptGround}
+The optimal action in the abstract MDP has a Q-value in the ground which is nearly optimal:
 
@@
 
-%Claim 2
-\begin{clm}
-\label{clm:optAbsActionNearOptGround}
-The optimal action in the abstract MDP has a Q value in the ground which is nearly optimal:
-\end{clm}
+That is, we prove that
 
@@
 \end{equation}
+\end{clm}
 
-By Equation \ref{eq:Q*Claim1}
+By Claim \ref{clm:closeQs}
 \begin{align}
@@
 
-Lastly again by Equation \ref{eq:Q*Claim1} we know
+Lastly again by Claim \ref{clm:closeQs} we know
 \begin{align}
@@
 \begin{clm}
-We conclude Lemma \ref{lma:Q*} by Claim \ref{clm:optAbsActionNearOptGround}.
+Lemma \ref{lma:Q*} follows from Claim \ref{clm:optAbsActionNearOptGround}.
 \end{clm}
@@
 \pi_G^*(s), \text{if $t<=0$}\\
-\pi_A^*(\ep(s)), \text{if $t > 0$}
+\pi_{GA}(s), \text{if $t > 0$}
 \end{cases}
@@
 
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
+For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ in the ground \ac{MDP} is as follows:
 \begin{multline*}
-V^{\pi_{A,t}}(s_G) = \\
-R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
+V_G^{\pi_{A,t}}(s_G) = \\
+R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
 \end{multline*}
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
+
 \textit{Base case: $t=0$}
 
-By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.
+By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$ so our bound trivially holds in this case.
 
@@
 \begin{equation}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
+V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 \begin{multline*}
-V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
+V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
 \end{multline*}
@@
 \begin{multline*}
-V^{\pi_{A,t}}(g, a) \geq R_G(s, \pi_{A,t}(g, a))\ + \\ \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
+V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
 \end{multline*}
@@
 %&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))
+&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G))
 \end{align*}
-Applying Equation \ref{eq:Q*Claim2} yields:
+Applying Claim \ref{clm:optAbsActionNearOptGround} yields:
 \begin{align*}
 &\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)
+&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
 \end{align*}
@@
 \begin{equation*}
-V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+V_G(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation*}
@@
 \begin{equation}
-\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
 
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
+Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
 
@@
 \begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
+\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
 \end{equation*}
@@
 \begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
+\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
 \end{equation*}

### 2016-02-03 paper/theory_results.tex
Added comment to axe absolute values
oh glob

--- 2016-02-03 paper/theory_results.tex
@@
 % Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from , in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
+%\subsection{Other Abstractions}
+%
+%We note that one natural way of approximating $\phi_{a^*}$ from , in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
 A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
 Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
+%
+%We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
+%
+%Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
 Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
+%
+%Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
+%
+%We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
 

### 2016-02-03 paper/theory_results.tex

--- 2016-02-03 paper/theory_results.tex
@@
 \end{thm}
+\enote{Axe the absolute values here and elsewhere}
 
@@
 
-% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).
+The proof follows a near identical strategy to that of Lemma~\ref{lma:bolt_lemma}.
+
+\dnote{Bounds for multi and bolt suspisiously similar. Double check math}
 
 % Subsection: Other Abstractions
-\subsection{Other Abstractions}
-
-We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
+%\subsection{Other Abstractions}
+%
+%We note that one natural way of approximating $\phi_{a^*}$ from , in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action.
 A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action.
 Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
-
-We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
-
-Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
+%
+%We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
+%
+%Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
 Furthermore, an MDP for which this is true is an awfully weird MDP...
-
-Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
-
-We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
+%
+%Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
+%
+%We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
 

### 2016-02-03 paper/conclusion.tex

@@
 There are many directions for future work.
+
+% Learning abs functions online.
 First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}.
+
+% Exploration is interesting.
 Learning abstraction functions online also has interesting implications for the exploration problem.
@@
 
-We are also interested in approximate relaxations of additional classes of abstraction functions, and in characterizing the necessary conditions for an abstraction that will preserve any notion of optimality.
-In particular, the abstraction class $\phi_{a^*}$ discussed by~\cite{li2006towards}, which is guaranteed to collapse states that share the optimal action and the optimal actions $Q^*$ value.
-To do this properly, one must apply confidence intervals to the event of each action's optimality, in addition to relaxing $Q^*$ equivalence to similarity.
-This abstraction class may also introduce compelling connections to temporal abstractions, including Options, discussed at length in reinforcement learning and planning \dnote{Options citations}.
-We investigated the use of options in the Taxi domain under $\phi_{a^*}$, and found a negligible difference in the degree and quality of compression compared to the compression without Options.
-In future work, we are interested in characterizing the relationship between temporal abstractions and approximate abstraction.
+% Necessary conditions.
+One question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
+the bound between the values under $\pi_G^*$, $\pi_{G,A}$ is less than $\textsc{VMax}$).
+In future work, we are interested in identifying these conditions.
+
+% Options/termporal abstraction
+In future work, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by Options, and approximate abstractions.
+Options have been discussed at length in reinforcement learning and planning \dnote{Options citations}.
+We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.
+
+% Compressibility
 Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.

### 2016-02-04 paper/theory_results.tex
Trying to get daves Lemma 3/4 commit
Unified notation for lemma 2

@@
 \enote{Axe the absolute values here and elsewhere}
+\enote{Unify the use of $\forall$ and ``:"s}
 
@@
 
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\phi_{model}$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
+Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
 \begin{multline}
 \epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR(s_1, a) - \mcR(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{g' \in X(s_A)}\mcT(s_1, a, g') - \mcT(s_2, a,g')\right| \leq \epsilon
+\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon \wedge\ \\
+\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon
 \end{multline}
-where $X(s_A) = \{ g' \in \mcS | \epM(g') = s_A \}$
-
-\enote{Do we want to make it clear that this is ground transitions and rewards?}
-
-\enote{Note that it is possible }
 
@@
 \label{lma:model}
-When $S_A$ is created using a function of the $\ep_{model}$ type:
+When $\mcS_A$ is created using a function of the $\ep_{model}$ type:
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
+\forall_{s \in \mcS_G} : | V_G(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
 \end{equation}
@@
 
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
+{\bf Proof:} Our proof proceeds as follows: we demonstrate that states aggregated under $\epM$ have $Q$-values all within a particular bound.
+Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$.
+Understanding $\epM$ as such abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
 
-Let $B$ stand for the maximum Q difference between any pair of ground states in the same abstract state under $\epM$:
+Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
 
 \begin{align*}
-B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
-=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
-& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|
+B = &\max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|\\
+&\text{Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.}\\
+=&\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
+& \gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
 \end{align*}
 \begin{multline*}
-\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)} \\ \left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]
+\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\ \left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) 		\max_{a'}Q_G({s_G}', a')	\right]
 \end{multline*}

### 2016-02-04 paper/results_discussion.tex
revamped intro, results, background a bit

@@
 \subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}
+\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
 }
 \subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
+\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
 }

### 2016-02-04 paper/theory_results.tex
Added some notes about Qmax
Added some notes

@@
 \enote{Axe the absolute values here and elsewhere}
+
 \enote{Unify the use of $\forall$ and ``:"s}
+
+\enote{Add for 0-1 normalized reward}
+
+\enote{Add note relating this all to Lihong for eps=0 and cut down the Lihong section}
 
@@
 
-% Q* Lemma
-We consider an approximate version of the $Q^*$-irrelevance abstraction. An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
+% Q* Lemma -- lemma 1
+We consider an approximate version of the $Q^*$-irrelevance abstraction.
+
+\bdefn{$\epQ$}
+An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
 \begin{equation}
@@
 \end{equation}
+\edefn
 
@@
 \begin{equation}
-\forall_{s \in \mcS_G}: | V^{\pi_G^*}(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G}: | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
 \end{equation}
@@
 \begin{equation*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\left[ w(g)\ Q_G(g,a)\right]
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right]
 \end{equation*}
@@
 
-% Subsection: Model Similarity
+% Subsection: Model Similarity -- lemma 2
 \subsection{Model Similarity: $\ep_{model}$}
@@
 
-Inspired by the model-irrelevance abstraction, we consider the approximate case. We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
+Inspired by the model-irrelevance abstraction, we consider the approximate case. 
+\bdefn{$\epM$}
+We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
 \begin{multline}
@@
 \end{multline}
+\edefn
 
@@
 \begin{equation}
-\forall_{s \in \mcS_G} : | V_G(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
+\forall_{s \in \mcS_G} : | V_G(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
 \end{equation}
@@
 
+\enote{Do we need to state what Q max is and that it is upper bounded by 1 over 1 minus gamma or is this common knowledge?}
+
 Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
@@
 
+\bdefn{$\phi_{bolt}$}
 We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$ satisfies:
@@
 \ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q^*(s_1,a)}}{\sum_b e^{Q^*(s_1,b)}} - \frac{e^{Q^*(s_2,a)}}{\sum_b e^{Q^*(s_2,b)}}\right| \leq \epsilon
+\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon
 \label{eq:phi_bolt}
 \end{multline}
+\edefn
 
@@
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
+\forall_{s \in \mcS_G} : | V^{\pi^*_G}(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
 \end{equation}
@@
 
-We consider a multinomial distribution over $Q^*$ for similar reasons as the Boltzmann. We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
+We consider a multinomial distribution over $Q^*$ for similar reasons as the Boltzmann.
+
+\bdefn{$\ep_{mult}$}
+We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
 \begin{multline}

### 2016-02-04 paper/theory_results.tex
Unified notation for all theory results yay

@@
 \begin{equation}
-\forall_{s \in \mcS_G} : | V_G(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
+\forall_{s \in \mcS_G} : | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
 \end{equation}
@@
 
-Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
@@
 
-Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal Q values as equivalent.
-This family of abstractions is appealing as the Boltzmman distribution over Q-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
+Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent.
+This family of abstractions is appealing as the Boltzmman distribution over $Q$-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
 
@@
 \begin{equation}
-\sum_b e^{Q^*(s_1,b)} - \sum_b e^{Q^*(s_2,b)} \leq k*\epsilon
+\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k*\epsilon
 \label{eq:bolt_denom}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} : | V^{\pi^*_G}(s) - V^{\pi_{GA}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
+\forall_{s \in \mcS_G} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
 \end{equation}
@@
 \begin{equation}
-1 + x + \delta = e^x
+ e^x = 1 + x + \delta  \approx 1 + x
 \label{eq:e_to_x_approx}
@@
 \begin{align*}
-|\frac{1 + Q(s_1,a) + \delta_1}{\sum_j e^{Q(s_1,a_j)}} - \frac{1 + Q(s_2,a) + \delta_2}{\sum_j e^{Q(s_1,a_j)} \pm k\epsilon}| \leq \epsilon
+|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\epsilon}| \leq \epsilon
 \end{align*}
@@
 \begin{equation}
-|Q(s_1,a) - Q(s_2,a)| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
+|Q_G(s_1,a) - Q_G(s_2,a)| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
 \label{eq:bolt_qs}
@@
 Consequently, we can consider $\widetilde{\phi}_{bolt}$ as a type of $\epQ$, where the difference in Q values is bounded by: $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
-The Lemma follows directly from Lemma~\ref{lma:Q*}.
+Lemma \ref{lma:bolt_lemma} follows directly from Lemma \ref{lma:Q*}.
 
@@
 
-We consider a multinomial distribution over $Q^*$ for similar reasons as the Boltzmann.
+We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
 
@@
 \ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)} - \frac{Q^*(s_1,a)}{\sum_b Q^*(s_1,b)}\right| \leq \epsilon
+\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon
 \end{multline}
@@
 \begin{equation}
-|\sum_i Q(s_1,a_i) - \sum_j Q(s_2,a_j) | \leq k\epsilon
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
+\forall_{s \in S_M} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
 \end{equation}
@@
 
-The proof follows a near identical strategy to that of Lemma~\ref{lma:bolt_lemma}.
+The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.
 

### 2016-02-04 paper/background.tex

--- 2016-02-03 paper/background.tex
@@
 \subsection{\acp{MDP} and Sequential Decision Making}
-An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that all reward functions are normalized to $[0,1]$.
+\enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
+An \ac{MDP} is a problem solved by a sequential decision making agent, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
+We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$.
+The solution to an \ac{MDP} is called a policy, denoted $\pi: \mathcal{S} \mapsto \mathcal{A}$.
 
-The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$.
-In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state.
-This goal policy is denoted $\pi^*$.
+The objective of an agent is to solve for the policy that maximizes its expected discounted reward from any state, denoted $\pi^*$.
 We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
@@
 \end{equation}
-
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively~\cite{kaelbling1996reinforcement}.
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively. For further background, see~\cite{kaelbling1996reinforcement}.
 

### 2016-02-04 paper/introduction.tex

@@
 % Existing work on state abstraction.
-Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+Thus, a key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
 These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
@@
 We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
-We then survey existing types in state abstraction as applied to sequential decision making.
-The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction.
+We then survey existing types of state abstraction as applied to sequential decision making.
+The following section introduces our primary result; bounds on the error guaranteed by four classes of approximate state abstraction.
 We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.

### 2016-02-04 paper/abstract.tex
abstract done

@@
 The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable.
-In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
-\ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences.
-We present theoretical guarantees of the quality of policies derived from four classes of approximate state abstraction.
-Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
+For instance, prohibitively difficult task representations can be condensed in such a way that essential information is preserved, and consequently, solutions are tractably computable.
+Because of the difficulty of acquiring perfect knowledge, agents must often perform approximate abstraction on the basis of incomplete knowledge.
+In this work, we investigate sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation.
+We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions.
+Additionally, we empirically demonstrate reduction in task complexity and bounded loss of optimality of behavior as knowledge becomes more approximate.
+
+%decreasing with degrees of incompleteness of knowledge in a variety of \acp{MDP}.
+%
+%reduction in task complexity at the cost of bounded increase in error of behavior.
+%
+%that the relationship between the degree of approximation and the degree of  achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
+
+%that achieves high degrees of compression while preserving near optimal behavior
+%In this work, we investigate a theory of approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior.
+
+% We fight exponentials with abstraction.

### 2016-02-04 paper/results_discussion.tex

@@
 %Explanation of what abstraction is used
-We run experiments on aggregation functions the $\ep{Q^*}$ abstraction.
-For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\ep{Q^*}$ criteria.
+We run experiments on aggregation functions the $\epQ$ abstraction.
+For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\epQ$ criteria.
 The order in which ground states are selected and then greedily added is randomized so there is randomization across trials.

### 2016-02-04 paper/abstract.tex
adding some changes to theory result

@@
 The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-For instance, prohibitively difficult task representations can be condensed in such a way that essential information is preserved, and consequently, solutions are tractably computable.
-Because of the difficulty of acquiring perfect knowledge, agents must often perform approximate abstraction on the basis of incomplete knowledge.
-In this work, we investigate sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation.
+Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
+However, perfect abstractions are often computationally intractable to compute and ineffective in environments where no two situations are exactly alike.
+For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.
+In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation.
 We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions.
 Additionally, we empirically demonstrate reduction in task complexity and bounded loss of optimality of behavior as knowledge becomes more approximate.
+
+% Old one:
+% Abstraction plays a fundamental role in learning.
+Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
+However, in natural environments, no two states are identical.
+This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
+
+%Because of the difficulty of acquiring perfect knowledge, agents must often perform approximate abstraction on the basis of incomplete knowledge.
+
+% There are a variety of attractive characteristics of approximate abstractions.
 

### 2016-02-04 paper/introduction.tex
adding some changes to theory result

@@
 Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
+Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant.
+Consequently, agents are able to solve considerably more complex problems than without the use of abstraction.
+However, perfect abstractions require complete knowledge that is often computationally intractable to compute.
+Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective.
+To overcome these issues, we investigate the space of approximate abstractions that enable agents to treat sufficiently similar states as identical.
 This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
+
+% What is approx abstraction, why good.
+%However, because of the difficulty of acquiring perfect knowledge, agents must often perform abstraction on the basis of incomplete knowledge. We call such abstractions {\it approximate}.
+
+%Agents are often faced with imperfect knowledge, so abstracting using complete knowledge is infeasible.
+However, agents may still perform abstractions by treating sufficiently similar situations as identical.
+We call such an abstraction {\it approximate}.
+
+%However, faced with imperfect knowledge, agents must often perform approximate abstractions on the basis of treating sufficiently similar situations as identical.
+
+% One like "natural environment", "states aren't identical" sentence.
+%However, in natural environments, no two situations are identical; approximate abstractions enable learning agents to treat sufficiently similar situations as equivalent.
+
+% One like "approx abstract because of approx knowledge"
+
+%This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
 
@@
 The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
+Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers three benefits.
 First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
 Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
+\dnote{Pick a version of this (either sentence 1 or 2)}
+Third, (1) approximate abstractions can achieve greater degrees of compression due to their relaxed criteria of equality.
+(2) In natural environments, no two states are identical, so approximate abstraction may be useful but exact abstraction is completely ineffective.
 

### 2016-02-04 paper/results_discussion.tex
Some random results discussion push

@@
 Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically.
-We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
+We attribute the sugdden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.

### 2016-02-04 paper/abstract.tex
intro abstract

@@
 Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
-However, perfect abstractions are often computationally intractable to compute and ineffective in environments where no two situations are exactly alike.
+However, perfect abstractions are often computationally intractable and ineffective in environments where no two situations are exactly alike.
 For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.
@@
 We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions.
-Additionally, we empirically demonstrate reduction in task complexity and bounded loss of optimality of behavior as knowledge becomes more approximate.
+Additionally, we empirically demonstrate that approximate abstractions lead to reduction in task complexity and bounded loss of optimality of behavior in a variety of environments.
+% Environments could also be tasks/problems/etc
+
+%as approximations become tighter, 
+% as knowledge becomes more approximate.
 

### 2016-02-04 paper/introduction.tex
intro abstract

--- 2016-02-04 paper/introduction.tex
@@
 Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems.
-However, in natural environments, no two states are identical.
+Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant.
+Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
+However, perfect abstractions require complete knowledge that is often computationally intractable.
+Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective.
+To overcome these issues we investigate the space of approximate abstractions that enable agents to treat sufficiently similar states as identical.
 This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
@@
 
-% Approximate abstraction
+% Thesis: Approximate abstraction for three reasons.
 The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits.
+Relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
 First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
+
+Second, approximate abstractions can achieve greater degrees of compression compared to perfect abstractions due to their relaxed criteria of equality.
+Approximate abstractions can be particularly effective in natural environments where no two states are identical.
+
+, so approximate abstraction may be useful but exact abstraction is completely ineffective.
+
+Third, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
 

### 2016-02-04 paper/abstract.tex
Worked on stuff while Dave away

@@
 Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
-However, perfect abstractions are often computationally intractable and ineffective in environments where no two situations are exactly alike.
+However, perfect abstractions, which treat fully identical situations alike, are often computationally intractable and ineffective in environments where no two situations are exactly alike.
 For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.

### 2016-02-04 paper/introduction.tex
Worked on stuff while Dave away

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, perfect abstractions require complete knowledge that is often computationally intractable.
+However, perfect abstractions, which treat fully identical situations alike, require complete knowledge that is often computationally intractable.
 Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective.
-To overcome these issues we investigate the space of approximate abstractions that enable agents to treat sufficiently similar states as identical.
+To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar states as identical.
 This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
+
+We now ground all this stuff in MDPs and stuff.
 
@@
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
+The thesis of this work is that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
 Relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
@@
 
-Second, approximate abstractions can achieve greater degrees of compression compared to perfect abstractions due to their relaxed criteria of equality.
-Approximate abstractions can be particularly effective in natural environments where no two states are identical.
+Second, because of their relaxed criteria of equality, approximate abstractions can achieve greater degrees of compression than perfect abstractions.
+This is particularly important in natural environments where no two states are identical.
 
-, so approximate abstraction may be useful but exact abstraction is completely ineffective.
-
-Third, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
+Third, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation by adjusting what they consider sufficiently similar states.
 

### 2016-02-04 paper/abstract.tex
Beep boop new intro and abstract

--- 2016-02-04 paper/abstract.tex
@@
 Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
-However, perfect abstractions are often computationally intractable and ineffective in environments where no two situations are exactly alike.
+However, perfect abstractions, which treat fully-identical situations as equivalent, are often computationally intractable and ineffective in environments where no two situations are exactly alike.
 For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.

### 2016-02-04 paper/introduction.tex
Beep boop new intro and abstract

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, perfect abstractions, which treat fully identical situations alike, require complete knowledge that is often computationally intractable.
+However, perfect abstractions, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable.
 Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective.
@@
 
-We now ground all this stuff in MDPs and stuff.
+\dnote{Want a clause, sentence, prhase, paragraph, that transitions us from the super high level biz in the first paragraph to the second paragraph}
+Abstraction in the context of planning and \ac{RL} in an \ac{MDP} takes the form of state aggregation. \dnote{rephrase and add a sentence or two that gets us to paragraph two}
 
@@
 First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-
-Second, because of their relaxed criteria of equality, approximate abstractions can achieve greater degrees of compression than perfect abstractions.
+Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than perfect abstractions.
 This is particularly important in natural environments where no two states are identical.
-
-Third, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation by adjusting what they consider sufficiently similar states.
+\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, they are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
 

### 2016-02-04 paper/introduction.tex
Intro edits

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, perfect abstractions, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable.
-Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective.
-To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar states as identical.
-This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
+However, perfect abstractions, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain.
+Furthermore, often no two situations are identical, so perfect abstraction is ineffective.
+To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar situations as identical.
+This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
+The remainder of our introduction contextualizes these intuitions in \acp{MDP}.
 
@@
 Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
+%However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
 
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy.
-Relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
+However, relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
 First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
 Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than perfect abstractions.
-This is particularly important in natural environments where no two states are identical.
+This is particularly important in environments where no two states are identical.
 \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, they are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
+The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incuring only bounded error in the resulting behavior.
 
@@
 This paper is organized as follows.
-We first introduce the necessary terminology and background of \ac{RL} and state abstraction.
+We first introduce the necessary terminology and background of \acp{MDP} and state abstraction.
 We then survey existing types of state abstraction as applied to sequential decision making.

### 2016-02-04 paper/abstract.tex
Switched from perfect to exact abstraction and other changes to introduction

--- 2016-02-04 paper/abstract.tex
@@
 Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
-However, perfect abstractions are often computationally intractable and ineffective in environments where no two situations are exactly alike.
+However, exact abstractions, which treat fully-identical situations as equivalent, are often computationally intractable and ineffective in environments where no two situations are exactly alike.
 For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.

### 2016-02-04 paper/introduction.tex
Switched from perfect to exact abstraction and other changes to introduction

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, perfect abstractions, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain.
-Furthermore, often no two situations are identical, so perfect abstraction is ineffective.
-To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar situations as identical.
+However, \textit{exact abstractions}, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain.
+Furthermore, often no two situations are identical, so exact abstraction is ineffective.
+To overcome these issues we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical.
 This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
 The remainder of our introduction contextualizes these intuitions in \acp{MDP}.
-
-\dnote{Want a clause, sentence, prhase, paragraph, that transitions us from the super high level biz in the first paragraph to the second paragraph}
-Abstraction in the context of planning and \ac{RL} in an \ac{MDP} takes the form of state aggregation. \dnote{rephrase and add a sentence or two that gets us to paragraph two}
 
@@
 Thus, a key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}.
-%However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.
+These methods are characterized by reducing \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
+In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, e.g.
+optimal $Q$-values.
+Existing work has characterized how exact abstractions can fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
 
 % Thesis: Approximate abstraction for three reasons.
-However, relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
-First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.
-Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than perfect abstractions.
+However, performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
+First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
+In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction.
+Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions.
 This is particularly important in environments where no two states are identical.
 \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, they are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
-The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incuring only bounded error in the resulting behavior.
+The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incurring only bounded error in the resulting behavior.
 

### 2016-02-04 paper/introduction.tex
Some intro commit

@@
 However, \textit{exact abstractions}, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain.
-Furthermore, often no two situations are identical, so exact abstraction is ineffective.
+Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
 To overcome these issues we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical.
@@
 Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain.
-Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a results of Bellman's curse of dimensionality.
+Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
 \dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.
@@
 Thus, a key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-These methods are characterized by reducing \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
+This agenda has given rise to methods that reduce \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
 In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, e.g.
 optimal $Q$-values.
-Existing work has characterized how exact abstractions can fully maintain optimality~\cite{li2006towards,dean1997modelmin}.
+Existing work has characterized how exact abstractions can fully maintain optimality in \acp{MDP}~\cite{li2006towards,dean1997modelmin}.
 
 % Thesis: Approximate abstraction for three reasons.
-However, performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
+Performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
@@
 Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions.
-This is particularly important in environments where no two states are identical.
-\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, they are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
+This difference is particularly important in environments where no two states are identical.
+\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
 The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incurring only bounded error in the resulting behavior.

### 2016-02-04 paper/introduction.tex
Intro done for now

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, \textit{exact abstractions}, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain.
+However, \textit{exact abstractions}, which treat fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
 Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
@@
 % Thesis: Approximate abstraction for three reasons.
-Performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits.
+The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
@@
 \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
-The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incurring only bounded error in the resulting behavior.
 

### 2016-02-04 paper/conclusion.tex
conc

@@
 % Summary of contributions.
-In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy in the abstract \ac{MDP}.
-This approach is appealing for two reasons.
+In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
+This approach is appealing for three reasons.
 First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
-Second, since the state-aggregation criteria are relaxed to approximate equality, methods that employ these techniques are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
-We evaluate our approaches empirically on four different \acs{MDP}, providing visuals of the compression, as well as displaying the relationship between $\epsilon$ and the degree of compress, as well as the value of the abstract policy.
+Second, approximate abstractions can achieve greater degrees of compression due to their relaxed criteria of equality.
+Third, methods that employ approximate aggregation techniques are able to tune the aggressiveness of abstraction all the while incurring bounded error.
+We empirically demonstrate the relationship between $\epsilon$ and the degree of compression, as well as the value of the abstract policy on four dramatically different \acs{MDP}.
 We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.
@@
 There are many directions for future work.
-
 % Learning abs functions online.
-First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}.
+First, we are interested investigating learning various approximate abstraction functions online in the planning or \ac{RL} setting, a strategy first demonstrated by \citeauthor{ortner2013adaptive}.
 
 % Exploration is interesting.
-Learning abstraction functions online also has interesting implications for the exploration problem.
-If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,
+%Learning abstraction functions online also has interesting implications for the exploration problem.
+If certain information informs the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, as an abstraction function will enable the agent to identify near-optimal behavior more quickly,
 
 % Necessary conditions.
-One question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
+Another question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
 the bound between the values under $\pi_G^*$, $\pi_{G,A}$ is less than $\textsc{VMax}$).
-In future work, we are interested in identifying these conditions.
-
+In future work, we hope to identify these conditions.
 % Options/termporal abstraction
-In future work, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by Options, and approximate abstractions.
-Options have been discussed at length in reinforcement learning and planning \dnote{Options citations}.
+In the future, we are also interested in characterizing the relationship between temporal abstractions, such as those afforded by Options~\cite{sutton1999between}, and approximate abstractions.
+Options have been discussed at length in reinforcement learning and planning~\cite{konidaris2007building,chentanez2004intrinsically}.
 We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.
-
 % Compressibility
-Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
+Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.

### 2016-02-04 paper/related_work.tex
Lihong section now greatly shortened

@@
 Several other projects have addressed similar topics.
-
-% Approximate abstraction work.
-%Dean: 
-%\begin{itemize}
-%\item \citep{dean1997model} Does abstraction with model equality.
-%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
-%\end{itemize}
-%
-%Boutilier:
-%\begin{itemize}
-%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
-%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
-%\end{itemize}
-%
-%Even~\cite{even2003approximate}: COLT paper on different metrics
-%
-%Ortner:
-%\begin{itemize}
-%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
-%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
-%\end{itemize}
 
@@
 \citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.
-
-%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}.
-All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP.
-However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction.
-Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.
+\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
 
@@
 
-% Other? Selecting abstractions
-%\subsection{Selecting Abstractions}
-%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.
+\subsection{Exact Abstraction Framework}
 
-% Defining
-
-% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.
-
-% Lihong/Walsh/Littman: Towards a unified theory...
-
-%\begin{itemize}
-%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
-%\item ALisp~\cite{andre2002state}
-%\item Aggregation in DP~\cite{Bean2011}
-%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
-%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon.
-Wowza.
-Only uses the whole model similarity business though.
-Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
-%
-%\item Selecting the state rep in RL~\cite{maillard2011selecting}
-%\item Near optimal state reps~\cite{ortner2014selecting}
-%\item SMDP homomorphisms~\cite{ravindran2003smdp}
-%\end{itemize}
+\citeauthor*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
+In particular, the authors define five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
+We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{model}$, to the approximate abstraction case.
+Note that when $\epsilon=0$ our generalizations are equivalent to $\phi_{Q^*}$ and $\phi_{model}$.
+Additionally, when $\epsilon=0$ our bounds indicate that no value is a lost, which is one of core results of \citeauthor{li2006towards}.

### 2016-02-04 paper/example_domains.tex
example rewritten, results rewritten

@@
 To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on four domains -- NChain, Taxi, Minefield and Random MDP, which we dub ``Random".
-These domains were selected for the variety they offer -- Nchain is relatively simple domain, Taxi is goal-based and hierarchical in nature, Minefield is stochastic and Random MDP has a high number of near-optimal behavior.
+These domains were selected for their variety -- NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.
 
@@
 
-NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses.
+NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
 In all states, the agent has two actions available: advance down the chain, or return to state 0.
@@
 Thus, the agent must explore down the chain and avoid the intermediate smaller rewards in order to find the large reward at the end.
-In many implementations, there is also a small slip probability that the applied action has the unintended effect of the opposing action (so advancing down the chain with probability $\rho$ will take the agent back to state 0, and vice versa).
+Transitions also have small slip probability such that the applied action has the unintended effect of the opposing action (so advancing down the chain with probability $\rho$ will take the agent back to state 0, and vice versa).
 In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
@@
 
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into hierarchical subgoals.
+Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into hierarchical subgoals~\cite{dietterich2000hierarchical}.
 The agent, operating in a grid world style domain, may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The agent must seek out passengers and take them to their destination.
-We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
+The goal is achieved when the agent has taken each passenger to its destination.
+
+%We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}.
 As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and abstract MDP in the same format.
@@
 % Taxi Compression Visuals
-\begin{figure}[h]
-\subfigure[Ground Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
-\subfigure[Abstract Taxi]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
-\label{fig:taxi-visual}
-\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
-\end{figure}
+%\begin{figure}[h]
+%\subfigure[Ground Taxi]{
+%\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
+%\subfigure[Abstract Taxi]{
+%\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
+%\label{fig:taxi-visual}
+%\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
+%\end{figure}
 
@@
 \label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=.8$}
+\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
 \end{figure}
@@
 For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
-The Random MDP and its compression are visualized in Figure~\ref{fig:minefield-visual}.
+
+%The Random MDP and its compression are visualized in Figure~\ref{fig:minefield-visual}.
 
 % Random Compression Visuals
-\begin{figure}
-\subfigure[Ground Random]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
-\subfigure[Abstract Random]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
-\end{figure}
+%\begin{figure}
+%\subfigure[Ground Random]{
+%\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
+%\subfigure[Abstract Random]{
+%\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
+%\label{fig:minefield-visual}
+%\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
+%\end{figure}

### 2016-02-04 paper/results_discussion.tex
Intro done for now
example rewritten, results rewritten

--- 2016-02-04 paper/results_discussion.tex
@@
 %Explanation of what abstraction is used
-We run experiments on aggregation functions the $\epQ$ abstraction.
+We run experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
 For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\epQ$ criteria.
-The order in which ground states are selected and then greedily added is randomized so there is randomization across trials.
+The order in which ground states are added is randomized, so there is randomization across trials.
 Every ground state is equally weighted in its abstract state.
@@
 Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}.
-200 Trials are run for each data point.
+In the Taxi and Random domains, 200 trials are run for each data point, whereas 20 trials are run for data points in Minefield and NChain.
 
 %Discuss results
+\enote{Make sure results discussion is consistent with "the thesis of this work..."}
+
 Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis of learnable and useful state aggregation criteria.
-In both NChain and Minefield, we observe that despite increasing $\epsilon$ to reduce the number of states which must be planned over, optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
-Similarly for Taxi and $\epsilon$ between $.02$ and $.025$ we observe a reduction in the number of states in the Abstract MDP while value is fully maintained.
+In both NChain and Minefield, we observe that as $\epsilon$ increases from $0$, the number of states which must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
+Similarly for Taxi, when $\epsilon$ is between $.02$ and $.025$ we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
 After $.025$, increased reduction in state space size comes at a cost of value.
-Lastly, as $\epsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states which must be planned over with a corresponding cost in the value of the derived policy.
+Lastly, as $\epsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
 
@@
 Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically.
-We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
+We attribute the sudden fall off of these quantities to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost in the state aggregation.
+Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost by the abstraction.
 
-\enote{Should we regenerate plots for nChain so it has CIs to match other plots?}
 % Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.

### 2016-02-04 paper/background.tex
Made background optimal policy consistent with rest of paper

@@
 \end{equation}
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively. For further background, see~\cite{kaelbling1996reinforcement}.
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\cite{kaelbling1996reinforcement}.
 
@@
 % Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section.
-Here, we survey their main results, which we then extend to the framework of approximate abstraction.
-
-In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}.
-For brevity, we include those that we build upon directly.
-(See their paper for full details.)
-
-\bdefn{$\phi_{Q^*}$}
-A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
-\begin{equation}
-\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
-\end{equation}
-\edefn
-
-\bdefn{$\phi_{model}$}
-A model-irrelevance abstraction, $\phi_{model}$, is one such that:
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a).
-\end{multline}
-and
-\begin{multline}
-\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') = \sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s').
-\end{multline}
-\edefn
-
-Intuitively, a $Q^*$-irrelevance is one that is guaranteed to compress states that share optimal Q functions.
-Critically, the direction of the implication is such that the abstraction is not guaranteed to abstract all states for which this condition is true, only that, if the abstraction function collapses two (or more) states to an abstract state, that those states have the same $Q^*$.
-Computing such a function is as difficult as solving the MDP, as it requires knowledge of the $Q*$, which is a sufficient condition for knowing the optimal policy.
-This is one of the motivations for investigating approximate abstractions, as we anticipate that an approximation of $Q^*$ is the sort of knowledge a learner can infer online.
-
-A model-irrelevance abstraction is one that is guaranteed to compress states that transition to the same compressed states, and have identical rewards.
-Critically, this need not require that the ground transition functions of any two compressed states are identical; only that their corresponding abstract state transitions {\it in the abstract} MDP are identical.
-Unlike the $Q^*$ irrelevance, in the planning setting we anticipate knowing the full transition function and reward function up front, so it is feasible that an abstraction function of this kind may be used.
-In a model based learning setting, we expect an approximate abstraction akin to model-irrelevance to be more realistic, as we anticipate reinforcement learners to be able to approximate the information content of the transition function and reward function during learning.

### 2016-02-04 paper/theory_results.tex
adding some changes to theory result
Small change to first sentence of theory results

@@
 % Intro to approx state abstraction results.
-Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods.
+Here, we introduce our formal analysis of approximate state abstraction, including results bounding the error associated with these abstraction methods.
 In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
@@
 
-\dnote{Bounds for multi and bolt suspisiously similar. Double check math}
+\dnote{Bounds for multi and bolt suspiciously similar. Double check math}
 

### 2016-02-04 paper/example_domains.tex
Tweaked mention of codebase

@@
 \section{Example Domains}
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on four domains -- NChain, Taxi, Minefield and Random MDP, which we dub ``Random".
+To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\epQ$ abstraction family on four domains -- NChain, Taxi, Minefield and Random.
 These domains were selected for their variety -- NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.
@@
 % Description of visuals.
-Our code base provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.
-The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted.
-We use the graph visualization library GraphStream~\cite{graphstream}.
 In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
 The thickness of the arrow indicates how much reward is associated with that transition.
-In the ground MDPs, states are labeled with a number.
-In some abstract MDPs, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were ignored).
+In the ground \acp{MDP}, states are labeled with a number.
+In some abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were not labelled).
+
+%Description of code base
+Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} and visualizing and evaluating the resulting abstract \acp{MDP}.
+We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
 

### 2016-02-04 paper/theory_results.tex
theory res

--- 2016-02-04 paper/theory_results.tex
@@
 % zzz too long... needs to be broken up.
-
 \begin{equation}
@@
 % Base Case t=0
-\textit{Base Case: $T = 0$}\\
+\textit{Base Case: $T = 0$}
+
 When $T = 0$, $Q_T = Q_G$, so the result trivially follows.
+
 % Base Case t=1
-\textit{Base Case: $T = 1$}\\
+\textit{Base Case: $T = 1$}
 \begin{align*}
@@
 \begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),\\
-&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_G(s_G, a).
+&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),
 \end{align*}
@@
 \begin{equation}
-\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
+\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\epsilon \gamma^t
 \end{equation}
@@
 \begin{equation}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
 \end{equation}
@@
 By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
-
 \begin{multline*}
-Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)* \\ 
+Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)\ * \\ 
  \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
@@
 \begin{multline*}
-\leq \sum_{g \in G(s_A)}w(g) * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
+\leq \sum_{g \in G(s_A)}w(g)\ * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
 \end{multline*}
@@
 \begin{align*}
-&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a)\\
-&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_G(s_G, a)
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a) \\
+\therefore \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| &\leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
 \end{align*}
-Thus,
-\begin{equation*}
-\left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
-\end{equation*}
-
 Since $s_G$ and $s_A$ are arbitrary we conclude
@@
 
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.
+As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$. \\
 
@@
 \label{clm:optAbsActionNearOptGround}
-The optimal action in the abstract MDP has a Q-value in the ground which is nearly optimal:
+%The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
 
@@
 
-Let $a^*_G$ stand for the optimal action for $s_G$: \\
-$a^*_G = \argmin Q_G(s_G, a)$
+Let $a^*_G$ stand for the optimal action in $s_G$:
+\[a^*_G = \argmin Q_G(s_G, a)\]
 
-Let $a^*_A$ stand for the optimal action for $s_A$:\\
- $a^*_A = \argmin Q_A(s_A, a)$
+Let $a^*_A$ stand for the optimal action in $s_A$:
+ \[a^*_A = \argmin Q_A(s_A, a)\]
 
-That is, we prove that
-
+The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
 \begin{equation}
@@
 
-By Claim \ref{clm:closeQs}
+By Claim \ref{clm:closeQs}:
 \begin{align}
@@
 
-By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$ so our bound trivially holds in this case.
+By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case.
 
@@
 \begin{align*}
-&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
-&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
+\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G) \\
+%&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
+\therefore V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{align*}
-
-Thus,
-\begin{equation*}
-V_G(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
-\end{equation*}
 Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
 \end{equation}
@@
 
-Thus, we conclude
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
-
-\begin{equation*}
-\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
-\end{equation*}
+Thus, we conclude Lemma~\ref{lma:Q*}
+%\begin{equation*}
+%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
+%\end{equation*}
+%\begin{equation*}
+%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
+%\end{equation*}
 
@@
 Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
-
-\begin{align*}
-B = &\max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|\\
-&\text{Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.}\\
-=&\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
-& \gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
-\end{align*}
+\begin{equation*}
+B = \max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|
+\end{equation*}
+Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.:
 \begin{multline*}
-\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\ \left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) 		\max_{a'}Q_G({s_G}', a')	\right]
+=\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
+\gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
+\end{multline*}
+\begin{multline*}
+\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\
+\left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \right]
 \end{multline*}
@@
 This family of abstractions is appealing as the Boltzmman distribution over $Q$-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
-
 \bdefn{$\phi_{bolt}$}
@@
 \end{equation}
-
 \begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$::
 \begin{equation}
-\forall_{s \in \mcS_G} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
+\forall_{s \in \mcS_G} : \left| V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \right| \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
 \end{equation}
@@
 We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
-
 \bdefn{$\ep_{mult}$}
@@
 \end{equation}
-
 \begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
@@
 
-{\bf Proof Sketch:}
+{\bf Proof Sketch:} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.
 
-The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.
-
-\dnote{Bounds for multi and bolt suspisiously similar. Double check math}
+\dnote{Bounds for multi and bolt suspiciously similar. Double check math}
 

### 2016-02-04 paper/example_domains.tex

@@
 % Description of visuals.
+We provide graphical visuals of both ground $\acp{MDP}$ and resulting abstract $\acp{MDP}$.
 In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
@@
 
-Minefield is a slight variant of Grid World.
-The transitions and rewards are perturbed, and there is no down action available to the agent.
-There is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right.
-The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
+Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $.2$.
+The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
 During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-We visualize the original Minefield, represented as a graph, and the abstract Minefield in ~\ref{ref:minefield-visual}.
+We visualize the original Minefield and the abstract Minefield in ~\ref{ref:minefield-visual}.
 

### 2016-02-04 paper/results_discussion.tex
Shortened nChain a bit

@@
 We run experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
-For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\epQ$ criteria.
-The order in which ground states are added is randomized, so there is randomization across trials.
+For each trial our aggregation greedily groups ground states into abstract states that in a way that satisfies the $\epQ$ criteria.
+The order in which ground states are grouped is randomized, so there is randomization across trials.
 Every ground state is equally weighted in its abstract state.
@@
 %Explanation of what plots done
-For each domain we report two quantities as a function of epsilon with \%95 confidence bars.
-First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
-The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
+For each domain we report two quantities as a function of epsilon with 95\% confidence bars.
+First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
+The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
 Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}.

### 2016-02-04 paper/example_domains.tex

@@
 This transition provides a large positive reward, $r_{large}$.
-Thus, the agent must explore down the chain and avoid the intermediate smaller rewards in order to find the large reward at the end.
-Transitions also have small slip probability such that the applied action has the unintended effect of the opposing action (so advancing down the chain with probability $\rho$ will take the agent back to state 0, and vice versa).
-In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
+Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.g In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
 

### 2016-02-04 paper/theory_results.tex
reformatted theory
reformatted more math

@@
 \begin{multline*}
-\leq \sum_{g \in G(s_A)}w(g)\ * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
+\leq \sum_{g \in G(s_A)}w(g) * \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr]
 \end{multline*}
@@
 \end{equation*}
-Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.:
+Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$:
 \begin{multline*}
-=\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
-\gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
+=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
+\biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
 \end{multline*}
 \begin{multline*}
-\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\
-\left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \right]
+\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}') -\\ 
+T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr]
 \end{multline*}
-By the similarity of transitions of grouped states under $\epM$:
+By similarity of transitions under $\epM$:
 \begin{align*}
@@
 \end{equation*}
-
 \enote{Do we need to state what Q max is and that it is upper bounded by 1 over 1 minus gamma or is this common knowledge?}
-
 Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
-
 \subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
@@
 \end{lma}
-
 We prove Lemma~\ref{lma:bolt_lemma} by using the approximation for $e^x$:
@@
 \begin{align*}
-|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\epsilon}| \leq \epsilon
+\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\epsilon}\right| \leq \epsilon
 \end{align*}
@@
 \begin{equation}
-|Q_G(s_1,a) - Q_G(s_2,a)| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
+\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
 \label{eq:bolt_qs}

### 2016-02-04 paper/conclusion.tex
Greatly shortened summary in conclusion

@@
 % Summary of contributions.
-In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
-This approach is appealing for three reasons.
-First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
+Approximate abstraction in \acp{MDP} offers considerable advantages over exact abstraction.
+In this work we prove bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
+We also empirically demonstrate that approximate abstractions can reduce state space size with negligible loss in the quality of the behavior.
+
+%First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
 Second, approximate abstractions can achieve greater degrees of compression due to their relaxed criteria of equality.
@@
 Another question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
-the bound between the values under $\pi_G^*$, $\pi_{G,A}$ is less than $\textsc{VMax}$).
+the bound between the values under $\pi_G^*$, $\pi_{GA}$ is less than $\textsc{VMax}$).
 In future work, we hope to identify these conditions.

### 2016-02-04 paper/results_discussion.tex
Maybe now results discussion consistent with thesis
Greatly shortened summary in conclusion

@@
 %Discuss results
-\enote{Make sure results discussion is consistent with "the thesis of this work..."}
-
-Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis of learnable and useful state aggregation criteria.
+Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis useful state aggregation criteria.
 In both NChain and Minefield, we observe that as $\epsilon$ increases from $0$, the number of states which must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).

### 2016-02-04 paper/theory_results.tex
Slight theory results shortenings

@@
 % Q* Lemma -- lemma 1
-We consider an approximate version of the $Q^*$-irrelevance abstraction.
+We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$.
 
@@
 
-Inspired by the model-irrelevance abstraction, we consider the approximate case. 
+Now consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$. 
 \bdefn{$\epM$}

### 2016-02-04 paper/example_domains.tex
small modification to theory results, trimmed example domains a bit

@@
 % Description of visuals.
-We provide graphical visuals of both ground $\acp{MDP}$ and resulting abstract $\acp{MDP}$.
+We provide graphical visuals of both ground \acp{MDP} and resulting abstract \acp{MDP}.
 In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
@@
 In the ground \acp{MDP}, states are labeled with a number.
-In some abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were not labelled).
+In the abstract \acp{MDP} we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states.
+%(some are visually unwieldy and so were not labelled).
 
 %Description of code base
-Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} and visualizing and evaluating the resulting abstract \acp{MDP}.
+Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
 We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
@@
 In all states, the agent has two actions available: advance down the chain, or return to state 0.
-The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain.
-This transition provides a large positive reward, $r_{large}$.
-Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.g In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
+The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain which provides a large positive reward, $r_{large}$.
+Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.
+In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
 
@@
 \label{fig:nchain-visual}
-\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
+\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\epsilon=0.5$}
 \end{figure}
@@
 
-Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into hierarchical subgoals~\cite{dietterich2000hierarchical}.
-The agent, operating in a grid world style domain, may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The goal is achieved when the agent has taken each passenger to its destination.
+Taxi has long been studied by the hierarchical reinforcement learning literature~\cite{dietterich2000hierarchical}.
+The agent, operating in a grid world style domain may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
+The goal is achieved when the agent has taken all passenger to their destinations.
 
@@
 
-Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $.2$.
+Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $x$.
 The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
 During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-We visualize the original Minefield and the abstract Minefield in ~\ref{ref:minefield-visual}.
+We visualize the original Minefield and the abstract Minefield in Figure~\ref{fig:minefield-visual}.
 
@@
 \label{fig:minefield-visual}
-\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction, with $\epsilon=1.1$}
 \end{figure}
@@
 
-The Random MDP domain we consider is as follows.
+The Random \ac{MDP} domain we consider is as follows.
 There are $N$ states, and $K$ actions.

### 2016-02-04 paper/example_domains.tex
trimmed code para'

@@
 %Description of code base
-Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
+Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
 We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.

### 2016-02-05 paper/conclusion.tex
adding michael's changes

@@
 Approximate abstraction in \acp{MDP} offers considerable advantages over exact abstraction.
-In this work we prove bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
+In this work, we proved bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
 We also empirically demonstrate that approximate abstractions can reduce state space size with negligible loss in the quality of the behavior.
@@
 % Learning abs functions online.
-First, we are interested investigating learning various approximate abstraction functions online in the planning or \ac{RL} setting, a strategy first demonstrated by \citeauthor{ortner2013adaptive}.
+First, we are interested in investigating learning various approximate abstraction functions online in the planning or \ac{RL} setting, a strategy first demonstrated by \citeauthor{ortner2013adaptive}.
+zzz what does that mean?
+% Necessary conditions.
+Another question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
+the bound between the values under $\pi_G^*$, $\pi_{GA}$ is less than $\textsc{VMax}$).
+zzz perhaps too vague
+% Options/termporal abstraction
+We investigated the use of Options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.
+In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by Options, and approximate abstractions.
+% Compressibility
+Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
 
@@
 If certain information informs the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, as an abstraction function will enable the agent to identify near-optimal behavior more quickly,
-
-% Necessary conditions.
-Another question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
-the bound between the values under $\pi_G^*$, $\pi_{GA}$ is less than $\textsc{VMax}$).
-In future work, we hope to identify these conditions.
-% Options/termporal abstraction
-In the future, we are also interested in characterizing the relationship between temporal abstractions, such as those afforded by Options~\cite{sutton1999between}, and approximate abstractions.
-Options have been discussed at length in reinforcement learning and planning~\cite{konidaris2007building,chentanez2004intrinsically}.
-We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.
-% Compressibility
-Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.

### 2016-02-05 paper/example_domains.tex
adding michael's changes

@@
 \section{Example Domains}
-To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\epQ$ abstraction family on four domains -- NChain, Taxi, Minefield and Random.
-These domains were selected for their variety -- NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.
+To illustrate our approximate abstraction functions, we apply $\epQ$ abstraction to four example domains---NChain, Taxi, Minefield and Random.
+These domains were selected for their diversity---NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.
 
 % Description of visuals.
-We provide graphical visuals of both ground \acp{MDP} and resulting abstract \acp{MDP}.
-In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions.
+We provide visuals of both ground \acp{MDP} and resulting abstract \acp{MDP} in which a grey circle indicates a state and colored arrows indicate transitions.
 The thickness of the arrow indicates how much reward is associated with that transition.
 In the ground \acp{MDP}, states are labeled with a number.
-In the abstract \acp{MDP} we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states.
+In the abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states.
 %(some are visually unwieldy and so were not labelled).
@@
 Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
-We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
+We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
 
@@
 
-NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
+NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian RL literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
 In all states, the agent has two actions available: advance down the chain, or return to state 0.
-The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain which provides a large positive reward, $r_{large}$.
-Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.
+The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain.
+The exception is that when the agent transitions to the last state in the chain, it receives a large positive reward, $r_{large}$.
+Transitions also have small slip probability $\rho$, such that the applied action results in the opposite dynamics.
 In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
@@
 
-Taxi has long been studied by the hierarchical reinforcement learning literature~\cite{dietterich2000hierarchical}.
-The agent, operating in a grid world style domain may move left, right, up, and down, as well as pickup a passenger and drop off a passenger.
-The goal is achieved when the agent has taken all passenger to their destinations.
+Taxi has long been studied by the hierarchical RL literature~\cite{dietterich2000hierarchical}.
+The agent, operating in a grid-world style domain, may move left, right, up, and down, as well as pick up a passenger and drop off a passenger.
+The goal is achieved when the agent has taken all passengers to their destinations.
 
@@
 
-Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $x$.
-The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name).
-During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
-We visualize the original Minefield and the abstract Minefield in Figure~\ref{fig:minefield-visual}.
+Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$.
+The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward.
+(These are the states with ``mines'' in them.) We set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
+We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.
+
+zzz problem: text says ``top row'', but image is oriented diagonally.
 
@@
 \label{fig:minefield-visual}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction, with $\epsilon=1.1$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\epsilon=1.1$}
 \end{figure} 
+zzz the lines are very thin... not visible to me.
 
@@
 
-The Random \ac{MDP} domain we consider is as follows.
-There are $N$ states, and $K$ actions.
-For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
+In the Random \ac{MDP} domain we consider, there are $N$ states and $K$ actions. For each state, each action transitions to one of two randomly selected states, each with probability $0.5$.
 

### 2016-02-05 paper/results_discussion.tex
adding michael's changes

@@
 %Explanation of what abstraction is used
-We run experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
-For each trial our aggregation greedily groups ground states into abstract states that in a way that satisfies the $\epQ$ criteria.
-The order in which ground states are grouped is randomized, so there is randomization across trials.
+We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions. 
+zzz why? wouldn't it be better to show all 4?
+For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.
+Since this approach represents an order-dependent approximation to the maximum amount of abstraction possible, we randomized the order in which states were considered across trials.
 Every ground state is equally weighted in its abstract state.
@@
 %Explanation of what plots done
-For each domain we report two quantities as a function of epsilon with 95\% confidence bars.
+For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
 First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
 The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
-Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}.
-In the Taxi and Random domains, 200 trials are run for each data point, whereas 20 trials are run for data points in Minefield and NChain.
+Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2} so the tradeoff between abstract state space size and near optimality is made evident.
+In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient for data points in Minefield and NChain.
+
+zzz the font size in the figures needs to be larger---too tiny for my eyes
 
 %Discuss results
-Our empirical results corroborate our thesis -- that approximate state abstractions can form the basis useful state aggregation criteria.
-In both NChain and Minefield, we observe that as $\epsilon$ increases from $0$, the number of states which must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
-Similarly for Taxi, when $\epsilon$ is between $.02$ and $.025$ we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
+Our empirical results corroborate our thesis---approximate state abstractions can decrease state space size while retaining bounded error.
+In both NChain and Minefield, we observe that, as $\epsilon$ increases from $0$, the number of states that must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
+Similarly for Taxi, when $\epsilon$ is between $.02$ and $.025$, we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
 After $.025$, increased reduction in state space size comes at a cost of value.
@@
 
+zzz why not include all the graphs in one figure?
+
+zzz wait, why do the policies in the highly abstracted random MDPs end up statistically significantly worse than random?? I'm not convinced these error bars are correct.
+
 Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}.
-Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically.
-We attribute the sudden fall off of these quantities to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable.
+Taxi exhibits relative stability in state space size and behavior for $\epsilon$ up to $.02$, at which point both fall off dramatically.
+We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible.
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost by the abstraction.
+Thus, even as the information for optimal behavior is lost with increasng $\epsilon$, there are many near-optimal policies available to the agent that remain available.
 

### 2016-02-05 paper/background.tex
Added Michael's final comments

@@
 
+zzz: I think empty sections like this are ugly. There ought to be some sort of preamble here.
+
 %MDP/SDM Background and Notation
@@
 \enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
-An \ac{MDP} is a problem solved by a sequential decision making agent, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
 Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
@@
 \begin{equation}
-Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s))
+Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s)).
 \end{equation}
@@
 \begin{equation}
-V^\pi(s) = \max_a Q^\pi(s,a)
+V^\pi(s) = \max_a Q^\pi(s,a).
 \end{equation}
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\cite{kaelbling1996reinforcement}.
+
+zzz no, that is not the standard definition. it would normally be $V^\pi(s) = Q^\pi(s,\pi(s))$.
+
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively.
+For further background, see~\namecite{kaelbling1996reinforcement}.
 
@@
 \subsection{Abstraction Notation}
-We build upon the notation used by \citeauthor{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
-We build heavily on their notation, and discuss other similarities in our work in the next section.
+We build upon the notation used by \citeauthoryear{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
+We build heavily on their notation, and discuss other similarities to our work in the next section.
 
@@
 
+zzz the space before the comma looks weird to me.
+
 \bdefn{$G$}
@@
 \begin{cases}
-\{g \in \mcS_G \mid \phi(g) = \phi(s) \}& s \in \mcS_G\\
-\{g \in \mcS_G \mid \phi(g)=s \}& s \in \mcS_A
+\{g \in \mcS_G \mid \phi(g) = \phi(s) \},& s \in \mcS_G,\\
+\{g \in \mcS_G \mid \phi(g)=s \},& s \in \mcS_A.
 \end{cases}
@@
 
+zzz it's weird that s is bound twice in this formula. is that needed/intentional?
+
 \bdefn{$\omega(s)$}
 We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$.
-The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
+The only restriction placed on the weighting scheme is that it induces a probability distribution on the states:
 \begin{equation}
-\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \texttt{ and }\hspace{6mm}  \omega(s) \in [0,1]
+\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \textrm{ and }\hspace{6mm}  \omega(s) \in [0,1].
 \end{equation}
@@
 \begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g),
+\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g).
 \end{equation}

### 2016-02-05 paper/related_work.tex
Added Michael's final comments

@@
 \subsection{Approximate State Abstraction}
-\citeauthor*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citeauthoryear*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
 They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
@@
 Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
+\citeauthoryear*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
+\citeauthoryear*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
 
-\subsection{Specific Abstraction Algorithms}
+zzz what's $gR$?
+
+\Subsection{Specific Abstraction Algorithms}
 Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
+\citeauthoryear*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work.
-For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.
+\citeauthoryear{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
+\citeauthoryear*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
+The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work zzz pointer??.
+For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthoryear{li2006towards}.
 
@@
 
-\citeauthor*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
-In particular, the authors define five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
+\citeauthoryear*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
+In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
 We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{model}$, to the approximate abstraction case.
-Note that when $\epsilon=0$ our generalizations are equivalent to $\phi_{Q^*}$ and $\phi_{model}$.
-Additionally, when $\epsilon=0$ our bounds indicate that no value is a lost, which is one of core results of \citeauthor{li2006towards}.
+Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods.
+Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citeauthoryear{li2006towards}.
+
+zzz you shouldn't have $\phi_{model}$ because the word model will be typeset as the product of five variables. Some math mode magic is needed.

### 2016-02-05 paper/theory_results.tex
small modification to theory results, trimmed example domains a bit
Aligned heterogenous mdp definitions
put notes back in, small edits to theory

@@
 \bdefn{$\pi_A^*$, $\pi_G^*$}
-We let $\pi_A^* : \mcS_A \rightarrow \mcA$ and $\pi_G^* : \mcS_G \rightarrow \mcA$ stand for the optimal policies in the abstract and ground \acp{MDP} respectively.
+We let $\pi_A^* : \mcS_A \rightarrow \mcA$ and $\pi_G^* : \mcS_G \rightarrow \mcA$ stand for the optimal policies in the abstract and ground \acp{MDP}, respectively.
 \edefn
@@
 We are interested in how the optimal policy in the abstract \ac{MDP} performs in the ground \ac{MDP}.
-As such we formally define the policy in the ground \ac{MDP} derived from optimal behavior in the abstract \ac{MDP}:
+As such, we formally define the policy in the ground \ac{MDP} derived from optimal behavior in the abstract \ac{MDP}:
 
 \bdefn{$\pi_{GA}$}
-Given a $s \in \mcS_G$ and a state aggregation function, $\phi$, 
+Given a state $s \in \mcS_G$ and a state aggregation function, $\phi$, 
 \begin{equation}
-\pi_{GA}(s)=\pi_A^*(\phi(s))
+\pi_{GA}(s)=\pi_A^*(\phi(s)).
 \end{equation}
@@
 
-We now define classes of abstraction based on functions state, action pairs.
+We now define classes of abstraction based on functions of state--action pairs.
 \bdefn{$\ep_f$}
@@
 \label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon
+\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon.
 \end{equation}
@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
+There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $1/\epsilon$:
 \begin{equation}
-\forall_{s \in \mathcal{S}_G}: | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(\epsilon).
+\forall_{s \in \mathcal{S}_G} | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(1/\epsilon).
 \end{equation}
@@
 Thus,
-\begin{equation}
-\mathcal{S}_T = \begin{cases}
+\begin{align*}
+\mathcal{S}_T &= \begin{cases}
 \mathcal{S}_G,& T \leq 0, \\
-\mathcal{S}_A,& \text{o/w},
-\end{cases}
-\end{equation}
-\begin{equation}
-\mathcal{R}_T(s,a) = \begin{cases}
+\mathcal{S}_A,& \text{o/w}
+\end{cases}\\
+%--
+\mathcal{R}_T(s,a) &= \begin{cases}
 \mathcal{R}_G(s,a),& T \leq 0, \\
-\mathcal{R}_A(s, a),& \text{o/w},
-\end{cases}
-\end{equation}
-\begin{equation}
-\mcT_T(s,a,s') = \begin{cases}
+\mathcal{R}_A(s, a),& \text{o/w}
+\end{cases}\\
+%--
+\mcT_T(s,a,s') &= \begin{cases}
 \mcT_G(s,a,s'),& T \leq 0, \\
 \underset{{g \in G(s)}}{\sum}\left[w(g)\mcT_G(g, a, s')\right],& T = 1, \\
-\mcT_A(s,a,s'),& \text{o/w}.
-\end{cases}
-\end{equation}
+\mcT_A(s,a,s'),& \text{o/w}
+\end{cases}\\
+\end{align*}
 
-It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
-% zzz too long... needs to be broken up.
+It follows that the $Q$ value of a state $s$ in $M^T$ for action $a$ is defined by:
 \begin{equation}
@@
 \begin{cases}
-	   Q_G(s, a) &  T=0\\
-	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
-	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a) &\text{o/w}
-
+	   Q_G(s, a), &  T=0,\\
+	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right], & T = 1,\\
+	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a), &\text{o/w},
 \end{cases}
 \end{equation}
-
-Where:
+where
 \begin{equation}
-\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a')
+\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
 \end{equation}
@@
 \end{align*}
-Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
+Since all co-aggregated states have $Q$ values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
 \begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),
+&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a).
 \end{align*}
@@
 \begin{equation}
-\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\epsilon \gamma^t
+\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\epsilon \gamma^t.
 \end{equation}
@@
 Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-
 We denote $\epQ(s_G)$ as $s_A$. 
-
 By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
 \begin{multline*}
-Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)\ * \\ 
- \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
+Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)\ \times \\ 
+ \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
 \end{multline*}
-Applying our inductive hypothesis yields,
+Applying our inductive hypothesis yields
+zzz what is it less than or equal to?
 \begin{multline*}
-\leq \sum_{g \in G(s_A)}w(g) * \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr]
+\leq \sum_{g \in G(s_A)}w(g) * \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
 \end{multline*}
 %&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-Then:
+Then,
 \begin{equation*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right]
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right].
 \end{equation*}
-Since all aggregated states have Q-values within $\epsilon$ of one another:
+zzz again, doesn't say what it is less than or equal to
+since all aggregated states have $Q$ values within $\epsilon$ of one another:
 \begin{align*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a) \\
+\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
 \therefore \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| &\leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
 \end{align*}
-Since $s_G$ and $s_A$ are arbitrary we conclude
+Since $s_G$ and $s_A$ are arbitrary, we conclude
 \begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t.
 \end{equation}
 
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$. \\
+As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore, Equation $\ref{eq:Q*Claim1}$ follows. \\
 
@@
 \label{clm:optAbsActionNearOptGround}
-%The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
+%The optimal action in the abstract MDP has a $Q$ value in the ground which is nearly optimal:
 
 Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.
-
-Let $a^*_G$ stand for the optimal action in $s_G$:
-\[a^*_G = \argmin Q_G(s_G, a)\]
-
-Let $a^*_A$ stand for the optimal action in $s_A$:
- \[a^*_A = \argmin Q_A(s_A, a)\]
-
-The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
+Let $a^*_G$ stand for the optimal action in $s_G$, and $a^*_A$ stand for the optimal action in $s_A$:
+\begin{align*}
+a^*_G = \argmin Q_G(s_G, a), \hspace{4mm}
+a^*_A = \argmin Q_A(s_A, a).
+\end{align*}
+The optimal action in the abstract MDP has a $Q$ value in the ground MDP that is nearly optimal:
 \begin{equation}
 \label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
+V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}.
 \end{equation}
@@
 
-By Claim \ref{clm:closeQs}:
+By Claim~\ref{clm:closeQs},
 \begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}.
 \label{eq:Q*OptActionResult}
 \end{align}
-
-By the definition of $a^*_A$ we know that 
+By the definition of $a^*_A$, we know that 
 \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}
+Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}.
 \end{align}
-
-Lastly again by Claim \ref{clm:closeQs} we know
+Lastly, again by Claim~\ref{clm:closeQs}, we know
 \begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
+Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}.
 \end{align}
-
-Therefore, we conclude Equation \ref{eq:Q*Claim2}.
+Therefore, Equation~\ref{eq:Q*Claim2} follows.
 
@@
 
-Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
+Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for $t$ steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:
 \begin{equation}
@@
 \begin{cases}
-\pi_G^*(s), \text{if $t<=0$}\\
-\pi_{GA}(s), \text{if $t > 0$}
+\pi_G^*(s), \text{if $t<=0$},\\
+\pi_{GA}(s), \text{if $t > 0$}.
 \end{cases}
 \end{equation}
+zzz inconsistent notation for cases. I like the ifs, but that's not how it appeared earlier.
 
@@
 V_G^{\pi_{A,t}}(s_G) = \\
-R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
+R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
 \end{multline*}
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{equation}
@@
 
-By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case.
+By definition, when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case.
 
@@
 
-Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.
-
+Consider a fixed but arbitrary state $s_G \in \mathcal{S}_G$.
 We assume for our inductive hypothesis that
 \begin{equation}
-V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G) + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
+V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G) + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{equation}
-By definition 
+By definition,
 \begin{multline*}
-V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
+V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
 \end{multline*}
@@
 \begin{multline*}
-V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
+V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right).
 \end{multline*}
-Therefore:
+Therefore,
+zzz more dangling inequalities below.
 \begin{align*}
 %&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G))
+&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G)).
 \end{align*}
-Applying Claim \ref{clm:optAbsActionNearOptGround} yields:
+Applying Claim~\ref{clm:optAbsActionNearOptGround} yields:
 \begin{align*}
@@
 %&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
-\therefore V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\therefore V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{align*}
 Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.
-
-Thus, from our base case and induction we conclude that
+Thus, from our base case and induction, we conclude that
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
+\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{equation}
@@
 Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
-
-Thus, we conclude Lemma~\ref{lma:Q*}
+Thus, we conclude Lemma~\ref{lma:Q*}.
 %\begin{equation*}
@@
 
-Now consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$. 
+Now, consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$. 
 \bdefn{$\epM$}
@@
 \epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon
+\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon\; \wedge\ \\
+\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon.
 \end{multline}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} : | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
+\forall_{s \in \mcS_G} | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}.
 \end{equation}
@@
 
-{\bf Proof:} Our proof proceeds as follows: we demonstrate that states aggregated under $\epM$ have $Q$-values all within a particular bound.
-Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$.
-Understanding $\epM$ as such abstractions allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
+{\bf Proof:} Our proof proceeds as follows.
+We demonstrate that states aggregated under $\epM$ have $Q$ values all within a particular bound.
+Consequently, $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$.
+Understanding $\epM$ as such an abstraction allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
 
-Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
+zzz so, these Qmodel things are formatted better. use the same formatting earlier?
+
+Let $B$ stand for the maximum $Q$ value difference between any pair of ground states in the same abstract state under $\epM$:
 \begin{equation*}
-B = \max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|
+B = \max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|,
 \end{equation*}
-Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$:
+where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$:
+zzz again... this dangling comparison operator thing is highly non-standard.
 \begin{multline*}
@@
 \leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}') -\\ 
-T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr]
+T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr].
 \end{multline*}
@@
 \begin{align*}
- \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
-\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}
+ \leq \epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \leq \epsilon + \gamma|\mcS_G|\epsilon Q_{max}.
 \end{align*}
+zzz similarly, Qmax needs to be formatting differently.
 Applying 0-1 reward normalization and algebra:
 \begin{equation*}
- \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
+ \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}.
 \end{equation*}
-\enote{Do we need to state what Q max is and that it is upper bounded by 1 over 1 minus gamma or is this common knowledge?}
-Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+\enote{Do we need to state what Q max is and that it is upper bounded by 1 over 1 minus gamma or is this common knowledge? zzz not common knowledge, no.}
+Since the $Q$ values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
@@
 
-Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent.
-This family of abstractions is appealing as the Boltzmman distribution over $Q$-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
+zzz same with Qbolt.
+
+Here, we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$ values as equivalent.
+This family of abstractions is appealing as the Boltzmman distribution over $Q$ values has been of interest in the RL literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
+zzz all this theory is quite abstract.
+is there some way to weave in a running example and/or to at least provide some more motiviation for why phiBoltz is desirable.
+Balancing exploration/exploitation isn't really a motivation for why values should be abstracted together.
+What do the first two abstraction types miss that this one provides?
+We didn't Lihong et al.
+study it in the exact case?
 \bdefn{$\phi_{bolt}$}
-We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$ satisfies:
+We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
 \begin{multline}
 \ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon
+\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon.
 \label{eq:phi_bolt}
@@
 \edefn
+That is, zzz explain.
 
@@
 \begin{equation}
-\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k*\epsilon
+\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k\times\epsilon.
 \label{eq:bolt_denom}
 \end{equation}
-\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$::
+\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$:
 \begin{equation}
-\forall_{s \in \mcS_G} : \left| V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \right| \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
+\forall_{s \in \mcS_G} \left| V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \right| \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
 \end{equation}
@@
 \end{lma}
-We prove Lemma~\ref{lma:bolt_lemma} by using the approximation for $e^x$:
+We prove Lemma~\ref{lma:bolt_lemma} using the approximation for $e^x$:
 \begin{equation}
@@
 \end{equation}
-Where $\delta$ is the error associated with the approximation.
+where $\delta$ is the error associated with the approximation.
 
@@
 \end{align*}
-
 It follows that:
 \begin{equation}
-\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)
+\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right).
 \label{eq:bolt_qs}
 \end{equation}
-
-Consequently, we can consider $\widetilde{\phi}_{bolt}$ as a type of $\epQ$, where the difference in Q values is bounded by: $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
-Lemma \ref{lma:bolt_lemma} follows directly from Lemma \ref{lma:Q*}.
+Consequently, we can consider $\widetilde{\phi}_{bolt}$ as a variation of $\epQ$, where the difference in $Q$ values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
+Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.
 
@@
 We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
+zzz a bit more info is needed. what advantages does it have over qboltz. if none, why do we need it?
 \bdefn{$\ep_{mult}$}
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
+We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$, satisfies
 \begin{multline}
 \ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon
+\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon.
 \end{multline}
 \edefn
+That is, zzz.
 
@@
 \begin{equation}
-\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon.
 \end{equation}
+zzz why is that ok? why is it useful? (overall, I think we should take a slightly more pedagogical perspective. we're not writing programs, we're writing explanations.
 \begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
 \begin{equation}
-\forall_{s \in S_M} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
+\forall_{s \in S_M} | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
 \end{equation}
@@
 
-{\bf Proof Sketch:} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.
+{\bf Proof Sketch:} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.
 

### 2016-02-05 paper/abstract.tex

--- 2016-02-04 paper/abstract.tex
@@
-The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction.
-Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
-However, perfect abstractions, which treat fully identical situations alike, are often computationally intractable and ineffective in environments where no two situations are exactly alike.
-For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent.
+The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using state abstraction.
+Prohibitively large task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable.
+However, exact abstractions, which treat only fully-identical situations as equivalent, fail to present opportunities for abstraction in environments where no two situations are exactly alike.
+For these reasons, we investigate approximate state abstractions, which treat nearly-identical situations as equivalent.
 In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation.

### 2016-02-05 paper/background.tex

@@
 
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively.
-For further background, see~\namecite{kaelbling1996reinforcement}.
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citep{kaelbling1996reinforcement}.
 
@@
 \subsection{Abstraction Notation}
-We build upon the notation used by \citeauthoryear{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
+We build upon the notation used by \citep{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
 We build heavily on their notation, and discuss other similarities to our work in the next section.

### 2016-02-05 paper/introduction.tex
Greatly shortened summary in conclusion

@@
 \section{Introduction}
+\label{sec:intro}
+
 Abstraction plays a fundamental role in learning.
@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, \textit{exact abstractions}, which treat fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
+However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
 Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
-To overcome these issues we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical.
+To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical.
 This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
@@
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.
+\dnote{Would prefer a different example} For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \enote{Cite Dabe Icaps}.
 
@@
 This agenda has given rise to methods that reduce \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, e.g.
-optimal $Q$-values.
+In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, for example, optimal $Q$-values.
 Existing work has characterized how exact abstractions can fully maintain optimality in \acp{MDP}~\cite{li2006towards,dean1997modelmin}.
@@
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior.
+The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
@@
 This difference is particularly important in environments where no two states are identical.
-\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
+\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
 

### 2016-02-05 paper/related_work.tex

@@
 \subsection{Approximate State Abstraction}
-\citeauthoryear*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citep*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
 They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
@@
 Several approaches build on the notion of $\epsilon$-homogeneity.
-\citeauthoryear*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citeauthoryear*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
+\citep*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
+\citep*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
 
@@
 
-\Subsection{Specific Abstraction Algorithms}
+\subsection{Specific Abstraction Algorithms}
 Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citeauthoryear*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
+\citep*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citeauthoryear{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citeauthoryear*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
+\citep{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
+\citep*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
 The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work zzz pointer??.
-For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthoryear{li2006towards}.
+For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citep{li2006towards}.
 
@@
 
-\citeauthoryear*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
+\citep*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
 In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
@@
 Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods.
-Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citeauthoryear{li2006towards}.
+Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citep{li2006towards}.
 

### 2016-02-05 paper/conclusion.tex
added note to remember things
Incorporated michael and stefanie comments

@@
 % Learning abs functions online.
-First, we are interested in investigating learning various approximate abstraction functions online in the planning or \ac{RL} setting, a strategy first demonstrated by \citeauthor{ortner2013adaptive}.
-zzz what does that mean?
+First, we are interested in extending the approach of \citeauthor{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting.
+\dnote{Add year if possible}
 % Necessary conditions.
-Another question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e.
-the bound between the values under $\pi_G^*$, $\pi_{GA}$ is less than $\textsc{VMax}$).
-zzz perhaps too vague
+While our work presents several sufficient conditions for achieving bounded error of learned behavior with approximate abstractions, we hope to investigate what conditions are strictly necessary for an approximate abstraction to achieve bounded error.
 % Options/termporal abstraction
-We investigated the use of Options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.
-In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by Options, and approximate abstractions.
+We investigated the use of options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options.
+In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by options, and approximate abstractions.
 % Compressibility
-Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
+Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the degree of abstraction achievable in \acp{MDP}.
 

### 2016-02-05 paper/mdp_background.tex
Incorporated michael and stefanie comments

--- 2016-02-05 paper/background.tex
@@
-\section{Background}
+\section{\acp{MDP} and Sequential Decision Making}
 
@@
 
-zzz: I think empty sections like this are ugly. There ought to be some sort of preamble here.
+%zzz: I think empty sections like this are ugly. There ought to be some sort of preamble here.
 
 %MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
 \enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
@@
 \begin{equation}
-V^\pi(s) = \max_a Q^\pi(s,a).
+V^\pi(s) = Q^\pi(s,a).
 \end{equation}
 
-zzz no, that is not the standard definition. it would normally be $V^\pi(s) = Q^\pi(s,\pi(s))$.
+%zzz no, that is not the standard definition. it would normally be $V^\pi(s) = Q^\pi(s,\pi(s))$.
 
 Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citep{kaelbling1996reinforcement}.
-
-%Lihong Section
-\subsection{Abstraction Notation}
-We build upon the notation used by \citep{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
-We build heavily on their notation, and discuss other similarities to our work in the next section.
-
-\bdefn{$M_G$, $M_A$}
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-Consequently, this mapping induces an abstract MDP.
-Let $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
-\edefn
-
-% States
-\bdefn{$\mcS_A$, $\phi$}
-The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$.
-More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
-\begin{equation}
-\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
-\end{equation}
-\edefn
-
-zzz the space before the comma looks weird to me.
-
-\bdefn{$G$}
-Given a $\phi$, each ground state has associated with it the ground states with which it is aggregated.
-Similarly, each abstract state has its constituent ground states.
-We let $G$ be the function that retrieves these states:
-\begin{equation}
-G(s)=
-\begin{cases}
-\{g \in \mcS_G \mid \phi(g) = \phi(s) \},& s \in \mcS_G,\\
-\{g \in \mcS_G \mid \phi(g)=s \},& s \in \mcS_A.
-\end{cases}
-\end{equation}
-\edefn
-
-The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that for each abstract state, the weighting is a convex combination across all ground states.
-
-zzz it's weird that s is bound twice in this formula. is that needed/intentional?
-
-\bdefn{$\omega(s)$}
-We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$.
-The only restriction placed on the weighting scheme is that it induces a probability distribution on the states:
-\begin{equation}
-\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \textrm{ and }\hspace{6mm}  \omega(s) \in [0,1].
-\end{equation}
-\edefn
-
-% Reward
-\bdefn{$\mcR_A$}
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{R}_A(s,a) = \sum_{g \in G(s)} \mathcal{R}_G(g,a) \omega(g) .
-\end{equation}
-\edefn
-
-% Transition
-\bdefn{$\mcT_A$}
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
-\begin{equation}
-\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g).
-\end{equation}
-\edefn
-
-%\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
-%\dnote{This should be done in the background section, right? Just defining a value fund under a policy}
-
-% Subsection: Exact Abstraction Framework

### 2016-02-05 paper/related_work.tex
Incorporated michael and stefanie comments

@@
 \citep*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citep*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $gR$ provided by UCRL~\cite{auer2009near}.
-
-zzz what's $gR$?
+\citep*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
 
@@
 \citep*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work zzz pointer??.
+The agent will learn to ignore state variables that don't impact optimal behavior.
 For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citep{li2006towards}.
@@
 In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
-We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{model}$, to the approximate abstraction case.
+We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
 Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods.
@@
 
-zzz you shouldn't have $\phi_{model}$ because the word model will be typeset as the product of five variables. Some math mode magic is needed.
+%zzz you shouldn't have $\phi_{model}$ because the word model will be typeset as the product of five variables. Some math mode magic is needed.

### 2016-02-05 paper/results_discussion.tex
Incorporated michael and stefanie comments

@@
 %Explanation of what abstraction is used
-We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions. 
-zzz why? wouldn't it be better to show all 4?
+We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions.  \dnote{Some explanation of why we didn't do all 4 abstractions}
 For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.
@@
 For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
-First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}.
+First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in the top row of Figure~\ref{fig:main_empirical_results1}.
 The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
-Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2} so the tradeoff between abstract state space size and near optimality is made evident.
+Second, we report the value under the abstract policy of the initial ground state, also shown in the bottom row of Figure~\ref{fig:main_empirical_results1} so the tradeoff between abstract state space size and near optimality is made evident.
 In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient for data points in Minefield and NChain.
-
-zzz the font size in the figures needs to be larger---too tiny for my eyes
 
@@
 
-zzz why not include all the graphs in one figure?
-
-zzz wait, why do the policies in the highly abstracted random MDPs end up statistically significantly worse than random?? I'm not convinced these error bars are correct.
+\dnote{Explanation of why abstract Random policy might be worse than random policy}
 
@@
 % Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
-\begin{figure}
-\label{fig:main_empirical_results1}
+\begin{figure*}
 \centering
-
 \subfigure[NChain]{
@@
 }
+\subfigure[Minefield]{
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Taxi]{
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Random]{
+\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
+}
+
 \subfigure[NChain]{
 \includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
-}
-
-\subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
 }
@@
 }
-
-\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
-\end{figure}
-
-% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
-\begin{figure}
-\label{fig:main_empirical_results2}
-\centering
-\subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
-}
 \subfigure[Taxi]{
 \includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
-}
-
-\subfigure[Random]{
-\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
 }
@@
 }
+\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
+\end{figure*}
 
-\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
-\end{figure}
+% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
+%\begin{figure}
+%\label{fig:main_empirical_results2}
+%\centering
+%\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
+%\end{figure}

### 2016-02-05 paper/theory_results.tex
Incorporated michael and stefanie comments

@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $1/\epsilon$:
+There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $1/\epsilon$:
 \begin{equation}
@@
 % Proof
-\textbf{Proof:}
+\textbf{Proof of Lemma~\ref{lma:Q*}:}
 \enote{I would like a quick overview of the proof here if nobody objects.}
@@
 \mathcal{S}_T &= \begin{cases}
-\mathcal{S}_G,& T \leq 0, \\
+\mathcal{S}_G,& \text{if } T \leq 0, \\
 \mathcal{S}_A,& \text{o/w}
@@
 \mathcal{R}_T(s,a) &= \begin{cases}
-\mathcal{R}_G(s,a),& T \leq 0, \\
+\mathcal{R}_G(s,a),& \text{if } T \leq 0, \\
 \mathcal{R}_A(s, a),& \text{o/w}
@@
 \mcT_T(s,a,s') &= \begin{cases}
-\mcT_G(s,a,s'),& T \leq 0, \\
-\underset{{g \in G(s)}}{\sum}\left[w(g)\mcT_G(g, a, s')\right],& T = 1, \\
+\mcT_G(s,a,s'),& \text{if }T \leq 0, \\
+\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
 \mcT_A(s,a,s'),& \text{o/w}
@@
 \begin{cases}
-	   Q_G(s, a), &  T=0,\\
-	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right], & T = 1,\\
+	   Q_G(s, a), &  \text{if } T=0,\\
+	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
 	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a), &\text{o/w},
@@
 \begin{align*}
-&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
+&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right].
 \end{align*}
-Since all co-aggregated states have $Q$ values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
+Since all co-aggregated states have $Q$ values within $\epsilon$ of one another and $\omega(g)$ induces a convex combination,
 \begin{align*}
@@
 \begin{multline*}
-Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)\ \times \\ 
+Q_T(s_A, a) = \sum_{g \in G(s_A)}\omega(g)\ \times \\ 
  \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
 \end{multline*}
-Applying our inductive hypothesis yields
-zzz what is it less than or equal to?
+Applying our inductive hypothesis yields:
 \begin{multline*}
-\leq \sum_{g \in G(s_A)}w(g) * \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
+Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
 \end{multline*}
-%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
+%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
 Then,
 \begin{equation*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right].
+Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
 \end{equation*}
-zzz again, doesn't say what it is less than or equal to
 since all aggregated states have $Q$ values within $\epsilon$ of one another:
 \begin{align*}
-\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
-\therefore \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| &\leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
+Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
+\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
 \end{align*}
@@
 \begin{cases}
-\pi_G^*(s), \text{if $t<=0$},\\
-\pi_{GA}(s), \text{if $t > 0$}.
+\pi_G^*(s), &\text{if } t<=0,\\
+\pi_{GA}(s), &\text{if } t > 0.
 \end{cases}
 \end{equation}
-zzz inconsistent notation for cases. I like the ifs, but that's not how it appeared earlier.
 
@@
 \begin{multline*}
-V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right).
+V_G^{\pi_{A,t}}(s_G) \geq R_G(s_G, \pi_{A,t}(s_G))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, \pi_{A,t}(s_G), {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right).
 \end{multline*}
 Therefore,
-zzz more dangling inequalities below.
 \begin{align*}
 %&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G)).
+V_G^{\pi_{A,t}}(s_G) &\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G)).
 \end{align*}
@@
 \begin{align*}
-\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G) \\
+&V_G^{\pi_{A,t}}(s_G) \geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G) \\
 %&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
-\therefore V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
+\therefore\ &V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{align*}
@@
 
-{\bf Proof:} Our proof proceeds as follows.
+{\bf Proof of Lemma~\ref{lma:model}:} Our proof proceeds as follows.
 We demonstrate that states aggregated under $\epM$ have $Q$ values all within a particular bound.
@@
 Understanding $\epM$ as such an abstraction allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
-
-zzz so, these Qmodel things are formatted better. use the same formatting earlier?
 
@@
 where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$:
-zzz again... this dangling comparison operator thing is highly non-standard.
 \begin{multline*}
-=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
+B=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
 \biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
@@
 \begin{multline*}
-\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}') -\\ 
+B\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}')\ -\\ 
 T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr].
@@
 \begin{align*}
- \leq \epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \leq \epsilon + \gamma|\mcS_G|\epsilon Q_{max}.
+B \leq \epsilon + \gamma \textsc{QMax} \sum_{s_A \in \mcS_A} \epsilon \leq \epsilon + \gamma|\mcS_G|\epsilon \textsc{QMax}.
 \end{align*}
-zzz similarly, Qmax needs to be formatting differently.
-Applying 0-1 reward normalization and algebra:
+Since \textsc{QMax} $\leq \frac{\textsc{RMax}}{1-\gamma}$, and we defined $\textsc{RMax} = 1$:
 \begin{equation*}
- \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}.
+B \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}.
 \end{equation*}
-\enote{Do we need to state what Q max is and that it is upper bounded by 1 over 1 minus gamma or is this common knowledge? zzz not common knowledge, no.}
 Since the $Q$ values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
-\subsection{Boltzmann over Optimal Q: $\ep_{bolt}$}
+\subsection{Boltzmann over Optimal Q: $\epB$}
 \label{sec:boltz}
 
-zzz same with Qbolt.
-
-Here, we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$ values as equivalent.
-This family of abstractions is appealing as the Boltzmman distribution over $Q$ values has been of interest in the RL literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
-zzz all this theory is quite abstract.
+%zzz all this theory is quite abstract.
 is there some way to weave in a running example and/or to at least provide some more motiviation for why phiBoltz is desirable.
@@
 study it in the exact case?
-\bdefn{$\phi_{bolt}$}
-We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
+Here, we introduce the approximate abstraction family, $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$ values as equivalent.
+This family of abstractions is appealing as the Boltzmman distribution naturally balances exploration and exploitation~\cite{sutton1998reinforcement}.
+
+\bdefn{$\epB$}
+We let $\epB$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
 \begin{multline}
-\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
+\epB(s_1) = \epB(s_2) \rightarrow \\
 \forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon.
@@
 \edefn
-That is, zzz explain.
+\dnote{Possible explanation of what Boltzmann does in language, here}
 
@@
 \end{equation}
-\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$:
+\begin{lma} When $S_A$ is created using a function of the $\epB$ type, for some non-negative constant $k \in \mathbb{R}$:
 \begin{equation}
@@
 
-{\bf Proof Sketch:}
+{\bf Proof Sketch of Lemma~\ref{lma:bolt_lemma}:}
 
@@
 \end{equation}
-Consequently, we can consider $\widetilde{\phi}_{bolt}$ as a variation of $\epQ$, where the difference in $Q$ values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
+Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$ values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
 Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.
@@
 % Subsection: Multinomial over Optimal Q
-\subsection{Multinomial over Optimal Q: $\ep_{mult}$}
+\subsection{Multinomial over Optimal Q: $\epMu$}
 \label{sec:mult}
@@
 We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
-zzz a bit more info is needed. what advantages does it have over qboltz. if none, why do we need it?
-\bdefn{$\ep_{mult}$}
-We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$, satisfies
+\dnote{Relationship between multi and bolts, why need this one, argument: it's simpler!
+simpler is good}
+\bdefn{$\epMu$}
+We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
 \begin{multline}
-\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
+\epMu(s_1) = \epMu(s_2) \rightarrow \\
 \forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon.
@@
 \edefn
-That is, zzz.
+\dnote{Some explanation of what this one does}
 
@@
 \end{equation}
-zzz why is that ok? why is it useful? (overall, I think we should take a slightly more pedagogical perspective. we're not writing programs, we're writing explanations.
-\begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
+\dnote{Some explanation of why it's okay to assume this.
+Answer: Q magnitudes can be artbirarily off, making the denominators similar lets us say, Hm.
+These q magnitudes are roughly in the same ballpark.}
+%zzz why is that ok? why is it useful? (overall, I think we should take a slightly more pedagogical perspective. we're not writing programs, we're writing explanations.
+\begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k \in \mathbb{R}$:
 \begin{equation}
@@
 \end{equation}
+\label{lma:mult_lemma}
 \end{lma}
 
-{\bf Proof Sketch:} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.
-
+{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.
 \dnote{Bounds for multi and bolt suspiciously similar. Double check math}

### 2016-02-05 paper/abstraction_notation.tex
adding new abstraction notation section

--- 2016-02-05 paper/background.tex
@@
-\section{Background}
-
-%First, some background.
-
-zzz: I think empty sections like this are ugly. There ought to be some sort of preamble here.
-
-%MDP/SDM Background and Notation
-\subsection{\acp{MDP} and Sequential Decision Making}
-\enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
-An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
-Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
-We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$.
-The solution to an \ac{MDP} is called a policy, denoted $\pi: \mathcal{S} \mapsto \mathcal{A}$.
-
-The objective of an agent is to solve for the policy that maximizes its expected discounted reward from any state, denoted $\pi^*$.
-We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$.
-We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$, defined by the Bellman Equation as:
-\begin{equation}
-Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s)).
-\end{equation}
-Similarly, the value function defined under a given policy, denoted $V^\pi(s)$, is defined as:
-\begin{equation}
-V^\pi(s) = \max_a Q^\pi(s,a).
-\end{equation}
-
-zzz no, that is not the standard definition. it would normally be $V^\pi(s) = Q^\pi(s,\pi(s))$.
-
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citep{kaelbling1996reinforcement}.
-
 %Lihong Section
-\subsection{Abstraction Notation}
+\section{Abstraction Notation}
 We build upon the notation used by \citep{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
-We build heavily on their notation, and discuss other similarities to our work in the next section.
 
@@
 
-zzz the space before the comma looks weird to me.
+%zzz the space before the comma looks weird to me.
 
@@
 \begin{cases}
-\{g \in \mcS_G \mid \phi(g) = \phi(s) \},& s \in \mcS_G,\\
-\{g \in \mcS_G \mid \phi(g)=s \},& s \in \mcS_A.
+\{g \in \mcS_G \mid \phi(g) = \phi(s) \},& \text{if } s \in \mcS_G,\\
+\{g \in \mcS_G \mid \phi(g)=s \},& \text{if } s \in \mcS_A.
 \end{cases}
@@
 
-zzz it's weird that s is bound twice in this formula. is that needed/intentional?
+%zzz it's weird that s is bound twice in this formula. is that needed/intentional?
 

### 2016-02-05 paper/theory_results.tex

@@
 In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
-
-%In general, our proof strategy for each of the included results is as follows:
-%\begin{itemize}
-%\item First, we relate the values of states in the ground MDP to the value of states in the abstract \ac{MDP},
-%\item then, we relate the value of states in the ground \ac{MDP} to the value of states in the abstract \ac{MDP} under the optimal abstract policy.
-%\end{itemize}
-
-% Explanation of the above.
-%The first statement is relating Q values defined over the ground MDP with Q values defined over the abstract MDP, while the second statement is comparing the optimal Q values in the ground MDP, with the Q values in the ground MDP under the abstract policy.
-This is because our learners will solve for the optimal policy in the abstract, and use it in the ground MDP by mapping each ground state to its abstract state and querying the abstract policy for behavior.
-That is:
-%\begin{equation}
-%\pi_G(s) = \pi_A(\phi(s))
-%\end{equation}
-
-% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
-% In response^^^ Could add a sentence pointing out how these differ.
 
@@
 \textbf{Proof of Lemma~\ref{lma:Q*}:}
-\enote{I would like a quick overview of the proof here if nobody objects.}
+We first demonstrate that $Q$-values in the abstract \ac{MDP} are boundedly close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}).
+We next leverage Claim \ref{clm:closeQs} to demonstrate that the optimal action in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}  (Claim \ref{clm:optAbsActionNearOptGround}).
+Lastly, we use Claim \ref{clm:optAbsActionNearOptGround} to conclude Lemma \ref{lma:Q*} (Claim \ref{clm:lmaFromClm}).
 % Claim 1:
@@
 Lemma \ref{lma:Q*} follows from Claim \ref{clm:optAbsActionNearOptGround}.
+\label{clm:lmaFromClm}
 \end{clm}

### 2016-02-05 paper/theory_results.tex
Removed abs values for bounds and :s for foralls

@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $1/\epsilon$:
+There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\epsilon}$:
 \begin{equation}
-\forall_{s \in \mathcal{S}_G} | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(1/\epsilon).
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\epsilon} \right).
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in \mcS_G}: | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon}{(1-\gamma)^2}.
 \end{equation}
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
+\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi_G^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} | V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}.
+\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}.
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} \left| V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \right| \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in S_M} | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
+\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
 \end{equation}

### 2016-02-05 paper/results_discussion.tex
Added justification for just doing Q* and not other abstractions in empirical results as well as replaced a bunch of Q values with Q-values.

@@
 %Explanation of what abstraction is used
-We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions.  \dnote{Some explanation of why we didn't do all 4 abstractions}
+We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
+We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other 3 functions are reducable to particular $\epQ$ functions.
 For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.

### 2016-02-05 paper/theory_results.tex
Added justification for just doing Q* and not other abstractions in empirical results as well as replaced a bunch of Q values with Q-values.

@@
 
+\label{sec:theory_results}
 % Intro to approx state abstraction results.
@@
 \label{clm:closeQs}
-Optimal $Q$ values in the abstract \ac{MDP} closely resemble optimal $Q$ values in the ground \ac{MDP}:
+Optimal $Q$-values in the abstract \ac{MDP} closely resemble optimal $Q$-values in the ground \ac{MDP}:
 \begin{equation}
@@
 
-It follows that the $Q$ value of a state $s$ in $M^T$ for action $a$ is defined by:
+It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
 \begin{equation}
@@
 \end{align*}
-Since all co-aggregated states have $Q$ values within $\epsilon$ of one another and $\omega(g)$ induces a convex combination,
+Since all co-aggregated states have $Q$-values within $\epsilon$ of one another and $\omega(g)$ induces a convex combination,
 \begin{align*}
@@
 \end{equation*}
-since all aggregated states have $Q$ values within $\epsilon$ of one another:
+since all aggregated states have $Q$-values within $\epsilon$ of one another:
 \begin{align*}
@@
 \label{clm:optAbsActionNearOptGround}
-%The optimal action in the abstract MDP has a $Q$ value in the ground which is nearly optimal:
+%The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
 
@@
 \end{align*}
-The optimal action in the abstract MDP has a $Q$ value in the ground MDP that is nearly optimal:
+The optimal action in the abstract MDP has a $Q$-value in the ground MDP that is nearly optimal:
 \begin{equation}
@@
 {\bf Proof of Lemma~\ref{lma:model}:} Our proof proceeds as follows.
-We demonstrate that states aggregated under $\epM$ have $Q$ values all within a particular bound.
+We demonstrate that states aggregated under $\epM$ have $Q$-values all within a particular bound.
 Consequently, $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$.
@@
 
-Let $B$ stand for the maximum $Q$ value difference between any pair of ground states in the same abstract state under $\epM$:
+Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
 \begin{equation*}
@@
 \end{equation*}
-Since the $Q$ values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
@@
 study it in the exact case?
-Here, we introduce the approximate abstraction family, $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$ values as equivalent.
+Here, we introduce the approximate abstraction family, $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent.
 This family of abstractions is appealing as the Boltzmman distribution naturally balances exploration and exploitation~\cite{sutton1998reinforcement}.
@@
 \end{equation}
-Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$ values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
+Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$-values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
 Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.

### 2016-02-05 paper/theory_results.tex
Cleaned up some optimal Q notation
formatting misc

@@
 \end{thm}
-\enote{Axe the absolute values here and elsewhere}
-
-\enote{Unify the use of $\forall$ and ``:"s}
-
-\enote{Add for 0-1 normalized reward}
-
-\enote{Add note relating this all to Lihong for eps=0 and cut down the Lihong section}
 
@@
 
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
+Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of infinite geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
 Thus, we conclude Lemma~\ref{lma:Q*}.
@@
 \epB(s_1) = \epB(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon.
+\forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \epsilon.
 \label{eq:phi_bolt}
@@
 \begin{equation}
-\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k\times\epsilon.
+\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k\times\epsilon.
 \label{eq:bolt_denom}
@@
 \epMu(s_1) = \epMu(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon.
+\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \epsilon.
 \end{multline}

### 2016-02-05 paper/example_domains.tex
Added justification for just doing Q* and not other abstractions in empirical results as well as replaced a bunch of Q values with Q-values.
ex

@@
 \section{Example Domains}
-To illustrate our approximate abstraction functions, we apply $\epQ$ abstraction to four example domains---NChain, Taxi, Minefield and Random.
+We apply approximate abstraction to four example domains---NChain, Taxi, Minefield and Random.
 These domains were selected for their diversity---NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.
@@
 
-zzz problem: text says ``top row'', but image is oriented diagonally.
-
 % Minefield Compression Visuals
@@
 \end{figure}
-zzz the lines are very thin... not visible to me.
 

### 2016-02-05 paper/introduction.tex
Incorporated michael and stefanie comments
revamped some intro stuff in light of stefie michael comments

@@
 
+% Summary of the four abstractions.
+We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior.
+Each function family introduced aggregates states based on different approximate criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
+Furthermore, we empirically demonstrate the relationship between the degree of compression and error incurred on a variety of \acp{MDP}.
+
 % Summary	
-This paper is organized as follows.
+%\dnote{If we keep this, add section numbers, make it match the actual sections b/c we changed their order}
+%This paper is organized as follows.
 We first introduce the necessary terminology and background of \acp{MDP} and state abstraction.

### 2016-02-05 paper/theory_results.tex
revamped some intro stuff in light of stefie michael comments

@@
 % Q* Lemma -- lemma 1
-We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$.
+We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$, where states are aggregated together when their optimal $Q$-values are within $\epsilon$.
 
@@
 
-Now, consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$. 
+Now, consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
 \bdefn{$\epM$}
@@
 study it in the exact case?
-Here, we introduce the approximate abstraction family, $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent.
+Here, we introduce $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values.
 This family of abstractions is appealing as the Boltzmman distribution naturally balances exploration and exploitation~\cite{sutton1998reinforcement}.
+We find this family particularly interesting for abstraction purposes as it is much less strict than $\epQ$, and allows for aggregation when $Q$-value ratios are similar but their magnitudes are different.
 
@@
 \edefn
-\dnote{Possible explanation of what Boltzmann does in language, here}
 
@@
 We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
-\dnote{Relationship between multi and bolts, why need this one, argument: it's simpler!
-simpler is good}
+Additionally, the multinomial distribution is appealing due to its simplicity.
 \bdefn{$\epMu$}

### 2016-02-05 paper/conclusion.tex
Cleaned up some math and made citations work properly

@@
 % Learning abs functions online.
-First, we are interested in extending the approach of \citeauthor{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting.
+First, we are interested in extending the approach of \citet{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting.
 \dnote{Add year if possible}

### 2016-02-05 paper/introduction.tex
Cleaned up some math and made citations work properly

@@
 Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a results of Bellman's curse of dimensionality.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality.
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
@@
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior.
+The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.

### 2016-02-05 paper/related_work.tex
Cleaned up some math and made citations work properly

@@
 \subsection{Approximate State Abstraction}
-\citep*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
 They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
@@
 Several approaches build on the notion of $\epsilon$-homogeneity.
-\citep*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
-\citep*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
+\citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
+\citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
 
@@
 Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citep*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
+\citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citep{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citep*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
+\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
+\citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
 The agent will learn to ignore state variables that don't impact optimal behavior.
-For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citep{li2006towards}.
+For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}.
 
@@
 
-\citep*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
+\citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
 In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
@@
 Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods.
-Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citep{li2006towards}.
+Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
 

### 2016-02-05 paper/theory_results.tex
Cleaned up some math and made citations work properly

@@
 % Q* Lemma -- lemma 1
-We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$, where states are aggregated together when their optimal $Q$-values are within $\epsilon$.
+We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\epsilon$.
 
@@
 \textbf{Proof of Lemma~\ref{lma:Q*}:}
-We first demonstrate that $Q$-values in the abstract \ac{MDP} are boundedly close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}).
+We first demonstrate that $Q$-values in the abstract \ac{MDP} are close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}).
 We next leverage Claim \ref{clm:closeQs} to demonstrate that the optimal action in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}  (Claim \ref{clm:optAbsActionNearOptGround}).
@@
 where
-\begin{equation}
+\begin{equation*}
 \sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
-\end{equation}
+\end{equation*}
 
@@
 \begin{equation}
+\label{eq:clm1Induct}
 \forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
@@
 We assume as our inductive hypothesis that:
-\begin{equation}
+\begin{equation*}
 \forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
-\end{equation}
+\end{equation*}
 
@@
 \end{align*}
-Since $s_G$ and $s_A$ are arbitrary, we conclude
-\begin{equation}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t.
-\end{equation}
+Since $s_G$ and $s_A$ are arbitrary, we conclude Equation \ref{eq:clm1Induct}.
 
-As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore, Equation $\ref{eq:Q*Claim1}$ follows. \\
+As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \epsilon \gamma^t \rightarrow \frac{\epsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.\\
 
@@
 
-Now, consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
+Now, consider an approximate version of \citet{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
 \bdefn{$\epM$}
@@
 \edefn
-\dnote{Some explanation of what this one does}
 
@@
 \end{equation}
-\dnote{Some explanation of why it's okay to assume this.
-Answer: Q magnitudes can be artbirarily off, making the denominators similar lets us say, Hm.
-These q magnitudes are roughly in the same ballpark.}
-%zzz why is that ok? why is it useful? (overall, I think we should take a slightly more pedagogical perspective. we're not writing programs, we're writing explanations.
 \begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k \in \mathbb{R}$:

### 2016-02-05 paper/example_domains.tex
Cleaned up some math and made citations work properly
Changed all epsilons to varepsilons

@@
 Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
-We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
+We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}.
 
@@
 \label{fig:nchain-visual}
-\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\epsilon=0.5$}
+\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\varepsilon=0.5$}
 \end{figure}
@@
 %\label{fig:upworld-visual}
-%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
+%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\varepsilon=0.5$}
 %\end{figure}
@@
 %\label{fig:taxi-visual}
-%\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
+%\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\varepsilon=0.03$}
 %\end{figure}
@@
 The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward.
-(These are the states with ``mines'' in them.) We set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
+(These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=1.1, \kappa = 5, x = 0.01$.
 We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.
@@
 \label{fig:minefield-visual}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\epsilon=1.1$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=1.1$}
 \end{figure}
@@
 %\label{fig:minefield-visual}
-%\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
+%\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\varepsilon=0.2$}
 %\end{figure}

### 2016-02-05 paper/introduction.tex
Changed all epsilons to varepsilons

@@
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
+The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.

### 2016-02-05 paper/related_work.tex
Changed all epsilons to varepsilons

@@
 \subsection{Approximate State Abstraction}
-\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other.
+\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other.
 They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
 This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
-Several approaches build on the notion of $\epsilon$-homogeneity.
-\citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions.
+Several approaches build on the notion of $\varepsilon$-homogeneity.
+\citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\varepsilon$-homogenous partitions.
 \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
@@
 We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
-Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods.
-Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
+Note that when $\varepsilon=0$ our generalizations are equivalent to the corresponding exact methods.
+Additionally, when $\varepsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
 

### 2016-02-05 paper/results_discussion.tex
Changed all epsilons to varepsilons

@@
 For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
-First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in the top row of Figure~\ref{fig:main_empirical_results1}.
+First, we compare the number of states in the abstract \ac{MDP} for different values of $\varepsilon$, shown in the top row of Figure~\ref{fig:main_empirical_results1}.
 The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
@@
 Our empirical results corroborate our thesis---approximate state abstractions can decrease state space size while retaining bounded error.
-In both NChain and Minefield, we observe that, as $\epsilon$ increases from $0$, the number of states that must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
-Similarly for Taxi, when $\epsilon$ is between $.02$ and $.025$, we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
+In both NChain and Minefield, we observe that, as $\varepsilon$ increases from $0$, the number of states that must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
+Similarly for Taxi, when $\varepsilon$ is between $.02$ and $.025$, we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
 After $.025$, increased reduction in state space size comes at a cost of value.
-Lastly, as $\epsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
+Lastly, as $\varepsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
 
@@
 Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}.
-Taxi exhibits relative stability in state space size and behavior for $\epsilon$ up to $.02$, at which point both fall off dramatically.
+Taxi exhibits relative stability in state space size and behavior for $\varepsilon$ up to $.02$, at which point both fall off dramatically.
 We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible.
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost with increasng $\epsilon$, there are many near-optimal policies available to the agent that remain available.
+Thus, even as the information for optimal behavior is lost with increasng $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
 
@@
 }
-\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
+\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
 \end{figure*}
@@
 %\centering
-%\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
+%\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value}
 %\end{figure}

### 2016-02-05 paper/theory_results.tex
Changed all epsilons to varepsilons

@@
 \bdefn{$\ep_f$}
-Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\epsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
+Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\varepsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}
 \label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \epsilon.
+\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \varepsilon.
 \end{equation}
@@
 
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\epsilon$ of each other for all actions.
+That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\varepsilon$ of each other for all actions.
 
@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\epsilon}$:
+There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
 \begin{equation}
-\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\epsilon} \right).
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\varepsilon} \right).
 \end{equation}
@@
 % Q* Lemma -- lemma 1
-We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\epsilon$.
+We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
 
@@
 \begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \epsilon.
+\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\varepsilon}{(1-\gamma)^2}.
 \end{equation}
@@
 \label{eq:Q*Claim1}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\varepsilon}{1-\gamma}.
 \end{equation}
@@
 \label{eq:clm1Induct}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \varepsilon \gamma^{t},
 \end{equation}
@@
 \end{align*}
-Since all co-aggregated states have $Q$-values within $\epsilon$ of one another and $\omega(g)$ induces a convex combination,
+Since all co-aggregated states have $Q$-values within $\varepsilon$ of one another and $\omega(g)$ induces a convex combination,
 \begin{align*}
-&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a).
+&Q_1(s,a) \leq \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
 \end{align*}
@@
 \begin{equation}
-\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\epsilon \gamma^t.
+\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
 \end{equation}
@@
 \begin{equation*}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
+\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \varepsilon \gamma^t.
 \end{equation*}
@@
 \begin{multline*}
-Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
+Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
 \end{multline*}
-%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
+%&\leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
 Then,
 \begin{equation*}
-Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
+Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
 \end{equation*}
-since all aggregated states have $Q$-values within $\epsilon$ of one another:
+since all aggregated states have $Q$-values within $\varepsilon$ of one another:
 \begin{align*}
-Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
-\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
+Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
+\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
 \end{align*}
@@
 
-As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \epsilon \gamma^t \rightarrow \frac{\epsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.\\
+As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.\\
 
@@
 \label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}.
+V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
 \end{equation}
@@
 \begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}.
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\varepsilon}{1-\gamma}.
 \label{eq:Q*OptActionResult}
@@
 \begin{align}
-Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma}.
+Q_A(s_G, a^*_G) + \frac{\varepsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma}.
 \end{align}
@@
 \begin{align}
-Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}.
+Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
 \end{align}
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
+\forall_{t, s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\varepsilon}{1-\gamma}.
 \end{equation}
@@
 \begin{equation}
-V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G) + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}.
+V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G) + \sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma}.
 \end{equation}
@@
 \begin{multline*}
-V_G^{\pi_{A,t}}(s_G) \geq R_G(s_G, \pi_{A,t}(s_G))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, \pi_{A,t}(s_G), {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right).
+V_G^{\pi_{A,t}}(s_G) \geq R_G(s_G, \pi_{A,t}(s_G))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, \pi_{A,t}(s_G), {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} \right).
 \end{multline*}
@@
 \begin{align*}
-%&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
-V_G^{\pi_{A,t}}(s_G) &\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G)).
+%&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
+V_G^{\pi_{A,t}}(s_G) &\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G)).
 \end{align*}
@@
 \begin{align*}
-&V_G^{\pi_{A,t}}(s_G) \geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G) \\
-%&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
-\therefore\ &V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
+&V_G^{\pi_{A,t}}(s_G) \geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} - \frac{2\varepsilon}{1-\gamma} + V_{G}(s_G) \\
+%&\leq \sum_{i=0}^{t}\gamma^i \frac{2\varepsilon}{1-\gamma} + V_G(s_G)
+\therefore\ &V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\varepsilon}{1-\gamma}.
 \end{align*}
@@
 \begin{equation}
-\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi_G^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}.
+\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi_G^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\varepsilon}{1-\gamma}.
 \end{equation}
 
-Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of infinite geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
+Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\varepsilon}{1-\gamma} \rightarrow \frac{2\varepsilon}{(1-\gamma)^2}$ by the sum of infinite geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
 Thus, we conclude Lemma~\ref{lma:Q*}.
 %\begin{equation*}
-%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
+%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\varepsilon}{(1-\gamma)^2}
 %\end{equation*}
 %\begin{equation*}
-%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
+%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\varepsilon}{(1-\gamma)^2}
 %\end{equation*}
@@
 
-Now, consider an approximate version of \citet{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
+Now, consider an approximate version of \citet{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\varepsilon$.
 \bdefn{$\epM$}
-We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
+We let $\epM$ define a type of abstraction that, for fixed $\varepsilon$, satisfies:
 \begin{multline}
 \epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon\; \wedge\ \\
-\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon.
+\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \varepsilon\; \wedge\ \\
+\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \varepsilon.
 \end{multline}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}.
+\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\varepsilon + 2\gamma((|\mcS_G|-1)\varepsilon)}{(1-\gamma)^3}.
 \end{equation}
@@
 We demonstrate that states aggregated under $\epM$ have $Q$-values all within a particular bound.
-Consequently, $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$.
+Consequently, $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\varepsilon$.
 Understanding $\epM$ as such an abstraction allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
@@
 \begin{multline*}
-B\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}')\ -\\ 
+B\leq \varepsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}')\ -\\ 
 T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr].
@@
 \begin{align*}
-B \leq \epsilon + \gamma \textsc{QMax} \sum_{s_A \in \mcS_A} \epsilon \leq \epsilon + \gamma|\mcS_G|\epsilon \textsc{QMax}.
+B \leq \varepsilon + \gamma \textsc{QMax} \sum_{s_A \in \mcS_A} \varepsilon \leq \varepsilon + \gamma|\mcS_G|\varepsilon \textsc{QMax}.
 \end{align*}
@@
 \begin{equation*}
-B \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}.
+B \leq \frac{\varepsilon + \gamma(|\mcS_G| - 1) \varepsilon}{1-\gamma}.
 \end{equation*}
-Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$.
+Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\varepsilon = B$.
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
@@
 \bdefn{$\epB$}
-We let $\epB$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
+We let $\epB$ define a family of abstractions that, for fixed $\varepsilon$, satisfies:
 \begin{multline}
 \epB(s_1) = \epB(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \epsilon.
+\forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \varepsilon.
 \label{eq:phi_bolt}
@@
 
-We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
+We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\varepsilon$:
 \begin{equation}
-\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k\times\epsilon.
+\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k\times\varepsilon.
 \label{eq:bolt_denom}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\varepsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k\right)}{(1-\gamma)^2}.
 \end{equation}
@@
 \begin{align*}
-\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\epsilon}\right| \leq \epsilon
+\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon
 \end{align*}
@@
 \begin{equation}
-\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right).
+\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right).
 \label{eq:bolt_qs}
 \end{equation}
-Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$-values is bounded by $\epsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k \right)$.
+Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$-values is bounded by $\varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right)$.
 Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.
@@
 \bdefn{$\epMu$}
-We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
+We let $\epMu$ define a type of abstraction that, for fixed $\varepsilon$, satisfies
 \begin{multline}
 \epMu(s_1) = \epMu(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \epsilon.
+\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \varepsilon.
 \end{multline}
@@
 
-We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
+We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\varepsilon$:
 \begin{equation}
-\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon.
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\varepsilon.
 \end{equation}
@@
 \begin{equation}
-\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
+\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\varepsilon|\mathcal{A}|}{1-\gamma} + k \varepsilon^2 + k}{(1-\gamma)^2}.
 \end{equation}

### 2016-02-05 paper/results_discussion.tex
added new visuals

--- 2016-02-05 paper/results_discussion.tex
@@
 \subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy.pdf}
 }
 \subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy.pdf}
 }
 \subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy.pdf}
 }
 \subfigure[Random]{
-\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
+\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy.pdf}
 }

### 2016-02-05 paper/introduction.tex
Deleted some notes

@@
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
-\dnote{Would prefer a different example} For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \enote{Cite Dabe Icaps}.
+For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \cite{abel2015goal}.
 

### 2016-02-05 paper/example_domains.tex
new visuals

--- 2016-02-05 paper/example_domains.tex
@@
 The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward.
-(These are the states with ``mines'' in them.) We set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.
+(These are the states with ``mines'' in them.) We set $N=10, M=4, \epsilon=0.5, \kappa = 5, x = 0.01$.
 We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.
@@
 \label{fig:minefield-visual}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\epsilon=1.1$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\epsilon=0.5$}
 \end{figure}

### 2016-02-05 paper/abstraction_notation.tex

@@
 \section{Abstraction Notation}
-We build upon the notation used by \citep{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
+We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
 

### 2016-02-05 paper/example_domains.tex

--- 2016-02-05 paper/example_domains.tex
@@
 \subsection{Minefield}
-
+>
 Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$.
 The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward.
-(These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=1.1, \kappa = 5, x = 0.01$.
+(These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$.
 We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.
@@
 \label{fig:minefield-visual}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=1.1$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=0.5$}
 \end{figure}

### 2016-02-05 paper/mdp_background.tex
Deleted more notes

@@
 %MDP/SDM Background and Notation
-\enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
-An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+gAn \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
 Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
@@
 
-Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citep{kaelbling1996reinforcement}.
+Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citet{kaelbling1996reinforcement}.

### 2016-02-05 paper/example_domains.tex
visuls

@@
 % Subsection: NChain.
-\subsection{NChain}
+%\subsection{NChain}
 
@@
 % NChain Compression Visuals.
-\begin{figure}[h]
-\subfigure[Ground NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
-\subfigure[Abstract NChain]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
-\label{fig:nchain-visual}
-\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\varepsilon=0.5$}
-\end{figure}
+%\begin{figure}[h]
+%\centering
+%\subfigure[Ground NChain]{
+%\includegraphics[width=0.42\columnwidth]{figures/ground_nchain_small.png}}
+%\subfigure[Abstract NChain]{
+%\includegraphics[width=0.42\columnwidth]{figures/abs_nchain.png}}
+%\label{fig:nchain-visual}
+%\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\varepsilon=0.5$}
+%\end{figure}
 
@@
 % Subsection: Taxi
-\subsection{Taxi}
+%\subsection{Taxi}
 
@@
 % Subsection: Minefield.
-\subsection{Minefield}
->
+%\subsection{Minefield}
 Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$.
@@
 \begin{figure}
+\centering
 \subfigure[Ground Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
+\includegraphics[width=0.4\columnwidth]{figures/ground_minefield.png}}
 \subfigure[Abstract Minefield]{
-\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
+\includegraphics[width=0.4\columnwidth]{figures/abs_minefield.png}}
 \label{fig:minefield-visual}
@@
 % Subsection: Random.
-\subsection{Random}
+%\subsection{Random}
 
-In the Random \ac{MDP} domain we consider, there are $N$ states and $K$ actions. For each state, each action transitions to one of two randomly selected states, each with probability $0.5$.
+In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states, each with probability $0.5$.
 

### 2016-02-05 paper/results_discussion.tex
visuls

@@
 Lastly, as $\varepsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
-
-\dnote{Explanation of why abstract Random policy might be worse than random policy}
+When $\varepsilon = 0$, there is no reduction in state space size whatsoever (the ground \ac{MDP} has 100 states), because no two states have identical optimal $Q$-values.
 
@@
 Thus, even as the information for optimal behavior is lost with increasng $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
+Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform slightly worse than random behavior, as seen in the Random MDP.
 

### 2016-02-05 paper/introduction.tex
visuals added comments removed

@@
 This difference is particularly important in environments where no two states are identical.
-\dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
+Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
 

### 2016-02-05 paper/theory_results.tex
Deleted more notes
Did widow lines
trying to shorten

@@
 
-As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.\\
+As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.
 
@@
 {\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.
-\dnote{Bounds for multi and bolt suspiciously similar. Double check math}
 

### 2016-02-05 paper/theory_results.tex
Reduced lemma 2 size

--- 2016-02-05 paper/theory_results.tex
@@
 
-{\bf Proof of Lemma~\ref{lma:model}:} Our proof proceeds as follows.
-We demonstrate that states aggregated under $\epM$ have $Q$-values all within a particular bound.
-Consequently, $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\varepsilon$.
-Understanding $\epM$ as such an abstraction allows us to conclude our bound by applying Lemma \ref{lma:Q*}.
+{\bf Proof of Lemma~\ref{lma:model}:}
 
-Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
+Let $B$ be the maximum $Q$-value difference between any pair of ground states in the same abstract state for $\epM$:
 \begin{equation*}

### 2016-02-05 paper/theory_results.tex
widow line

@@
 
-{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.
+{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without $e^x \approx 1+x$.
 

### 2016-02-05 paper/example_domains.tex
Did widow lines
trying to shorten
Fixed typo
prepping for merge

@@
 % Description of visuals.
-We provide visuals of both ground \acp{MDP} and resulting abstract \acp{MDP} in which a grey circle indicates a state and colored arrows indicate transitions.
+We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain.
+A grey circle indicates a state and colored arrows indicate transitions.
 The thickness of the arrow indicates how much reward is associated with that transition.
@@
 
-NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian RL literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
+NChain is a simple \ac{MDP} investigated in the Bayesian \ac{RL} literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
 In all states, the agent has two actions available: advance down the chain, or return to state 0.
-The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain.
-The exception is that when the agent transitions to the last state in the chain, it receives a large positive reward, $r_{large}$.
+The agent receives $.2$ reward for returning to state 0, and no reward for advancing down the chain.
+The exception is that when the agent transitions to the last state in the chain, it receives $1.0$ reward.
 Transitions also have small slip probability $\rho$, such that the applied action results in the opposite dynamics.
-In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
+In our implementation, we set $N=10$ and $\rho=0.2$.
 
@@
 \subfigure[Ground Minefield]{
-\includegraphics[width=0.4\columnwidth]{figures/ground_minefield.png}}
+\includegraphics[width=0.35\columnwidth]{figures/ground_minefield.png}}
 \subfigure[Abstract Minefield]{
-\includegraphics[width=0.4\columnwidth]{figures/abs_minefield.png}}
+\includegraphics[width=0.35\columnwidth]{figures/abs_minefield.png}}
 \label{fig:minefield-visual}
@@
 
-In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states, each with probability $0.5$.
+In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states, probability $0.5$.
 

### 2016-02-05 paper/introduction.tex
prepping for merge

@@
 % Summary of the four abstractions.
-We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior.
-Each function family introduced aggregates states based on different approximate criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
+We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
 Furthermore, we empirically demonstrate the relationship between the degree of compression and error incurred on a variety of \acp{MDP}.

### 2016-02-05 paper/theory_results.tex
More widow line

--- 2016-02-05 paper/theory_results.tex
@@
 
-We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
-Additionally, the multinomial distribution is appealing due to its simplicity.
+We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to the Boltzmann distribution.
+Additionally, the multinomial distribution is appealing for its simplicity.
 \bdefn{$\epMu$}

### 2016-02-05 paper/theory_results.tex
More widows I think

--- 2016-02-05 paper/theory_results.tex
@@
 
-We now introduce some additional notation to formally discuss these results.
+We first introduce some additional notation.
 
@@
 
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
+Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
 Thus,

### 2016-02-05 paper/example_domains.tex

@@
 NChain is a simple \ac{MDP} investigated in the Bayesian \ac{RL} literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}.
-In all states, the agent has two actions available: advance down the chain, or return to state 0.
+In our implementation, we set $N=10$, normalized rewards between $0$ and $1$, and used a slip probability of $0.2$.
+
+%In all states, the agent has two actions available: advance down the chain, or return to state 0.
 The agent receives $.2$ reward for returning to state 0, and no reward for advancing down the chain.
@@
 \subfigure[Ground Minefield]{
-\includegraphics[width=0.35\columnwidth]{figures/ground_minefield.png}}
+\includegraphics[width=0.32\columnwidth]{figures/ground_minefield.png}}
 \subfigure[Abstract Minefield]{
-\includegraphics[width=0.35\columnwidth]{figures/abs_minefield.png}}
+\includegraphics[width=0.32\columnwidth]{figures/abs_minefield.png}}
 \label{fig:minefield-visual}
@@
 
-In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states, probability $0.5$.
+In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states with probability $0.5$.
 

### 2016-02-05 paper/results_discussion.tex

@@
 We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
-We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other 3 functions are reducable to particular $\epQ$ functions.
+We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions.
 For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.

### 2016-02-05 paper/results_discussion.tex
Widow line

@@
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost with increasng $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
-Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform slightly worse than random behavior, as seen in the Random MDP.
+Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
+Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
 

### 2016-02-05 paper/theory_results.tex
widowl

@@
 study it in the exact case?
-Here, we introduce $\epB$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values.
-This family of abstractions is appealing as the Boltzmman distribution naturally balances exploration and exploitation~\cite{sutton1998reinforcement}.
-We find this family particularly interesting for abstraction purposes as it is much less strict than $\epQ$, and allows for aggregation when $Q$-value ratios are similar but their magnitudes are different.
+Here, we introduce $\epB$, which aggregates states with similar Boltzmann distributions on $Q$-values.
+This family of abstractions is appealing as Boltzmman distributions balance exploration and exploitation~\cite{sutton1998reinforcement}.
+We find this family particularly interesting for abstraction purposes as, unlike $\epQ$, it allows for aggregation when $Q$-value ratios are similar but their magnitudes are different.
 

### 2016-02-05 paper/results_discussion.tex
shortened up

--- 2016-02-05 paper/results_discussion.tex
@@
 Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost with increasng $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
+Thus, even as the information for optimal behavior is lost with increasing $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
 Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform slightly worse than random behavior, as seen in the Random MDP.

### 2016-02-05 paper/theory_results.tex
shortened up

--- 2016-02-05 paper/theory_results.tex
@@
 
-We first introduce some additional notation.
+We now introduce some additional notation to formally discuss these results.
 
@@
 
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
+Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.
 Thus,
@@
 \end{equation*}
-where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$:
-\begin{multline*}
-B=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
-\biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
-\end{multline*}
+where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$. Since difference of rewards is bounded by $\varepsilon$:
+% Removed for space
+%\begin{multline*}
+%B=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
+%\biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
+%\end{multline*}
 \begin{multline*}

### 2016-02-05 paper/mdp_background.tex
shroteinings

@@
 %MDP/SDM Background and Notation
-gAn \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
 Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.

### 2016-02-05 paper/results_discussion.tex
prep for merge

--- 2016-02-05 paper/results_discussion.tex
@@
 \section{Approximate Abstraction on Example Domains}
-%Explanation of what abstraction is used
-We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions.
-We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions.
-For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.
-Since this approach represents an order-dependent approximation to the maximum amount of abstraction possible, we randomized the order in which states were considered across trials.
-Every ground state is equally weighted in its abstract state.
-
-%Explanation of what plots done
-For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
-First, we compare the number of states in the abstract \ac{MDP} for different values of $\varepsilon$, shown in the top row of Figure~\ref{fig:main_empirical_results1}.
-The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
-Second, we report the value under the abstract policy of the initial ground state, also shown in the bottom row of Figure~\ref{fig:main_empirical_results1} so the tradeoff between abstract state space size and near optimality is made evident.
-In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient for data points in Minefield and NChain.
-
-%Discuss results
-Our empirical results corroborate our thesis---approximate state abstractions can decrease state space size while retaining bounded error.
-In both NChain and Minefield, we observe that, as $\varepsilon$ increases from $0$, the number of states that must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
-Similarly for Taxi, when $\varepsilon$ is between $.02$ and $.025$, we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
-After $.025$, increased reduction in state space size comes at a cost of value.
-Lastly, as $\varepsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
-When $\varepsilon = 0$, there is no reduction in state space size whatsoever (the ground \ac{MDP} has 100 states), because no two states have identical optimal $Q$-values.
-
-Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}.
-Taxi exhibits relative stability in state space size and behavior for $\varepsilon$ up to $.02$, at which point both fall off dramatically.
-We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible.
-Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
-Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
 
 % Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
-\begin{figure*}
+\begin{figure*}[t]
 \centering
@@
 
+%Explanation of what abstraction is used
+We ran experiments with aggregation functions in the $\epQ$ family of approximate abstractions.
+We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions.
+For the purpose of illustrating what kinds of approximations are possible we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria.
+Since this approach represents an order-dependent approximation to the maximum amount of abstraction possible, we randomized the order in which states were considered across trials.
+Every ground state is equally weighted in its abstract state.
+
+%Explanation of what plots done
+For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
+First, we compare the number of states in the abstract \ac{MDP} for different values of $\varepsilon$, shown in the top row of Figure~\ref{fig:main_empirical_results1}.
+The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
+Second, we report the value under the abstract policy of the initial ground state, also shown in the bottom row of Figure~\ref{fig:main_empirical_results1} so the tradeoff between abstract state space size and near optimality is made evident.
+In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient for data points in Minefield and NChain.
+
+%Discuss results
+Our empirical results corroborate our thesis---approximate state abstractions can decrease state space size while retaining bounded error.
+In both NChain and Minefield, we observe that, as $\varepsilon$ increases from $0$, the number of states that must be planned over is reduced, and optimal behavior is either fully maintained (NChain) or very nearly maintained (Minefield).
+Similarly for Taxi, when $\varepsilon$ is between $.02$ and $.025$, we observe a reduction in the number of states in the abstract \ac{MDP} while value is fully maintained.
+After $.025$, increased reduction in state space size comes at a cost of value.
+Lastly, as $\varepsilon$ is increased in the Random domain, there is a smooth reduction in the number of abstract states with a corresponding cost in the value of the derived policy.
+When $\varepsilon = 0$, there is no reduction in state space size whatsoever (the ground \ac{MDP} has 100 states), because no two states have identical optimal $Q$-values.
+
+Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}.
+Taxi exhibits relative stability in state space size and behavior for $\varepsilon$ up to $.02$, at which point both fall off dramatically.
+We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible.
+Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
+Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
+Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
+
 % Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.

### 2016-02-05 paper/theory_results.tex
shroteinings
prep for merge

--- 2016-02-05 paper/theory_results.tex
@@
 
-It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
+The $Q$-value of a state $s$ in $M^T$ for action $a$ is:
 \begin{equation}
@@
 \end{lma}
-We prove Lemma~\ref{lma:bolt_lemma} using the approximation for $e^x$:
+We use the approximation for $e^x$, with $\delta$ error:
 \begin{equation}
- e^x = 1 + x + \delta  \approx 1 + x
+ e^x = 1 + x + \delta  \approx 1 + x.
 \label{eq:e_to_x_approx}
 \end{equation}
-where $\delta$ is the error associated with the approximation.
 

### 2016-02-05 paper/results_discussion.tex
In length now yay

@@
 The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over.
-Second, we report the value under the abstract policy of the initial ground state, also shown in the bottom row of Figure~\ref{fig:main_empirical_results1} so the tradeoff between abstract state space size and near optimality is made evident.
-In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient for data points in Minefield and NChain.
+Second, we report the value under the abstract policy of the initial ground state, also shown in the bottom row of Figure~\ref{fig:main_empirical_results1}.
+In the Taxi and Random domains, 200 trials were run for each data point, whereas 20 trials were sufficient in Minefield and NChain.
 
@@
 Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
-Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
+%Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
 

### 2016-02-05 paper/results_discussion.tex
Changes section name and added sentence

@@
-\section{Approximate Abstraction on Example Domains}
+\section{Empirical Results}
 
@@
 We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible.
-Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available.
-%Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
+Conversely, in the Random domain, a great deal of near optimal policies are available to the agent.
+Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near optimal policies available to the agent that remain available.
+Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
 

### 2016-02-05 paper/introduction.tex
Up through abstraction notation

@@
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
-For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \cite{abel2015goal}.
+For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects with which it is working \cite{abel2015goal}.
 

### 2016-02-05 paper/related_work.tex
Up through abstraction notation

@@
 \citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other.
-They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP.
-This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
+They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}.
 Several approaches build on the notion of $\varepsilon$-homogeneity.
@@
 \citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
-The agent will learn to ignore state variables that don't impact optimal behavior.
 For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}.
@@
 We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
-Note that when $\varepsilon=0$ our generalizations are equivalent to the corresponding exact methods.
-Additionally, when $\varepsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
+Our generalizations are equivalent to theirs when exact criteria are used.
+Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
 

### 2016-02-05 paper/abstraction_notation.tex
Pushing us over

@@
 \bdefn{$M_G$, $M_A$}
-We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme.
-Consequently, this mapping induces an abstract MDP.
+We understand an abstraction as a mapping from the state space of a ground \ac{MDP}, $M_G$, to that of an abstract MDP, $M_A$, using a state-aggregation scheme.
+Consequently, this mapping induces an abstract \ac{MDP}.
 Let $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
@@
 We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$.
-The only restriction placed on the weighting scheme is that it induces a probability distribution on the states:
+The only restriction placed on the weighting scheme is that it induces a probability distribution on the ground states of each abstract state:
 \begin{equation}

### 2016-02-05 paper/example_domains.tex
adding results ex and theory changes

@@
 Taxi has long been studied by the hierarchical RL literature~\cite{dietterich2000hierarchical}.
-The agent, operating in a grid-world style domain, may move left, right, up, and down, as well as pick up a passenger and drop off a passenger.
+The agent, operating in a Grid World style domain~\cite{russell1995modern}, may move left, right, up, and down, as well as pick up a passenger and drop off a passenger.
 The goal is achieved when the agent has taken all passengers to their destinations.
@@
 %\subsection{Minefield}
-Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$.
+Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$.
 The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward.
@@
 \subfigure[Ground Minefield]{
-\includegraphics[width=0.32\columnwidth]{figures/ground_minefield.png}}
+\includegraphics[width=0.34\columnwidth]{figures/ground_minefield.png}}
 \subfigure[Abstract Minefield]{
-\includegraphics[width=0.32\columnwidth]{figures/abs_minefield.png}}
+\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
 \label{fig:minefield-visual}

### 2016-02-05 paper/theory_results.tex
Compiling now...
adding results ex and theory changes

@@
 \label{eq:Q*Claim2}
-V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
+V_G(s_G) \leq Q_G(s_G, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
 \end{equation}
@@
 \begin{align}
-&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\varepsilon}{1-\gamma}.
+&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma}.
 \label{eq:Q*OptActionResult}
 \end{align}
+
 By the definition of $a^*_A$, we know that 
 \begin{align}
-Q_A(s_G, a^*_G) + \frac{\varepsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma}.
+Q_A(s_A, a^*_G) + \frac{\varepsilon}{1-\gamma} \leq Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma}.
 \end{align}
+
 Lastly, again by Claim~\ref{clm:closeQs}, we know
 \begin{align}
-Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
+Q_A(s_A, a^*_A) + \frac{\varepsilon}{1-\gamma} \leq Q_G(s_g, a^*_A) + \frac{2\varepsilon}{1-\gamma}.
 \end{align}
@@
 
-We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\varepsilon$:
+We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k \in \mathbb{R}$, of $\varepsilon$:
 \begin{equation}

### 2016-04-30 icml_workshop/conclusion.tex
icml workshop

--- 2016-02-05 paper/conclusion.tex
@@
 In this work, we proved bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
-We also empirically demonstrate that approximate abstractions can reduce state space size with negligible loss in the quality of the behavior.
+We also empirically demonstrate that approximate abstractions can reduce state space size with minor loss in the quality of the behavior.
 
@@
 Third, methods that employ approximate aggregation techniques are able to tune the aggressiveness of abstraction all the while incurring bounded error.
-We empirically demonstrate the relationship between $\epsilon$ and the degree of compression, as well as the value of the abstract policy on four dramatically different \acs{MDP}.
+We empirically demonstrate the relationship between $\varepsilon$ and the degree of compression, as well as the value of the abstract policy on four dramatically different \acs{MDP}.
 We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.
@@
 First, we are interested in extending the approach of \citet{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting.
-\dnote{Add year if possible}
 % Necessary conditions.
@@
 % Options/termporal abstraction
-We investigated the use of options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options.
-In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by options, and approximate abstractions.
+%We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options. 
+In the future, we are interested in characterizing the relationship between temporal abstractions, such as options ~\cite{sutton1999between}, and approximate abstractions.
 % Compressibility

### 2016-04-30 icml_workshop/abstraction_desiderata.tex
adding some more structure to tex

\section{Two Desiderata for Abstraction in RL}

We propose the following two desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
\begin{enumerate}
\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller \dnote{requires further info}. In general, \acp{MDP} of interest that are intractable are typically made so in virtue of the size of their state space, not the size of the action space or transition model.
\item \textsc{Optimality}: To induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
\end{enumerate}

\dnote{Defense of the desiderata}

Critically, either desiderata is trivial to satisfy on its own.

Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space $S_1$, which consists of a single (arbitrary) state from $S_G$. Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.

Now consider \textsc{Optimality}. Again, we can develop a simple method for satisfying this desiderata on its own. Namely, consider the MDP $M_A$, that is identical to $M_G$. Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.

The interesting case is satisfying {\it both} desiderata. To the best of our knowledge, no theory of temporal abstraction sufficiently satisfies the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.

### 2016-04-30 icml_workshop/introduction.tex
adding some more structure to tex

--- 2016-02-05 paper/introduction.tex
@@
 
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant.
+\dnote{Abstraction pitch}
+% Introduce a pitch about abstraction that's a bit different from our other paper.
+Intelligent agents that leverage abstraction may reason about just the salient features of their environment, while ignoring what is irrelevant.
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
@@
 % Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
+%Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
 Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
@@
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
-For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \cite{abel2015goal}.
+For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects with which it is working \cite{abel2015goal}.
 
+\dnote{Prior work summary}
 % Existing work on state abstraction.
-Thus, a key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-This agenda has given rise to methods that reduce \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
+A key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+This agenda has given rise to various methods of abstraction that reduce the size of \acp{MDP} with large state spaces; \dnote{Overview of abstraction methods}
+
+\dnote{Close with a lack of clarity about what is meaningful to retain from an abstraction theory}
+
+In this work, we propose two desiderata on theories of abstraction in the context of planning or learning in an \ac{MDP}; the first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}, while the second we coin \textsc{Optimality}, stating that abstractions ought to maintain at least some notion of optimality.
+We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata.
+In light of these desiderata, we propose a formal framework that allows for simple state-abstraction methods as well as extension to temporal abstractions.
+We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata.
+Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions.
+We argue that the present state of the literature is inconclusive as to the effectiveness of options in general, and that, the theory of temporal abstraction afforded by the state aggregation approach allows for the satisfaction of both \textsc{Compressibility} and \textsc{Optimality}.
+We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.
+
+% ---- OLD STUFF ----
 In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, for example, optimal $Q$-values.

### 2016-04-30 icml_workshop/abstraction_desiderata.tex
Some commits

@@
 \begin{enumerate}
-\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller \dnote{requires further info}.
-In general, \acp{MDP} of interest that are intractable are typically made so in virtue of the size of their state space, not the size of the action space or transition model.
+\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller. \footnote{where smallness is understood as defined in the of \cite{LITTMAN COMPLEXITY}  blah blah blah}
 \item \textsc{Optimality}: To induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
@@
 
-Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space $S_1$, which consists of a single (arbitrary) state from $S_G$.
+Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state from $S_G$.
 Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.
@@
 The interesting case is satisfying {\it both} desiderata.
-To the best of our knowledge, no theory of temporal abstraction sufficiently satisfies the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
+To the best of our knowledge, no theory of temporal abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.

### 2016-04-30 icml_workshop/introduction.tex
Some commits

@@
 This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-The remainder of our introduction contextualizes these intuitions in \acp{MDP}.
+The remainder of our introduction contextualizes these intuitions in \acp{MDP}.%This is the paragraph from ICML 2016
 
@@
 We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata.
-In light of these desiderata, we propose a formal framework that allows for simple state-abstraction methods as well as extension to temporal abstractions.
-We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata.
+
+In light of these desiderata, we summarize a formal framework that allows for simple state-abstraction methods as well as propose an extension to temporal abstractions.
+\enote{Summarize the formal abstraction bit -- MDP} We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata.
 Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions.
@@
 We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.
+
+%
 

### 2016-04-30 icml_workshop/introduction.tex
Ellis first writeup of introduction.

--- 2016-02-05 paper/introduction.tex
@@
 
-Abstraction plays a fundamental role in learning.
-Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant.
-Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
+\dnote{Abstraction pitch}
+%Abstraction is useful
+Intelligent agents that leverage abstraction may reason about the salient features of their environment, while ignoring what is irrelevant.
+Consequently, agents that utilize abstraction are able to solve considerably more complex problems than they would be able to without the use of abstraction.
+
+%Planning and RL is hard
+For this reason abstraction is of considerable interest in planning and \ac{RL} work.\cite{LIHONG, US ICML, OTHERS} Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity} and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous.
+\cite{HARD LARGE CONTINOUS ACTION SPACE}.
+Abstraction, then, promises an alluring avenue through which planning and \ac{RL} techniques might gain traction in complex domains.
+
+%Summarize related work
+Indeed BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK
+
+%We propose desiderata
+In this work, we formalize what it means for an abstraction to be good in planning and \ac{RL}.
+In particular, we propose  two desiderata that a good abstraction should hope to satisfy.
+The first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}.
+The second we coin \textsc{Optimality}, which states that abstractions ought to maintain at least some notion of optimality.
+
+%We summarize framework, propose extension and then ground out desiderata in framework
+Lastly, we summarize our previously proposed formal framework for state-abstraction methods, propose an extension to temporally-extended abstractions and then formally ground out the two desiderata with the extended framework.
+
+%Current scrap
+%---------------
+%We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata.
+Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions.
+We argue that the present state of the literature is inconclusive as to the effectiveness of options in general, and that, the theory of temporal abstraction afforded by the state aggregation approach allows for the satisfaction of both \textsc{Compressibility} and \textsc{Optimality}.
+We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.
+
+%However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
 Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
@@
 
-% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
-Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality.
-Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
-For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects with which it is working \cite{abel2015goal}.
+%We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata.
 
+%\dnote{Prior work summary}
 % Existing work on state abstraction.
-Thus, a key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-This agenda has given rise to methods that reduce \textit{ground} \acp{MDP} with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity.
-In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, for example, optimal $Q$-values.
+%A key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
+This agenda has given rise to various methods of abstraction that reduce the size of \acp{MDP} with large state spaces; \dnote{Overview of abstraction methods}
+
+%\dnote{Close with a lack of clarity about what is meaningful to retain from an abstraction theory}
+
+% ---- OLD STUFF ----
+%In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, for example, optimal $Q$-values.
 Existing work has characterized how exact abstractions can fully maintain optimality in \acp{MDP}~\cite{li2006towards,dean1997modelmin}.
@@
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
+%The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
@@
 % Summary of the four abstractions.
-We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
+%We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
 Furthermore, we empirically demonstrate the relationship between the degree of compression and error incurred on a variety of \acp{MDP}.

### 2016-04-30 icml_workshop/desiderata.tex
adding desid

--- 2016-04-30 icml_workshop/abstraction_desiderata.tex
@@
 \begin{enumerate}
-\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller. \footnote{where smallness is understood as defined in the of \cite{LITTMAN COMPLEXITY}  blah blah blah}
-\item \textsc{Optimality}: To induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
+\item \textsc{Compressibility}: A theory ought to give guidance on how to compress $M_G$ to be significantly smaller.
+\footnote{where smallness is understood as in \cite{littman1995complexity}, with respect to $|\mathcal{S}|$, $|\mathcal{A}|$, and the information content required to represent input-output pairs of $\mathcal{T}$ and $\mathcal{R}$.}
+\item \textsc{Optimality}: A theory ought to provide a method for inducing an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
 \end{enumerate}
 
-\dnote{Defense of the desiderata}
+% Defense of the desiderata.
+Abstraction is aimed at reducing the dimensionality of an entity; this {\it reduction} is captured by \textsc{Compressibility}, while the {\it preservation} of critical information content of the entity is captured by \textsc{Optimality}.
+\dnote{Note about how to satisfy them?}.
 
@@
 Now consider \textsc{Optimality}.
-Again, we can develop a simple method for satisfying this desiderata on its own.
-Namely, consider the MDP $M_A$, that is identical to $M_G$.
+Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$.
 Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.
 
-The interesting case is satisfying {\it both} desiderata.
+In isolation, either is trivially satisfiable.
+
+The interesting (and difficult) case is satisfying {\it both} desiderata.
 To the best of our knowledge, no theory of temporal abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
+After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

### 2016-04-30 icml_workshop/introduction.tex
adding intro

@@
 %Planning and RL is hard
-For this reason abstraction is of considerable interest in planning and \ac{RL} work.\cite{LIHONG, US ICML, OTHERS} Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity} and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous.
+For this reason abstraction is of considerable interest in planning and \ac{RL} work.\cite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state} Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity}, and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous.
 \cite{HARD LARGE CONTINOUS ACTION SPACE}.
-Abstraction, then, promises an alluring avenue through which planning and \ac{RL} techniques might gain traction in complex domains.
+Abstraction, then, promises an alluring avenue through which planning and \ac{RL} techniques may gain traction in complex domains.
 
 %Summarize related work
-Indeed BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK BLAH BLAH BLAH LOOK AT ALL THIS RELATED WORK
+\dnote{summary of related}
 
 %We propose desiderata
-In this work, we formalize what it means for an abstraction to be good in planning and \ac{RL}.
-In particular, we propose  two desiderata that a good abstraction should hope to satisfy.
+In this work, we formalize what it means for an abstraction to be effective in planning and \ac{RL}.
+In particular, we propose  two desiderata that a theory of abstraction should satisfy.
 The first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}.
@@
 %We summarize framework, propose extension and then ground out desiderata in framework
-Lastly, we summarize our previously proposed formal framework for state-abstraction methods, propose an extension to temporally-extended abstractions and then formally ground out the two desiderata with the extended framework.
+Additionally, we summarize our previously proposed formal framework for state-abstraction methods, and demonstrate that the framework allows for careful formal analysis of temporally-extended abstractions.
+In particular the framework allows us to characterize what types of temporal abstraction do and do not satisfy the \textsc{Compressibility} and \textsc{Optimality}.
+Of special interest is determining proving what the necessary or sufficient conditions are for an option to be useful in planning or learning.
 

### 2016-04-30 icml_workshop/related_work.tex
icml workshop

--- 2016-02-05 paper/related_work.tex
@@
 
-Several other projects have addressed similar topics.
+Considerable work in planning and \ac{RL} has grappled with, either in the form of state aggregation (DEFINE?) or temporally extended actions (DEFINE?).
+
+\subsection{Abstraction as State Aggregation}
 
 \subsection{Approximate State Abstraction}
+
 \citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other.
@@
 
-\subsection{Specific Abstraction Algorithms}
+\dnote{We'll definitely need to discuss Bai, Srivasta, and Russell's new paper at IJCAI 2016.}
+
 Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
@@
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
+
 \citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
 \citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
-For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}.
+
+For a more complete survey of algorithms that leverage state aggregation in past reinforcement-learning papers, see \citet{li2006towards}.
 
@@
 
-%zzz you shouldn't have $\phi_{model}$ because the word model will be typeset as the product of five variables. Some math mode magic is needed.
+\subsection{Abstraction as Temporal Extension}
+Previous \textit{macro-action} or \textit{options}

### 2016-04-30 icml_workshop/framework.tex
adding framy

\section{Abstraction Framework}

In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}. In this work we develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$,

Formalism

Extension to Temp Ext

Satisfying Desiderata

### 2016-04-30 icml_workshop/desiderata.tex
Touched up Dave's desidarata section

@@
 Critically, either desiderata is trivial to satisfy on its own.
-
-Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state from $S_G$.
+Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action).
 Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.
-
 Now consider \textsc{Optimality}.
@@
 
-In isolation, either is trivially satisfiable.
-
 The interesting (and difficult) case is satisfying {\it both} desiderata.
-To the best of our knowledge, no theory of temporal abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
+To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
 After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

### 2016-04-30 icml_workshop/introduction.tex
adding intro changes

@@
 
-\dnote{Abstraction pitch}
-%Abstraction is useful
+% Abstraction is useful.
 Intelligent agents that leverage abstraction may reason about the salient features of their environment, while ignoring what is irrelevant.
@@
 
-%Planning and RL is hard
-For this reason abstraction is of considerable interest in planning and \ac{RL} work.\cite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state} Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity}, and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous.
-\cite{HARD LARGE CONTINOUS ACTION SPACE}.
+% Planning and RL is hard.
+For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
+Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity}, and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous~\cite{antos2008fitted,konidaris2014constructing}.
 Abstraction, then, promises an alluring avenue through which planning and \ac{RL} techniques may gain traction in complex domains.
 
-%Summarize related work
+% Summarize related work.
 \dnote{summary of related}
+Lorem ipsum.
 
-%We propose desiderata
-In this work, we formalize what it means for an abstraction to be effective in planning and \ac{RL}.
+% We propose desiderata.
+In this work, we characterize what it means for an abstraction to be effective in planning and \ac{RL}.
 In particular, we propose  two desiderata that a theory of abstraction should satisfy.
@@
 
-%We summarize framework, propose extension and then ground out desiderata in framework
+% Outline: We summarize framework, propose extension and then ground out desiderata in framework.
 Additionally, we summarize our previously proposed formal framework for state-abstraction methods, and demonstrate that the framework allows for careful formal analysis of temporally-extended abstractions.
 In particular the framework allows us to characterize what types of temporal abstraction do and do not satisfy the \textsc{Compressibility} and \textsc{Optimality}.
-Of special interest is determining proving what the necessary or sufficient conditions are for an option to be useful in planning or learning.
-
-%Current scrap
-%---------------
-%We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata.
-Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions.
-We argue that the present state of the literature is inconclusive as to the effectiveness of options in general, and that, the theory of temporal abstraction afforded by the state aggregation approach allows for the satisfaction of both \textsc{Compressibility} and \textsc{Optimality}.
-We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.
-
-%However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
-Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
-To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical.
-This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.
-The remainder of our introduction contextualizes these intuitions in \acp{MDP}.
-
-%We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata.
-
-%\dnote{Prior work summary}
-% Existing work on state abstraction.
-%A key research agenda for planning and \ac{RL} is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}.
-This agenda has given rise to various methods of abstraction that reduce the size of \acp{MDP} with large state spaces; \dnote{Overview of abstraction methods}
-
-%\dnote{Close with a lack of clarity about what is meaningful to retain from an abstraction theory}
-
-% ---- OLD STUFF ----
-%In the context of \acp{MDP}, we understand exact abstractions as those that aggregate states with equal values of particular quantities, for example, optimal $Q$-values.
-Existing work has characterized how exact abstractions can fully maintain optimality in \acp{MDP}~\cite{li2006towards,dean1997modelmin}.
-
-% Thesis: Approximate abstraction for three reasons.
-%The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
-First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.
-In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction.
-Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions.
-This difference is particularly important in environments where no two states are identical.
-Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
-
-% Summary of the four abstractions.
-%We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
-Furthermore, we empirically demonstrate the relationship between the degree of compression and error incurred on a variety of \acp{MDP}.
-
-% Summary	
-%\dnote{If we keep this, add section numbers, make it match the actual sections b/c we changed their order}
-%This paper is organized as follows.
-We first introduce the necessary terminology and background of \acp{MDP} and state abstraction.
-We then survey existing types of state abstraction as applied to sequential decision making.
-The following section introduces our primary result; bounds on the error guaranteed by four classes of approximate state abstraction.
-We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.
+Of special interest is proving what the necessary or sufficient conditions are for an option to be useful in planning or learning.
+\dnote{come back to dis sentence}

### 2016-04-30 icml_workshop/introduction.tex
Added MDP background and consistency with 3 desiderata

@@
 For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
+Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.
+
+A \ac{MDP} is a 5-tuple, $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+$\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
+We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$.
+The solution to an \ac{MDP} is called a policy, denoted $\pi: \mathcal{S} \mapsto \mathcal{A}$.
+The objective of an agent is to solve for the policy that maximizes its expected discounted reward from any state, denoted $\pi^*$.
+
  Although planning for optimal behavior in \acp{MDP} is known to be P-Complete in the size of the state and action space~\cite{papadimitriou1987complexity,littman1995complexity}, and many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples only polynomial in the size of the state space~\cite{strehl2009reinforcement}, many state spaces are known to grown super-polynomially with the number of variables that characterize the domain \cite{abel2015goal} and robust action spaces are often large or even continuous~\cite{antos2008fitted,konidaris2014constructing}.
@@
 In this work, we characterize what it means for an abstraction to be effective in planning and \ac{RL}.
-In particular, we propose  two desiderata that a theory of abstraction should satisfy.
+In particular, we propose three desiderata that a theory of abstraction should satisfy.
 The first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}.
 The second we coin \textsc{Optimality}, which states that abstractions ought to maintain at least some notion of optimality.
+The last we term \textsc{Efficient-Computability} which states that an abstraction ought to be tractably computable.
 
@@
 Additionally, we summarize our previously proposed formal framework for state-abstraction methods, and demonstrate that the framework allows for careful formal analysis of temporally-extended abstractions.
-In particular the framework allows us to characterize what types of temporal abstraction do and do not satisfy the \textsc{Compressibility} and \textsc{Optimality}.
+In particular the framework allows us to characterize what types of temporal abstraction do and do not satisfy \textsc{Compressibility}, \textsc{Optimality} and \textsc{Efficient-Computability}.
 Of special interest is proving what the necessary or sufficient conditions are for an option to be useful in planning or learning.

### 2016-04-30 icml_workshop/desiderata.tex
adding dizzy

@@
-\section{Two Desiderata for Abstraction in RL}
+\section{Three Desiderata for Abstraction in RL}
 
-We propose the following two desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
+We propose the following three desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
 \begin{enumerate}
-\item \textsc{Compressibility}: A theory ought to give guidance on how to compress $M_G$ to be significantly smaller.
+\item \textsc{Compressibility}: An abstraction ought to compress $M_G$ to be significantly smaller.
 \footnote{where smallness is understood as in \cite{littman1995complexity}, with respect to $|\mathcal{S}|$, $|\mathcal{A}|$, and the information content required to represent input-output pairs of $\mathcal{T}$ and $\mathcal{R}$.}
-\item \textsc{Optimality}: A theory ought to provide a method for inducing an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
+\item \textsc{Optimality}: An abstraction ought to induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
+\item \textsc{Efficient-Computability}: An abstraction ought to consist of information that is efficient to compute.
 \end{enumerate}
@@
 % Defense of the desiderata.
-Abstraction is aimed at reducing the dimensionality of an entity; this {\it reduction} is captured by \textsc{Compressibility}, while the {\it preservation} of critical information content of the entity is captured by \textsc{Optimality}.
-\dnote{Note about how to satisfy them?}.
+Abstraction, more generally, is aimed at reducing the dimensionality of an entity; this {\it reduction} is captured by \textsc{Compressibility}, while the {\it preservation} of critical information content of the entity is captured by \textsc{Optimality}.
+Relevant to planning and RL is the third criteria; that the information given be easy to compute.
+We take these three statements as guiding principles on abstractions for planning and \ac{RL} \dnote{Note about how to satisfy them?}.
 
-Critically, either desiderata is trivial to satisfy on its own.
+Critically, all three desiderata are trivial to satisfy on their own.
 Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action).

### 2016-04-30 icml_workshop/desiderata.tex
minor desiderata changes

--- 2016-04-30 icml_workshop/desiderata.tex
@@
 The interesting (and difficult) case is satisfying {\it both} desiderata.
-To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
+To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata.
 After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

### 2016-04-30 icml_workshop/abstract.tex
First pass at abstract

Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable fun. Unsurprisingly, then, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions. However, there exists little work detailing what good abstractions ought to formally accomplish. In this work we propose three desiderata that abstractions in planning and \ac{RL}. We summarize existing work on unifying state aggregation methods, propose an extension of this work to temporally extended actions and suggest how to formally ground out these three desiderata in our extended framework. \enote{Maybe also add experimental results, Dave?}

### 2016-04-30 icml_workshop/framework.tex
beep

@@
 In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}.
-In this work we develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$,
+We develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.
 
-Formalism
+More formally, we think of abstraction in terms of a state aggregation function mapping ground states of a {\it ground} MDP to abstract states of an {\it abstract} MDP.
 
-Extension to Temp Ext
+We consider several {\it types} of aggregation function families; each of which ensures that all aggregated states are within $\varepsilon$ of one another with respect to some function of interest.
+The four families are:
+\begin{enumerate}
+\item $\epQ$: states that are aggregated have similar $Q^*$ values
+\item $\epM$: states that are aggregated have similar transition functions and reward functions.
+\item $\epMu$: states that are aggregated have similar multinomial distributions over $Q^*$ values.
+\item $\epB$: states that are aggregated have similar Boltzmann distributions over $Q^*$ values.
+\end{enumerate}
+
+Our main result is that, any instance of any of the above abstraction functions will induce an abstract \ac{MDP} such that, the optimal policy of the abstract MDP, denoted $\pi_A^*$, when used to solve the ground MDP, has value that is within a polynomial of $\varepsilon$ of the true optimal value function.
+Here, $\varepsilon$ determines how aggressive the abstraction is; for a $\varepsilon=0$, the state aggregation functions will only aggregate states that share exact values.
+
+\begin{thm}
+There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
+\begin{equation}
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{A}^*}(s) \leq poly \left (\frac{1}{\varepsilon} \right).
+\end{equation}
+\end{thm}
+
+This theorem satisfies the \textsc{Value} desiderata.
+Moreover, we stipulate that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}.
+Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is achievable under this framework.
+
+% Subsection: Temporal Abstraction
+\subsection{Temporal Abstraction}
+Most critically, however, is the framework's natural extension to temporal abstraction. To do so, we consider a pair of functions: $\{\widetilde{\phi}_f, \Delta_g\}$, where:
+\begin{equation}
+\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g \mathcal{A}_G \mapsto \mathcal{A}_A
+\end{equation}
+
+Now, the abstract MDP is fully distinct from $M_G$, in that it also has a unique set of abstract actions.
+As before, we can prove bounds on the value lost under different {\it kinds} of functions $\Delta_g$, which will provide a clear distinction between which abstract actions can preserve value, and which do not.
+In the next section, we show some preliminary empirical results to demonstrate how this process works.
 
 Satisfying Desiderata
+
+\dnote{put epsilon in subscript of phi}

### 2016-04-30 icml_workshop/introduction.tex
beep

@@
 % Planning and RL is hard.
-For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
+For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,anand2015novel,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
 Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.

### 2016-04-30 icml_workshop/desiderata.tex

--- 2016-04-30 icml_workshop/desiderata.tex
@@
 Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.
+Lastly for \textsc{Efficient-Computability}, returning an MDP $M_A$, such that $M_A$ is identical to $M_G$ is trivially efficiently computable.
 
-The interesting (and difficult) case is satisfying {\it both} desiderata.
-To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.
+The interesting (and difficult) case is satisfying {\it all three} desiderata.
+To the best of our knowledge, no abstraction has been formally proven to satisfy all three.
+In the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata.
 After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

### 2016-04-30 icml_workshop/abstract.tex
abstract.tex

@@
-Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable fun.
-Unsurprisingly, then, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions.
+Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable ones.
+Unsurprisingly, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions.
 However, there exists little work detailing what good abstractions ought to formally accomplish.
-In this work we propose three desiderata that abstractions in planning and \ac{RL}.
+In this work we propose three desiderata on abstractions in the context of planning and \ac{RL}.
 We summarize existing work on unifying state aggregation methods, propose an extension of this work to temporally extended actions and suggest how to formally ground out these three desiderata in our extended framework.

### 2016-05-01 icml_workshop/framework.tex
Added section on grounding out des. in our framework.

@@
 In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}.
-We develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.
+We developed a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.
 
@@
 \begin{equation}
-\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{A}^*}(s) \leq poly \left (\frac{1}{\varepsilon} \right).
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\varepsilon \right).
 \end{equation}
@@
 % Subsection: Temporal Abstraction
-\subsection{Temporal Abstraction}
-Most critically, however, is the framework's natural extension to temporal abstraction. To do so, we consider a pair of functions: $\{\widetilde{\phi}_f, \Delta_g\}$, where:
+\subsection{Extending to Temporal Abstraction}
+Most critically, however, is the framework's natural extension to temporal abstraction. To do so, we consider a pair of functions: $(\widetilde{\phi}_f, \Delta_g)$, where:
 \begin{equation}
-\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g \mathcal{A}_G \mapsto \mathcal{A}_A
+\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g : \mathcal{A}_G \mapsto \mathcal{A}_A
 \end{equation}
@@
 \dnote{put epsilon in subscript of phi}
+
+% Subsection: Grounding out Desiderata
+\subsection{Grounding out Desiderata in Framework}
+
+We now ground out the three desiderata with our formal framework:
+
+\begin{enumerate}
+%Compressibility
+\item \textsc{Compressibility}: $|\mcS_G - \mcS_A| \geq B_1$ and $|\mcA_G - \mcA_A| \geq B_2$ where $B_1$ and $B_2$ are ``sufficiently" large.
+
+%Optimality
+\item \textsc{Optimality}: $\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{A}^*} \leq B_3$ where $B_3$ is not ``unreasonably" large.
+
+%Efficient-Computability
+\item \textsc{Efficient-Computability}: $\widetilde{\phi}_f$ and $\Delta_g$ ought to be polynomially computable in the relevant quantities, namely $\mcS_G$, $\mcA_G$ and the representation of $\mcT$ and $\mcR$.
+\end{enumerate}

### 2016-05-01 icml_workshop/introduction.tex
adding rel work

--- 2016-04-30 icml_workshop/introduction.tex
@@
 % Planning and RL is hard.
-For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
+For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,baird1995residual,sutton1999policy,mnih2015human,konidaris2007building,dietterich2000hierarchical,sacerdoti1974planning,hauskrecht1998hierarchical,anand2015novel,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
 Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.

### 2016-05-01 icml_workshop/related_work.tex
adding rel work

@@
 Previous \textit{macro-action} or \textit{options}
+
+\subsection{Abstraction as Function Approximation}
+
+The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}.
+The use of such techniques achieves abstraction of a certain form - states that share some number of state variables receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state.
+While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class).
+Given that the goal of this work is to characterize effective abstractions by evaluating their relative satisfaction of each of our three desiderata, we stipulate that such analysis will prove illusive for these approaches.

### 2016-05-01 icml_workshop/related_work.tex
added a bunch of rel work

@@
 
-Considerable work in planning and \ac{RL} has grappled with, either in the form of state aggregation (DEFINE?) or temporally extended actions (DEFINE?).
+Considerable work in planning and \ac{RL} has investigated abstraction. We group prior literature into approaches of state aggregation, temporally extended actions, or function approximation.
 
+% Subsection: Abstraction as State Aggregation
 \subsection{Abstraction as State Aggregation}
-
-\subsection{Approximate State Abstraction}
 
@@
 \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
+\citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
+Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
+\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
+\citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
+For a more complete survey of literature on state aggregation, see \citet{li2006towards}.
 
@@
 
-Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs.
-\citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction.
-Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
+% Subsection: Abs as Temp Ext.
+\subsection{Temporal Abstraction}
+Previous \textit{macro-action} or \textit{options}
 
-\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
+% Subsection: Abstraction as Func Approx
+\subsection{Abstraction as Function Approximation}
 
-For a more complete survey of algorithms that leverage state aggregation in past reinforcement-learning papers, see \citet{li2006towards}.
+The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}.
+The use of such techniques achieves abstraction of a certain form - states that share some number of state variables receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state.
+While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class).
+Given that the goal of this work is to characterize effective abstractions by evaluating their relative satisfaction of each of our three desiderata, we stipulate that such analysis will prove illusive for these approaches.
 
+% Subsection: Exact Abstraction Framework
 \subsection{Exact Abstraction Framework}
@@
 Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
-
-\subsection{Abstraction as Temporal Extension}
-Previous \textit{macro-action} or \textit{options}
-
-\subsection{Abstraction as Function Approximation}
-
-The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}.
-The use of such techniques achieves abstraction of a certain form - states that share some number of state variables receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state.
-While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class).
-Given that the goal of this work is to characterize effective abstractions by evaluating their relative satisfaction of each of our three desiderata, we stipulate that such analysis will prove illusive for these approaches.

### 2016-05-01 icml_workshop/framework.tex
A merge and stuff

@@
 \section{Abstraction Framework}
+\cite{li2006towards} previously provided a unifying treatment of state aggregation functions.
+In this work a state abstraction function produces an abstract \ac{MDP}, $M$ from a ground \ac{MDP}, $M_G$ b $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} $M)A$ DO THIS BETTER
 
-In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}.
+ \cite{li2006towards} provides sufficient conditions on a state aggregation function, $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$ to fully maintain optimality.
+Thus, \cite{li2006towards} provides sufficient conditions whereby \textsc{Optimality} and (hopefully but not provably) \textsc{Compressability} are satisfied.
+However, the criteria proposed by \cite{li2006towards} are no more difficult than solving the ground \ac{MDP} and so this work fails to satisfy \textsc{Efficient-Computability}.
+In hopes to provide a notion that satisfies \textsc{Efficient-Computability} we provided an $\epsilon$-relaxation of the conditions proposed in \cite{li2006towards}.
+
+ provides a number of sufficient conditions whereby optimality in the abstract \ac{MDP} is fully maintained when the abstract \ac{MDP} is generated by a state aggregation function, $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$ which reduced of an
+
+provided a number of sufficient conditions under which However, . understands an abstraction as a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$
+
 We developed a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.
@@
 This theorem satisfies the \textsc{Value} desiderata.
-Moreover, we stipulate that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}.
-Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is achievable under this framework.
+Moreover, we suspect that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}.
+Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is provably achievable under this framework.
 

### 2016-05-01 icml_workshop/introduction.tex
icml workshop draft

@@
 For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,baird1995residual,sutton1999policy,mnih2015human,konidaris2007building,dietterich2000hierarchical,sacerdoti1974planning,hauskrecht1998hierarchical,anand2015novel,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}.
-Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.
+Planning and \ac{RL} formalize the sequential decision making problem as solving for optimal behavior in \acp{MDP}.
 
-A \ac{MDP} is a 5-tuple, $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
+An \ac{MDP} is a 5-tuple, $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
 $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
@@
 % Summarize related work.
-\dnote{summary of related}
-Lorem ipsum.
+Much has been done to mitigate the computational burden of large $\mathcal{S}$ and $\mathcal{A}$ in \acp{MDP}.
+A vast body of literature has investigated state abstraction methods, which seek to compress large state spaces into small ones.
+Additionally, function approximation has achieved a great deal of success in \ac{RL} for estimating the model, the value function, or the policy directly~\cite{mnih2015human,sutton1999policy,baird1995residual}.
+Lastly, hierarchical and skill based approaches have investigated temporal abstractions, such as options~\cite{sutton1999between}, which can serve as mechanisms for simplifying tasks~\cite{konidaris2015constructing}.
+
+Notably, these methods are all evaluated under different criteria; some approaches are tested on different empirical domains, while others are shown to possess desirable theoretical properties.
+Furthermore, even when evaluated under similar criteria, the reliability and usefulness of the abstraction method is left unclear, as is the case with options.
+\cite{jong2008utility} demonstrate that options are not always useful, and can occasionally increase learning time.
+Conversely, other work have demonstrated that options can be useful in a variety of domains~\cite{sutton1999between}.
 
 % We propose desiderata.
+
 In this work, we characterize what it means for an abstraction to be effective in planning and \ac{RL}.
-In particular, we propose three desiderata that a theory of abstraction should satisfy.
-The first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}.
+The primary agenda of this characterization is to unify the goals of work in abstraction as it relates to \acp{MDP}..
+To this end, we propose three desiderata that an abstraction ought to satisfy.
+The first we call \textsc{Compressibility}, which stipulates that an abstraction ought to achieve {\it compression}.
 The second we coin \textsc{Optimality}, which states that abstractions ought to maintain at least some notion of optimality.
 The last we term \textsc{Efficient-Computability} which states that an abstraction ought to be tractably computable.
+We summarize the state of current abstraction approaches in \ac{RL} and planning, and discuss a recent framework we developed as it relates to these desiderata.
 
 % Outline: We summarize framework, propose extension and then ground out desiderata in framework.
-Additionally, we summarize our previously proposed formal framework for state-abstraction methods, and demonstrate that the framework allows for careful formal analysis of temporally-extended abstractions.
+%Additionally, we summarize our previously proposed formal framework for state-abstraction methods, and demonstrate that the framework allows for careful formal analysis of temporally-extended abstractions.
 In particular the framework allows us to characterize what types of temporal abstraction do and do not satisfy \textsc{Compressibility}, \textsc{Optimality} and \textsc{Efficient-Computability}.
-Of special interest is proving what the necessary or sufficient conditions are for an option to be useful in planning or learning.
+An open problem of special interest is to prove what the necessary or sufficient conditions are for an option to be useful in planning or learning.
 \dnote{come back to dis sentence}

### 2016-05-01 icml_workshop/recent_work.tex
icml workshop draft

\section{Relevance to Our Recent Work}

% Paragraph on approximate state abstraction
% We propose epsilon extension of Lihong.
In this document, we offered three desiderata on abstractions in RL. We take these as guiding principles for methods of abstraction.

In search of abstractions that satisfy all three desiderata, including \textsc{Efficient-Computability}, our recent work on approximate state abstraction~\cite{abelhershko2016approx} developed an $\epsilon$-relaxation of the conditions proposed in \cite{li2006towards}.
We consider the abstraction pipeline in which, given a ground MDP $M_G$, an approximate state abstraction function induces a full abstract \ac{MDP} $M_A$. We then apply the optimal abstract policy, $\pi_{GA}$, in the ground MDP; our main result bounds the sub-optimality of this policy for four types of approximate abstraction functions:
\begin{thm}
There exist at least four classes of approximate state abstraction\footnote{Analogously interpreted as state-aggregation functions.} functions for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\varepsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\varepsilon \right).
\end{equation}
\end{thm}

This theorem suggests that approximate state abstractions satisfy the \textsc{Value} desiderata. Moreover, we suspect that functions of these types are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}. Furthermore, in this work we empirically demonstrate the compressibility of these functions, and consider it an open problem of analysis as to what degree of compressibility is achievable under this framework.

We can formally ground each desiderata in the language of this framework as follows:
\begin{enumerate}
%Compressibility
\item \textsc{Compressibility}: $|\mcS_G - \mcS_A| \geq B_1$ and $|\mcA_G - \mcA_A| \geq B_2$ where $B_1$ and $B_2$ are ``sufficiently" large.

%Optimality
\item \textsc{Optimality}: $\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}} \leq B_3$ where $B_3$ is not ``unreasonably" large.

%Efficient-Computability
\item \textsc{Efficient-Computability}: $\widetilde{\phi}_f$ and $\Delta_g$ ought to be polynomially computable in the relevant quantities, namely $\mcS_G$, $\mcA_G$ and the representation of $\mcT$ and $\mcR$.
\end{enumerate}

Such a formal treatment will enable extension to questions regarding the utility of temporal abstractions.

To incorporate temporally extended actions, we consider pair of functions: $(\widetilde{\phi}_f, \Delta_g)$, where:
\begin{equation}
\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g : \mathcal{A}_G \mapsto \mathcal{A}_A
\end{equation}

Now, the abstract MDP is fully distinct from $M_G$, in that it also has a unique set of abstract actions. As before, we can prove bounds on the value lost under different {\it kinds} of functions $\Delta_g$, which will provide a clear distinction between which abstract actions can preserve value, and which do not. In future work, we are interested in characterizing precisely what types of abstract actions can satisfy these desiderata, using this framework.

% DISCUSSION?

### 2016-05-03 icml_workshop/abstract.tex

@@
-Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable ones.
+Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction, intelligent agents may pare down otherwise prohibitively large problems into tractably solvable ones.
 Unsurprisingly, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions.
 However, there exists little work detailing what good abstractions ought to formally accomplish.
-In this work we propose three desiderata on abstractions in the context of planning and \ac{RL}.
-We summarize existing work on unifying state aggregation methods, propose an extension of this work to temporally extended actions and suggest how to formally ground out these three desiderata in our extended framework.
-\enote{Maybe also add experimental results, Dave?}
+In this work we propose three desiderata on abstractions in the context of planning and \ac{RL} to motivate future research.
+We summarize existing work on unifying state aggregation methods, and discuss how our recent work in approximate state abstraction relates to these three desiderata.

### 2016-05-03 icml_workshop/desiderata.tex

@@
 
-We propose the following three desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
+We propose the following three desiderata on abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
 \begin{enumerate}
@@
 \item \textsc{Optimality}: An abstraction ought to induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
-\item \textsc{Efficient-Computability}: An abstraction ought to consist of information that is efficient to compute.
+\item \textsc{Efficient-Computability}: An abstraction ought to consist of information that is easier to compute than $\pi^*$ for $M_G$.
 \end{enumerate}
@@
 Abstraction, more generally, is aimed at reducing the dimensionality of an entity; this {\it reduction} is captured by \textsc{Compressibility}, while the {\it preservation} of critical information content of the entity is captured by \textsc{Optimality}.
-Relevant to planning and RL is the third criteria; that the information given be easy to compute.
-We take these three statements as guiding principles on abstractions for planning and \ac{RL} \dnote{Note about how to satisfy them?}.
+The third criteria is relevant to planning and RL; that the information relevant to the abstraction be easy to compute.
+We take these three statements as guiding principles on abstractions for planning and \ac{RL}.
+\dnote{Note about how to satisfy them?
+What does it look like for one to be satisfied?}
 
-Critically, all three desiderata are trivial to satisfy on their own.
+All three desiderata are trivial to satisfy on their own.
 Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action).
@@
 Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$.
-Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.
+The optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.
 Lastly for \textsc{Efficient-Computability}, returning an MDP $M_A$, such that $M_A$ is identical to $M_G$ is trivially efficiently computable.
 
-The interesting (and difficult) case is satisfying {\it all three} desiderata.
-To the best of our knowledge, no abstraction has been formally proven to satisfy all three.
+The case of interest is an abstraction that satisfies {\it all three} desiderata.\footnote{Note that satisfying any {\it two} criteria is also trivial} To the best of our knowledge, no existing abstraction has been formally proven to satisfy all three desiderata (or something similar to all three).
+
 In the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata.

### 2016-05-03 icml_workshop/related_work.tex

@@
-\section{Related Work}
+\section{Survey of Abstraction Methods}
 
-Considerable work in planning and \ac{RL} has investigated abstraction. We group prior literature into approaches of state aggregation, temporally extended actions, or function approximation.
+Considerable work in planning and \ac{RL} has investigated abstraction.
+We group prior literature into approaches of temporal abstraction, function approximation, and state aggregation and discuss the work's relationship to the desiderata.
+
+% Subsection: Abs as Temp Ext.
+\subsection{Temporal Abstraction}
+A major agenda has been developing a formal framework around skills and temporally extended actions, including options~\cite{sutton1999between,barto2004intrinsically} and macro-actions~\cite{hauskrecht1998hierarchical}.~\cite{konidaris2007building} developed a method for building options that are transferable between similar tasks.~\cite{konidaris2014constructing} leveraged options to impose a discretized state space onto a continuous space.
+Notably, the resulting discretized state space, along with the given options, was shown to have the property that {\it any} plan consisting of these options would be {\it feasible}; i.e.
+that the sequence of operators would be executable.
+While this work can considerably compress a given task, no value is guaranteed to be preserved when transferring to the discretized state space.
+\cite{jong2008utility} demonstrate that options are not always useful in the classic four-room domain.
+In fact, they demonstrate that options paired with the principle of optimism under uncertainty can increase learning time.
+Conversely, other work has demonstrated that options can be useful in a variety of domains~\cite{sutton1999between,chentanez2004intrinsically}.
+
+We are not aware of any work that generally characterizes what constitutes a good option, and what constitutes a bad option.
+Under the guise of the three desiderata, we consider this to be an important direction for future work.
+
+% Subsection: Abstraction as Func Approx
+\subsection{Abstraction as Function Approximation}
+
+The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains with large state spaces~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}.
+The use of such techniques achieves abstraction of a certain form - states that share characteristics receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state, also achieving a compressed representation.
+While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class).
+Given the sorts of assumptions required, we stipulate that general analysis regarding our three desiderata will prove illusive for these approaches.
 
@@
 \subsection{Abstraction as State Aggregation}
+
+\citet{li2006towards} developed a unifying framework for state abstraction approaches in \acp{MDP}.
+In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
+A state-aggregation function maps ground states of a ground MDP, $M_G$, to abstract states of an abstract MDP $M_A$.
+Their work provides sufficient conditions on a state aggregation function to fully maintain optimality.
+Consequently, these sufficient conditions satisfy \textsc{Optimality} and potentially\footnote{Degree of compressibility has not been proven, yet.} \textsc{Compressibility} are satisfied.
+However, the criteria proposed by \cite{li2006towards} are as difficult as solving the ground \ac{MDP} and so this approach does not satisfy \textsc{Efficient-Computability}.
 
@@
 
-% Subsection: Abs as Temp Ext.
-\subsection{Temporal Abstraction}
-Previous \textit{macro-action} or \textit{options}
-
-% Subsection: Abstraction as Func Approx
-\subsection{Abstraction as Function Approximation}
-
-The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}.
-The use of such techniques achieves abstraction of a certain form - states that share some number of state variables receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state.
-While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class).
-Given that the goal of this work is to characterize effective abstractions by evaluating their relative satisfaction of each of our three desiderata, we stipulate that such analysis will prove illusive for these approaches.
-
-% Subsection: Exact Abstraction Framework
-\subsection{Exact Abstraction Framework}
-
-\citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
-In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
-We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
-Our generalizations are equivalent to theirs when exact criteria are used.
-Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
+\enote{Add notes about how these relate to desiderata}

### 2016-05-21 paper/theory_results.tex
Fixed mathcal v mathbb of R

@@
 \bdefn{$\ep_f$}
-Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathcal{R}$ and a fixed non-negative $\varepsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
+Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and a fixed non-negative $\varepsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}

### 2016-05-21 paper/introduction.tex
Changed classes of abstraction to types of abstraction

@@
 % Summary of the four abstractions.
-We support this thesis by describing four different classes of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
+We support this thesis by describing four different types of approximate abstraction functions that preserve near-optimal behavior by aggregating states on different criteria: $\epQ$, on similar optimal $Q$-values, $\epM$, on similarity of rewards and transitions, $\epB$, on similarity of a Boltzmann distribution over optimal $Q$-values, and $\epMu$, on similarity of a multinomial distribution over optimal $Q$-values.
 Furthermore, we empirically demonstrate the relationship between the degree of compression and error incurred on a variety of \acp{MDP}.

### 2016-05-21 paper/theory_results.tex
Added QED to end of lemma proofs
Changed wedge for AND
Changed classes of abstraction to types of abstraction

@@
 
-We now define classes of abstraction based on functions of state--action pairs.
+We now define types of abstraction based on functions of state--action pairs.
 \bdefn{$\ep_f$}
@@
 \begin{thm}
-There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
+There exist at least four types of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
 \begin{equation}
@@
 Thus, we conclude Lemma~\ref{lma:Q*}.
+\qed
 %\begin{equation*}
@@
 \epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \varepsilon\; \wedge\ \\
+\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \varepsilon\; \text{~AND}\ \\
 \forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \varepsilon.
@@
 Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
+\qed
+
 \subsection{Boltzmann over Optimal Q: $\epB$}
@@
 Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.
+\qed
 
@@
 {\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without $e^x \approx 1+x$.
+\qed
 

### 2016-05-21 paper/example_domains.tex
Fixed figure 6 to be figure 1 by moving label to after caption

@@
 (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$.
-We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.
+We depict the original Minefield and an abstract Minefield in Figure \ref{fig:minefield-vis}.
 
@@
 \includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
-\label{fig:minefield-visual}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=0.5$}
+\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
+\varepsilon=0.5$}
+\label{fig:minefield-vis}
 \end{figure}

### 2016-05-22 paper/paper.tex
Starting to unify notation
Added new definition command and starting to unify notation more
Notation for Lemma 1 fixed
Switched from perfect to exact abstraction and other changes to introduction
adding amssymb
put notes back in, small edits to theory
Incorporated michael and stefanie comments
More widow line
Compiling now...
Added gamma used and fixed typo in paper.tex comment
prepping for merge

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{amsthm}%For stating numbered theorems
@@
 \newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
-\usepackage{icml2016/icml2016} 
+\usepackage[accepted] {icml2016/icml2016}
 \usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage
@@
 \newtheorem{clm}{Claim}
+
+\newtheoremstyle{dotless}{}{}{\itshape}{}{\bfseries}{}{ }{}
+\theoremstyle{dotless}
 \newtheorem{defn}{Definition}
 
-\icmltitlerunning{Near Optimal Behavior with Approximate State Abstraction}
+\newcommand{\bdefn}[1]{
+\begin{defn} {\boldmath (#1)}\textbf{:}
+}
+
+\newcommand{\edefn}[1]{
+\end{defn}
+}
+
+%\icmltitlerunning{Near Optimal Behavior via Approximate State Abstraction}
 
@@
 \newcommand{\epQ}{\ep_{Q^*}}
+\newcommand{\epB}{\ep_{\text{bolt}}}
+\newcommand{\epMu}{\ep_{\text{mult}}}
 \newcommand{\epM}{\ep_{\text{model}}}
@@
 \newcommand{\mcR}{\mathcal{R}}
+\newcommand{\mcA}{\mathcal{A}}
 \newcommand{\pM}{\phi_{\text{model}}}
@@
 
+%\newcommand\dnote[1]{\textcolor{blue}{\vspace{-1mm}}}
+%\newcommand\enote[1]{\textcolor{green}{\vspace{-1mm}}}
+
 % --- DOCUMENT ---
@@
 % Suboptimality Bounds for Approximate State Abstraction
-\icmltitle{Near Optimal Behavior with Approximate State Abstraction}
+\icmltitle{Near Optimal Behavior via Approximate State Abstraction}
+
+\begin{center}
+\large{\it To appear at ICML 2016}
+\end{center}
 
 % Paper Meta Info
-\icmlauthor{David Abel}{david_abel@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
-\icmladdress{Brown University,
-            115 Waterman Street, Providence, RI 02906}
-
+\icmlauthor{David Abel\dagger}{david\_abel@brown.edu}
+%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
+\icmlauthor{D. Ellis Hershkowitz\dagger}{david\_hershkowitz@brown.edu}
+%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
+\icmlauthor{Michael L.\ Littman}{michael\_littman@brown.edu}
+%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
 \icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
-
-\vskip 0.3in
+\vspace{0.3in}
 ]
@@
 % ---------------------------------------
-\input{background.tex}
+\input{mdp_background.tex}
 
@@
 \input{related_work.tex}
+
+% -----------------------------------------------
+% --- SECTION: Abstraction Notion ---
+% -----------------------------------------------
+\input{abstraction_notation.tex}
 
@@
 % ------------------------------------------------------------------------------------
-% --- SECTION: Approximate Abstraction on Example Domains ---
+% --- SECTION: Approximate Abstraction on Example Domains ---s
 % ------------------------------------------------------------------------------------
@@
 
+\newpage
 % --- BIBLIOGRAPHY ---

### 2016-05-22 paper/mdp_background.tex
prep for merge
Up through abstraction notation

@@
 An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$.
-Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
+Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s,a, s')$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards.
 We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$.
@@
 \begin{equation}
-V^\pi(s) = Q^\pi(s,a).
+V^\pi(s) = Q^\pi(s,\pi(s)).
 \end{equation}
-
-%zzz no, that is not the standard definition. it would normally be $V^\pi(s) = Q^\pi(s,\pi(s))$.
-
 Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ or $V^{\pi^*}$ and $Q^*$ or $Q^{\pi^*}$, respectively. For further background, see~\citet{kaelbling1996reinforcement}.

### 2016-05-22 paper/related_work.tex

@@
 \citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}.
-In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
-We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
+In particular, the authors defined five types of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}.
+We generalize two of these five types, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
 Our generalizations are equivalent to theirs when exact criteria are used.

### 2016-05-23 paper/mdp_background.tex
adding changes for camera ready: ferns added, lemma 3 and 4 beefed up, vareps added to functions

@@
 \begin{equation}
-Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s)).
+Q^\pi(s,a) = \mathcal{R}(s,a) + \gamma \sum_{s'} \mathcal{T}(s,a,s') Q^\pi(s',\pi(s')).
 \end{equation}
-Similarly, the value function defined under a given policy, denoted $V^\pi(s)$, is defined as:
+We let \textsc{RMax} denote the maximum reward (which is 1), and \textsc{QMax} denote the maximum Q value, which is $\frac{\textsc{RMax}}{1-\gamma}$.
+
+The value function defined under a given policy, denoted $V^\pi(s)$, is defined as:
 \begin{equation}

### 2016-05-23 paper/theory_results.tex
adding changes for camera ready: ferns added, lemma 3 and 4 beefed up, vareps added to functions

@@
 We now define types of abstraction based on functions of state--action pairs.
-\bdefn{$\ep_f$}
-Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and a fixed non-negative $\varepsilon \in \mathbb{R}$, we define $\ep_f$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
+\bdefn{$\ep_{f,\varepsilon}$}
+Given a function $f: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and a fixed non-negative $\varepsilon \in \mathbb{R}$, we define $\ep_{f,\varepsilon}$ as a type of approximate state-aggregation function that satisfies the following for any two ground states $s_1$ and $s_2$:
 \begin{equation}
 \label{eq:phi_f}
-\ep_f(s_1) = \ep_f(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \varepsilon.
+\ep_{f,\varepsilon}(s_1) = \ep_{f,\varepsilon}(s_2) \rightarrow \forall_a \left|f(s_1, a) - f(s_2, a)\right| \leq \varepsilon.
 \end{equation}
@@
 
-That is, when $\ep_f$ aggregates states, all aggregated states have values of $f$ within $\varepsilon$ of each other for all actions.
+That is, when $\ep_{f,\varepsilon}$ aggregates states, all aggregated states have values of $f$ within $\varepsilon$ of each other for all actions.
 
@@
 \begin{thm}
-There exist at least four types of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
+There exist at least four types of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in ${\varepsilon}$:
 \begin{equation}
-\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\varepsilon} \right).
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left ({\varepsilon} \right).
 \end{equation}
@@
 
+We prove this theorem in the following sections by proving bounds on the error of each individual approximate state-aggregation function type.
+
 % Subsection: Optimal Q Function
-\subsection{Optimal Q Function: $\ep_{Q^*}$}
+\subsection{Optimal Q Function: $\ep_{Q^*,\varepsilon}$}
 \label{sec:Q*}
@@
 \begin{equation}
-\ep_{Q^*}(s_1) = \ep_{Q^*}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
+\ep_{Q^*,\varepsilon}(s_1) = \ep_{Q^*,\varepsilon}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
 \end{equation}
@@
 \label{lma:Q*}
-When $\ep_{Q^*}$ is used to create the abstract state space $\mcS_A$:
+When $\ep_{Q^*,\varepsilon}$ is used to create the abstract state space $\mcS_A$:
 \begin{equation}
@@
 % Subsection: Model Similarity -- lemma 2
-\subsection{Model Similarity: $\ep_{model}$}
+\subsection{Model Similarity: $\ep_{model,\varepsilon}$}
 \label{sec:model}
@@
 \label{lma:model}
-When $\mcS_A$ is created using a function of the $\ep_{model}$ type:
+When $\mcS_A$ is created using a function of the $\ep_{model,\varepsilon}$ type:
 \begin{equation}
@@
 \end{equation}
+We let $\delta_1$ denote the error in approximating $e^{Q_G(s_1,a)}$, and $\delta_2$ denote the error in approximating $e^{Q_G(s_2,a)}$.
 
@@
 \left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon
+\label{eq:bolt_with_approx}
 \end{align*}
-It follows that:
+There are two cases of interest - either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}.
+That is, we either have $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
+
+First suppose the former. It follows by algebra that:
+\begin{equation}
+-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon} \leq \varepsilon
+\end{equation}
+
+By algebra, we see that:
+\begin{multline*}
+-\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
+k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
+\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
+\end{multline*}
+
+In the minimal case, it follows that:
+\begin{equation}
+-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon} \leq \varepsilon
+\end{equation}
+
+By similar algebra to the maximal case:
+\begin{multline*}
+-\varepsilon \left(-k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
+-k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
+\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
+\end{multline*}
+
+From both cases, it follows that:
 \begin{equation}

### 2016-05-24 Workspace and Code/stateAbstraction/src/plotting/plotter.py
Updated plotter to use bigger font sizes in appropraite ways

@@ -147,16 +147,18 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 	plt.ylim([0,maxY *1.2])
 
 	#Set font
-	font = {'family' : 'normal',
-	        'size'   : 15}
+	fontMed = {'family' : 'normal',
+	        'size'   : 25}
+	fontBig = {'family' : 'normal',
+	        'size'   : 30}
 
-	matplotlib.rc('font', **font)
-	plt.xlabel(xAxisLabel)
-	plt.ylabel(yAxisLabel)
-	plt.title(taskName[0].upper() + taskName[1:] + ': ' + xAxisLabel + ' vs. ' + yAxisLabel)
+	# matplotlib.rc('font', **font)
+	plt.xlabel(xAxisLabel, **fontMed)
+	plt.ylabel(yAxisLabel, **fontMed)
+	plt.title(xAxisLabel + ' vs. ' + yAxisLabel, **fontBig)
 
 	plt.grid(True)
-	plt.legend()
+	plt.legend(prop={'size':22})
 	plt.savefig(taskName.lower() + '/' + xAxisLabel.lower() + '_vs_' + yAxisLabel.lower().replace(" ", "_") + '.pdf', format="pdf")
 	plt.clf()
 	# plt.show()
@@ -220,7 +222,7 @@ def makePlot(taskName):
 
 	# Plot with CIs.
 	plotWithConfidenceIntervals(numAbstractStatesEpsilons, [numAbstractStates, numGroundStates],"Num Abstract States", taskName, yDataNames=["Num. Abstract States", "Num. Ground States"])
-	plotWithConfidenceIntervals(abstratStateValEpsilons, [abstractStateVals, groundStateVals, randPolVal], "Value of Abstract Policy Init Ground State", taskName, yDataNames=["Val. Abstract Policy", "Val. Optimal Policy", "Val. Random Policy"])
+	plotWithConfidenceIntervals(abstratStateValEpsilons, [abstractStateVals, groundStateVals, randPolVal], "Value of Abstract Policy", taskName, yDataNames=["Val. Abstract Policy", "Val. Optimal Policy", "Val. Random Policy"])
 
 	#Old plotting without CIs
 	# plot(epsilons, [numStates, numGroundStatesYData], "Num Abstract States", taskName, yDataNames=["Num. Abstract States", "Num. Ground States"])

### 2016-05-24 Workspace and Code/stateAbstraction/src/plotting/plotter.py
Increased font size of plots and messed with markers a tiny bit

@@ -133,7 +133,7 @@ def	plotWithConfidenceIntervals(xData, allYData, yAxisLabel, taskName, confidenc
 				means.append(mean)
 				numTrials.append(numTrial)
 			maxY = max(maxY, max(means))
-			plt.errorbar(xData, means, yerr=errors, label=legendInfo)
+			plt.errorbar(xData, means, yerr=errors, label=legendInfo, marker='x', markersize=15)
 			if (annotateWithTrialNumber):
 				#Add annotation of # trials
 				for (i, x), y in zip(enumerate(xData), means):

### 2016-05-24 paper/theory_results.tex
Claim 1 revisions for camera ready done

@@
 
-Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
+Consider a non-Markovian decision process of the same form as an \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
 Thus,
@@
 \mathcal{S}_T &= \begin{cases}
-\mathcal{S}_G,& \text{if } T \leq 0, \\
+\mathcal{S}_G,& \text{if } T = 0, \\
 \mathcal{S}_A,& \text{o/w}
@@
 \mathcal{R}_T(s,a) &= \begin{cases}
-\mathcal{R}_G(s,a),& \text{if } T \leq 0, \\
+\mathcal{R}_G(s,a),& \text{if } T = 0, \\
 \mathcal{R}_A(s, a),& \text{o/w}
@@
 \mcT_T(s,a,s') &= \begin{cases}
-\mcT_G(s,a,s'),& \text{if }T \leq 0, \\
+\mcT_G(s,a,s'),& \text{if }T = 0, \\
 \underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
@@
 
-The $Q$-value of a state $s$ in $M^T$ for action $a$ is:
+The $Q$-value of state $s$ in $\mathcal{S}_T$ for action $a$ is:
 \begin{equation}
@@
 	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
-	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a), &\text{o/w},
+	   \mathcal{R}_A(s,a) + \sigma_{T-1}(s,a), &\text{o/w},
 \end{cases}
@@
 \begin{equation*}
-\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
+\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(s,a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
 \end{equation*}
@@
 \label{eq:clm1Induct}
-\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \varepsilon \gamma^{t},
+\forall_{T, s_G \in \mathcal{S}_G, a} |Q_T(s_T, a) - Q_G(s_G, a) | \leq \sum_{t=0}^{T-1} \varepsilon \gamma^{t},
 \end{equation}
+where $s_T = s_G$ if $T=0$ and $s_T = \epQ(s_G)$ otherwise.
 
@@
 
-When $T = 0$, $Q_T = Q_G$, so the result trivially follows.
+When $T = 0$, $Q_T = Q_G$, so this base case trivially follows.
 
 % Base Case t=1
-\textit{Base Case: $T = 1$}
+\textit{Base Case: $T = 1$}\\
+By definition of $Q_T$, we have that $Q_1$ is
 \begin{align*}
@@
 \begin{align*}
-&Q_1(s,a) \leq \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
+&Q_1(s_T,a) \leq \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
 \end{align*}
@@
 \begin{equation}
-\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
+\left| Q_{1}(s_T, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
 \end{equation}
+%
 % Inductive Case
@@
 \begin{equation*}
-\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \varepsilon \gamma^t.
+\forall_{s_G \in \mathcal{S}_G, a} |Q_{T-1}(s_T, a) - Q_G(s_G, a) | \leq \sum_{t=0}^{T-2} \varepsilon \gamma^t.
 \end{equation*}
@@
 Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
-We denote $\epQ(s_G)$ as $s_A$. 
-By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
+Since $T > 1$, $s_T$ is $\epQ(s_G)$.
+By definition of $Q_{T}(s_T, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
 \begin{multline*}
-Q_T(s_A, a) = \sum_{g \in G(s_A)}\omega(g)\ \times \\ 
+Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \\ 
  \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
@@
 \begin{multline*}
-Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
+Q_T(s_T, a) \leq \sum_{g \in G(s_T)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
 \end{multline*}
@@
 \begin{equation*}
-Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
+Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_T)}\left[ \omega(g)\ Q_G(g,a)\right].
 \end{equation*}
@@
 \begin{align*}
-Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
-\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
+Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
+\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
 \end{align*}
-Since $s_G$ and $s_A$ are arbitrary, we conclude Equation \ref{eq:clm1Induct}.
+Since $s_G$ is arbitrary, we conclude Equation \ref{eq:clm1Induct}.
 
-As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.
+As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$.
+Thus, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.
 

### 2016-05-24 paper/theory_results.tex
../theory_results.tex

@@
 By the approximation in Equation~\ref{eq:e_to_x_approx} and the assumption in Equation~\ref{eq:bolt_denom}:
-\begin{align*}
-\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon
-\label{eq:bolt_with_approx}
-\end{align*}
-There are two cases of interest - either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}.
-That is, we either have $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
+\begin{align}
+\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon \label{eq:bolt_with_approx}
+\end{align}
+Either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}.
+That is, either $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
 

### 2016-05-24 paper/theory_results.tex
Doing some compressions for spcae

@@
 We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
-
 \bdefn{$\epQ$}
 An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
+\vspace{-1mm}%vspace for more space
 \begin{equation}
@@
 \label{lma:Q*}
-When $\ep_{Q^*,\varepsilon}$ is used to create the abstract state space $\mcS_A$:
+When a $\ep_{Q^*,\varepsilon}$ type creates $\mcS_A$:
+\vspace{-2mm}%vspace for more space
 \begin{equation}
@@
 \end{equation}
+\vspace{-4mm}%vspace for more space
 \end{lma}
-
 % Proof
@@
 Lastly, we use Claim \ref{clm:optAbsActionNearOptGround} to conclude Lemma \ref{lma:Q*} (Claim \ref{clm:lmaFromClm}).
+
 % Claim 1:
@@
 \end{cases}\\
-%--
+\end{align*}
+\begin{align*}
 \mathcal{R}_T(s,a) &= \begin{cases}
@@
 \end{cases}\\
-%--
+\end{align*}
+\begin{align*}
 \mcT_T(s,a,s') &= \begin{cases}
@@
 \end{align*}
-
 The $Q$-value of state $s$ in $\mathcal{S}_T$ for action $a$ is:
@@
 \end{equation*}
-
 We proceed by induction on $T$ to show that:
@@
 \end{align*}
-Thus,
 \begin{equation}
-\left| Q_{1}(s_T, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
+\therefore \left| Q_{1}(s_T, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
 \end{equation}
@@
 %&\leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
-Then,
-\begin{equation*}
-Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_T)}\left[ \omega(g)\ Q_G(g,a)\right].
-\end{equation*}
-since all aggregated states have $Q$-values within $\varepsilon$ of one another:
+%Then,
+%\begin{equation*}
+%Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in G(s_T)}\left[ \omega(g)\ Q_G(g,a)\right].
+%\end{equation*}
+Since all aggregated states have $Q$-values within $\varepsilon$ of one another:
 \begin{align*}
 Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
-\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
+%\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
 \end{align*}
-Since $s_G$ is arbitrary, we conclude Equation \ref{eq:clm1Induct}.
-
+$s_G$ is arbitrary so we conclude Equation \ref{eq:clm1Induct}.
 As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$.
-Thus, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.
+Thus, Equation \ref{eq:clm1Induct} gives Claim \ref{clm:closeQs}.
 
@@
 \label{lma:model}
-When $\mcS_A$ is created using a function of the $\ep_{model,\varepsilon}$ type:
+When $\mcS_A$ is created using a $\ep_{model,\varepsilon}$ type:
 \begin{equation}
@@
 \end{equation*}
-Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\varepsilon = B$.
-Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
+Since the $Q$-values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\ep_{Q^*,B}$. Applying Lemma \ref{lma:Q*} yields Lemma \ref{lma:model}.
 \qed
@@
 \end{lma}
+\vspace{-3mm}%vspace for more space
 We use the approximation for $e^x$, with $\delta$ error:
@@
 \end{equation}
-
-By algebra, we see that:
+%By algebra, we see that:
 \begin{multline*}
@@
 
-In the minimal case, it follows that:
-\begin{equation}
--\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon} \leq \varepsilon
-\end{equation}
+%In the minimal case, it follows that:
+%\begin{equation}
+%-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon} \leq \varepsilon
+%\end{equation}
 
-By similar algebra to the maximal case:
-\begin{multline*}
--\varepsilon \left(-k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
--k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
-\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
-\end{multline*}
+%By similar algebra to the maximal case:
+%\begin{multline*}
+%-\varepsilon \left(-k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
+%-k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
+%\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
+%\end{multline*}
 
-From both cases, it follows that:
+A similar equation follows if we suppose the latter and combining these equations gives us:
 \begin{equation}
@@
 \end{equation}
-Consequently, we can consider $\epB$ as a variation of $\epQ$, where the difference in $Q$-values is bounded by $\varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right)$.
-Lemma~\ref{lma:bolt_lemma} then follows directly from Lemma~\ref{lma:Q*}.
+Consequently, we can consider $\epB$ as a of the $\ep_{Q^*,B}$ type, where $B = \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right)$.
+Lemma~\ref{lma:bolt_lemma} then follows from Lemma~\ref{lma:Q*}.
 \qed
@@
 \end{lma}
-
+\vspace{-7mm}%vspace for more space
 {\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without $e^x \approx 1+x$.

### 2016-05-24 paper/example_domains.tex
Doing some compressions for spcae
prepping for merge

@@
 %Description of code base
-Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
+Our code base\footnote{Available here: \url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
 We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}.
+For all experiments, we set $\gamma$ to $0.95$.
 

### 2016-05-26 paper/abstraction_notation.tex
final pass

@@
 \section{Abstraction Notation}
-We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.
+We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP}.
 
@@
 
-The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition.
-We make no assumptions about the weighting scheme, except that for each abstract state, the weighting is a convex combination across all ground states.
+The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the abstract state.
 
@@
 \begin{equation}
-\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \textrm{ and }\hspace{6mm}  \omega(s) \in [0,1].
+\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \hspace{3mm} \textrm{ AND }\hspace{3mm}  \omega(s) \in [0,1].
 \end{equation}
@@
 \bdefn{$\mcR_A$}
-The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
+The abstract reward function $\mathcal{R}_A: \mathcal{S}_A \times \mathcal{A} \mapsto [0,1]$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
 \begin{equation}
@@
 \bdefn{$\mcT_A$}
-The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
+The abstract transition function $\mathcal{T}_A: \mathcal{S}_A \times \mathcal{A} \times \mathcal{S}_A \mapsto [0,1]$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
 \begin{equation}

### 2016-05-26 paper/introduction.tex
added authorship comment
final pass

@@
 Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction.
-However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain.
+However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is computationally intractable to obtain.
 Furthermore, often no two situations are identical, so exact abstractions are often ineffective.
@@
 Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
-Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality.
+Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain - a result of Bellman's curse of dimensionality.
 Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks.
@@
 
+\footnotetext[2]{The first two authors contributed equally.}
+\renewcommand*{\thefootnote}{\arabic{footnote}}
+
 % Thesis: Approximate abstraction for three reasons.
-The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\varepsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits.
+The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality to similarity achieves polynomially bounded error in the resulting behavior while offering three benefits.
 First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}.

### 2016-05-26 paper/mdp_background.tex
final pass

@@
 \end{equation}
-We let \textsc{RMax} denote the maximum reward (which is 1), and \textsc{QMax} denote the maximum Q value, which is $\frac{\textsc{RMax}}{1-\gamma}$.
+We let \textsc{RMax} denote the maximum reward (which is 1), and \textsc{QMax} denote the maximum $Q$ value, which is $\frac{\textsc{RMax}}{1-\gamma}$.
 

### 2016-05-26 paper/related_work.tex
adding changes for camera ready: ferns added, lemma 3 and 4 beefed up, vareps added to functions
final pass

@@
 \subsection{Approximate State Abstraction}
-\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other.
+\citet{dean1997model} leverage the notion of {\it bisimulation} to investigate partitioning an \ac{MDP}'s state space into clusters of states whose transition model and reward function are within $\varepsilon$ of each other.
 They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}.
-Several approaches build on the notion of $\varepsilon$-homogeneity.
-\citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\varepsilon$-homogenous partitions.
+
+Several approaches build on \citet{dean1997model}.
+\citet{ferns2004metrics,ferns2006methods} investigated state similarity metrics for \acp{MDP}; they bounded the value difference of ground states and abstract states for several bisimulation metrics that induce an abstract MDP.
+This differs from our work which develops a theory of abstraction that bounds the suboptimality of applying the optimal policy of an abstract MDP to its ground MDP, covering four types of state abstraction, one of which closely parallels bisimulation.
+\citet{even2003approximate} analyzed different distance metrics used in identifying state space partitions subject to $\varepsilon$-similarity.
 \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
@@
 We generalize two of these five types, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case.
-Our generalizations are equivalent to theirs when exact criteria are used.
+Our generalizations are equivalent to theirs when exact criteria are used (i.e.
+$\varepsilon = 0$).
 Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.

### 2016-05-26 paper/theory_results.tex
final pass

@@
 Here, we introduce our formal analysis of approximate state abstraction, including results bounding the error associated with these abstraction methods.
-In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
+In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.
 
@@
 
-We now introduce the main result of the paper.
+We now introduce our main result.
 
@@
 
-We prove this theorem in the following sections by proving bounds on the error of each individual approximate state-aggregation function type.
+We prove this theorem in the following sections by proving polynomial bounds on the error of each individual approximate state-aggregation function type.
 
@@
 % Q* Lemma -- lemma 1
-We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
+We consider an approximate version of \citet{li2006towards}'s $\phi_{Q^*}$. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\varepsilon$.
 \bdefn{$\epQ$}
-An approximate $Q$ function has the same form as Equation~\ref{eq:phi_f}:
+An approximate $Q$ function abstraction has the same form as Equation~\ref{eq:phi_f}:
 \vspace{-1mm}%vspace for more space
@@
 \end{cases}\\
-\end{align*}
-\begin{align*}
 \mcT_T(s,a,s') &= \begin{cases}
@@
 \mcT_A(s,a,s'),& \text{o/w}
-\end{cases}\\
+\end{cases}
 \end{align*}
@@
 \end{equation}
-where
+where:
 \begin{equation*}
@@
 \begin{align*}
-Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a). \\
+Q_T(s_T, a) \leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
 %\therefore\ \left| Q_{T}(s_T, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\varepsilon \gamma^t
@@
 \end{clm}
-
 By Claim~\ref{clm:closeQs},
@@
 \end{align}
-
 By the definition of $a^*_A$, we know that 
@@
 \end{align}
-
 Lastly, again by Claim~\ref{clm:closeQs}, we know

### 2016-05-26 paper/example_domains.tex
removing minefield

@@
 % Description of visuals.
-We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain.
+%We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain.
 A grey circle indicates a state and colored arrows indicate transitions.
@@
 %Description of code base
-Our code base\footnote{Available here: \url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
+Our code base\footnote{\url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
 We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}.
@@
 (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$.
-We depict the original Minefield and an abstract Minefield in Figure \ref{fig:minefield-vis}.
-
 % Minefield Compression Visuals
-\begin{figure}
-\centering
-\subfigure[Ground Minefield]{
-\includegraphics[width=0.34\columnwidth]{figures/ground_minefield.png}}
-\subfigure[Abstract Minefield]{
-\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
-\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
-\varepsilon=0.5$}
-\label{fig:minefield-vis}
-\end{figure}
-
+%\begin{figure}
+%\centering
+%\subfigure[Ground Minefield]{
+%\includegraphics[width=0.3\columnwidth]{figures/ground_minefield.png}}
+%\subfigure[Abstract Minefield]{
+%\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
+%\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
+%\varepsilon=0.5$}
+%\label{fig:minefield-vis}
+%\end{figure} 
 % Subsection: Random.
 %\subsection{Random}
-
 In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states with probability $0.5$.

### 2016-05-26 paper/example_domains.tex
Final pass with Dave and Ellis

@@
 Our code base\footnote{\url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}.
-We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}.
+We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{\url{http://burlap.cs.brown.edu/}}.
 For all experiments, we set $\gamma$ to $0.95$.

### 2016-05-26 paper/results_discussion.tex
Final pass with Dave and Ellis

@@
 %Explanation of what abstraction is used
-We ran experiments with aggregation functions in the $\epQ$ family of approximate abstractions.
+We ran experiments on the $\epQ$ type aggregation functions.
 We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions.
@@
 
-%Explanation of what plots done
+%Explanation of what plots done/gamma used
 For each domain, we report two quantities as a function of epsilon with 95\% confidence bars.
@@
 Conversely, in the Random domain, a great deal of near optimal policies are available to the agent.
-Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near optimal policies available to the agent that remain available.
-Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
+Thus, even as the information for optimal behavior is lost, there are many near optimal policies available to the agent that remain available.
+% Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
 

### 2016-05-26 paper/theory_results.tex
Final pass with Dave and Ellis

@@
 \begin{equation}
-\ep_{Q^*,\varepsilon}(s_1) = \ep_{Q^*,\varepsilon}(s_2) \rightarrow \forall_a \left|Q_G^*(s_1, a) - Q_G^*(s_2, a)\right| \leq \varepsilon.
+\ep_{Q^*,\varepsilon}(s_1) = \ep_{Q^*,\varepsilon}(s_2) \rightarrow \forall_a \left|Q_G(s_1, a) - Q_G(s_2, a)\right| \leq \varepsilon.
 \end{equation}
@@
 \label{lma:Q*}
-When a $\ep_{Q^*,\varepsilon}$ type creates $\mcS_A$:
+When a $\ep_{Q^*,\varepsilon}$ type abstraction is used to create the abstract \ac{MDP}:
 \vspace{-2mm}%vspace for more space
@@
 
-Consider a non-Markovian decision process of the same form as an \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
+Consider a non-Markovian decision process of the same form as an \ac{MDP}, $M_T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer an $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$.
 Thus,
@@
 \mathcal{S}_T &= \begin{cases}
-\mathcal{S}_G,& \text{if } T = 0, \\
-\mathcal{S}_A,& \text{o/w}
+\mathcal{S}_G& \text{if } T = 0 \\
+\mathcal{S}_A& \text{o/w}
 \end{cases}\\
@@
 \mathcal{R}_T(s,a) &= \begin{cases}
-\mathcal{R}_G(s,a),& \text{if } T = 0, \\
-\mathcal{R}_A(s, a),& \text{o/w}
+\mathcal{R}_G(s,a)& \text{if } T = 0\\
+\mathcal{R}_A(s, a)& \text{o/w}
 \end{cases}\\
 \mcT_T(s,a,s') &= \begin{cases}
-\mcT_G(s,a,s'),& \text{if }T = 0, \\
-\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
-\mcT_A(s,a,s'),& \text{o/w}
+\mcT_G(s,a,s')& \text{if }T = 0\\
+\underset{{g \in G(s)}}{\sum}\left[\mcT_G(g, a, s') \omega(g) \right]& \text{if } T = 1\\
+\mcT_A(s,a,s')& \text{o/w}
 \end{cases}
@@
 \begin{cases}
-	   Q_G(s, a), &  \text{if } T=0,\\
-	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
-	   \mathcal{R}_A(s,a) + \sigma_{T-1}(s,a), &\text{o/w},
+	   Q_G(s, a) &  \text{if } T=0\\
+	   \underset{g \in G(s)}{\sum} \left[ Q_G(g,a) \omega(g) \right] & \text{if } T = 1\\
+	   \mathcal{R}_A(s,a) + \sigma_{T-1}(s,a) &\text{o/w}
 \end{cases}
@@
 \begin{align*}
-&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right].
+&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ Q_G(g,a) \omega(g) \right].
 \end{align*}
@@
 Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \\ 
- \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
+ \left[ \mathcal{R}_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} \mathcal{T}_G(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
 \end{multline*}
@@
 \end{align*}
-$s_G$ is arbitrary so we conclude Equation \ref{eq:clm1Induct}.
+Since $s_G$ is arbitrary we conclude Equation \ref{eq:clm1Induct}.
 As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \varepsilon \gamma^t \rightarrow \frac{\varepsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$.
-Thus, Equation \ref{eq:clm1Induct} gives Claim \ref{clm:closeQs}.
+Thus, Equation \ref{eq:clm1Induct} yields Claim \ref{clm:closeQs}.
 
@@
 \begin{align*}
-a^*_G = \argmin Q_G(s_G, a), \hspace{4mm}
-a^*_A = \argmin Q_A(s_A, a).
+a^*_G = \argmax_a Q_G(s_G, a), \hspace{4mm}
+a^*_A = \argmax_a Q_A(s_A, a).
 \end{align*}
@@
 \begin{cases}
-\pi_G^*(s), &\text{if } t<=0,\\
-\pi_{GA}(s), &\text{if } t > 0.
+\pi_G^*(s) &\text{if } t= 0\\
+\pi_{GA}(s) &\text{if } t > 0
 \end{cases}
@@
 
-For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ in the ground \ac{MDP} is as follows:
+For $t > 0$, the value of this policy for $s_G \in \mathcal{S}_G$ in the ground \ac{MDP} is:
 \begin{multline*}
@@
 \end{multline*}
+
+For $t=0$, $V_G^{\pi_{A,t}}(s_G)$ is simply $V_G(s_G)$.
+
 %Start induction on following the optimal abstract policy
@@
 \end{equation*}
-where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$. Since difference of rewards is bounded by $\varepsilon$:
+where $s_A \in \mcS_A$ and $s_1, s_2 \in G(s_A)$. Since difference of rewards is bounded by $\varepsilon$:
 % Removed for space
@@
 \end{align*}
-Since \textsc{QMax} $\leq \frac{\textsc{RMax}}{1-\gamma}$, and we defined $\textsc{RMax} = 1$:
+Since \textsc{QMax} $= \frac{\textsc{RMax}}{1-\gamma}$, and we defined $\textsc{RMax} = 1$:
 \begin{equation*}
@@
 This family of abstractions is appealing as Boltzmman distributions balance exploration and exploitation~\cite{sutton1998reinforcement}.
-We find this family particularly interesting for abstraction purposes as, unlike $\epQ$, it allows for aggregation when $Q$-value ratios are similar but their magnitudes are different.
+We find this type particularly interesting for abstraction purposes as, unlike $\epQ$, it allows for aggregation when $Q$-value ratios are similar but their magnitudes are different.
 
 \bdefn{$\epB$}
-We let $\epB$ define a family of abstractions that, for fixed $\varepsilon$, satisfies:
+We let $\epB$ define a type of abstractions that, for fixed $\varepsilon$, satisfies:
 \begin{multline}
@@
 \end{equation}
-We let $\delta_1$ denote the error in approximating $e^{Q_G(s_1,a)}$, and $\delta_2$ denote the error in approximating $e^{Q_G(s_2,a)}$.
+We let $\delta_1$ denote the error in approximating $e^{Q_G(s_1,a)}$ and $\delta_2$ denote the error in approximating $e^{Q_G(s_2,a)}$.
 
@@
 \end{align}
-Either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}.
-That is, either $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
+Either $\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon$ is  $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
 
@@
 \begin{equation}
-\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\varepsilon.
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k \times \varepsilon.
 \end{equation}

### 2017-01-12 arxiv_paper/abstract.tex
Adding arxiv version

--- 2016-02-05 paper/abstract.tex
@@
 However, exact abstractions, which treat only fully-identical situations as equivalent, fail to present opportunities for abstraction in environments where no two situations are exactly alike.
-For these reasons, we investigate approximate state abstractions, which treat nearly-identical situations as equivalent.
-In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation.
-We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions.
+In this work, we investigate approximate state abstractions, which treat nearly-identical situations as equivalent.
+We present theoretical guarantees of the quality of behaviors derived from four types of approximate abstractions.
 Additionally, we empirically demonstrate that approximate abstractions lead to reduction in task complexity and bounded loss of optimality of behavior in a variety of environments.

### 2017-01-12 arxiv_paper/conclusion.tex
Adding arxiv version

--- 2016-04-30 icml_workshop/conclusion.tex
@@
 Approximate abstraction in \acp{MDP} offers considerable advantages over exact abstraction.
-In this work, we proved bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}.
-We also empirically demonstrate that approximate abstractions can reduce state space size with minor loss in the quality of the behavior.
-
-%First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
+First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}.
 Second, approximate abstractions can achieve greater degrees of compression due to their relaxed criteria of equality.
 Third, methods that employ approximate aggregation techniques are able to tune the aggressiveness of abstraction all the while incurring bounded error.
-We empirically demonstrate the relationship between $\varepsilon$ and the degree of compression, as well as the value of the abstract policy on four dramatically different \acs{MDP}.
+In this work, we proved bounds for the value lost when behaving according to the optimal policy of the abstract \ac{MDP}, and empirically demonstrate that approximate abstractions can reduce state space size with minor loss in the quality of the behavior.
 We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.
+
+%We empirically demonstrate the relationship between $\varepsilon$ and the degree of compression, as well as the value of the abstract policy on four dramatically different \acs{MDP}.
 
@@
 % Learning abs functions online.
-First, we are interested in extending the approach of \citet{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting.
+First, we are interested in extending the approach of \citet{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting, particularly when the agent must solve a collection of related MDPs.
 % Necessary conditions.
@@
 %We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options. 
-In the future, we are interested in characterizing the relationship between temporal abstractions, such as options ~\cite{sutton1999between}, and approximate abstractions.
+Further, we are interested in characterizing the relationship between temporal abstractions, such as options ~\cite{sutton1999between}, and approximate abstractions.
 % Compressibility

### 2017-01-12 arxiv_paper/example_domains.tex
Adding arxiv version

\section{Example Domains}
We apply approximate abstraction to four example domains---NChain, Taxi, Minefield and Random. These domains were selected for their diversity---NChain is relatively simple, Taxi is goal-based and hierarchical in nature, Minefield is stochastic, and Random MDP has many near-optimal policies.

%Description of code base
Our code base\footnote{\url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{\url{http://burlap.cs.brown.edu/}}. For all experiments, we set $\gamma$ to $0.95$.

\subsection{Visualizations}

% Description of visuals.
We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain. A grey circle indicates a state and colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In the abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states (some are visually unwieldy and so were not labelled).

% Subsection: NChain.
\subsubsection{NChain}

NChain is a simple \ac{MDP} investigated in the Bayesian \ac{RL} literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}. In our implementation, we set $N=10$, normalized rewards between $0$ and $1$, and used a slip probability of $0.2$.

In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives $.2$ reward for returning to state 0, and no reward for advancing down the chain. The exception is that when the agent transitions to the last state in the chain, it receives $1.0$ reward. Transitions also have small slip probability $\rho$, such that the applied action results in the opposite dynamics. In our implementation, we set $N=10$ and $\rho=0.2$.
% NChain Compression Visuals.
\begin{figure}[h]
\centering
\subfigure[Ground NChain]{
\includegraphics[width=0.20\columnwidth]{figures/ground_nchain_small.png}}
\hspace{6mm}
\subfigure[Abstract NChain]{
\includegraphics[width=0.20\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\varepsilon=0.5$}
\end{figure}

% Subsection: UpWorld.
\subsubsection{UpWorld}

The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner. The agent may move left, right, and up. The agent receives positive reward for transitioning to any state at the top of the grid, where moving up in the top cells self transitions. the agent receives 0 reward for all other transitions. Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward. During experimentation, we set $N=10$, $M=4$.

As an aside, UpWorld illustrates a compelling property with respect to state abstraction: the optimal {\it exact} $Q^*$ abstraction function (when $\eps=0$) can always construct an abstract MDP with $|\mc{S}_A| = N$, the height of the grid, with no change in the value of the optimal policy. Consequently, letting $M$ be arbitrarily large, UpWorld offers an arbitrary reduction in the size of the MDP through abstraction, at no cost to the value of the optimal policy. More succinctly: \\

\noindent {\bf Remark}: {\it The optimal exact abstraction, $\phi_{Q^*,0}$, always induces an abstract MDP with an optimal policy of equal value to the true optimal policy. Further, $\phi_{Q^*,0}$ will reduce the size of the abstract state space from $N \times M$ to just $N$.} \\

This is a result of the property of UpWorld that all states in the same row will always have the same $Q$ value.
\begin{figure}[h]
\centering
\subfigure[Ground UpWorld]{
\includegraphics[width=0.25\columnwidth]{figures/ground_upworld.png}}
\hspace{6mm}
\subfigure[Abstract UpWorld]{
\includegraphics[width=0.14\columnwidth]{figures/abs_upworld.pdf}}
\label{fig:upworld-visual}
\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\varepsilon=0.5$}
\end{figure}

% Subsection: Taxi
\subsubsection{Taxi}

Taxi has long been studied by the hierarchical RL literature~\cite{dietterich2000hierarchical}. The agent, operating in a Grid World style domain~\cite{russell1995modern}, may move left, right, up, and down, as well as pick up a passenger and drop off a passenger. The goal is achieved when the agent has taken all passengers to their destinations.

We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}. As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and abstract MDP in the same format.

% Taxi Compression Visuals
\begin{figure}[h]
\centering
\subfigure[Ground Taxi]{
\includegraphics[width=0.25\columnwidth]{figures/ground_taxi.png}}
\hspace{6mm}
\subfigure[Abstract Taxi]{
\includegraphics[width=0.25\columnwidth]{figures/abs_taxi.png}}
\label{fig:taxi-visual}
\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\varepsilon=0.03$}
\end{figure}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

% Subsection: Minefield.
\subsubsection{Minefield}
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$.
% Minefield Compression Visuals
\begin{figure}[h]
\centering
\subfigure[Ground Minefield]{
\includegraphics[width=0.15\columnwidth]{figures/ground_minefield.png}}
\hspace{6mm}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.15\columnwidth]{figures/abs_minefield.png}}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
\varepsilon=0.5$}
\label{fig:minefield-vis}
\end{figure} 
 Subsection: Random.
\subsection{Random}
In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states with probability $0.5$. The Random MDP and its compression are visualized in Figure~\ref{fig:minefield-visual}.

% Random Compression Visuals
\begin{figure}[h]
\centering
\subfigure[Ground Random]{
\includegraphics[width=0.25\columnwidth]{figures/ground_random.png}}
\hspace{6mm}
\subfigure[Abstract Random]{
\includegraphics[width=0.25\columnwidth]{figures/abs_random.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\varepsilon=0.2$}
\end{figure}

### 2017-01-12 arxiv_paper/introduction.tex
Adding arxiv version

--- 2016-05-26 paper/introduction.tex
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.40\columnwidth]{figures/main_diagram}
+\caption{We investigate families of abstraction functions that induce abstract MDP's whose optimal policies have bounded value in the original MDP.}
+\end{figure}
+
 % Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
 Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}.
-Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}.
+Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{Strehl2009}.
 Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain - a result of Bellman's curse of dimensionality.

### 2017-01-12 arxiv_paper/related_work.tex
Adding arxiv version

--- 2016-05-26 paper/related_work.tex
@@
 This differs from our work which develops a theory of abstraction that bounds the suboptimality of applying the optimal policy of an abstract MDP to its ground MDP, covering four types of state abstraction, one of which closely parallels bisimulation.
-\citet{even2003approximate} analyzed different distance metrics used in identifying state space partitions subject to $\varepsilon$-similarity.
+\citet{even2003approximate} analyzed different distance metrics used in identifying state space partitions subject to $\varepsilon$-similarity, also providing value bounds (their Lemma 4) for $\eps$-homogeneity subject to the $L_\infty$ norm, which parallels our Claim 2.
 \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.
+\citet{Hostetler2014} apply state abstraction to the planning problem.
+Specifically, they investigate state abstraction for Monte Carlo Tree Search and expectimax search, giving value bounds of applying the optimal abstract action in the ground tree(s), similarly to our setting.~\citet{jiang2014improving} analyze a similar setting, applying abstractions to the Upper Confidence Bound applied to Trees algorithm, introduced by~\citet{kocsis2006bandit}.
+
+\citet{hutter2016extreme,hutter2014extreme} investigates state aggregation beyond the MDP setting.
+Hutter presents a variety of results for aggregation functions in reinforcement learning.
+Most relevant to our investigation is Hutter's Theorem 8, which illustrates properties of aggregating states based on similar $Q$ values.
+Hutter's Theorem part (a) parallels our Claim: both bound the value difference between ground and abstraction states, and part (b) is analogous to our Lemma 1: both bound the value difference of applying the optimal abstraction policy in the ground, and part (c) is a repetition of the comment given by~\citet{li2006towards} that $Q^*$ abstractions preserve the optimal value function.
+For Lemma 1, our proof strategies differ from Hutter's, but the result is the same.
+
+~\citet{mandelefficient} advance Bayesian aggregation in RL to define Thompson Clustering for Reinforcement Learning (TCRL), an extension of which achieves near-optimal Bayesian regret bounds.
+~\citet{Jiang2015} analyze the problem of choosing between two candidate abstractions.
+They develop an algorithm based on statistical tests that trades of the approximation error with the estimation error of the two abstractions, yielding a loss bound on the quality of the chosen policy.
 
@@
 Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.
-\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.
-\citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.
-For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}.
+\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied.~\citet{bakker2004hierarchical} also target hierarchical abstraction, focusing on subgoal discovery.
+\citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.~\citet{Dayan1993} develop ``Feudal Reinforcement Learning" which presents an early form of hierarchical RL that restructures $Q$ Learning to manage the decomposition of a task into subtasks.
+For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}, and for a survey of early works on hierarchical reinforcement learning, see \citet{barto2003recent}.
 
@@
 $\varepsilon = 0$).
-Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.
+Additionally, when exact criteria are used our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.~\citet{walsh2006transferring} build on the framework they previously developed by showing empirically how to transfer abstractions between structurally related MDPs.
 

### 2017-01-12 arxiv_paper/results_discussion.tex
Adding arxiv version

--- 2016-05-26 paper/results_discussion.tex
@@
 \section{Empirical Results}
-
-% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
-\begin{figure*}[t]
-\centering
-\subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
-}
-\subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
-}
-\subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
-}
-\subfigure[Random]{
-\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
-}
-
-\subfigure[NChain]{
-\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy.pdf}
-}
-\subfigure[Minefield]{
-\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy.pdf}
-}
-\subfigure[Taxi]{
-\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy.pdf}
-}
-\subfigure[Random]{
-\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy.pdf}
-}
-\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
-\end{figure*}
 
@@
 
+% HERE
+
 %Discuss results
@@
 Thus, even as the information for optimal behavior is lost, there are many near optimal policies available to the agent that remain available.
+
+% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
+\begin{figure*}
+\centering
+\subfigure[Upworld]{
+\includegraphics[width=0.26\columnwidth]{figures/upworld_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Upworld]{
+\includegraphics[width=0.26\columnwidth]{figures/upworld_epsilon_vs_value_of_abstract_policy.pdf}
+} \\
+\subfigure[NChain]{
+\includegraphics[width=0.26\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[NChain]{
+\includegraphics[width=0.26\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy.pdf}
+} \\
+\subfigure[Minefield]{
+\includegraphics[width=0.26\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Minefield]{
+\includegraphics[width=0.26\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy.pdf}
+} \\
+\subfigure[Taxi]{
+\includegraphics[width=0.26\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Taxi]{
+\includegraphics[width=0.26\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy.pdf}
+} \\
+\subfigure[Random]{
+\includegraphics[width=0.26\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
+}
+\subfigure[Random]{
+\includegraphics[width=0.26\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy.pdf}
+} \\
+\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
+\end{figure*}
+
 % Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
-
-% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
-%\begin{figure}
-%\label{fig:main_empirical_results2}
-%\centering
-%\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value}
-%\end{figure}

### 2017-01-12 arxiv_paper/theory_results.tex
Adding arxiv version

--- 2016-05-26 paper/theory_results.tex
@@
 \begin{equation}
-\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left ({\varepsilon} \right).
+\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq \eta_f
 \end{equation}
@@
 
-We prove this theorem in the following sections by proving polynomial bounds on the error of each individual approximate state-aggregation function type.
+Where $\eta_f$ is a polynomial of epsilon that differs between abstraction function families:
+\begin{align*}
+\eta_{Q^*} &= \frac{2\eps}{(1-\gamma)^2} \\
+\eta_{\text{model}} &= \frac{2\eps + 2\gamma \left( |\mc{S}_G|\eps - \eps \right)}{(1-\gamma)^3} \\
+\eta_{\text{bolt}} &= \frac{2\eps\left(\frac{|\mc{A}|}{1-\gamma} + \eps k_{\text{bolt}} + k_{\text{bolt}}\right)}{(1-\gamma)^2} \\
+\eta_{\text{mult}} &= \eps\left(\frac{|\mc{A}|}{1-\gamma} + \eps k_{\text{mult}} + k_{\text{mult}}\right)
+\end{align*}
+
+Where for $\eta_{\text{bolt}}$ and $\eta_{mult}$, we also assume that the difference in the normalizing terms of each distribution is bounded by some non-negative constant, $k_{\text{mult}}, k_{\text{bolt}} \in \mathbb{R}$, of $\varepsilon$:
+\begin{align*}
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | &\leq k_{\text{mult}} \times \varepsilon \\
+\left |\sum_i e^{Q_G(s_1,a_i)} - \sum_j e^{Q_G(s_2,a_j)} \right | &\leq k_{\text{bolt}} \times \varepsilon \\
+\end{align*}
+
+Naturally, the bound is meaningless for $\eta_f \geq \frac{\textsc{RMax}}{1-\gamma} = \frac{1}{1-\gamma}$, since this is the maximum possible value in any MDP (and we assumed the range of $\mc{R}$ is $[0,1]$).
+In light of this, observe that for $\eps = 0$, all of the above bounds are exactly 0, and are equal to $\frac{1}{1-\gamma}$ contingent on the setting of $\eps$.
+Any value of $\eps$ interpolated between these two points achieves different degrees of abstraction, with different degrees of bounded loss.
+
+We prove this theorem in the following sections by proving polynomial bounds (in terms of $\eps)$ on the error of each individual approximate state-aggregation function type.
 
@@
 % Proof
-\textbf{Proof of Lemma~\ref{lma:Q*}:}
+\noindent \textbf{Proof of Lemma~\ref{lma:Q*}:}
 We first demonstrate that $Q$-values in the abstract \ac{MDP} are close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}).
@@
 Lastly, we use Claim \ref{clm:optAbsActionNearOptGround} to conclude Lemma \ref{lma:Q*} (Claim \ref{clm:lmaFromClm}).
+\\
 
@@
 \mathcal{S}_A& \text{o/w}
-\end{cases}\\
+\end{cases}
 \end{align*}
@@
 \end{equation}
-where $s_T = s_G$ if $T=0$ and $s_T = \epQ(s_G)$ otherwise.
+where $s_T = s_G$ if $T=0$ and $s_T = \epQ(s_G)$ otherwise. \\
 
 % Base Case t=0
-\textit{Base Case: $T = 0$}
+\noindent \textit{Base Case: $T = 0$} \\
 
-When $T = 0$, $Q_T = Q_G$, so this base case trivially follows.
+\noindent When $T = 0$, $Q_T = Q_G$, so this base case trivially follows. \\
 
 % Base Case t=1
-\textit{Base Case: $T = 1$}\\
+\noindent \textit{Base Case: $T = 1$} \\
+
 By definition of $Q_T$, we have that $Q_1$ is
@@
 \begin{align*}
-&Q_1(s_T,a) \leq \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a).
+&Q_1(s_T,a) \leq \varepsilon \gamma^t + \varepsilon + Q_G(s_G, a) \\
+\therefore& \left| Q_{1}(s_T, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
 \end{align*}
-\begin{equation}
-\therefore \left| Q_{1}(s_T, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\varepsilon \gamma^t.
-\end{equation}
-%
+
 % Inductive Case
-\textit{Inductive Case: $T > 1$}
+\noindent \textit{Inductive Case: $T > 1$} \\
 
@@
 By definition of $Q_{T}(s_T, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
-\begin{multline*}
-Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \\ 
- \left[ \mathcal{R}_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} \mathcal{T}_G(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
-\end{multline*}
+\[
+Q_T(s_T, a) = \sum_{g \in G(s_T)}\omega(g)\ \times \left[ \mathcal{R}_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} \mathcal{T}_G(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
+\]
 Applying our inductive hypothesis yields:
-\begin{multline*}
-Q_T(s_T, a) \leq \sum_{g \in G(s_T)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
-\end{multline*}
+\[
+Q_T(s_T, a) \leq \sum_{g \in G(s_T)}\omega(g) \times \biggl[ R_G(g,a)\ + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \varepsilon \gamma^t) \biggr].
+\]
 %&\leq \gamma\sum_{t=0}^{T-2} \varepsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
@@
 \end{clm}
-By Claim~\ref{clm:closeQs},
+\noindent By Claim~\ref{clm:closeQs},
 \begin{align}
@@
 For $t > 0$, the value of this policy for $s_G \in \mathcal{S}_G$ in the ground \ac{MDP} is:
-\begin{multline*}
-V_G^{\pi_{A,t}}(s_G) = \\
-R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
-\end{multline*}
+\[
+V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) +\ \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
+\]
 
@@
 
-\textit{Base case: $t=0$}
+\noindent \textit{Base case: $t=0$} \\
 
-By definition, when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case.
+By definition, when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case. \\
 
-\textit{Inductive case: $t > 0$}
+\noindent \textit{Inductive case: $t > 0$} \\
 
@@
 By definition,
-\begin{multline*}
-V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
-\end{multline*}
+\[
+V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}').
+\]
 Applying our inductive hypothesis yields:
-\begin{multline*}
-V_G^{\pi_{A,t}}(s_G) \geq R_G(s_G, \pi_{A,t}(s_G))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, \pi_{A,t}(s_G), {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} \right).
-\end{multline*}
+\[
+V_G^{\pi_{A,t}}(s_G) \geq R_G(s_G, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, \pi_{A,t}(s_G), {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\varepsilon}{1-\gamma} \right).
+\]
 Therefore,
@@
 \epM(s_1) = \epM(s_2) \rightarrow \\
-\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \varepsilon\; \text{~AND}\ \\
+\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \varepsilon\; \text{~AND}\ \
 \forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \varepsilon.
@@
 
-{\bf Proof of Lemma~\ref{lma:model}:}
+\noindent {\bf Proof of Lemma~\ref{lma:model}:} \\
 
@@
 \end{equation*}
-where $s_A \in \mcS_A$ and $s_1, s_2 \in G(s_A)$. Since difference of rewards is bounded by $\varepsilon$:
+where $s_A \in \mcS_A$ and $s_1, s_2 \in G(s_A)$. First, we expand:
 % Removed for space
-%\begin{multline*}
-%B=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \\
-%\biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
-%\end{multline*}
-\begin{multline*}
-B\leq \varepsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}')\ -\\ 
-T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr].
-\end{multline*}
+\begin{equation}
+B=\max_{s_A, s_1, s_2, a}      \biggl|\mcR_G(s_1, a) - \mcR_G(s_2, a)\ + \gamma \sum_{{s_G}' \in \mcS_G} \biggl[(\mcT_G(s_1,a,{s_G}') -\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')\biggr]\biggr|
+\end{equation}
+Since difference of rewards is bounded by $\varepsilon$:
+\begin{equation}
+B\leq \varepsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \biggl[(T_G(s_1, a, {s_G}')\ - T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \biggr].
+\end{equation}
 By similarity of transitions under $\epM$:
@@
 \end{align*}
-Since \textsc{QMax} $= \frac{\textsc{RMax}}{1-\gamma}$, and we defined $\textsc{RMax} = 1$:
+Recall that \textsc{QMax} $= \frac{\textsc{RMax}}{1-\gamma}$, and we defined $\textsc{RMax} = 1$:
 \begin{equation*}
@@
 We let $\epB$ define a type of abstractions that, for fixed $\varepsilon$, satisfies:
-\begin{multline}
-\epB(s_1) = \epB(s_2) \rightarrow \\
-\forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \varepsilon.
+\begin{equation}
+\epB(s_1) = \epB(s_2) \rightarrow \forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \varepsilon.
 \label{eq:phi_bolt}
-\end{multline}
+\end{equation}
 \edefn
 
-We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\varepsilon$:
+We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k_{\text{bolt}}  \in \mathbb{R}$, of $\varepsilon$:
 \begin{equation}
-\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k\times\varepsilon.
+\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k_{\text{bolt}} \times\varepsilon.
 \label{eq:bolt_denom}
@@
 \begin{equation}
-\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\varepsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k\right)}{(1-\gamma)^2}.
+\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\varepsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + \varepsilon k_{\text{bolt}}  + k_{\text{bolt}} \right)}{(1-\gamma)^2}.
 \end{equation}
@@
 \end{equation}
-We let $\delta_1$ denote the error in approximating $e^{Q_G(s_1,a)}$ and $\delta_2$ denote the error in approximating $e^{Q_G(s_2,a)}$.
+We let $\delta_1$ denote the error in approximating $e^{Q_G(s_1,a)}$ and $\delta_2$ denote the error in approximating $e^{Q_G(s_2,a)}$. \\
 
-{\bf Proof Sketch of Lemma~\ref{lma:bolt_lemma}:}
+\noindent {\bf Proof of Lemma~\ref{lma:bolt_lemma}:} \\
 
@@
 \begin{align}
-\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon \label{eq:bolt_with_approx}
+\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \underbrace{\pm k\varepsilon}_{\circled{a}}}\right| \leq \varepsilon \label{eq:bolt_with_approx}
 \end{align}
-Either $\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon$ is  $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
+Either term \circled{a} is positive or negative. First suppose the former. It follows by algebra that:
+\begin{equation}
+-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} + \varepsilon k_{\text{bolt}} } \leq \varepsilon
+\end{equation}
+Moving terms:
+\begin{multline}
+-\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
+\varepsilon k_{\text{bolt}} \left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
+\varepsilon \left(\varepsilon k_{\text{bolt}}  + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
+\label{eq:a_p_case}
+\end{multline}
+When \circled{a} is the negative case, it follows that:
+\begin{equation}
+-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} - \varepsilon k_{\text{bolt}} } \leq \varepsilon
+\end{equation}
 
-First suppose the former. It follows by algebra that:
+By similar algebra that yielded Equation~\ref{eq:a_p_case}:
+\begin{multline}
+-\varepsilon \left(-\varepsilon k_{\text{bolt}}  + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
+-k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
+\varepsilon \left(\varepsilon k_{\text{bolt}}  + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
+\label{eq:a_m_case}
+\end{multline}
+
+Combining Equation~\ref{eq:a_p_case} and Equation~\ref{eq:a_m_case} results in:
 \begin{equation}
--\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon} \leq \varepsilon
-\end{equation}
-%By algebra, we see that:
-\begin{multline*}
--\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
-k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
-\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
-\end{multline*}
-
-%In the minimal case, it follows that:
-%\begin{equation}
-%-\varepsilon \leq \frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon} \leq \varepsilon
-%\end{equation}
-
-%By similar algebra to the maximal case:
-%\begin{multline*}
-%-\varepsilon \left(-k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2 \leq \\
-%-k\varepsilon\left(\frac{1+Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}}\right) + Q_G(s_1,a) - Q_G(s_2,a) \leq \\
-%\varepsilon \left(k\varepsilon + \sum_j e^{Q_G(s_1,a_j)}\right) - \delta_1 + \delta_2
-%\end{multline*}
-
-A similar equation follows if we suppose the latter and combining these equations gives us:
-\begin{equation}
-\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right).
+\left|Q_G(s_1,a) - Q_G(s_2,a)\right| \leq \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + \varepsilon k_{\text{bolt}}  + k_{\text{bolt}}  \right).
 \label{eq:bolt_qs}
 \end{equation}
-Consequently, we can consider $\epB$ as a of the $\ep_{Q^*,B}$ type, where $B = \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + k\varepsilon + k \right)$.
+Consequently, we can consider $\epB$ as a special case of the $\ep_{Q^*,B}$ type, where $B = \varepsilon \left(\frac{|\mathcal{A}|}{1-\gamma} + \varepsilon k_{\text{bolt}}  + k_{\text{bolt}}  \right)$.
 Lemma~\ref{lma:bolt_lemma} then follows from Lemma~\ref{lma:Q*}.
@@
 We let $\epMu$ define a type of abstraction that, for fixed $\varepsilon$, satisfies
-\begin{multline}
-\epMu(s_1) = \epMu(s_2) \rightarrow \\
-\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \varepsilon.
-\end{multline}
+\begin{equation}
+\epMu(s_1) = \epMu(s_2) \rightarrow \forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \varepsilon.
+\end{equation}
 \edefn
 
-We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k \in \mathbb{R}$, of $\varepsilon$:
+We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k_{\text{mult}} \in \mathbb{R}$, of $\varepsilon$:
 \begin{equation}
-\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k \times \varepsilon.
+\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k_{\text{mult}} \times \varepsilon.
 \end{equation}
-\begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k \in \mathbb{R}$:
+\begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k_{\text{mult}} \in \mathbb{R}$:
 \begin{equation}
-\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\varepsilon|\mathcal{A}|}{1-\gamma} + k \varepsilon^2 + k}{(1-\gamma)^2}.
+\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\varepsilon|\mathcal{A}|}{1-\gamma} + \varepsilon^2 k_{\text{mult}} + k_{\text{mult}}}{(1-\gamma)^2}.
 \end{equation}
@@
 \vspace{-7mm}%vspace for more space
-{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without $e^x \approx 1+x$.
-\qed
+\noindent {\bf Proof of Lemma~\ref{lma:mult_lemma}} \\
+
+\noindent The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without the approximation $e^x \approx 1+x$. \qed
 
 % Subsection: Other Abstractions
-%\subsection{Other Abstractions}
+\subsection{Other Abstractions}
 %
@@
 %
-%Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
+
+We now consider state aggregation functions that group states solely on reward similarity. That is, $f = \mc{R}$:
+\bdefn{$\phi_{\mc{R},\eps}$}
+The approximate Reward function abstraction family has the same form as Equation~\ref{eq:phi_f}:
+\vspace{-1mm}%vspace for more space
+\begin{equation}
+\ep_{\mcR,\varepsilon}(s_1) = \ep_{\mcR,\varepsilon}(s_2) \rightarrow \forall_a \left|\mcR(s_1, a) - \mcR(s_2, a)\right| \leq \varepsilon.
+\end{equation}
+\edefn
+
+\noindent {\bf Remark}: {\it Without other assumptions, any abstraction function of the approximate Reward family induces MDP's whose optimal policies can be arbitrarily low value in the true MDP:
+\begin{equation}
+\forall_{s \in \mcS_G} V_G^{\pi_G^*}(s) \leq V_G^{\pi_{GA}} + \frac{\textsc{RMax}}{1-\gamma}
+\end{equation}}
+
+The above Remark is proven by the following simple counterexample MDP with adversarial transitions that ensure the abstract MDP's optimal policy fails:
+
+\dnote{Counterexample}
+
+%Additionally, we do {\it not} give provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results.
 Furthermore, an MDP for which this is true is an awfully weird MDP...
